### 2016-12-21 docs/IEEE/paper.tex
Paper kick start.

\documentclass[pageno]{jpaper}

\newcommand{\pactedition}{26th}
\newcommand{\pactyear}{17}
\newcommand{\pactcompyear}{20\pactyear}

%replace XXX with the submission number you are given from the PACT submission site.
\newcommand{\pactsubmissionnumber}{XXX}

\usepackage[normalem]{ulem}

\begin{document}

\title{Task Mining in Irregular Programs.}

\date{}
\maketitle

\thispagestyle{empty}

\begin{abstract}
We need to write our abstract here.
\end{abstract}

\section{Introduction}
\label{sec:intro}

\section{Overview}
\label{sec:ovf}

\section{Solution}
\label{sec:sol}

\section{Evaluation}
\label{sec:eval}

\section{Related Work}
\label{sec:rw}

\section{Conclusion}
\label{sec:conc}

\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
\bibliographystyle{IEEEtranS}
\bibliography{references}

\end{document}

### 2017-01-12 docs/IEEE/paper.tex
Contributions.

@@
 
+The key contribution of this paper is a technique to run programs in parallel.
+This technique consists of a data-flow like hardware,
+a runtime environment that detects dependences between data, plus a
+static analysis that finds potentially dependent code.
+Instructions are scheduled to run in parallel if they do not contain data
+dependences, which are detected on the fly by the runtime environment.
+However, not every pair of instructions need to be checked -- only those pairs
+that a static analysis points as potentially interdependent.
+The final product of this combination of hardware, static analysis, runtime checks
+and code generator is a high-performant framework that lets us run algorithms that
+are traditionally difficult to parallelize.
+
 \section{Overview}

### 2017-01-26 docs/IEEE/paper.tex
Paper

--- 2016-12-21 docs/IEEE/paper.tex
@@
 
+The key contribution of this paper is a fully automatic technique to find parallelism in programs, and to annotate them so to make this parallelism explicit.
+This technique consists in the combination of static and a dynamic analyses that increase the volume of tasks that can run in parallel.
+The static analysis finds independent code, which can be safely executed in parallel.
+However, due to its conservative nature, the static analysis misses potential parallelization opportunities.
+These tasks, which we cannot show to be independent due, for instance, to poor aliasing information, are solved at runtime by the data-flow engine.
+The final product of this combination is a high-performant framework that
+lets us run algorithms that are traditionally difficult to parallelize.
+
 \section{Overview}

### 2017-02-09 docs/IEEE/paper.tex
Wrote part of the introduction. 1st draft. Added some stuff to RW.txt

@@
 
+% CONTEXT
+Applications are usually written sequentially, regardless of the availability of a parallel architecture.
+Sequential code is often very irregular, and it is difficult for the compiler to be precise about whether a piece of code is independent or not.
+
+%- Applications are usually written sequentially regardless of the availability of a parallel architecture
+%- Hence sequential code is often irregular
+%- However, sometimes many paralellism opportunities are missed during a sequential execution
+
+% PROBLEM
+Extensive work has been done to decide whether loops are irregular or parallel. However, due to the conservatively trait of the static analyses, very often a
+loop or a code fragment is marked as irregular and dependent when in reality it might run in parallel most of the time.
+Finding this parallelism opportunities in irregular sequential code is hard because the programmer has to bear many aspects of it such as dependences between array-like structures.
+The OpenMP tasking model allows the programmer to point out regions in the sequential code that can be parallelized, and although some work has been done to generate OpenMP annotations automatically, the burden of finding code regions to be annotated still lies upon the programmer.
+
+% SOLUTION
+Our work focuses on finding irregular parallelism and automatic generating compiler directives to make this parallelism explicit.
+We present a fully automatic technique based on parallelism speculation that finds parallelism in programs and correctly annotates them so to make this parallelism explicit.
+It is a speculative technique that consists in the combination of static and dynamic analyses that increase the volume of tasks that can run in parallel.
+The static analysis finds irregular loops (i.e., loops with loop-carried dependences) and then speculates whether these loops can be safely executed in parallel. These loops
+are annotated with compiler directives, to point out the possibility of task-parallelization within that sequence of code. Then a runtime able to compile these directives shall run them
+and create the tasks for the annotated code. If the code is independent, the task-parallelized code will yield a great increase in performance. 
+However, if the code is indeed dependent and cannot be executed in parallel, the runtime will solve the dependences and execute the code sequentially. 
+This ensures correctness and makes the technique safe.
+
+% TESTS AND RESULTS
+We have implemented this technique in the LLVM compiler infrastructure.
+We tested our technique on three large benchmarks (CASTOR, LG Graphical Application, ???) and compared it to the manually annotated version.
+We show that XX\% of the manually annotated regions are found by our technique.
+Our technique also finds XX\% more possible task regions than what is manually annotated.
+Regarding performance, the automatically annotated code can be up to X times faster than the manually annotated one.
+
+%Fernando's first draft
+//DRAFT
 The key contribution of this paper is a fully automatic technique to find parallelism in programs, and to annotate them so to make this parallelism explicit.

### 2017-02-11 docs/IEEE/paper.tex
Improved introduction

--- 2017-01-26 docs/IEEE/paper.tex
@@
 
-The key contribution of this paper is a fully automatic technique to find parallelism in programs, and to annotate them so to make this parallelism explicit.
-This technique consists in the combination of static and a dynamic analyses that increase the volume of tasks that can run in parallel.
-The static analysis finds independent code, which can be safely executed in parallel.
-However, due to its conservative nature, the static analysis misses potential parallelization opportunities.
-These tasks, which we cannot show to be independent due, for instance, to poor aliasing information, are solved at runtime by the data-flow engine.
+% CONTEXT
+It is undeniable that parallel computing is nowadays the most pursued alternative by the developers 
+when striving for more application performance \cite{hwu2014ahead}. Two main reasons stand behind 
+the actual urge for parallel programming. First, programmers often code in simple parallel patterns 
+\cite{pinto2015large}, which evidences their awareness and will for parallelism. Second, the ever 
+increasing industry of multi-cores and many-cores architectures propitiates the development of software 
+with such behaviour \cite{haugen2016performance, vandierendonck2013analysis}. And although extensive 
+work has been done to scavenge parallelism in regular applications \cite{kulkarni2009much}, finding good 
+parallel opportunities in irregular code remains a grueling task.
+
+% PROBLEM
+Finding parallelism in sequentially-written code is hard because the programmer has to bear many aspects 
+such as dependences between arrays, synchronization, scalability and race conditions.
+Besides, even if we rely on static analyses to infer parallel regions, the results are imprecise 
+\cite{kulkarni2007optimistic}. Due to the conservative trait of the static analyses, a
+loop is frequently marked as iteration-dependent when, in reality, it might run in parallel most of the time. 
+Some dependences pointed by the compiler might never occur during runtime. 
+The OpenMP task scheduling model allows the programmer to point out regions in the sequential code that 
+can be parallelized \cite{openmp2009}, which provides an easy way of parallelizing without reimplementation. 
+Work has been carried out to generate OpenMP annotations automatically given a set of instructions that define 
+a region \cite{gleison2016, pingali2011tao, wanggenerating}. Yet, the burden of finding code regions to be 
+annotated with task directives still lies upon the programmer.
+
+% SOLUTION
+%Our work focuses on finding irregular code  and automatic generating compiler directives to make the parallelism explicit.
+We present a fully automatic technique that finds parallelism in irregular programs and correctly annotates 
+them so to make this pattern explicit.
+It is a speculative technique that consists in the combination of static and dynamic analyses that increase 
+the volume of tasks that can run in parallel.
+The static analysis finds irregular loops (i.e., loops with loop-carried dependences) and then speculates 
+whether these loops can be safely executed in parallel or not. These loops
+are annotated with compiler directives, to point out the possibility of task-parallelization within that sequence of code. 
+Then a runtime able to compile these directives runs the tasks for the annotated code. 
+During execution, the dependences are resolved by the runtime and the code is executed in parallel.
+
+The key insight of the tool is that it does not rely on the programmer to find possible parallel sites. 
+It does so automatically, and the runtime is solely responsible for unraveling the dependences between tasks. 
 The final product of this combination is a high-performant framework that
 lets us run algorithms that are traditionally difficult to parallelize.
+
+% TESTS AND RESULTS
+We have implemented this technique in the LLVM compiler infrastructure.
+We tested our technique on three large benchmarks (CASTOR, LG Graphical Application, ???) and compared it to the manually annotated version.
+We show that XX\% of the manually annotated regions are found by our technique.
+Our technique also finds XX\% more possible task regions than what is manually annotated.
+Regarding performance, the automatically annotated code can be up to X times faster than the manually annotated one.
+
+%Fernando's first draft
+%//DRAFT
+%The key contribution of this paper is a fully automatic technique to find parallelism in programs, and to annotate them so to make this parallelism explicit.
+%This technique consists in the combination of static and a dynamic analyses that increase the volume of tasks that can run in parallel.
+%The static analysis finds independent code, which can be safely executed in parallel.
+%However, due to its conservative nature, the static analysis misses potential parallelization opportunities.
+%These tasks, which we cannot show to be independent due, for instance, to poor aliasing information, are solved at runtime by the data-flow engine.
 

### 2017-02-14 docs/IEEE/paper.tex
Added guido's modifications. I accidentally deleted his commit earlier

@@
 
+% To turn comments OFF simply comment out the \Commentstrue line
+\newif\ifComments\Commentstrue
+
+\ifComments
+\newcommand{\marcio}[1]{\noindent\textcolor{violet}{Marcio: {#1}}}
+\newcommand{\guido}[1]{\noindent\textcolor{magenta}{Guido: {#1}}}
+\newcommand{\fernando}[1]{\noindent\textcolor{brown}{Fernando: {#1}}}
+\newcommand{\cesar}[1]{\noindent\textcolor{magenta}{Cesar: {#1}}}
+\newcommand{\pedro}[1]{\noindent\textcolor{brown}{Pedro: {#1}}}
+\newcommand{\rmv}[1]{\noindent\textcolor{gray}{Removed: {#1}}}
+\newcommand{\new}[1]{\noindent\textcolor{blue}{ {#1}}}
+\newcommand{\ed}[1]{\noindent\textcolor{red}{ {#1}}}
+\else
+\newcommand{\marcio}[1]{}
+\newcommand{\guido}[1]{}
+\newcommand{\fernando}[1]{}
+\newcommand{\cesar}[1]{}
+\newcommand{\pedro}[1]{}
+\newcommand{\rmv}[1]{}
+\newcommand{\new}[1]{#1}
+\newcommand{\ed}[1]{}
+\fi
+
 \begin{document}
 
-\title{Task Mining in Irregular Programs.}
+\guido{Not sure if we should dive into a discussion of what is a regular or an irregular program; to be even more precise we are actually mining task parallelism (for this moment) only within loops; hence I propose this new title}
+\title{\rmv{Task Mining in Irregular Programs.}\new{Automatic Mining of Task Parallelism in Loops}}
 
@@
 % CONTEXT
-It is undeniable that parallel computing is nowadays the most pursued alternative by the developers 
-when striving for more application performance \cite{hwu2014ahead}. Two main reasons stand behind 
-the actual urge for parallel programming. First, programmers often code in simple parallel patterns 
-\cite{pinto2015large}, which evidences their awareness and will for parallelism. Second, the ever 
-increasing industry of multi-cores and many-cores architectures propitiates the development of software 
-with such behaviour \cite{haugen2016performance, vandierendonck2013analysis}. And although extensive 
-work has been done to scavenge parallelism in regular applications \cite{kulkarni2009much}, finding good 
-parallel opportunities in irregular code remains a grueling task.
+It is undeniable that parallel computing is nowadays the most pursued alternative by the developers  when striving for more application performance \cite{hwu2014ahead}.
+Two main reasons stand behind  the actual urge for parallel programming.
+\ed{First, the ever  increasing industry of multi-cores and many-cores architectures propitiates the development of software  with such behaviour \cite{haugen2016performance, vandierendonck2013analysis}.} \guido{Fine, but it seems to me a very convoluted way to say that this was due to the emergence of multicore/manycore  architectures as the alternative to maintain transistor power-density under control.} \rem{Second, programmers often code in simple parallel patterns  \cite{pinto2015large}, which evidences their awareness and will for parallelism}.
+\guido{Not sure if programming using patterns is an evidence that supports the urge for interest in parallel programming; on the contrary, it seems to me that it is more a consequence to tackle the complexity of the problem.}
+
+Although extensive  work has been done to scavenge parallelism in regular applications \cite{kulkarni2009much}, finding good  parallel opportunities in irregular code remains a grueling task.
+\guido{We need to re-phrase this if we want to use this statement to introduce the motivation to our work; a number of the examples that we are using do not have pointers, and thus could not be classified as irregular code....}
 
 % PROBLEM
-Finding parallelism in sequentially-written code is hard because the programmer has to bear many aspects 
-such as dependences between arrays, synchronization, scalability and race conditions.
-Besides, even if we rely on static analyses to infer parallel regions, the results are imprecise 
-\cite{kulkarni2007optimistic}. Due to the conservative trait of the static analyses, a
-loop is frequently marked as iteration-dependent when, in reality, it might run in parallel most of the time. 
-Some dependences pointed by the compiler might never occur during runtime. 
-The OpenMP task scheduling model allows the programmer to point out regions in the sequential code that 
-can be parallelized \cite{openmp2009}, which provides an easy way of parallelizing without reimplementation. 
-Work has been carried out to generate OpenMP annotations automatically given a set of instructions that define 
-a region \cite{gleison2016, pingali2011tao, wanggenerating}. Yet, the burden of finding code regions to be 
-annotated with task directives still lies upon the programmer.
+\ed{Programming parallel applications is a hard task, as programmers have to take care of many aspects of the job such as identify and keep variable dependences correct and assure synchronization and scalability of threads/processes while avoiding race conditions.} \ed{On the other hand, finding parallelism in \rem{sequentially-written} \guido{programs are typically "sequentially written"}  \ed{annotated sequential  code is not a simple task} as compiler static analyses is not precise enough to identify  parallel regions~\cite{kulkarni2007optimistic}.
+For example,} due  to the conservative trait of static analyses, loops are frequently marked as iteration-dependent when, in reality, \ed{their iterations might run in parallel most of the time.
+As a matter of fact,  many dependences pointed by the compiler might never occur during runtime, resulting in missing opportunities for parallelization.}
+
+\new{A way to approach this problem is to use a programming model that can capture and enforce dependences between iterations at runtime when they occur.
+In such model  those iterations that do not have {\it loop-carried} dependencies are free to run in parallel, while iterations that dynamically create loop-carried dependences are serialized and dispatched in dependence order by  a system runtime.
+In recent years, task-based execution models  have proven itself to be a scalable and quite flexible approach to extract regular and irregular parallelism from sequential code ~\cite{starss,bddt,cilk,sequoia,dandelion,legion,ooojava,dague}.
+In this model the programmer uses a {\it task} directive to mark  code regions in the program that are potential tasks and lists their corresponding dependecies.
+OpenMP task scheduling~\cite{openmp2009}  is an example of such model.
+Although OpenMP task simplifies the mechanics of dispatching and running tasks, the burden of finding code regions to be  annotated with task directives still lies upon the programmer.}
+
+Work has been carried out to generate OpenMP annotations automatically given a set of instructions that define  a region \cite{gleison2016, pingali2011tao, wanggenerating}.
+\guido{Need to provide a short paragraph here to give an idea why these works do not solve the problem of automatically extracting parallelism from loops with loop carried-depedenciss}.
 
 % SOLUTION
+%Guido: This is an ambitious objective; ou work is more modest.
 %Our work focuses on finding irregular code  and automatic generating compiler directives to make the parallelism explicit.
-We present a fully automatic technique that finds parallelism in irregular programs and correctly annotates 
-them so to make this pattern explicit.
-It is a speculative technique that consists in the combination of static and dynamic analyses that increase 
-the volume of tasks that can run in parallel.
+\ed{This paper presents an automatic technique that extracts task parallelism from loops which cannot be proved by static analysis to be loop-carried independent. } 
+\rmv{It is a speculative technique that consists in the combination of static and dynamic analyses that increase 
+the volume of tasks that can run in parallel.} \guido{Do not mention speculation here as it usually is applied to TLS or TM}
+
+\guido{I HAVE STOPPED HERE; WILL CONTINUE LATER}
+
 The static analysis finds irregular loops (i.e., loops with loop-carried dependences) and then speculates 

### 2017-02-22 docs/IEEE/paper.tex
Added Guido's modifications to the paper and the example of section 2

@@
 \guido{Not sure if we should dive into a discussion of what is a regular or an irregular program; to be even more precise we are actually mining task parallelism (for this moment) only within loops; hence I propose this new title}
-\title{\rmv{Task Mining in Irregular Programs.}\new{Automatic Mining of Task Parallelism in Loops}}
+\pedro{I think we should say "Automatic Mining of Task Parallelism in Programs" because we might mine task parallelism in recursive functions as well.}
+\title{\rmv{Task Mining in Irregular Programs.}\new{Automatic Mining of Task Parallelism in Programs}}
 
@@
 % CONTEXT
-It is undeniable that parallel computing is nowadays the most pursued alternative by the developers  when striving for more application performance \cite{hwu2014ahead}.
+It is undeniable that parallel computing is nowadays the most pursued alternative by developers  when striving for more application performance \cite{hwu2014ahead}.
 Two main reasons stand behind  the actual urge for parallel programming.
-\ed{First, the ever  increasing industry of multi-cores and many-cores architectures propitiates the development of software  with such behaviour \cite{haugen2016performance, vandierendonck2013analysis}.} \guido{Fine, but it seems to me a very convoluted way to say that this was due to the emergence of multicore/manycore  architectures as the alternative to maintain transistor power-density under control.} \rem{Second, programmers often code in simple parallel patterns  \cite{pinto2015large}, which evidences their awareness and will for parallelism}.
+\ed{First, the ever  increasing industry of multi-cores and many-cores architectures propitiates the development of software  with such behaviour \cite{haugen2016performance, vandierendonck2013analysis}.} \guido{Fine, but it seems to me a very convoluted way to say that this was due to the emergence of multicore/manycore  architectures as the alternative to maintain transistor power-density under control.} \ed{Second, programmers often code in simple parallel patterns  \cite{pinto2015large}, which evidences their awareness and will for parallelism}.
 \guido{Not sure if programming using patterns is an evidence that supports the urge for interest in parallel programming; on the contrary, it seems to me that it is more a consequence to tackle the complexity of the problem.}
@@
 % PROBLEM
-\ed{Programming parallel applications is a hard task, as programmers have to take care of many aspects of the job such as identify and keep variable dependences correct and assure synchronization and scalability of threads/processes while avoiding race conditions.} \ed{On the other hand, finding parallelism in \rem{sequentially-written} \guido{programs are typically "sequentially written"}  \ed{annotated sequential  code is not a simple task} as compiler static analyses is not precise enough to identify  parallel regions~\cite{kulkarni2007optimistic}.
-For example,} due  to the conservative trait of static analyses, loops are frequently marked as iteration-dependent when, in reality, \ed{their iterations might run in parallel most of the time.
-As a matter of fact,  many dependences pointed by the compiler might never occur during runtime, resulting in missing opportunities for parallelization.}
+Programming parallel applications is a hard task, as programmers ought to take care of many aspects of the job such as identifying and keeping variable dependences correct and assuring synchronization and scalability of threads/processes whilst avoiding race conditions.
+However, finding parallelism in programs that were not coded in a parallel paradigm \rmv{annotated sequential  code} is not a simple task, as compiler static analyses are not precise enough to identify  parallel regions \cite{kulkarni2007optimistic}.
+For example, due  to the conservative trait of static analyses, loops are frequently marked as iteration-dependent when, in reality, their iterations might run in parallel most of the time.
+As a matter of fact,  many dependences pointed by the compiler might never occur during runtime, resulting in several missing opportunities for parallelization.
 
-\new{A way to approach this problem is to use a programming model that can capture and enforce dependences between iterations at runtime when they occur.
-In such model  those iterations that do not have {\it loop-carried} dependencies are free to run in parallel, while iterations that dynamically create loop-carried dependences are serialized and dispatched in dependence order by  a system runtime.
+A way to approach this problem is to use a programming model that can capture and enforce dependences between iterations at runtime whenever they occur.
+In such model, those iterations that do not have {\it loop-carried} dependencies are free to run in parallel, while iterations that dynamically create loop-carried dependences are serialized and dispatched in dependence order by  a system runtime.
 In recent years, task-based execution models  have proven itself to be a scalable and quite flexible approach to extract regular and irregular parallelism from sequential code ~\cite{starss,bddt,cilk,sequoia,dandelion,legion,ooojava,dague}.
-In this model the programmer uses a {\it task} directive to mark  code regions in the program that are potential tasks and lists their corresponding dependecies.
-OpenMP task scheduling~\cite{openmp2009}  is an example of such model.
-Although OpenMP task simplifies the mechanics of dispatching and running tasks, the burden of finding code regions to be  annotated with task directives still lies upon the programmer.}
+In this model, the programmer uses a {\it task} directive to mark  code regions in the program that are potential tasks and lists their corresponding dependences.
+The OpenMP task scheduling~\cite{openmp2009}  is an example of such model.
+Although OpenMP task simplifies the mechanics of dispatching and running tasks, the burden of finding code regions to be annotated with task directives still lies upon the programmer.
 
@@
 \ed{This paper presents an automatic technique that extracts task parallelism from loops which cannot be proved by static analysis to be loop-carried independent. }
-\rmv{It is a speculative technique that consists in the combination of static and dynamic analyses that increase 
-the volume of tasks that can run in parallel.} \guido{Do not mention speculation here as it usually is applied to TLS or TM}
 
@@
 
+%EXAMPLE - BFS
+
 \section{Solution}

### 2017-02-22 tests/overview/bfs.cpp

@@ -1,27 +1,63 @@
 #include <iostream>
 #include <omp.h>
-#define N 100
+#include <math.h>
+#define N 5
 
-void bfs(int* G, int* node, int* neigh);
+void bfs(int** G, int* node, int* neigh);
+
+void fillgraph(int** G);
+
+void printGraph(int** G);
 
 int main()
 {
-	int* G = (int*)malloc(N*N*sizeof(int));
+	int **G;
+	G = (int**)malloc(N*sizeof(int*));
+	for (int i=0; i<N; i++)
+		G[i] = (int*)malloc(N*sizeof(int));
 	int neigh[N];
+	int visited[N];
 
-	bfs(G, &G[0], neigh);
+	fillgraph(G);
+	printGraph(G);
+
+	// bfs(G, G[0], neigh);
+
+	for (int i = 0; i < N; i++)
+		std::cout << "Node " << i << " has " << neigh[i] << " neighbors" << std::endl;
 
 	return 0;
 }
 
-void bfs(int* G, int* node, int* neigh)
+void bfs(int** G, int* node,int* neigh)
 {
 	for (int i=0; i<N; i++)
 		if (node[i])
 		{
 			neigh[i]++;
-			bfs(G, &G[i*N], neigh);			
+			bfs(G, G[i], neigh);			
 		}
+}
+
+void fillgraph(int** G)
+{
+	for (int i = 0; i < N; i++)
+		for (int j = 0; j < N; j++)
+		{
+			G[i][j] = rand()%N;
+		}
+}
+
+void printGraph(int** G)
+{
+	for (int i = 0; i < N; i++)
+	{
+		for (int j = 0; j < N; j++)
+		{
+			std::cout << G[i][j] << " ";
+		}
+		std::cout << std::endl;
+	}
 }
 
 

### 2017-03-09 docs/IEEE/paper.tex
Fixed bug in TaskMiner. Added new toy benchmarks (ruben's) inside tests folder. Added evaluation to the paper

@@
 
+We aimed to show that our tool exceeded in three main aspects that surround parallel programming. Thus our work evaluation stands on these 3 pillars:
+
+\begin{itemize}
+
+\item Practicality
+\item Applicability
+\item Performance
+
+\end{itemize}
+
+\textbf{\textit{Practicality}}.
+Programming in a parallel pattern is deemed difficult by programmers mainly because of the complexity of its data structures and algorithms.
+We show that our tool is simple and practical, for it does not involve changing the code and data structures in order to fit in a parallel pattern.
+The code is simply annotated by compiler directives.
+
+\textbf{\textit{Applicability}}.
+
+\textbf{\textit{Performance}}.
+When it comes to parallel computing, it is undeniable that the main achievable goal should be performance.
+There's no reason why programmers would opt for parallelism other than the desire for faster programs.
+Therefore, we ought to show that the programs annotated with TaskMiner are faster than their serial counterparts.
+
 \section{Related Work}

### 2017-03-09 TaskMiner.cpp

@@ -1,6 +1,7 @@
 //LLVM IMPORTS
 #include "llvm/Analysis/LoopInfo.h" 
 #include "llvm/ADT/Statistic.h"
+#include "llvm/IR/Attributes.h"
 
 //MY IMPORTS
 #include "TaskMiner.h"
@@ -28,15 +29,18 @@ TaskMiner::~TaskMiner()
 void TaskMiner::getAnalysisUsage(AnalysisUsage &AU) const
 {
 	AU.addRequired<LoopInfoWrapperPass>();
-	AU.addRequired<DepAnalysis>();
+	// AU.addRequired<DepAnalysis>();
 	AU.setPreservesAll();
 }
 
 bool TaskMiner::runOnFunction(Function &F)
 {
+	if (F.isDiscardableIfUnused())
+		return false;
+
 	LIWP = &(getAnalysis<LoopInfoWrapperPass>());
 	LI = &(LIWP->getLoopInfo());
-	DA = &(getAnalysis<DepAnalysis>());
+	// DA = &(getAnalysis<DepAnalysis>());
 
 	getLoopsInfo(F);
 	mineFunctionCallTasks(F);
@@ -44,20 +48,36 @@ bool TaskMiner::runOnFunction(Function &F)
 	//Resolve each task's ins and outs sets
 	resolveInsAndOutsSets();
 
+	return false;
+}
+
+bool TaskMiner::doFinalization(Module &M)
+{
+	getStats();
+
 	#ifdef DEBUG_PRINT
 		int i = 0;
 		for (auto &task : tasks)
 		{
 			errs() << "Task #" << i;
-			// task->print(errs());
 			task->print(errs());
 			i++;
 		}
+		printLoops();
 	#endif
 
-	getStats();
-
 	return false;
+}
+
+
+void TaskMiner::printLoops()
+{
+	for (auto &loop : loops)
+	{
+		errs() << loop.first << ":\n";
+		loop.second.print();
+		errs() << "\n";
+	}
 }
 
 void TaskMiner::LoopData::print()
@@ -111,7 +131,8 @@ void TaskMiner::getLoopsInfo(Function &F)
 				loops[loop].innerBBs.push_back(BB);
 			}
 		}
-	}
+	}		
+	//colaesce loops by induction variable
 }
 
 void TaskMiner::mineFunctionCallTasks(Function &F)
@@ -124,8 +145,10 @@ void TaskMiner::mineFunctionCallTasks(Function &F)
 	//we don't have any heuristics to decide whether it will be a code fragment
[…]

### 2017-03-09 TaskMiner.h

@@ -52,6 +52,7 @@ namespace llvm
 		~TaskMiner();
 		void getAnalysisUsage(AnalysisUsage &AU) const override;
 		bool runOnFunction(Function &func) override;
+		bool doFinalization(Module &M) override;
 		std::list<Task*> getTasks();
 
 		struct LoopData
@@ -69,10 +70,15 @@ namespace llvm
 		void getStats();
 		void getLoopsInfo(Function &F);
 		void mineFunctionCallTasks(Function &F);
+		void insertNewFunctionCallTask(Task &T);
+
 		std::map<Loop*, TaskMiner::LoopData> loops;
 		DepAnalysis* DA = 0;
 		LoopInfo* LI = 0;
 		LoopInfoWrapperPass* LIWP = 0;
+
+		//Debugging purposes only
+		void printLoops();
 	};
 
 	class Task
@@ -120,7 +126,7 @@ namespace llvm
 	public:
 		FunctionCallTask(Loop* parent, CallInst* CI) : Task(FCALL_TASK, parent), functionCall(CI) {};
 		~FunctionCallTask() {};
-		CallInst* getFunctionCall();
+		CallInst* getFunctionCall() const;
 		bool resolveInsAndOutsSets() override;
 		raw_ostream& print(raw_ostream& os) const override;
 

### 2017-03-09 tests/rubens/ldp/TODO/bfs/bfs-seq.cpp

@@ -1,0 +1,81 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "ldp/graph.hpp"
+# include "../../timing.h"
+
+
+// Traverses the matrix in a depth-first fashion (no-LDP)
+void bfs(struct Graph& graph, int root) {
+
+	if (graph.node[root].visited) return;
+	graph.node[root].visited = true;
+
+	for (int i = 0; i < graph.node[root].length; ++i) {
+
+		int child = graph.node[root].edge[i].node;
+		if (!graph.node[child].visited) dfs(graph, child);
+
+	}
+
+}
+
+void graph_dfs(struct Graph& graph, int root) {
+
+	for (int i = 0; i < graph.num_nodes; ++i) graph.node[i].visited = false;
+	dfs(graph, root);
+
+}
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *distance = new int[num_nodes * num_nodes];
+	struct Node *node = new struct Node[num_nodes];
+	struct Edge *edge = new struct Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	double elapsed(0);
+
+	// Traversing
+	struct Graph graph;
+	graph_build(graph, node, num_nodes, edge, num_edges, distance);
+	graph_dump(graph);
+
+	reset_and_start_timer();
+	for (int i(0); i < num_nodes; ++i) graph_dfs(graph, i);
+	elapsed += get_elapsed_mcycles();
+
+	graph_dump(graph);
+	print_runtime(elapsed);
+
+	delete[] node;
+	delete[] edge;
+	delete[] distance;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/TODO/bfs/objs/bfs_ispc_sse2.h

@@ -1,0 +1,78 @@
+//
+// objs/bfs_ispc_sse2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_BFS_ISPC_SSE2_H
+#define ISPC_OBJS_BFS_ISPC_SSE2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
+    extern void graph_dfs(struct Graph &graph, int32_t root);
[…]

### 2017-03-09 tests/rubens/ldp/TODO/floyd-warshall/floyd-warshall.cpp

@@ -1,0 +1,62 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "../../timing.h"
+# include "floyd-warshall_ispc.h"
+
+# define INF (1 << 29)
+
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *distance = new int[num_nodes * num_nodes];
+	struct ispc::Node *node = new struct ispc::Node[num_nodes];
+	struct ispc::Edge *edge = new struct ispc::Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	// Traversing
+	struct ispc::Graph graph;
+	ispc::graph_build(graph, node, num_nodes, edge, num_edges, distance);
+	ispc::graph_dump(graph);
+
+	reset_and_start_timer();
+	ispc::graph_floyd_warshall(graph);
+	double elapsed = get_elapsed_mcycles();
+
+	ispc::graph_dump(graph);
+
+	std::cout << std::fixed, std::cout.precision(3);
+	std::cout << "\n\n-- ldp::BellmanFord:\n    "
+		<< elapsed << " million cycles" << std::endl;
+
+	delete[] node;
+	delete[] edge;
+	delete[] distance;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/TODO/floyd-warshall/objs/floyd-warshall_ispc_avx.h

@@ -1,0 +1,77 @@
+//
+// objs/floyd-warshall_ispc_avx.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_FLOYD_WARSHALL_ISPC_AVX_H
+#define ISPC_OBJS_FLOYD_WARSHALL_ISPC_AVX_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
[…]

### 2017-03-09 tests/rubens/ldp/TODO/floyd-warshall/objs/floyd-warshall_ispc_avx2.h

@@ -1,0 +1,77 @@
+//
+// objs/floyd-warshall_ispc_avx2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_FLOYD_WARSHALL_ISPC_AVX2_H
+#define ISPC_OBJS_FLOYD_WARSHALL_ISPC_AVX2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
[…]

### 2017-03-09 tests/rubens/ldp/TODO/fpgrowth/objs/fpgrowth_ispc_avx2.h

@@ -1,0 +1,79 @@
+//
+// objs/fpgrowth_ispc_avx2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_FPGROWTH_ISPC_AVX2_H
+#define ISPC_OBJS_FPGROWTH_ISPC_AVX2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_bellman_ford(struct Graph &graph, int32_t root);
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
[…]

### 2017-03-09 tests/rubens/ldp/TODO/sort/sort-par.cpp

@@ -1,0 +1,101 @@
+/*
+  Copyright (c) 2013, Durham University
+  All rights reserved.
+
+  Redistribution and use in source and binary forms, with or without
+  modification, are permitted provided that the following conditions are
+  met:
+
+    * Redistributions of source code must retain the above copyright
+      notice, this list of conditions and the following disclaimer.
+
+    * Redistributions in binary form must reproduce the above copyright
+      notice, this list of conditions and the following disclaimer in the
+      documentation and/or other materials provided with the distribution.
+
+    * Neither the name of Durham University nor the names of its
+      contributors may be used to endorse or promote products derived from
+      this software without specific prior written permission.
+
+
+   THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+   IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+   TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+   PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER
+   OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+   EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
+   PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+   PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+   LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+   NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+   SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.  
+*/
+
+/* Author: Tomasz Koziara */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <algorithm>
+#include <iostream>
+#include <string>
+#include <sstream>
+#include <cassert>
+#include <iomanip>
+#include "../timing.h"
[…]

### 2017-03-09 tests/rubens/ldp/bellman-ford/bellman-ford-ldp.cpp

@@ -1,0 +1,60 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "../../timing.h"
+# include "ldp/common.hpp"
+# include "bellman-ford_ispc.h"
+
+# define INF (1 << 29)
+
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *distance = new int[num_nodes * num_nodes];
+	struct ispc::Node *node = new struct ispc::Node[num_nodes];
+	struct ispc::Edge *edge = new struct ispc::Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	// Traversing
+	struct ispc::Graph graph;
+	ispc::graph_build(graph, node, num_nodes, edge, num_edges, distance);
+	// ispc::graph_dump(graph);
+
+	reset_and_start_timer();
+	for (int i(0); i < num_nodes; ++i) ispc::graph_bellman_ford(graph, i);
+	double elapsed = get_elapsed_mcycles();
+
+	// ispc::graph_dump(graph);
+	print_runtime(elapsed);
+
+	delete[] node;
+	delete[] edge;
+	delete[] distance;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/bellman-ford/objs/bellman-ford_ispc_avx.h

@@ -1,0 +1,78 @@
+//
+// objs/bellman-ford_ispc_avx.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_BELLMAN_FORD_ISPC_AVX_H
+#define ISPC_OBJS_BELLMAN_FORD_ISPC_AVX_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_bellman_ford(struct Graph &graph, int32_t root);
+    extern void graph_bellman_ford_par(struct Graph &graph, int32_t root);
[…]

### 2017-03-09 tests/rubens/ldp/bellman-ford/objs/bellman-ford_ispc_avx2.h

@@ -1,0 +1,78 @@
+//
+// objs/bellman-ford_ispc_avx2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_BELLMAN_FORD_ISPC_AVX2_H
+#define ISPC_OBJS_BELLMAN_FORD_ISPC_AVX2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_bellman_ford(struct Graph &graph, int32_t root);
+    extern void graph_bellman_ford_par(struct Graph &graph, int32_t root);
[…]

### 2017-03-09 tests/rubens/ldp/bellman-ford/objs/bellman-ford_ispc_sse2.h

@@ -1,0 +1,78 @@
+//
+// objs/bellman-ford_ispc_sse2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_BELLMAN_FORD_ISPC_SSE2_H
+#define ISPC_OBJS_BELLMAN_FORD_ISPC_SSE2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_bellman_ford(struct Graph &graph, int32_t root);
+    extern void graph_bellman_ford_par(struct Graph &graph, int32_t root);
[…]

### 2017-03-09 tests/rubens/ldp/bookfilter/bookfilter-ldp.cpp

@@ -1,0 +1,83 @@
+# include <vector>
+# include <fstream>
+# include <iostream>
+# include <algorithm>
+
+# include "../../timing.h"
+# include "ldp/common.hpp"
+# include "bookfilter_ispc.h"
+
+# define MAX_LENGTH (1 << 13)
+
+
+int main (int argc, char *argv[]) {
+
+	double elapsed(0);
+
+	size_t num_lines;
+	std::cin >> num_lines, std::cin.ignore(256, '\n');
+
+	ispc::String *page = new ispc::String[num_lines];
+	ispc::String *output = new ispc::String[num_lines];
+	ispc::String *pattern = new ispc::String;
+
+	std::string input_pattern;
+	std::getline(std::cin, input_pattern);
+
+	pattern->length = input_pattern.size();
+	pattern->data = (int8_t *) input_pattern.data();
+
+	std::string line;
+	size_t count = 0;
+	while (std::getline(std::cin, line)) {
+
+		uint32_t len = line.length();
+
+		page[count].length = len;
+		page[count].data = new int8_t[len + 1];
+		std::copy_n((int8_t *) line.data(), len, page[count].data);
+
+		output[count].length = 0;
+		output[count].data = new int8_t[len + 1];
+
+		++count;
+
+	}
+
+	reset_and_start_timer();
+	ispc::bookfilter_ldp(page, count, *pattern, output);
+	elapsed += get_elapsed_mcycles();
+
+/*
+	std::cout << "SO FAR SO GOOD!" << std::endl;
+
+	for (int i = 0; i < count; ++i) {
+
+		std::cout << "[";
+		for (int j = 0; j < page[i].length; ++j) {
+			std::cout << (char) page[i].data[j];
+		}
+		std::cout << "] : [";
+		if (output[i].length == 0) std::cout << "--";
+		for (int j = 0; j < output[i].length; ++j) {
+			std::cout << (char) output[i].data[j];
+		}
+		std::cout << "]\n";
+
+		delete[] page[i].data;
+		delete[] output[i].data;
+
+		page[i].data = nullptr;
+		output[i].data = nullptr;
+
+	}
+
+	delete pattern;
+
+	delete[] page;
+	delete[] output;
+*/
+	print_runtime(elapsed);
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/bookfilter/bookfilter-seq.cpp

@@ -1,0 +1,104 @@
+# include <string>
+# include <vector>
+
+# include "../../timing.h"
+# include "ldp/common.hpp"
+
+# define MAX_LENGTH (1 << 13)
+
+
+// Precomputes the matching table to the given pattern
+void preKMP(const std::string& pattern, std::vector<int>& table) {
+
+	table.resize(0);
+	table.resize(pattern.size());
+
+	int pos(0);
+	table[pos] = 0;
+
+	// Computing table[i] for the entire pattern
+	int i(1), length(pattern.size());
+	while (i < length) {
+
+		if (pattern[i] == pattern[pos]) {
+			++pos, table[i] = pos, ++i;
+		} else if (pos != 0) {
+			pos = table[pos - 1];
+		} else table[i] = 0, ++i;
+
+	}
+
+}
+
+// Finds occurrences of pattern in the target text
+void KMP(const std::string& text, const std::string& pattern,
+	const std::vector<int>& table) {
+
+	int m(pattern.size()), n(text.size());
+
+	int i(0), j(0);
+	while (i < n) {
+
+		if (pattern[j] == text[i]) ++i, ++j;
+
+		if (j == m) {
+
+			std::cout << "match => " << (i - j) << "\n";
+			j = table[j - 1];
+
+		} else if (i < n and pattern[j] != text[i]) {
+
+			// Skipping characters from table[0 .. table[j - 1]],
+			// as they have already matched
+			if (j != 0) j = table[j-1];
+			else ++i;
+
+		}
+
+	}
+
+}
+
+
+int main(int argc, char *argv[]) {
+
+	/*
+	double elapsed(0);
+
+	// Input pattern
+	std::string pattern(MAX_LENGTH, '\0');
+	std::cin.getline(&pattern[0], MAX_LENGTH);
+	pattern.resize(std::cin.gcount() - 1);
+
+	std::vector<int> table;
+
+	reset_and_start_timer();
+	preKMP(pattern, table);
+	elapsed += get_elapsed_mcycles();
+
+	// Input data
+	std::string text(MAX_LENGTH, '\0');
+	std::cin.read(&text[0], MAX_LENGTH);
+
+	while (std::cin.gcount()) {
+
+		text.resize(std::cin.gcount());
+
+		// Looking for pattern in input string
+		reset_and_start_timer();
+		KMP(text, pattern, table);
+		elapsed += get_elapsed_mcycles();
+
[…]

### 2017-03-09 tests/rubens/ldp/bookfilter/objs/bookfilter_ispc.h

@@ -1,0 +1,72 @@
+//
+// objs/bookfilter_ispc.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_BOOKFILTER_ISPC_H
+#define ISPC_OBJS_BOOKFILTER_ISPC_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_String__
+#define __ISPC_STRUCT_String__
+struct String {
+    int32_t length;
+    int8_t * data;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void bookfilter_lch(const struct String * page, const int32_t num_pages, const struct String &pattern, struct String * output);
+    extern void bookfilter_ldp(const struct String * page, const int32_t num_pages, const struct String &pattern, struct String * output);
+    extern void bookfilter_par(const struct String * page, const int32_t num_pages, const struct String &pattern, struct String * output);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
[…]

### 2017-03-09 tests/rubens/ldp/cc-leader/cc-leader-ldp.cpp

@@ -1,0 +1,60 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "../../timing.h"
+# include "ldp/common.hpp"
+# include "cc-leader_ispc.h"
+
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *rank = new int[num_nodes];
+	struct ispc::Node *node = new struct ispc::Node[num_nodes];
+	struct ispc::Edge *edge = new struct ispc::Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	// Traversing
+	struct ispc::Graph graph;
+	ispc::graph_build(graph, node, num_nodes, edge, num_edges, NULL);
+	// ispc::graph_dump(graph);
+
+	reset_and_start_timer();
+	ispc::graph_cc_leader(rank, graph);
+	double elapsed = get_elapsed_mcycles();
+
+	// for (int i = 0; i < num_nodes; ++i) std::cout << rank[i] << " ";
+	// std::cout << std::endl;
+
+	print_runtime(elapsed);
+
+	delete[] node;
+	delete[] edge;
+	delete[] rank;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/cc-leader/cc-leader-par.cpp

@@ -1,0 +1,60 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "../../timing.h"
+# include "ldp/common.hpp"
+# include "cc-leader_ispc.h"
+
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *rank = new int[num_nodes];
+	struct ispc::Node *node = new struct ispc::Node[num_nodes];
+	struct ispc::Edge *edge = new struct ispc::Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	// Traversing
+	struct ispc::Graph graph;
+	ispc::graph_build(graph, node, num_nodes, edge, num_edges, NULL);
+	// ispc::graph_dump(graph);
+
+	reset_and_start_timer();
+	ispc::graph_cc_leader_par(rank, graph);
+	double elapsed = get_elapsed_mcycles();
+
+	// for (int i = 0; i < num_nodes; ++i) std::cout << rank[i] << " ";
+	// std::cout << std::endl;
+
+	print_runtime(elapsed);
+
+	delete[] node;
+	delete[] edge;
+	delete[] rank;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/dfs/dfs-par.cpp

@@ -1,0 +1,65 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "../../timing.h"
+# include "dfs_ispc.h"
+# include "ldp/common.hpp"
+
+# define INF (1 << 29)
+
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *distance = new int[num_nodes * num_nodes];
+	struct ispc::Node *node = new struct ispc::Node[num_nodes];
+	struct ispc::Edge *edge = new struct ispc::Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	double elapsed(0);
+
+	// Traversing
+	struct ispc::Graph graph;
+	ispc::graph_build(graph, node, num_nodes, edge, num_edges, distance);
+	// ispc::graph_dump(graph);
+
+	float *f = new float[num_nodes];
+
+	reset_and_start_timer();
+	for (int i(0); i < num_nodes; ++i) ispc::graph_dfs_par(graph, i, f);
+	elapsed += get_elapsed_mcycles();
+
+	// ispc::graph_dump(graph);
+	print_runtime(elapsed);
+
+	delete[] f;
+	delete[] node;
+	delete[] edge;
+	delete[] distance;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/dfs/dfs-seq.cpp

@@ -1,0 +1,89 @@
+# include <cstring>
+# include <iomanip>
+# include <iostream>
+
+# include "../../timing.h"
+# include "ldp/graph.hpp"
+# include "ldp/common.hpp"
+
+
+// Traverses the matrix in a depth-first fashion (no-LDP)
+void dfs(struct Graph& graph, int root, float *f) {
+
+	if (graph.node[root].visited) return;
+	graph.node[root].visited = true;
+
+	// Eventual computations
+	f[root] = graph.node[root].length / float(graph.num_nodes);
+
+	// Traversal
+	for (int i = 0; i < graph.node[root].length; ++i) {
+
+		int child = graph.node[root].edge[i].node;
+		if (!graph.node[child].visited) dfs(graph, child, f);
+
+	}
+
+}
+
+void graph_dfs(struct Graph& graph, int root, float *f) {
+
+	for (int i = 0; i < graph.num_nodes; ++i) graph.node[i].visited = false;
+	dfs(graph, root, f);
+
+}
+
+int main (int argc, char *argv[]) {
+
+	int num_nodes, num_edges;
+	std::cin >> num_nodes >> num_edges;
+
+	int *distance = new int[num_nodes * num_nodes];
+	struct Node *node = new struct Node[num_nodes];
+	struct Edge *edge = new struct Edge[num_edges];
+
+	int count(0);
+	int u, v, weight, last = -1;
+	while (count < num_edges and std::cin >> u >> v >> weight) {
+
+		while (last < u) {
+			++last;
+			node[last].length = 0;
+			node[last].edge = NULL;
+			node[last].visited = false;
+		}
+
+		if (node[u].length == 0) node[u].edge = &edge[count];
+
+		edge[count].node = v;
+		edge[count].weight = weight;
+
+		++node[u].length;
+		++count;
+
+	}
+
+	double elapsed(0);
+
+	// Traversing
+	struct Graph graph;
+	graph_build(graph, node, num_nodes, edge, num_edges, distance);
+	// graph_dump(graph);
+
+	float *f = new float[num_nodes];
+
+	reset_and_start_timer();
+	for (int i(0); i < num_nodes; ++i) graph_dfs(graph, i, f);
+	elapsed += get_elapsed_mcycles();
+
+	// graph_dump(graph);
+	print_runtime(elapsed);
+
+	delete[] f;
+	delete[] node;
+	delete[] edge;
+	delete[] distance;
+
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/dfs/objs/dfs_ispc_avx2.h

@@ -1,0 +1,78 @@
+//
+// objs/dfs_ispc_avx2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_DFS_ISPC_AVX2_H
+#define ISPC_OBJS_DFS_ISPC_AVX2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
+    extern void graph_dfs(struct Graph &graph, int32_t root);
[…]

### 2017-03-09 tests/rubens/ldp/dfs/objs/dfs_ispc_sse4.h

@@ -1,0 +1,78 @@
+//
+// objs/dfs_ispc_sse4.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_DFS_ISPC_SSE4_H
+#define ISPC_OBJS_DFS_ISPC_SSE4_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
+    extern void graph_dfs(struct Graph &graph, int32_t root);
[…]

### 2017-03-09 tests/rubens/ldp/kmeans/objs/kmeans_ispc_avx.h

@@ -1,0 +1,177 @@
+//
+// objs/kmeans_ispc_avx.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_KMEANS_ISPC_AVX_H
+#define ISPC_OBJS_KMEANS_ISPC_AVX_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_vector_Point__
+#define __ISPC_STRUCT_vector_Point__
+struct vector_Point {
+    struct Point * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_int__
+#define __ISPC_STRUCT_vector_int__
+struct vector_int {
+    int32_t * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Point__
+#define __ISPC_STRUCT_Point__
+struct Point {
+    int32_t label;
+    int32_t centroid;
+    struct vector_int dist;
+    struct vector_int coord;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_double__
+#define __ISPC_STRUCT_vector_double__
+struct vector_double {
+    double * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_float__
+#define __ISPC_STRUCT_vector_float__
+struct vector_float {
+    float * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_int16__
[…]

### 2017-03-09 tests/rubens/ldp/kmeans/objs/kmeans_ispc_sse2.h

@@ -1,0 +1,177 @@
+//
+// objs/kmeans_ispc_sse2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_KMEANS_ISPC_SSE2_H
+#define ISPC_OBJS_KMEANS_ISPC_SSE2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_vector_Point__
+#define __ISPC_STRUCT_vector_Point__
+struct vector_Point {
+    struct Point * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_int__
+#define __ISPC_STRUCT_vector_int__
+struct vector_int {
+    int32_t * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Point__
+#define __ISPC_STRUCT_Point__
+struct Point {
+    int32_t label;
+    int32_t centroid;
+    struct vector_int dist;
+    struct vector_int coord;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_double__
+#define __ISPC_STRUCT_vector_double__
+struct vector_double {
+    double * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_float__
+#define __ISPC_STRUCT_vector_float__
+struct vector_float {
+    float * data;
+    int32_t empty;
+    int32_t length;
+    int32_t allocated;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_vector_int16__
[…]

### 2017-03-09 tests/rubens/ldp/ldp/objs/graph_ispc.h

@@ -1,0 +1,91 @@
+//
+// objs/graph_ispc.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_GRAPH_ISPC_H
+#define ISPC_OBJS_GRAPH_ISPC_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_Graph__
+#define __ISPC_STRUCT_Graph__
+struct Graph {
+    int32_t num_nodes;
+    int32_t num_edges;
+    struct Node * node;
+    struct Edge * edge;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Node__
+#define __ISPC_STRUCT_Node__
+struct Node {
+    bool visited;
+    int32_t length;
+    struct Edge * edge;
+    int32_t * distance;
+};
+#endif
+
+#ifndef __ISPC_STRUCT_Edge__
+#define __ISPC_STRUCT_Edge__
+struct Edge {
+    int32_t node;
+    int32_t weight;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void graph_build(struct Graph &graph, struct Node * node, const int32_t &num_nodes, struct Edge * edge, const int32_t &num_edges, int32_t * distance);
[…]

### 2017-03-09 tests/rubens/ldp/sort/objs/quicksort_ispc_avx2.h

@@ -1,0 +1,54 @@
+//
+// objs/quicksort_ispc_avx2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_QUICKSORT_ISPC_AVX2_H
+#define ISPC_OBJS_QUICKSORT_ISPC_AVX2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void mergesort_lch(int32_t * array, int32_t len);
+    extern void mergesort_lch_bi(int32_t * array, int32_t len);
+    extern void mergesort_ldp(int32_t * array, int32_t len);
+    extern void mergesort_ldp_bi(int32_t * array, int32_t len);
+    extern void quicksort_lch(int32_t * array, int32_t len);
+    extern void quicksort_lch_bi(int32_t * array, int32_t len);
+    extern void quicksort_ldp(int32_t * array, int32_t len);
+    extern void quicksort_ldp_bi(int32_t * array, int32_t len);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_QUICKSORT_ISPC_AVX2_H

### 2017-03-09 tests/rubens/ldp/sort/objs/quicksort_ispc_sse2.h

@@ -1,0 +1,54 @@
+//
+// objs/quicksort_ispc_sse2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_QUICKSORT_ISPC_SSE2_H
+#define ISPC_OBJS_QUICKSORT_ISPC_SSE2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void mergesort_lch(int32_t * array, int32_t len);
+    extern void mergesort_lch_bi(int32_t * array, int32_t len);
+    extern void mergesort_ldp(int32_t * array, int32_t len);
+    extern void mergesort_ldp_bi(int32_t * array, int32_t len);
+    extern void quicksort_lch(int32_t * array, int32_t len);
+    extern void quicksort_lch_bi(int32_t * array, int32_t len);
+    extern void quicksort_ldp(int32_t * array, int32_t len);
+    extern void quicksort_ldp_bi(int32_t * array, int32_t len);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_QUICKSORT_ISPC_SSE2_H

### 2017-03-09 tests/rubens/ldp/sort/objs/sort_ispc_avx.h

@@ -1,0 +1,54 @@
+//
+// objs/sort_ispc_avx.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_SORT_ISPC_AVX_H
+#define ISPC_OBJS_SORT_ISPC_AVX_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void mergesort_lch(int32_t * array, int32_t len);
+    extern void mergesort_lch_bi(int32_t * array, int32_t len);
+    extern void mergesort_ldp(int32_t * array, int32_t len);
+    extern void mergesort_ldp_bi(int32_t * array, int32_t len);
+    extern void quicksort_lch(int32_t * array, int32_t len);
+    extern void quicksort_lch_bi(int32_t * array, int32_t len);
+    extern void quicksort_ldp(int32_t * array, int32_t len);
+    extern void quicksort_ldp_bi(int32_t * array, int32_t len);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_SORT_ISPC_AVX_H

### 2017-03-09 tests/rubens/ldp/sort/objs/sort_ispc_sse2.h

@@ -1,0 +1,54 @@
+//
+// objs/sort_ispc_sse2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_SORT_ISPC_SSE2_H
+#define ISPC_OBJS_SORT_ISPC_SSE2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void mergesort_lch(int32_t * array, int32_t len);
+    extern void mergesort_lch_bi(int32_t * array, int32_t len);
+    extern void mergesort_ldp(int32_t * array, int32_t len);
+    extern void mergesort_ldp_bi(int32_t * array, int32_t len);
+    extern void quicksort_lch(int32_t * array, int32_t len);
+    extern void quicksort_lch_bi(int32_t * array, int32_t len);
+    extern void quicksort_ldp(int32_t * array, int32_t len);
+    extern void quicksort_ldp_bi(int32_t * array, int32_t len);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_SORT_ISPC_SSE2_H

### 2017-03-09 tests/rubens/ldp/string/objs/string_ispc_sse2.h

@@ -1,0 +1,57 @@
+//
+// objs/string_ispc_sse2.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_STRING_ISPC_SSE2_H
+#define ISPC_OBJS_STRING_ISPC_SSE2_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_String__
+#define __ISPC_STRUCT_String__
+struct String {
+    int32_t length;
+    int8_t * data;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void String_match_lch(struct String &text, struct String &pattern, int32_t * matches, int32_t &num_matches);
+    extern void String_match_ldp(struct String &text, struct String &pattern, int32_t * matches, int32_t &num_matches);
+    extern void String_match_par(struct String &text, struct String &pattern, int32_t * matches, int32_t &num_matches);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_STRING_ISPC_SSE2_H

### 2017-03-09 tests/rubens/ldp/string/objs/string_ispc_sse4.h

@@ -1,0 +1,57 @@
+//
+// objs/string_ispc_sse4.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_STRING_ISPC_SSE4_H
+#define ISPC_OBJS_STRING_ISPC_SSE4_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+#ifndef __ISPC_STRUCT_String__
+#define __ISPC_STRUCT_String__
+struct String {
+    int32_t length;
+    int8_t * data;
+};
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void String_match_lch(struct String &text, struct String &pattern, int32_t * matches, int32_t &num_matches);
+    extern void String_match_ldp(struct String &text, struct String &pattern, int32_t * matches, int32_t &num_matches);
+    extern void String_match_par(struct String &text, struct String &pattern, int32_t * matches, int32_t &num_matches);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_STRING_ISPC_SSE4_H

### 2017-03-09 tests/rubens/ldp/string/string-ldp.cpp

@@ -1,0 +1,55 @@
+# include <vector>
+# include <fstream>
+# include <iostream>
+
+# include "string_ispc.h"
+# include "../../timing.h"
+# include "ldp/common.hpp"
+
+# define MAX_LENGTH (1 << 13)
+
+
+int main (int argc, char *argv[]) {
+
+	double elapsed(0);
+
+	ispc::String text;
+	ispc::String pattern;
+
+	int num_matches(0);
+	std::vector<int> matches(MAX_LENGTH, 0);
+
+	// Input pattern
+	std::string word(MAX_LENGTH, '\0');
+	std::cin.getline(&word[0], MAX_LENGTH);
+
+	pattern.data = (int8_t *) word.data();
+	pattern.length = std::cin.gcount() - 1;
+
+	// Input data
+	std::string buffer(MAX_LENGTH, '\0');
+	std::cin.read(&buffer[0], MAX_LENGTH);
+
+	while (std::cin.gcount()) {
+
+		text.data = (int8_t *) buffer.data();
+		text.length = std::cin.gcount();
+		buffer[text.length] = 0;
+
+		// Looking for pattern in input string
+		reset_and_start_timer();
+		ispc::String_match_ldp(text, pattern, matches.data(), num_matches);
+		elapsed += get_elapsed_mcycles();
+
+		// Copying the last (|pattern| - 1) characters to the beginning
+		// of the buffer before reading the next chunk of data
+		int len(pattern.length - 1);
+		buffer.replace(0, len, &buffer[text.length - 1 - len]);
+		std::cin.read(&buffer[len], MAX_LENGTH);
+
+	}
+
+	print_runtime(elapsed);
+	return 0;
+
+}

### 2017-03-09 tests/rubens/ldp/test/objs/foo_ispc.h

@@ -1,0 +1,66 @@
+//
+// objs/foo_ispc.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_FOO_ISPC_H
+#define ISPC_OBJS_FOO_ISPC_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void fooo();
+    extern void hello_world();
+    extern void mem_access(int32_t *  * data, int32_t length);
+    extern void proc_matrix();
+    extern void toy(int32_t *  * data, int32_t length);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+
[…]

### 2017-03-09 tests/rubens/ldp/test/objs/foo_ispc_sse4.h

@@ -1,0 +1,51 @@
+//
+// objs/foo_ispc_sse4.h
+// (Header automatically generated by the ispc compiler.)
+// DO NOT EDIT THIS FILE.
+//
+
+#ifndef ISPC_OBJS_FOO_ISPC_SSE4_H
+#define ISPC_OBJS_FOO_ISPC_SSE4_H
+
+#include <stdint.h>
+
+
+
+#ifdef __cplusplus
+namespace ispc { /* namespace */
+#endif // __cplusplus
+
+#ifndef __ISPC_ALIGN__
+#if defined(__clang__) || !defined(_MSC_VER)
+// Clang, GCC, ICC
+#define __ISPC_ALIGN__(s) __attribute__((aligned(s)))
+#define __ISPC_ALIGNED_STRUCT__(s) struct __ISPC_ALIGN__(s)
+#else
+// Visual Studio
+#define __ISPC_ALIGN__(s) __declspec(align(s))
+#define __ISPC_ALIGNED_STRUCT__(s) __ISPC_ALIGN__(s) struct
+#endif
+#endif
+
+
+///////////////////////////////////////////////////////////////////////////
+// Functions exported from ispc code
+///////////////////////////////////////////////////////////////////////////
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+extern "C" {
+#endif // __cplusplus
+    extern void fooo();
+    extern void hello_world();
+    extern void mem_access(int32_t *  * data, int32_t length);
+    extern void proc_matrix();
+    extern void toy(int32_t *  * data, int32_t length);
+#if defined(__cplusplus) && (! defined(__ISPC_NO_EXTERN_C) || !__ISPC_NO_EXTERN_C )
+} /* end extern C */
+#endif // __cplusplus
+
+
+#ifdef __cplusplus
+} /* namespace */
+#endif // __cplusplus
+
+#endif // ISPC_OBJS_FOO_ISPC_SSE4_H

### 2017-03-09 tests/rubens/ldp/utils/binary-line-generator.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python
+
+
+from sys import argv
+from random import randint, sample
+
+
+num_lines = int(argv[1])
+line_len = int(argv[2])
+pattern_len = int(argv[3])
+prob = float(argv[4]) / 100
+
+prob = min(prob, 100)
+line_len = max(line_len, pattern_len)
+
+pattern = bin(randint(1 << pattern_len, 2 << pattern_len))[-pattern_len:]
+
+num_occur = int(prob * num_lines)
+matches = sample(xrange(0, num_lines), num_occur)
+
+# Printing arguments
+print(num_lines)
+print(pattern)
+
+# Printing binary lines
+matches.sort(reverse=True)
+for i in xrange(num_lines):
+
+	line = ""
+	while len(line) < line_len:
+		line += bin(randint(0, 2 << 100))[2:]
+
+	if matches and matches[-1] == i:
+		line += pattern
+		matches.pop()
+
+	print(line[-line_len:])

### 2017-03-09 tests/rubens/ldp/utils/graph-generator-barabasi.py

@@ -1,0 +1,22 @@
+#!/usr/bin/python
+
+
+from sys import argv, exit
+from random import randint
+from networkx import barabasi_albert_graph
+
+if len(argv) != 3:
+	print("%s <num_vertices:int> <outdegree:int>" % (argv[0]))
+	exit()
+
+num_vertices = int(argv[1])
+outdegree = int(argv[2])
+
+graph = barabasi_albert_graph(num_vertices, outdegree)
+edges = graph.edges()
+
+print(num_vertices)
+print(len(edges))
+
+for (u, v) in sorted(edges):
+	print("%d\t%d\t%d" % (u, v, randint(0, 100)))

### 2017-03-09 tests/rubens/ldp/utils/graph-generator-erdos.py

@@ -1,0 +1,22 @@
+#!/usr/bin/python
+
+
+from sys import argv, exit
+from random import randint
+from networkx import erdos_renyi_graph
+
+if len(argv) != 3:
+	print("%s <num_vertices:int> <probability:int>" % (argv[0]))
+	exit()
+
+num_vertices = int(argv[1])
+probability = float(argv[2]) / 100
+
+graph = erdos_renyi_graph(num_vertices, probability, directed=True)
+edges = graph.edges()
+
+print(num_vertices)
+print(len(edges))
+
+for (u, v) in sorted(edges):
+	print("%d\t%d\t%d" % (u, v, randint(0, 100)))

### 2017-03-09 tests/rubens/ldp/utils/ingen-book.sh

@@ -1,0 +1,9 @@
+#! /bin/bash
+
+
+outfolder="$1"
+mkdir -p "${outfolder}/80"
+
+for i in 1000 5000 10000 15000 20000 25000; do
+	./binary-line-generator.py 10000 $i 8 40 > "${outfolder}/80/${i}.dat"
+done                                         

### 2017-03-09 tests/rubens/ldp/utils/ingen-graph-octree.sh

@@ -1,0 +1,10 @@
+#! /bin/bash
+
+
+outfolder="$1"
+mkdir -p "${outfolder}"
+
+# Iterate through the depth of the tree
+for depth in {1..8}; do
+	./graph-generator-narytree.py 8 ${depth} > "${outfolder}/${depth}.dat"
+done

### 2017-03-09 tests/rubens/ldp/utils/ldp-exec.sh

@@ -1,0 +1,102 @@
+#! /bin/bash
+
+
+source ldp-ui.sh
+
+# -----------------------------------------------------------------------------
+# Execution
+
+# Executes the selected benchmark
+Setup() {
+
+	# Validating logfile folder
+	[[ -z ${logfolder} ]] && logfolder="$(pwd)"
+	[[ ! -d ${logfolder} ]] && \
+		echo "$0 (line $LINENO): logfile folder" ${logfolder}
+
+	logfolder="$(readlink -f ${logfolder})"
+
+	# Creating logfile
+	timestamp=$(date "+%m%d%Y%H%M%S")
+	logfile="${logfolder}/${timestamp}.log"
+
+	touch ${logfile}
+	Info "logfile created" ${logfile}
+
+	# Validating benchmark ID
+	[[ ${benchID} -lt 0 || ${benchID} -gt ${#bench[@]} ]] \
+		&& Errr "benchmark ID" ${benchID}
+
+}
+
+RunBenchmark() {
+
+	root="$(readlink -m $(pwd)/../${bench[$benchID]})"
+	[[ ! -d ${root} ]] && Errr "directory path" ${root}
+
+	bin_seq="${root}/${bench[$benchID]}-seq"
+	bin_ldp="${root}/${bench[$benchID]}-ldp"
+	bin_par="${root}/${bench[$benchID]}-par"
+	bin_lch="${root}/${bench[$benchID]}-lch"
+
+	Info "entering execution folder"
+	cd ${logfolder}
+
+	# Creating output files
+	errfile_seq="${logfolder}/${timestamp}-seq.err"
+	outfile_seq="${logfolder}/${timestamp}-seq.out"
+
+	errfile_ldp="${logfolder}/${timestamp}-ldp.err"
+	outfile_ldp="${logfolder}/${timestamp}-ldp.out"
+
+	errfile_par="${logfolder}/${timestamp}-par.err"
+	outfile_par="${logfolder}/${timestamp}-par.out"
+
+	errfile_lch="${logfolder}/${timestamp}-lch.err"
+	outfile_lch="${logfolder}/${timestamp}-lch.out"
+
+	Info "output and error files created: ${logfolder}/${timestamp}-*"
+	touch ${errfile_seq} ${outfile_seq}
+	touch ${errfile_ldp} ${outfile_ldp}
+	touch ${errfile_par} ${outfile_par}
+	touch ${errfile_lch} ${outfile_lch}
+
[…]

### 2017-03-09 tests/rubens/ldp/utils/ldp-ui.sh

@@ -1,0 +1,114 @@
+#! /bin/bash
+
+
+# Global constant variables
+declare -ar bench=( $(cat bench.cfg) )
+
+# Global variables
+declare -i benchID=-1
+declare -i num_runs=-1
+declare -i display_width=80
+
+declare infile logfolder inputdir
+declare timestamp outfile errfile logfile
+
+# -----------------------------------------------------------------------------
+# User Interface
+Arguments() {
+
+	[[ $# -eq 0 ]] && PrintHelp
+
+	local -i i=1
+	while [[ $i -le $# ]]; do
+
+		arg=${@:$i:1}
+
+		case $arg in
+		-h )
+			PrintHelp
+			;;
+		--help )
+			(( ++i ))
+			display_width=${@:$1:1}
+			PrintHelp
+			;;
+		-b )
+			(( ++i ))
+			benchID=${@:$i:1}
+			;;
+		-i )
+			(( ++i ))
+			infile="${@:$i:1}"
+			;;
+		-I )
+			(( ++i ))
+			inputdir=${@:$i:1}
+			;;
+		--list-bench )
+			ListBenchmarks
+			;;
+		-l )
+			(( ++i ))
+			timestamp=${@:$i:1}
+			;;
+		-L )
+			(( ++i ))
+			logfolder=${@:$i:1}
+			;;
+		-n )
+			(( ++i ))
+			num_runs=${@:$i:1}
+			;;
+		* )
+			echo "$0 (line $LINENO): unknown option #$i '$arg'"
+			;;
+		esac
+
+		(( ++i ))
+
+	done
+
+}
+
+# Help
+PrintHelp() {
+	(echo .ll ${display_width}; cat arguments.1) | nroff -man | sed 's/.//g'
+	exit 1
+}
+
+# Lists available benchmarks
+ListBenchmarks() {
+	(echo .ll ${display_width}; cat benchmarks.1) | nroff -man | sed 's/.//g'
+	exit 1
+}
+
+# Dumps execution messages
+Debug() {
+	[[ ! -f ${logfile} ]] && Error "invalid logfile!"
+	echo "[$(date '+%m-%d-%Y %H:%M:%S')] -- $1" >> ${logfile}
+}
+
+Info() {
+	Debug "Info: $1"
+}
+
+Warn() {
+	Debug "Warn: $1"
+}
+
+Errr() {
+
[…]

### 2017-03-09 tests/toys/taskminer.sh

@@ -1,1 +1,0 @@
-/Users/pedroramos/programs/llvm/Debug+Asserts/bin/opt -load LLVMTaskMiner.dylib $1 -disable-output -taskminer -stats

### 2017-03-09 tests/toys/testpass.sh

@@ -1,1 +1,0 @@
-opt -load LLVMTaskMiner.dylib $1 -disable-output -testpass

### 2017-10-31 docs/ACM/paper.tex
Putting paper in ACM format.

--- 2017-03-09 docs/IEEE/paper.tex
@@
-\documentclass[pageno]{jpaper}
+%% For double-blind review submission
+\documentclass[sigplan,10pt,review,anonymous]{acmart}
+\settopmatter{printfolios=true}
+%% For final camera-ready submission
+%\documentclass[acmlarge]{acmart}\settopmatter{}
 
-\newcommand{\pactedition}{26th}
-\newcommand{\pactyear}{17}
-\newcommand{\pactcompyear}{20\pactyear}
+\makeatletter\if@ACM@journal\makeatother
 
-%replace XXX with the submission number you are given from the PACT submission site.
-\newcommand{\pactsubmissionnumber}{XXX}
+%% Journal information (used by PACMPL format)
+%% Supplied to authors by publisher for camera-ready submission
+\acmJournal{PACMPL}
+\acmVolume{1}
+\acmNumber{1}
+\acmArticle{1}
+\acmYear{2017}
+\acmMonth{1}
+\acmDOI{10.1145/nnnnnnn.nnnnnnn}
+\startPage{1}
+\else\makeatother
 
-\usepackage[normalem]{ulem}
+%% Conference information (used by SIGPLAN proceedings format)
+%% Supplied to authors by publisher for camera-ready submission
+\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
+\acmYear{2017}
+\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
+\acmDOI{10.1145/nnnnnnn.nnnnnnn}
+\startPage{1}
+\fi
+
+\newcommand{\fer}[1]{\textcolor{red}{#1}}
+
+%% For review submission
+\setcopyright{none}
+
+%% Bibliography style
+\bibliographystyle{ACM-Reference-Format}
+\citestyle{acmauthoryear}
+
+%% Packages that we are using in this version of the work:
+\usepackage{hyperref}
 
@@
 
-\guido{Not sure if we should dive into a discussion of what is a regular or an irregular program; to be even more precise we are actually mining task parallelism (for this moment) only within loops; hence I propose this new title}
-\pedro{I think we should say "Automatic Mining of Task Parallelism in Programs" because we might mine task parallelism in recursive functions as well.}
-\title{\rmv{Task Mining in Irregular Programs.}\new{Automatic Mining of Task Parallelism in Programs}}
+\title[Automatic Identification and Annotation of Parallel Tasks in Programs]
+{Automatic Identification and Annotation of Parallel Tasks in Programs}
 
-\date{}
-\maketitle
+\author{Pedro Henrique Ramos Costa}
+\authornote{with author1 note}          %% \authornote is optional;
+\orcid{nnnn-nnnn-nnnn-nnnn}
+\affiliation{
+  \position{Researcher}
+  \department{DCC}
+  \institution{UFMG}
+  \streetaddress{6627 Antonio Carlos Avenue}
+  \city{Belo Horizonte}
+  \state{Minas Gerais}
+  \postcode{31.270-213}
+  \country{Brazil}
+}
+\email{pedroramos@dcc.ufmg.br}
 
-\thispagestyle{empty}
+\author{Gleison Souza Diniz Mendonc\c{c}a}
+\authornote{with author1 note}          %% \authornote is optional;
+\orcid{nnnn-nnnn-nnnn-nnnn}
+\affiliation{
+  \position{Researcher}
+  \department{DCC}
+  \institution{UFMG}
+  \streetaddress{6627 Antonio Carlos Avenue}
+  \city{Belo Horizonte}
+  \state{Minas Gerais}
+  \postcode{31.270-213}
+  \country{Brazil}
+}
+\email{gleison.mendonca@dcc.ufmg.br}
+
+\author{Divino C\'{e}sar}
+\authornote{with author1 note}
+\orcid{nnnn-nnnn-nnnn-nnnn}
+\affiliation{
+  \position{Researcher}
+  \department{IC}
+  \institution{UNICAMP}
+  \streetaddress{Cidade Universit\'{a}ria}
+  \city{Campinas}
+  \state{S\~{a}o Paulo}
+  \postcode{13083-970}
+  \country{Brazil}
+}
+\email{divcesar@gmail.com}
+
+\author{Guido Ara\'{u}jo}
+\authornote{with author1 note}
+\orcid{nnnn-nnnn-nnnn-nnnn}
+\affiliation{
+  \position{Professor}
+  \department{IC}
+  \institution{UNICAMP}
+  \streetaddress{Cidade Universit\'{a}ria}
+  \city{Campinas}
+  \state{S\~{a}o Paulo}
+  \postcode{13083-970}
+  \country{Brazil}
+}
+\email{guido@ic.unicamp.br}
+
+\author{Fernando Magno Quint\~{a}o Pereira}
+\authornote{with author1 note}
+\orcid{nnnn-nnnn-nnnn-nnnn}
+\affiliation{
+  \position{Professor}
+  \department{DCC}
+  \institution{UFMG}
+  \streetaddress{6627 Antonio Carlos Avenue}
+  \city{Belo Horizonte}
+  \state{Minas Gerais}
+  \postcode{31.270-213}
+  \country{Brazil}
+}
+\email{fernando@dcc.ufmg.br}          %% \email is recommended
 
@@
 \end{abstract}
+
+%% 2012 ACM Computing Classification System (CSS) concepts
+%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
+ \begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10011006.10011041</concept_id>
+<concept_desc>Software and its engineering~Compilers</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011006.10011008.10011024.10011035</concept_id>
+<concept_desc>Software and its engineering~Procedures, functions and subroutines</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10003752.10003766.10003776</concept_id>
+<concept_desc>Theory of computation~Regular languages</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10003752.10010124.10010131.10010134</concept_id>
+<concept_desc>Theory of computation~Operational semantics</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Compilers}
+\ccsdesc[300]{Software and its engineering~Procedures, functions and subroutines}
+\ccsdesc[300]{Theory of computation~Regular languages}
+\ccsdesc[300]{Theory of computation~Operational semantics}
+
+\keywords{Parallelism, Tasks, OpenMP}
+
+\maketitle
 
@@
 
-\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
-\bibliographystyle{IEEEtranS}
 \bibliography{references}

### 2017-10-31 tests/benchmarks/bots/jacobi/jacobi_MI.c
added new benchmark: poisson

@@ -1,0 +1,150 @@
+# include "poisson.h"
+#include <omp.h>
+
+#define min(a, b) ((a<b)?a:b)
+#define max(a, b) ((a>b)?a:b)
+
+/* #pragma omp task/taskwait version of SWEEP. */
+void sweep (int nx, int ny, double dx, double dy, double *f_,
+        int itold, int itnew, double *u_, double *unew_, int block_size)
+{
+    int it;
+    double (*f)[nx][ny] = (double (*)[nx][ny])f_;
+    double (*u)[nx][ny] = (double (*)[nx][ny])u_;
+    double (*unew)[nx][ny] = (double (*)[nx][ny])unew_;
+    int block_x, block_y;
+
+    if (block_size == 0)
+        block_size = nx;
+
+    int max_blocks_x = (nx / block_size);
+    int max_blocks_y = (ny / block_size);
+
+#pragma omp parallel \
+    shared(u_, unew_, f, max_blocks_x, max_blocks_y, nx, ny, dx, dy, itold, itnew, block_size) \
+    private(it, block_x, block_y)
+#pragma omp single
+    {
+        for (it = itold + 1; it <= itnew; it++) {
+            // Save the current estimate.
+            for (block_x = 0; block_x < max_blocks_x; block_x++) {
+                for (block_y = 0; block_y < max_blocks_y; block_y++) {
+#pragma omp task shared(u_, unew_, block_size, nx, ny) firstprivate(block_x, block_y) \
+                    depend(in: unew[block_x * block_size: block_size][block_y * block_size: block_size]) \
+                    depend(out: u[block_x * block_size: block_size][block_y * block_size: block_size])
+                    copy_block(nx, ny, block_x, block_y, u_, unew_, block_size);
+                }
+            }
+
+            // Compute a new estimate.
+            for (block_x = 0; block_x < max_blocks_x; block_x++) {
+                for (block_y = 0; block_y < max_blocks_y; block_y++) {
+                    int xdm1 = block_x == 0 ? 0 : 1;
+                    int xdp1 = block_x == max_blocks_x-1 ? 0 : +1;
+                    int ydp1 = block_y == max_blocks_y-1 ? 0 : +1;
+                    int ydm1 = block_y == 0 ? 0 : 1;
+#pragma omp task shared(u_, unew_, f_, dx, dy, nx, ny, block_size) firstprivate(block_x, block_y, xdm1, xdp1, ydp1, ydm1) \
[…]

### 2017-10-31 tests/benchmarks/bots/jacobi/poisson.c

@@ -1,0 +1,256 @@
+# include <stdlib.h>
+# include <stdio.h>
+# include <math.h>
+# include <time.h>
+# include <string.h>
+# include "poisson.h"
+
+
+
+double r8mat_rms(int nx, int ny, double *a_);
+void rhs(int nx, int ny, double *f_, int block_size);
+void timestamp(void);
+double u_exact(double x, double y);
+double uxxyy_exact(double x, double y);
+
+/*
+Purpose:
+
+MAIN is the main program for POISSON_OPENMP.
+
+Discussion:
+
+POISSON_OPENMP is a program for solving the Poisson problem.
+
+This program uses OpenMP for parallel execution.
+
+The Poisson equation
+
+- DEL^2 U(X,Y) = F(X,Y)
+
+is solved on the unit square [0,1] x [0,1] using a grid of NX by
+NX evenly spaced points.  The first and last points in each direction
+are boundary points.
+
+The boundary conditions and F are set so that the exact solution is
+
+U(x,y) = sin ( pi * x * y)
+
+so that
+
+- DEL^2 U(x,y) = pi^2 * ( x^2 + y^2) * sin ( pi * x * y)
+
+The Jacobi iteration is repeatedly applied until convergence is detected.
+
+For convenience in writing the discretized equations, we assume that NX = NY.
+
+Licensing:
+
+This code is distributed under the GNU LGPL license.
+
+Modified:
+
+14 December 2011
+
+Author:
+
+John Burkardt
+*/
+
+/******************************************************************************/
+
+double run(struct user_parameters* params)
+{
+    int matrix_size = params->matrix_size;
+    if (matrix_size <= 0) {
+        matrix_size = 512;
+        params->matrix_size = matrix_size;
+    }
+    int block_size = params->blocksize;
+    if (block_size <= 0) {
+        block_size = 128;
+        params->blocksize = block_size;
+    }
+    int niter = params->titer;
+    if (niter <= 0) {
+        niter = 4;
+        params->titer = niter;
+    }
+    double dx;
+    double dy;
+    double error;
+    int ii,i;
+    int jj,j;
+    int nx = matrix_size;
+    int ny = matrix_size;
+    double *f_ = malloc(nx * nx * sizeof(double));
+    double (*f)[nx][ny] = (double (*)[nx][ny])f_;
+    double *u_ = malloc(nx * nx * sizeof(double));
[…]

### 2017-10-31 tests/benchmarks/bots/jacobi/poisson.h

@@ -1,0 +1,117 @@
+#ifndef KASTORS_POISSON_H
+#define KASTORS_POISSON_H
+# include <assert.h>
+
+typedef struct user_parameters user_parameters;
+
+struct user_parameters {
+    int check;
+    int succeed;
+    char* string2display;
+    int niter;
+    int titer;
+    int matrix_size;
+    int submatrix_size;
+    int blocksize;
+    int iblocksize;
+    int cutoff_depth;
+    int cutoff_size;
+};
+
+extern double run(struct user_parameters* params);
+
+/******************************************************************************/
+/*
+  Purpose:
+
+  SWEEP carries out one step of the Jacobi iteration.
+
+  Discussion:
+
+  Assuming DX = DY, we can approximate
+
+  - (d/dx d/dx + d/dy d/dy) U(X,Y)
+
+  by
+
+  (U(i-1,j) + U(i+1,j) + U(i,j-1) + U(i,j+1) - 4*U(i,j)) / dx / dy
+
+  The discretization employed below will not be correct in the general
+  case where DX and DY are not equal.  It's only a little more complicated
+  to allow DX and DY to be different, but we're not going to worry about
+  that right now.
+
+  Licensing:
+
+  This code is distributed under the GNU LGPL license.
+
+  Modified:
+
+  14 December 2011
+
+  Author:
+
+  John Burkardt
+
+  Parameters:
+
+  Input, int NX, NY, the X and Y grid dimensions.
+
+  Input, double DX, DY, the spacing between grid points.
+
+  Input, double F[NX][NY], the right hand side data.
+
+  Input, int ITOLD, the iteration index on input.
+
+  Input, int ITNEW, the desired iteration index
+  on output.
+
+  Input, double U[NX][NY], the solution estimate on
+  iteration ITNEW-1.
+
+  Input/output, double UNEW[NX][NY], on input, the solution
+  estimate on iteration ITOLD.  On output, the solution estimate on
+  iteration ITNEW.
+*/
+void sweep(int nx, int ny, double dx, double dy, double *f,
+	   int itold, int itnew, double *u, double *unew, int block_size);
+void sweep_seq(int nx, int ny, double dx, double dy, double *f,
+	   int itold, int itnew, double *u, double *unew);
+
+
+static inline void copy_block(int nx, int ny, int block_x, int block_y, double *u_, double *unew_, int block_size) {
+    int i, j, start_i, start_j;
[…]

### 2017-10-31 docs/ACM/paper.tex
Adding an introduction to the paper.

@@
 \fi
+\newcommand\dawn{\mbox{\textsf{DawnCC}}}
+\newcommand\Taskminer{\mbox{\textsf{TaskMiner}}}
 
@@
 
-\title[Automatic Identification and Annotation of Parallel Tasks in Programs]
+\title[Automatic Identification and Annotation of Parallel Tasks in Structured
+Programs]
 {Automatic Identification and Annotation of Parallel Tasks in Programs}
@@
 
-% CONTEXT
-It is undeniable that parallel computing is nowadays the most pursued alternative by developers  when striving for more application performance \cite{hwu2014ahead}.
-Two main reasons stand behind  the actual urge for parallel programming.
-\ed{First, the ever  increasing industry of multi-cores and many-cores architectures propitiates the development of software  with such behaviour \cite{haugen2016performance, vandierendonck2013analysis}.} \guido{Fine, but it seems to me a very convoluted way to say that this was due to the emergence of multicore/manycore  architectures as the alternative to maintain transistor power-density under control.} \ed{Second, programmers often code in simple parallel patterns  \cite{pinto2015large}, which evidences their awareness and will for parallelism}.
-\guido{Not sure if programming using patterns is an evidence that supports the urge for interest in parallel programming; on the contrary, it seems to me that it is more a consequence to tackle the complexity of the problem.}
+Annotation systems have risen to a place of prominence as a simple and
+effective way to write parallel programs.
+Examples of such systems include OpenMP~\cite{JaegerCP15},
+OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10} and OpenSs~\cite{MeenderinckJ11}.
+Annotations work as a meta-language: they let developers grant parallel
+semantics to syntax originally written to execute sequentially.
+The compiler-related literature contains a generous load of success stories
+describing the use of annotation systems to parallelize programs.
+Combined with modern accelerators, they have led to substantial performance
+gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
+Yet, even if convenient, the use of annotations is not straightforward.
 
-Although extensive  work has been done to scavenge parallelism in regular applications \cite{kulkarni2009much}, finding good  parallel opportunities in irregular code remains a grueling task.
-\guido{We need to re-phrase this if we want to use this statement to introduce the motivation to our work; a number of the examples that we are using do not have pointers, and thus could not be classified as irregular code....}
+Annotations such as OpenMP or OpenACC still require developers to
+worry about typical hassles of the parallel world, such as race conditions,
+or deadlocks.
+Moreover, because they are used in tandem with imperative programming languages,
+such troubles are only made worse by pointer aliasing.
+There exist tools that insert automatic annotations in
+programs~\cite{gleison2016,Pingali11,wanggenerating}.
+All these technologies explore data-parallelism -- the possibility of running
+the same computation independently on different data.
+Task parallelism remains still uncharted land, in what concerns automatic
+annotation.
+Such fact is unfortunate, because much of the power of current annotation
+systems lays on their ability to create tasks \ed{We need to find references!}.
+This ability brings said systems closer to irregular programs such as those
+that implement graphs and worklist algorithms \`{a} la
+Pingali~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
+We address this omission in this work.
 
-% PROBLEM
-Programming parallel applications is a hard task, as programmers ought to take care of many aspects of the job such as identifying and keeping variable dependences correct and assuring synchronization and scalability of threads/processes whilst avoiding race conditions.
-However, finding parallelism in programs that were not coded in a parallel paradigm \rmv{annotated sequential  code} is not a simple task, as compiler static analyses are not precise enough to identify  parallel regions \cite{kulkarni2007optimistic}.
-For example, due  to the conservative trait of static analyses, loops are frequently marked as iteration-dependent when, in reality, their iterations might run in parallel most of the time.
-As a matter of fact,  many dependences pointed by the compiler might never occur during runtime, resulting in several missing opportunities for parallelization.
+This paper describes \Taskminer, the first compiler that mines task parallelism
+from programs.
+To fulfill this goal \Taskminer{} solves three challenges.
+First, it find program regions, e.g., loops or functions, that can be
+effectively mapped onto tasks.
+Second, it determines symbolic bounds to all the memory blocks accesses within
+those regions.
+Third, it maps such information back into source code, producing annotations
+that programmers can read.
+The goal of this paper is to describe the design and the implementation of these
+three technologies, and to demonstrate their benefit.
 
-A way to approach this problem is to use a programming model that can capture and enforce dependences between iterations at runtime whenever they occur.
-In such model, those iterations that do not have {\it loop-carried} dependencies are free to run in parallel, while iterations that dynamically create loop-carried dependences are serialized and dispatched in dependence order by  a system runtime.
-In recent years, task-based execution models  have proven itself to be a scalable and quite flexible approach to extract regular and irregular parallelism from sequential code ~\cite{starss,bddt,cilk,sequoia,dandelion,legion,ooojava,dague}.
-In this model, the programmer uses a {\it task} directive to mark  code regions in the program that are potential tasks and lists their corresponding dependences.
-The OpenMP task scheduling~\cite{openmp2009}  is an example of such model.
-Although OpenMP task simplifies the mechanics of dispatching and running tasks, the burden of finding code regions to be annotated with task directives still lies upon the programmer.
-
-Work has been carried out to generate OpenMP annotations automatically given a set of instructions that define  a region \cite{gleison2016, pingali2011tao, wanggenerating}.
-\guido{Need to provide a short paragraph here to give an idea why these works do not solve the problem of automatically extracting parallelism from loops with loop carried-depedenciss}.
-
-% SOLUTION
-%Guido: This is an ambitious objective; ou work is more modest.
-%Our work focuses on finding irregular code  and automatic generating compiler directives to make the parallelism explicit.
-\ed{This paper presents an automatic technique that extracts task parallelism from loops which cannot be proved by static analysis to be loop-carried independent. }
-
-\guido{I HAVE STOPPED HERE; WILL CONTINUE LATER}
-
-The static analysis finds irregular loops (i.e., loops with loop-carried dependences) and then speculates 
-whether these loops can be safely executed in parallel or not. These loops
-are annotated with compiler directives, to point out the possibility of task-parallelization within that sequence of code. 
-Then a runtime able to compile these directives runs the tasks for the annotated code. 
-During execution, the dependences are resolved by the runtime and the code is executed in parallel.
-
-The key insight of the tool is that it does not rely on the programmer to find possible parallel sites. 
-It does so automatically, and the runtime is solely responsible for unraveling the dependences between tasks. 
-The final product of this combination is a high-performant framework that
-lets us run algorithms that are traditionally difficult to parallelize.
-
-% TESTS AND RESULTS
-We have implemented this technique in the LLVM compiler infrastructure.
-We tested our technique on three large benchmarks (CASTOR, LG Graphical Application, ???) and compared it to the manually annotated version.
-We show that XX\% of the manually annotated regions are found by our technique.
-Our technique also finds XX\% more possible task regions than what is manually annotated.
-Regarding performance, the automatically annotated code can be up to X times faster than the manually annotated one.
-
-%Fernando's first draft
-%//DRAFT
-%The key contribution of this paper is a fully automatic technique to find parallelism in programs, and to annotate them so to make this parallelism explicit.
-%This technique consists in the combination of static and a dynamic analyses that increase the volume of tasks that can run in parallel.
-%The static analysis finds independent code, which can be safely executed in parallel.
-%However, due to its conservative nature, the static analysis misses potential parallelization opportunities.
-%These tasks, which we cannot show to be independent due, for instance, to poor aliasing information, are solved at runtime by the data-flow engine.
+Such benefit is performance and readability.
+\Taskminer{} receives as input a C program, and produces, as output, a C
+program annotated with OpenMP directives that identify tasks.
+We are currently able to annotate non-trivial programs, involving every
+sort of composite type available in the C language, e.g., arrays, structs,
+unions and pointers to these aggregates.
+Some of these programs, such as those taken from the
+Kastor~\cite{Virouleau14} or Bots~\cite{Duran09}
+benchmark suites, are large and complex; thus, their manual annotation is a
+time consuming and error prone task.
+Yet, our automatically annotated programs not only approximate the execution
+times of the parallel versions of those benchmarks, but are much faster than
+their sequential -- unannotated -- versions.
 

### 2017-10-31 docs/ACM/paper.tex

@@
 Programs]
-{Automatic Identification and Annotation of Parallel Tasks in Programs}
+{Automatic Identification and Annotation of Parallel Tasks in Structured Programs}
 
@@
 gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
-Yet, even if convenient, the use of annotations is not straightforward.
+Yet, even if convenient, the use of annotations is not straightforward, and
+lacks supporting tools.
 
 Annotations such as OpenMP or OpenACC still require developers to
-worry about typical hassles of the parallel world, such as race conditions,
+worry about typical hassles of the parallel world, such as race conditions
 or deadlocks.
@@
 Pingali~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
-We address this omission in this work.
+The goal of this work is to address this omission.
 
@@
 First, it find program regions, e.g., loops or functions, that can be
-effectively mapped onto tasks.
-Second, it determines symbolic bounds to all the memory blocks accesses within
-those regions.
+effectively mapped onto tasks (Section~\ref{sub:region}).
+Second, it determines symbolic bounds to all the memory blocks accessed within
+those regions (Section~\ref{sub:symb}).
 Third, it maps such information back into source code, producing annotations
-that programmers can read.
+that programmers can read (Section~\ref{sub:ir}).
 The goal of this paper is to describe the design and the implementation of these
@@
 times of the parallel versions of those benchmarks, but are much faster than
-their sequential -- unannotated -- versions.
+their sequential --unannotated-- versions, as we report in Section~\ref{sec:eval}.
 
@@
 
-%EXAMPLE - BFS
-
 \section{Solution}
 \label{sec:sol}
+
+\subsection{Mapping Program Regions to Tasks}
+\label{sub:region}
+
+\subsection{Find Symbolic Bounds of Arrays}
+\label{sub:symb}
+
+\subsection{From IR to Source Code}
+\label{sub:ir}
 

### 2017-11-05 docs/ACM/paper.tex
Adding references to Tareador.

@@
 Examples of such systems include OpenMP~\cite{JaegerCP15},
-OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10} and OpenSs~\cite{MeenderinckJ11}.
+OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
+OpenSs~\cite{MeenderinckJ11} and Tareador~\cite{Ayguade15}.
 Annotations work as a meta-language: they let developers grant parallel
@@
 There exist tools that insert automatic annotations in
-programs~\cite{gleison2016,Pingali11,wanggenerating}.
+programs~\cite{Mendonca16,Pingali11,Nugteren14}.
 All these technologies explore data-parallelism -- the possibility of running

### 2017-11-09 docs/ACM/paper.tex
Changes in the introduction.

@@
 OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
-OpenSs~\cite{MeenderinckJ11} and Tareador~\cite{Ayguade15}.
+OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
+Tareador~\cite{Ayguade15}.
 Annotations work as a meta-language: they let developers grant parallel
@@
 Such fact is unfortunate, because much of the power of current annotation
-systems lays on their ability to create tasks \ed{We need to find references!}.
+systems lays on their ability to create tasks~\cite{Ayguade09}.
 This ability brings said systems closer to irregular programs such as those
@@
 
-This paper describes \Taskminer, the first compiler that mines task parallelism
+This paper describes \Taskminer, a compiler that mines task parallelism
 from programs.
-To fulfill this goal \Taskminer{} solves three challenges.
-First, it find program regions, e.g., loops or functions, that can be
+To fulfill this goal \Taskminer{} solves many challenges.
+First, it finds program regions, e.g., loops or functions, that can be
 effectively mapped onto tasks (Section~\ref{sub:region}).
@@
 that programmers can read (Section~\ref{sub:ir}).
-The goal of this paper is to describe the design and the implementation of these
-three technologies, and to demonstrate their benefit.
+Fourth, it extracts parameters from the code to estimate the profitability of
+tasks, given the cost to create them.
+These parameters feed conditional checks, which, at runtime, enable or disable
+the creation of tasks (Section~\ref{sub:profit}).
+Finally, \Taskminer{} determines which program variables need to be replicated at
+each new task, or shared among them (Section~\ref{sub:variance}).
+This paper describes the design and the implementation of these technologies, and
+demonstrate their benefit.
 
@@
 
+% The ability to handle pointers through speculative parallelization.
+
+% when applied to general-purpose integer-intensive applications that have complex control flow and excessive pointer accesses, traditional parallelization tech- niques become quite ineffective, as they need to conservatively ensure program correctness by synchronizing all potential dependences in the program
+
+% For example in 473.astar if we ignore dependences that only occur in less than 20% of all iterations, we can parallelize loops that correspond to 96% of total execution.
+
 \section{Solution}
@@
 
-\subsection{Find Symbolic Bounds of Arrays}
+\subsection{Finding Symbolic Bounds of Arrays}
 \label{sub:symb}
 
-\subsection{From IR to Source Code}
+\subsection{Mapping IR onto Source Code}
 \label{sub:ir}
+
+\subsection{Estimating the Profitability of Tasks}
+\label{sub:ir}
+
+\subsection{Separating Private from Shared Variables}
+\label{sub:profit}
+
+\subsection{Mapping IR onto Source Code}
+\label{sub:variance}
 
@@
 
+% Talk about annotations vs libraries, e.g., Wool, Intel TBB. See: "A Comparison of some recent Task-based Parallel Programming Models"
+
 \section{Conclusion}

### 2017-11-17 docs/ACM/paper.tex
Adding examples to section 2.
Discussing the challenges.

@@
 \usepackage{hyperref}
+\usepackage{amsmath}
 
@@
 \newcommand\Taskminer{\mbox{\textsf{TaskMiner}}}
+
+\newtheorem{Challenge}{Challenge}[section]
 
@@
 First, it finds program regions, e.g., loops or functions, that can be
-effectively mapped onto tasks (Section~\ref{sub:region}).
+effectively mapped onto tasks (Section~\ref{sub:identification}).
 Second, it determines symbolic bounds to all the memory blocks accessed within
@@
 
+The automatic insertion of effective OpenMP annotations into C/C++ programs
+required us to deal with a number of challenges.
+If left unsolved, these challenges would restrict our interventions in programs
+to very trivial annotations, which would hardly be of any use.
+In the rest of this section, we discuss the most important challenges, using
+this discussion as a motivation to the developments that follow in
+Section~\ref{sec:sol}.
+
+\begin{Challenge}
+\label{ch:Regions}
+Identify the memory region covered by a task.
+\end{Challenge}
+
+Figure~\ref{fig:ex_Regions} illustrates Challenge~\ref{ch:Regions}, and shows
+how we solve it~\footnote{Figures~\ref{fig:ex_Regions}-\ref{fig:ex_cutoff} shows
+programs that we have annotated without any human intervention.
+Statements in black font are part of the original program.
+Annotations appear in grey.}.
+That program receives an $\mathsf{M}\times\mathsf{N}$ matrix \textsf{V}, in
+linearized format, and produces a vector \textsf{U}, so that \textsf{U[i]}
+contains the sum of all the elements in line \textsf{i} of matrix \textsf{V}.
+For reasons that will be made more clear in Section~\ref{sub:identification},
+our static analysis determines that each iteration of the outermost loops
+could be made into a task.
+Thus, tasks comprise the innermost loop, and traverse the memory region
+between addresses $\textsf{\&V + i * N}$ and $\textsf{\&V + i * N + M}$.
+The identification of such ranges involves the use of a symbolic algebra,
+which we have borrowed from the compiler-related literature, as we
+explain in Section~\ref{sub:symb}.
+Figure~\ref{fig:ex_Regions} also lets us introduce the second challenge that we
+tackle in this paper:
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.95\columnwidth]{images/ex_Regions}
+\caption{Write caption here.}
+\label{fig:ex_Regions}
+\end{center}
+\end{figure}
+
+\begin{Challenge}
+\label{ch:cost}
+Estimate the profitability of tasks at runtime.
+\end{Challenge}
+
+The creation of tasks involves a non-negligible runtime cost, which includes
+the allocation of resources, and the scheduling of the task proper.
+Ideally, this cost should be paid only when the task performs an amount of
+work that is sufficiently large to pay for its management cost.
+Being an interesting program property, on Rice's sense~\cite{Rice53}, the amount
+of work performed by a task cannot be discovered statically.
+However, we can try to approximate this quantity, using, to this end, program
+symbols, which are replaced with actual values at runtime.
+For instance, in Figure~\ref{fig:ex_Regions}, we know that the body of the
+innermost loop is formed by five instructions.
+Thus, we approximate the amount of work performed by a task with the
+expression \textsf{5 * M}.
+We use the runtime value of \textsf{M} to determine, during the execution of the
+program, if we create a task, or not.
+Such test is carried out by the guard at line 7 of the figure, which is part of
+OpenMP's syntax.
+
+\begin{Challenge}
+\label{ch:cutoff}
+Bound the creation of recursive tasks.
+\end{Challenge}
+
+To introduce Challenge~\ref{ch:cutoff}, we quote Duran {\em et al.}:
+``{\em In task parallel languages, an important factor for achieving a good
+performance is the use of a cut-off technique to reduce the number of tasks
+created}"~\cite{Duran08}.
+This observation is particularly true in the context of recursive, fine-grain,
+tasks.
+Figure~\ref{fig:ex_cutoff} provides such an example.
+To place a limit on the number of tasks simultaneously in flight, we associate
+the invocation of recursive functions annotated with task pragmas with a
+counter -- \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:cutoff}.
+The guard in line 7 ensures that we never exceed \textsf{DEPTH\_CUTOFF}, a
+predetermined threshold.
+The code generation algorithms that we discuss in this paper are
+parameterized by constants such as \textsf{DEPTH\_CUTOFF}, or
+\textsf{WORK\_CUTOFF} in Figure~\ref{fig:ex_Regions}.
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.95\columnwidth]{images/ex_cutoff}
+\caption{Write caption here.}
+\label{fig:ex_cutoff}
+\end{center}
+\end{figure}
+
+\begin{Challenge}
+\label{ch:privatize}
+Identify private and shared variables.
+\end{Challenge}
+
+The two previous challenges are related to the performance of annotated
+programs: if left unsolved, we shall have correct, albeit inefficient programs.
+Challenges~\ref{ch:Regions}, and~\ref{ch:privatize}, on the other hand, are
+related to correctness.
+Challenge~\ref{ch:privatize} asks for the identification of variables that
+must be replicated among threads.
+This process of replication is called {\em privatization}.
+As an example, variable \textsf{j} in Figure~\ref{fig:ex_privatize} must
+be privatized.
+In the absence of such action, that variable will be shared among all the
+tasks created at line 5 of Figure~\ref{fig:ex_privatize}.
+Because \textsf{j} is writte within these tasks, race conditions would
+ensue.
+In Section~\ref{sub:variance} we explain how we separate private from
+shared variables.
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=1\columnwidth]{images/ex_privatize}
+\caption{Write caption here.}
+\label{fig:ex_privatize}
+\end{center}
+\end{figure}
+
 % The ability to handle pointers through speculative parallelization.
@@
 \subsection{Mapping Program Regions to Tasks}
-\label{sub:region}
+\label{sub:identification}
 
@@
 \subsection{Estimating the Profitability of Tasks}
-\label{sub:ir}
+\label{sub:profit}
 
 \subsection{Separating Private from Shared Variables}
-\label{sub:profit}
-
-\subsection{Mapping IR onto Source Code}
 \label{sub:variance}

### 2017-11-17 docs/ACM/paper.tex
Fixing one tiny typo.

@@
 the invocation of recursive functions annotated with task pragmas with a
-counter -- \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:cutoff}.
+counter -- \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:ex_cutoff}.
 The guard in line 7 ensures that we never exceed \textsf{DEPTH\_CUTOFF}, a

### 2017-11-17 docs/ACM/paper.tex
Discussion about challenges.

@@
 If left unsolved, these challenges would restrict our interventions in programs
-to very trivial annotations, which would hardly be of any use.
+to trivial annotations, which would hardly be of any use.
 In the rest of this section, we discuss the most important challenges, using
@@
 Figure~\ref{fig:ex_Regions} illustrates Challenge~\ref{ch:Regions}, and shows
-how we solve it~\footnote{Figures~\ref{fig:ex_Regions}-\ref{fig:ex_cutoff} shows
+how we solve it\footnote{Figures~\ref{fig:ex_Regions}-\ref{fig:ex_cutoff} shows
 programs that we have annotated without any human intervention.
@@
 contains the sum of all the elements in line \textsf{i} of matrix \textsf{V}.
-For reasons that will be made more clear in Section~\ref{sub:identification},
+For reasons to be considered in Section~\ref{sub:identification},
 our static analysis determines that each iteration of the outermost loops
@@
 explain in Section~\ref{sub:symb}.
-Figure~\ref{fig:ex_Regions} also lets us introduce the second challenge that we
-tackle in this paper:
+Figure~\ref{fig:ex_Regions} also introduces the second challenge that we
+tackle:
 
@@
 
-The creation of tasks involves a non-negligible runtime cost, which includes
-the allocation of resources, and the scheduling of the task proper.
-Ideally, this cost should be paid only when the task performs an amount of
-work that is sufficiently large to pay for its management cost.
+The creation of tasks involves a non-negligible runtime cost due to allocation and
+scheduling of resources.
+Ideally, this cost should be paid only for tasks that perform an amount of work
+sufficiently large to pay for their management.
 Being an interesting program property, on Rice's sense~\cite{Rice53}, the amount
 of work performed by a task cannot be discovered statically.
-However, we can try to approximate this quantity, using, to this end, program
-symbols, which are replaced with actual values at runtime.
+As we show in Section~\ref{sub:profit}, we can try to approximate this quantity, using,
+to this end, program symbols, which are replaced with actual values at runtime.
 For instance, in Figure~\ref{fig:ex_Regions}, we know that the body of the
@@
 
-To introduce Challenge~\ref{ch:cutoff}, we quote Duran {\em et al.}:
+We introduce Challenge~\ref{ch:cutoff} by quoting Duran {\em et al.}:
 ``{\em In task parallel languages, an important factor for achieving a good
@@
 This observation is particularly true in the context of recursive, fine-grain,
-tasks.
+tasks, as we analyze in Section~\ref{sub:rec}.
 Figure~\ref{fig:ex_cutoff} provides such an example.
@@
 predetermined threshold.
-The code generation algorithms that we discuss in this paper are
+This example, together with Figure~\ref{fig:ex_Regions}, lets us emphasize that
+the code generation algorithms presented in this paper are
 parameterized by constants such as \textsf{DEPTH\_CUTOFF}, or
@@
 programs: if left unsolved, we shall have correct, albeit inefficient programs.
-Challenges~\ref{ch:Regions}, and~\ref{ch:privatize}, on the other hand, are
+Challenges~\ref{ch:Regions}, and~\ref{ch:privatize}, in turn, are
 related to correctness.
@@
 tasks created at line 5 of Figure~\ref{fig:ex_privatize}.
-Because \textsf{j} is writte within these tasks, race conditions would
+Because \textsf{j} is written within these tasks, race conditions would
 ensue.
-In Section~\ref{sub:variance} we explain how we separate private from
+Section~\ref{sub:variance} explains how we separate private and
 shared variables.
@@
 
-\subsection{Mapping IR onto Source Code}
-\label{sub:ir}
-
 \subsection{Estimating the Profitability of Tasks}
@@
 
+\subsection{Limiting the Creation of Recursive Tasks}
+\label{sub:rec}
+
 \subsection{Separating Private from Shared Variables}
 \label{sub:variance}
+
+\subsection{Mapping IR onto Source Code}
+\label{sub:ir}
 
@@
 We aimed to show that our tool exceeded in three main aspects that surround parallel programming. Thus our work evaluation stands on these 3 pillars:
+
+% In section 4.
+“Evaluation", subsection “Performance"; you state the only reason why programmers will strive for parallelism would be to achieve higher performance (faster program execution).
+I do not fully agree, and I believe we discussed that point earlier.
+There may be cases where performance of a single big core would be good enough to meet some target schedule (either response time or frame rate, etc.) still you may want to explore parallel versions of the code running on a cluster of smaller cores or a combination of a slow CPU and GPU to achieve better power efficiency.
+
+% I believe this paper could be made stronger by also investigating the impact of power efficiency as a component of the cost function - if one looks at the latest processor chips from Intel and AMD, I can (finally) see there is a trend to increase the number of cores for all platforms.
+
+% In the past there has been not much opportunity to take advantage of parallelism on 2 core platforms (especially notebook designs used to limit the number of real cores), but with 6 or 8 core processors entering the main stream, we may take advantage of running more processors slower (lower voltage) or spreading out the workload over a larger die area.
+It is quite interesting to note that running one core hot will increase the leakage in that area of the die much more (exponentially with temperature), so distributing work over a larger die area results in reduced leakage - having said that, a similar effect can be achieved by migrating the workload from core to core.
 

### 2017-11-17 docs/ACM/paper.tex
Adding an abstract to the paper.

@@
 %% Supplied to authors by publisher for camera-ready submission
-\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
+\acmConference[PL'17]{IEEE}{2018}{Planet Earh}
 \acmYear{2017}
@@
 \begin{abstract}
-We need to write our abstract here.
+This paper reports the design and implementation of a suit of static analysis
+and code generation techniques to annotate programs with OpenMP pragmas for
+task parallelism.
+These techniques deal with problems such as the discovery and use of program
+symbols to estimate the profit of tasks, bound their recursive depth and limit
+the memory regions onto which they operate.
+These techniques have been implemented into the first source-to-source
+compiler able to insert OpenMP pragmas into C/C++ programs without human
+intervention.
+By building onto the solid collection of static analyses available in LLVM,
+and relying on OpenMP's runtime ability to disambiguate pointers, we show that
+we can annotate large and convoluted programs, often replicating the performance
+gains of handmade annotation.
 \end{abstract}
@@
 semantics to syntax originally written to execute sequentially.
-The compiler-related literature contains a generous load of success stories
-describing the use of annotation systems to parallelize programs.
+%The compiler-related literature contains a generous load of success stories
+%describing the use of annotation systems to parallelize programs.
 Combined with modern accelerators, they have led to substantial performance
@@
 There exist tools that insert automatic annotations in
-programs~\cite{Mendonca16,Pingali11,Nugteren14}.
+programs~\cite{Amini12,Guelton12,Mendonca16,Pingali11,Nugteren14}.
 All these technologies explore data-parallelism -- the possibility of running
@@
 those regions (Section~\ref{sub:symb}).
-Third, it maps such information back into source code, producing annotations
-that programmers can read (Section~\ref{sub:ir}).
-Fourth, it extracts parameters from the code to estimate the profitability of
+Third, it extracts parameters from the code to estimate the profitability of
 tasks, given the cost to create them.
 These parameters feed conditional checks, which, at runtime, enable or disable
-the creation of tasks (Section~\ref{sub:profit}).
-Finally, \Taskminer{} determines which program variables need to be replicated at
+the creation of tasks (Section~\ref{sub:profit}) and limit their recursion
+depth (Section~\ref{sub:rec}).
+Additionally, \Taskminer{} determines which program variables need to be replicated at
 each new task, or shared among them (Section~\ref{sub:variance}).
+Finally, it maps all this information back into source code, producing annotations
+that programmers can read (Section~\ref{sub:ir}).
 This paper describes the design and the implementation of these technologies, and
@@
 \includegraphics[width=0.95\columnwidth]{images/ex_Regions}
-\caption{Write caption here.}
+\caption{Challenges~\ref{ch:Regions} and~\ref{ch:cost}: identifying memory regions
+with symbolic limits, and using runtime information to estimate the profit of
+tasks.}
 \label{fig:ex_Regions}
@@
 \includegraphics[width=0.95\columnwidth]{images/ex_cutoff}
-\caption{Write caption here.}
+\caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks with
+counter associated with function calls.}
 \label{fig:ex_cutoff}
@@
 \includegraphics[width=1\columnwidth]{images/ex_privatize}
-\caption{Write caption here.}
+\caption{Challenge~\ref{ch:privatize}: variable \textsf{j} must be replicated among
+tasks, to avoid the occurrence of data races.}
 \label{fig:ex_privatize}
@@
 
-We aimed to show that our tool exceeded in three main aspects that surround parallel programming. Thus our work evaluation stands on these 3 pillars:
+%We aimed to show that our tool exceeded in three main aspects that surround parallel programming. Thus our work evaluation stands on these 3 pillars:
 
@@
 
-\begin{itemize}
+%\begin{itemize}
 
-\item Practicality
-\item Applicability
-\item Performance
+%\item Practicality
+%\item Applicability
+%\item Performance
 
-\end{itemize}
+%\end{itemize}
 
-\textbf{\textit{Practicality}}.
+%\textbf{\textit{Practicality}}.
 Programming in a parallel pattern is deemed difficult by programmers mainly because of the complexity of its data structures and algorithms.
@@
 
-\textbf{\textit{Applicability}}.
+%\textbf{\textit{Applicability}}.
 
-\textbf{\textit{Performance}}.
+%\textbf{\textit{Performance}}.
 When it comes to parallel computing, it is undeniable that the main achievable goal should be performance.

### 2017-11-20 docs/ACM/paper.tex
added a few lines in paper section 2

@@
 \begin{abstract}
-This paper reports the design and implementation of a suit of static analysis
+This paper reports the design and implementation of a suit of static analyses
 and code generation techniques to annotate programs with OpenMP pragmas for
@@
 Annotation systems have risen to a place of prominence as a simple and
-effective way to write parallel programs.
+effective means to write parallel programs.
 Examples of such systems include OpenMP~\cite{JaegerCP15},
@@
 gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
-Yet, even if convenient, the use of annotations is not straightforward, and
-lacks supporting tools.
+Nevertheless, although convenient, the use of annotations is not straightforward, and
+still lacks supporting tools.
+%replaced:
+%Yet, even if convenient,
 
@@
 worry about typical hassles of the parallel world, such as race conditions
-or deadlocks.
+and deadlocks.
 Moreover, because they are used in tandem with imperative programming languages,
@@
 the same computation independently on different data.
-Task parallelism remains still uncharted land, in what concerns automatic
+Thus, task parallelism remains still uncharted land in what concerns automatic
 annotation.
-Such fact is unfortunate, because much of the power of current annotation
+Such fact is unfortunate, since much of the power of current annotation
 systems lays on their ability to create tasks~\cite{Ayguade09}.
@@
 Pingali~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
-The goal of this work is to address this omission.
+The purpose of this work is to address this omission.
 
@@
 from programs.
-To fulfill this goal \Taskminer{} solves many challenges.
+In order to fulfil this goal, \Taskminer{} solves many challenges.
 First, it finds program regions, e.g., loops or functions, that can be
@@
 that programmers can read (Section~\ref{sub:ir}).
-This paper describes the design and the implementation of these technologies, and
-demonstrate their benefit.
+This work demonstrates the design and the implementation of these technologies, 
+as well as their benefit.
 
-Such benefit is performance and readability.
+The major benefit provided by \Taskminer is, essentially, performance and readability.
 \Taskminer{} receives as input a C program, and produces, as output, a C
-program annotated with OpenMP directives that identify tasks.
+program annotated with OpenMP directives that enclose potential tasks.
 We are currently able to annotate non-trivial programs, involving every
@@
 Section~\ref{sec:sol}.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.95\columnwidth]{images/ex_Regions}
+\caption{Challenges~\ref{ch:Regions} and~\ref{ch:cost}: identifying memory regions
+with symbolic limits, and using runtime information to estimate the profit of
+tasks.}
+\label{fig:ex_Regions}
+\end{center}
+\end{figure}
 
@@
 
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=0.95\columnwidth]{images/ex_Regions}
-\caption{Challenges~\ref{ch:Regions} and~\ref{ch:cost}: identifying memory regions
-with symbolic limits, and using runtime information to estimate the profit of
-tasks.}
-\label{fig:ex_Regions}
-\end{center}
-\end{figure}
-
 \begin{Challenge}
@@
 
-The creation of tasks involves a non-negligible runtime cost due to allocation and
-scheduling of resources.
+The creation of tasks involves a non-negligible runtime cost due to allocation,
+scheduling of resources and real-time management of the task dependence graph.
 Ideally, this cost should be paid only for tasks that perform an amount of work
@@
 Such test is carried out by the guard at line 7 of the figure, which is part of
-OpenMP's syntax.
+OpenMP's syntax. Also, we provide a reliable estimate on the \emph{workload cutoff}
+from which a task can be safely spawned without producing performance overhead.
+This \emph{cutoff} considers factors such as number of available cores
+and runtime information on the task dispatch cost in terms of machine
+instructions. This is further explained in Section \ref{sub:profit}.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.95\columnwidth]{images/ex_cutoff}
+\caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks with
+counter associated with function calls.}
+\label{fig:ex_cutoff}
+\end{center}
+\end{figure}
 
@@
 tasks, as we analyze in Section~\ref{sub:rec}.
-Figure~\ref{fig:ex_cutoff} provides such an example.
+Figure~\ref{fig:ex_cutoff} provides an example.
 To place a limit on the number of tasks simultaneously in flight, we associate
@@
 parameterized by constants such as \textsf{DEPTH\_CUTOFF}, or
-\textsf{WORK\_CUTOFF} in Figure~\ref{fig:ex_Regions}.
+\textsf{WORK\_CUTOFF} in Figure~\ref{fig:ex_Regions}. Although these
+have default estimates, we provide them as parameters to be set at will.
 
-\begin{figure}[t!]
+\begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.95\columnwidth]{images/ex_cutoff}
-\caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks with
-counter associated with function calls.}
-\label{fig:ex_cutoff}
+\includegraphics[width=1\columnwidth]{images/ex_privatize}
+\caption{Challenge~\ref{ch:privatize}: variable \textsf{j} must be replicated among
+tasks, to avoid the occurrence of data races.}
+\label{fig:ex_privatize}
 \end{center}
@@
 ensue.
-Section~\ref{sub:variance} explains how we separate private and
+Section~\ref{sub:variance} explains how we distinguish private from
 shared variables.
-
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=1\columnwidth]{images/ex_privatize}
-\caption{Challenge~\ref{ch:privatize}: variable \textsf{j} must be replicated among
-tasks, to avoid the occurrence of data races.}
-\label{fig:ex_privatize}
-\end{center}
-\end{figure}
 

### 2017-12-06 docs/ACM/paper.tex
Adding Section 2.1 to the paper.

@@
 
-This paper describes \Taskminer, a compiler that mines task parallelism
-from programs.
-In order to fulfil this goal, \Taskminer{} solves many challenges.
+This paper describes \Taskminer, a source-to-source compiler that exposes task
+parallelism in C/C++ programs.
+To fulfil this goal, \Taskminer{} solves different challenges.
 First, it finds program regions, e.g., loops or functions, that can be
 effectively mapped onto tasks (Section~\ref{sub:identification}).
-Second, it determines symbolic bounds to all the memory blocks accessed within
+Second, it determines symbolic bounds to the memory blocks accessed within
 those regions (Section~\ref{sub:symb}).
-Third, it extracts parameters from the code to estimate the profitability of
-tasks, given the cost to create them.
+Third, it extracts parameters from the code to estimate when it is profitable to
+create tasks.
 These parameters feed conditional checks, which, at runtime, enable or disable
@@
 depth (Section~\ref{sub:rec}).
-Additionally, \Taskminer{} determines which program variables need to be replicated at
-each new task, or shared among them (Section~\ref{sub:variance}).
-Finally, it maps all this information back into source code, producing annotations
-that programmers can read (Section~\ref{sub:ir}).
-This work demonstrates the design and the implementation of these technologies, 
-as well as their benefit.
+Fourth, \Taskminer{} determines which program variables need to be 
+replicated in new tasks, or shared among them (Section~\ref{sub:variance}).
+Finally, it maps all this information back into source code, producing
+readable annotations (Section~\ref{sub:ir}).
 
@@
 
-\section{Overview}
+\section{Advantages and Difficulties}
 \label{sec:ovf}
+
+The use of OpenMP pragmas as the concrete means to explore, without human
+intervention, task parallelism in programs presents difficulties and
+advantages.
+Such challenges and benefits have guided the design and implementation of the
+techniques that we discuss in Section~\ref{sec:sol}.
+In the rest of this section, we discuss them.
+
+\subsection{The Advantages}
+\label{sub:adv}
+
+The main advantage of using OpenMP to split a program into parallel tasks is
+its runtime.
+This runtime lets us circumvent the shortcomings that pointer aliasing
+impose on the automatic parallelization of code.
+Aliasing -- the possibility of two pointers dereferencing the same
+memory region -- either prevents parallelism altogether, or forces compilers to
+resort to complex runtime checks to identify it
+dynamically~\cite{Alves15,Rus02}.
+The OpenMP runtime shields us from having to implement such checks, because
+it already checks for dependencies among tasks, and dispatches them in a
+correct order~\cite{LaGrone11}.
+An OpenMP task descriptor contains the task's status (running, waiting) and a
+list of memory addresses the task registered as input arguments.
+
+The process of checking for dependencies can be as simple as checking if an
+incoming task in the system accesses a memory address already in use by a
+previous task in flight.
+It can also be complex, involving checks over long ranges of addresses
+(in case the runtime system supports dependence checking for memory ranges).
+This process can also include memory labelling and renaming (in case the
+runtime system is able to remove false dependencies).
+Regardless of its capacity -- which is not the same across every OpenMP
+implementation -- the runtime system will represent dependencies using a task
+dependence graph (TDG)~\cite{Duran08}.
+In this directed acyclic graph, nodes denote tasks and edges represent
+dependences between them.
+Tasks are dispatched for execution according to a topological ordering of this
+graph~\cite{Planas15}.
+
+This runtime support allows the parallelization of irregular applications,
+such as programs that traverse data-structures formed by a mesh of pointers.
+As an example, Figure~\ref{fig:book_filter} shows an application that
+finds patterns in lines of a book.
+The book is given as an array of pointers; each pointer leads to a
+string representing a --potentially-- different line.
+The natural parallelization of this program consists in firing off a task
+to process each line.
+Figure~\ref{fig:book_filter} has been annotated automatically by the \Taskminer.
+We emphasize that neither the runtime checks of Alves
+{\em et al.}~\cite{Alves15} or Rus {\em et al.}~\cite{Rus02}, nor a
+context and flow sensitive alias analysis, \`{a} la Whaley and
+Lam~\cite{Whaley04} would be able to ensure the automatic parallelization of
+this program.
+
+\subsection{The Difficulties}
+\label{sub:dif}
 
@@
 to trivial annotations, which would hardly be of any use.
-In the rest of this section, we discuss the most important challenges, using
-this discussion as a motivation to the developments that follow in
-Section~\ref{sec:sol}.
+Our first challenge is inherent to any automatic parallelization system.
 
@@
 performance is the use of a cut-off technique to reduce the number of tasks
-created}"~\cite{Duran08}.
+created}"~\cite{Duran08b}.
 This observation is particularly true in the context of recursive, fine-grain,

### 2017-12-06 docs/ACM/paper.tex
Working a bit further on Section 2.

@@
 memory region -- either prevents parallelism altogether, or forces compilers to
-resort to complex runtime checks to identify it
-dynamically~\cite{Alves15,Rus02}.
-The OpenMP runtime shields us from having to implement such checks, because
+resort to complex runtime checks to ensure its correctness~\cite{Alves15,Rus02}.
+The OpenMP runtime shields us from this problem, because
 it already checks for dependencies among tasks, and dispatches them in a
@@
 The process of checking for dependencies can be as simple as checking if an
-incoming task in the system accesses a memory address already in use by a
-previous task in flight.
+incoming task accesses a memory address already in use by a task in flight.
 It can also be complex, involving checks over long ranges of addresses
@@
 
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/ex_book_filter}
+\caption{The benefits of the OpenMP runtime environment.
+Neither the runtime checks of Alves~\cite{Alves15} or Rus~\cite{Rus02}, nor
+Whaley's context and flow sensitive alias analysis would be able to ensure the
+correctness of the automatic parallelization of this program.}
+\label{fig:ex_book_filter}
+\end{center}
+\end{figure}
+
 This runtime support allows the parallelization of irregular applications,
 such as programs that traverse data-structures formed by a mesh of pointers.
-As an example, Figure~\ref{fig:book_filter} shows an application that
+As an example, Figure~\ref{fig:ex_book_filter} shows an application that
 finds patterns in lines of a book.
@@
 to process each line.
-Figure~\ref{fig:book_filter} has been annotated automatically by the \Taskminer.
-We emphasize that neither the runtime checks of Alves
-{\em et al.}~\cite{Alves15} or Rus {\em et al.}~\cite{Rus02}, nor a
-context and flow sensitive alias analysis, \`{a} la Whaley and
-Lam~\cite{Whaley04} would be able to ensure the automatic parallelization of
-this program.
+Figure~\ref{fig:ex_book_filter} has been annotated automatically by the
+\Taskminer.
+The OpenMP execution environment ensures the correct scheduling of the tasks
+created at lines 9 and 11, through runtime checks.
+Therefore, the ability to disambiguate memory regions statically is not
+essential for correctness, although it is important for efficiency reasons,
+as we will mention in Challenge~\ref{ch:Regions}.
 
@@
 
-The creation of tasks involves a non-negligible runtime cost due to allocation,
-scheduling of resources and real-time management of the task dependence graph.
+The creation of tasks involves a heavy runtime cost due to allocation,
+scheduling and real-time management of the task dependence graph.
 Ideally, this cost should be paid only for tasks that perform an amount of work
@@
 \begin{center}
-\includegraphics[width=0.95\columnwidth]{images/ex_cutoff}
+\includegraphics[width=0.9\columnwidth]{images/ex_cutoff}
 \caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks with

### 2017-12-10 docs/ACM/paper.tex
Guido's pass 2

@@
 %describing the use of annotation systems to parallelize programs.
+\guido{What do you mean by modern accelerators? Not clear.}
 Combined with modern accelerators, they have led to substantial performance
 gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
+\guido{Suppport what?}
 Nevertheless, although convenient, the use of annotations is not straightforward, and
-still lacks supporting tools.
+still lacks supporting tools \new{that can help programmers check if the annotation is
+correct or effective}.
 %replaced:
@@
 Thus, task parallelism remains still uncharted land in what concerns automatic
-annotation.
-Such fact is unfortunate, since much of the power of current annotation
+annotation. Such fact is unfortunate, since much of the power of current annotation
 systems lays on their ability to create tasks~\cite{Ayguade09}.
+\guido{Why the ability to create tasks makes such programs similar to irregular code?
+Which features of irregular code are resposible for such similarities? Not clear to the 
+reader}
 This ability brings said systems closer to irregular programs such as those
@@
 Fourth, \Taskminer{} determines which program variables need to be 
-replicated in new tasks, or shared among them (Section~\ref{sub:variance}).
+\rmv{replicated} \new{privatized}  in new tasks, or shared among them (Section~\ref{sub:variance}).
 Finally, it maps all this information back into source code, producing
@@
 
-The major benefit provided by \Taskminer is, essentially, performance and readability.
+\guido{How about saving programmer's time by doing automatic annotation?}
+The major \ed{benefits provided by \Taskminer are, essentially, performance and readability.}
 \Taskminer{} receives as input a C program, and produces, as output, a C
@@
 times of the parallel versions of those benchmarks, but are much faster than
+\guido{Revisit later if necessary}
 their sequential --unannotated-- versions, as we report in Section~\ref{sec:eval}.
@@
 Such challenges and benefits have guided the design and implementation of the
-techniques that we discuss in Section~\ref{sec:sol}.
-In the rest of this section, we discuss them.
+techniques \rmv{that we discuss} \new{described in} ection~\ref{sec:sol}.
+\guido{The techniques or the advantages/difficulties? Ambiguous.} 
+In the rest of this section \ed{we discuss such advantage and difficulties.}
 
@@
 
-The main advantage of using OpenMP to split a program into parallel tasks is
-its runtime.
-This runtime lets us circumvent the shortcomings that pointer aliasing
+\guido{The runtime is a consequence; the main advantage is the possibility of leaving to a
+runtime the task of handling dependences dynamically.} 
+The main advantage of using OpenMP \new{annotations} to split a program into parallel tasks is
+\new{the ability  of leaving the job of  handling dependences to a runtime.}
+\new{The OpenMP runtime maintains a task dependence graph which dynamically exposes more parallelism 
+opportunities than those resulting from a conservative  compile-time  analysis.}
+\new{In particular, the} runtime lets us circumvent the shortcomings that pointer aliasing
 impose on the automatic parallelization of code.
@@
 it already checks for dependencies among tasks, and dispatches them in a
-correct order~\cite{LaGrone11}.
-An OpenMP task descriptor contains the task's status (running, waiting) and a
-list of memory addresses the task registered as input arguments.
+correct order~\cite{LaGrone11}. \ed{To achieve that, OpenMP runtime uses task descriptors that contain}
+\guido{The descriptor does not keep task status; this is done in the runtime.}
+\rmv{task's status (running, waiting)} \ed{a task identifier and  a list of memory addresses corresponding to the task input /output arguments.}
 
 The process of checking for dependencies can be as simple as checking if an
-incoming task accesses a memory address already in use by a task in flight.
+incoming task accesses a memory address already in use by \ed{an in-flight task}.
 It can also be complex, involving checks over long ranges of addresses
@@
 dependences between them.
-Tasks are dispatched for execution according to a topological ordering of this
+Tasks are dispatched for execution according to a \new{dynamic} topological ordering of this
 graph~\cite{Planas15}.
@@
 
-This runtime support allows the parallelization of irregular applications,
+\guido{Now it is clear the relevance for irregular programs.}
+\ed{The OpenMP runtime} support allows the parallelization of irregular applications,
 such as programs that traverse data-structures formed by a mesh of pointers.
+\guido{A litte bit more details: }
+\new{In such programs, control construcs (e.g. {\tt if} statement) make the execution 
+of certain pieces of code  dependent on the program input. When using 
+task parallelism the runtime can capture such dependences. This is not possible 
+otherwise, since compile-time dependence analyzers must be conservative and eventually
+skip some parallelization opportunity.}
+
 As an example, Figure~\ref{fig:ex_book_filter} shows an application that
@@
 to process each line.
-Figure~\ref{fig:ex_book_filter} has been annotated automatically by the
+Figure~\ref{fig:ex_book_filter} has been annotated automatically by \rmv{the}
 \Taskminer.
 The OpenMP execution environment ensures the correct scheduling of the tasks
-created at lines 9 and 11, through runtime checks.
+created at lines 9 and 11, \ed{by}  \guido{This is vague:} \rmv{runtime checks.} 
+\new{assuring that the annotated input dependencies {\tt line} and {\tt pattern}  are 
+respected at runtime.}
+\guido{Not clear. Need more details here. Adding:} \new{Pointer-based dependencies
+can address various memory regions. Hence, in order to enable the automatic
+synthesis of task annotations a system must be able to precisely define which 
+memory region a pointer dependency is pointing to.}
+\guido{Not clear why it is not important for correctness.}
 Therefore, the ability to disambiguate memory regions statically is not

### 2018-01-08 Task.cpp
Added support for Privatization

@@ -90,6 +90,11 @@ bool Task::hasLoadInstructionInDependence() const
 	return false;
 }
 
+bool Task::resolvePrivateValues()
+{
+
+}
+
 FunctionCallTask::FunctionCallTask(CallInst* CI)
 	: Task(FCALL_TASK)
 	, functionCall(CI)

### 2018-01-08 Task.h

@@ -15,6 +15,7 @@
 
 #include <set>
 #include <stack>
+#include <list>
 
 namespace llvm
 {
@@ -45,16 +46,19 @@ namespace llvm
 			{}
 		virtual ~Task() {};
 		
-		//Getters
+		//Getters & Setters
 		TaskKind getKind() const { return kind; }
 		std::set<Value*> getLiveIN() const;
 		std::set<Value*> getLiveOUT() const;
 		std::set<Value*> getLiveINOUT() const;
 		std::set<BasicBlock*> getbbs() const;
 		CostModel getCost() const { return CM; }
+		std::list<Value*> getPrivateValues() { return privateValues; };
+		void addPrivateValue(Value* V) { privateValues.push_back(V); };
 
 		//Methods
 		virtual bool resolveInsAndOutsSets() { return false; }
+		bool resolvePrivateValues();
 		virtual CostModel computeCost() { return CM; }
 		void addBasicBlock(BasicBlock* bb) { bbs.insert(bb); }
 		bool hasLoadInstructionInDependence() const;
@@ -66,6 +70,7 @@ namespace llvm
 
 	private:
 		const TaskKind kind;
+		std::list<Value*> privateValues;
 
 	protected:
 		//Cost model
@@ -107,7 +112,7 @@ namespace llvm
 	public:
 		RegionTask() 
 			: Task(REGION_TASK)
-			{}
+			{ level = 0; }
 		~RegionTask() {}
 		bool resolveInsAndOutsSets() override;
 		CostModel computeCost() override;
@@ -117,6 +122,7 @@ namespace llvm
 		BasicBlock* getHeaderBB() { return header; };
 
 	private:
+		int level;
 		BasicBlock* header;
 	};
 

### 2018-01-08 docs/ACM/code/algorithm.py

@@ -13,14 +13,13 @@ def minetasks(P):
 	CFG = ControlFlowGraph(P) # O(N^2)
 	PDG = ProgramDependenceGraph(P)	# O(N^2)
 	H = findHelices(PDG);	# O(N^2)
-	REGIONS = []
 	TASKREGIONS = []
 	for h in H:	# O(N^2)
 		reg = CFG.findMinimalCoveringRegion(h)
-		REGIONS.append(reg)
-	for r in REGIONS: # O(N^2)
-		while (r.expand(1)):
-			TASKREGIONS.append(r)
+		TASKREGIONS.append(reg)
+	for r in TASKREGIONS: # O(N^3)
+		r.expand();
+
 	ANN = Annotator()														
 	NEW_PROGRAM = ANN.annotate(P, TASKREGIONS) # O(N^2)
 
@@ -93,33 +92,24 @@ class Region:
 
 	# Expansion of one level is O(N)
 	def expand(self):
-		self.basicblocks.append(f()) # add new basic blocks to the list
-		self.resolveDependencies()
-
-		return self.checkExpansion()
-
-	def resolveDependencies(self):
-		return f() # resolve dependencies for a given set of basic blocks
-
-	# Expansion of N levels is O(N^2)
-	def expand(self, n_levels):
-		while (n_levels > 0):
-			if (not self.expand()):
-				break
+		canExpand = True
+		while (canExpand):
+			self.basicblocks.append(f()) # add new basic blocks to the list
+			self.resolveDependencies()
 			self.level += 1
-			n_levels -= 1
-
-		return self.checkExpansion()
+			canExpand = self.checkExpansion()
 
 	# it checks:
 		# - if two tasks have merged O(N) 
 		# - if dependencies have been conserved or reduced O(1)
 		# - if parallelism has not decreased O(1)
-
 	# it also does:
 		# - privatization analysis O(N)
 	def checkExpansion(self):
 		return f()  
+
+	def resolveDependencies(self):
+		return f() # resolve dependencies for a given set of basic blocks
 
 # I don'w know much about the annotator. 
 # I know it receives a program and generates 

### 2018-01-08 tests/benchmarks/toys/private/priv.c

@@ -4,7 +4,7 @@
 int sum_range(int* V, int N, int L, int U, int* A)
 {
 	int i=0, sum=0;
-	while (i < N)
+	for (i = 0; i < N; i++)
 	{
 		int j = V[i];
 		A[i] = 0;
@@ -13,8 +13,9 @@ int sum_range(int* V, int N, int L, int U, int* A)
 			A[i] += V[j];
 			j++;				
 		}
-		i++;		
+		sum += A[i];
 	}
+
 	return sum;
 }
 

### 2018-01-08 tests/benchmarks/toys/private/priv_MI.c

@@ -6,18 +6,21 @@ int sum_range(int* V, int N, int L, int U, int* A)
 	int i=0, sum=0;
 	#pragma omp parallel
 	#pragma omp single
-	while (i < N)
+	for (i = 0; i < N; i++)
 	{
-		int j = V[i];
-		A[i] = 0;
-		#pragma omp untied default(shared) firstprivate(i, j)
-		for (; j < L; j++)
+		#pragma omp untied default(shared) firstprivate(i)
 		{
-			A[i] += V[j];
-			j++;				
+			int j = V[i];
+			A[i] = 0;
+			for (; j < L; j++)
+			{
+				A[i] += V[j];
+				j++;				
+			}
+			sum += A[i];
 		}
-		i++;		
 	}
+
 	return sum;
 }
 

### 2018-01-08 docs/ACM/paper.tex
Adding algorithm to paper.

@@
 semantics to syntax originally written to execute sequentially.
-%The compiler-related literature contains a generous load of success stories
-%describing the use of annotation systems to parallelize programs.
-\guido{What do you mean by modern accelerators? Not clear.}
-Combined with modern accelerators, they have led to substantial performance
-gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
-\guido{Suppport what?}
-Nevertheless, although convenient, the use of annotations is not straightforward, and
-still lacks supporting tools \new{that can help programmers check if the annotation is
-correct or effective}.
+%\guido{What do you mean by modern accelerators? Not clear.}
+Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
+to substantial performance gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
+%\guido{Suppport what?}
+Nevertheless, although convenient, the use of annotations is not straightforward, 
+and still lacks supporting tools that help programmers to check if annotations
+are correct and/or effective.
 %replaced:
@@
 
-Annotations such as OpenMP or OpenACC still require developers to
-worry about typical hassles of the parallel world, such as race conditions
-and deadlocks.
-Moreover, because they are used in tandem with imperative programming languages,
-such troubles are only made worse by pointer aliasing.
+%Annotations such as OpenMP or OpenACC still require developers to
+%worry about typical hassles of the parallel world, such as race conditions
+%and deadlocks.
+%Moreover, because they are used in tandem with imperative programming languages,
+%such troubles are only made worse by pointer aliasing.
 There exist tools that insert automatic annotations in
@@
 the same computation independently on different data.
-Thus, task parallelism remains still uncharted land in what concerns automatic
-annotation. Such fact is unfortunate, since much of the power of current annotation
+Another form of parallelism, based on tasks, remains still uncharted land in what
+concerns automatic annotation.
+Such fact is unfortunate, since much of the power of current annotation
 systems lays on their ability to create tasks~\cite{Ayguade09}.
-\guido{Why the ability to create tasks makes such programs similar to irregular code?
-Which features of irregular code are resposible for such similarities? Not clear to the 
-reader}
-This ability brings said systems closer to irregular programs such as those
-that implement graphs and worklist algorithms \`{a} la
-Pingali~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
+%\guido{Why the ability to create tasks makes such programs similar to irregular code?
+%Which features of irregular code are resposible for such similarities? Not clear to the 
+%reader}
+As we illustrate in Section~\ref{sub:adv}, task parallelism -- the power to run
+different routines simultaneously on independent data -- brings annotation systems
+closer to irregular programs such as those that process graphs and
+worklists~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
 The purpose of this work is to address this omission.
@@
 Fourth, \Taskminer{} determines which program variables need to be 
-\rmv{replicated} \new{privatized}  in new tasks, or shared among them (Section~\ref{sub:variance}).
+privatized in new tasks, or shared among them (Section~\ref{sub:variance}).
 Finally, it maps all this information back into source code, producing
@@
 
-\guido{How about saving programmer's time by doing automatic annotation?}
-The major \ed{benefits provided by \Taskminer are, essentially, performance and readability.}
-\Taskminer{} receives as input a C program, and produces, as output, a C
-program annotated with OpenMP directives that enclose potential tasks.
+In this paper, we defend the thesis that automatic task annotations are
+effective and useful.
+Our techniques enhance the productivity of developers, because they save them
+the time to annotate programs.
+\Taskminer{} receives as input C code, and produces, as output, a C
+program annotated with human-readable OpenMP task directives.
 We are currently able to annotate non-trivial programs, involving every
@@
 times of the parallel versions of those benchmarks, but are much faster than
-\guido{Revisit later if necessary}
+\guido{Numbers?}
 their sequential --unannotated-- versions, as we report in Section~\ref{sec:eval}.
@@
 
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/alg_main}
+\caption{The main steps of our code generator.}
+\label{fig:alg_main}
+\end{center}
+\end{figure}
+
 \subsection{Mapping Program Regions to Tasks}
 \label{sub:identification}
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/expand_alg}
+\caption{Discovery of tasks via expansion of hammock regions.}
+\label{fig:expand_alg}
+\end{center}
+\end{figure}
 

### 2018-01-08 docs/ACM/paper.tex
Added stuff to paper.

@@
 
+The algorithm to find tasks is illustrated in Figure \ref{fig:alg_main}. It uses
+information of two abstract program structures: the \emph{Control Flow Graph (CFG)} and
+the \emph{Program Dependence Graph (PDG)}. The key intuition behind
+finding potential tasks relies on a concept that we call \emph{Helices}. A \emph{Helix}
+is a set of nodes in the PDG that depend on a Strong Connected Component (SCC) but \emph{do not
+integrate the SCC}. Strong Connected Components in the Dependence Graph represent statically
+detected iteration dependence, so it arises with loops or with recursive patterns (when the Graph is
+interprocedural).  \Figure \ref{fig:helix}  shows what represents a \emph{Helix}.
+The insight behind \emph{Helices} is that they represent instructions that are deemed
+to repeat more than once and, since they do not have a cycle, they can be executed in parallel.
+
+Therefore, the first step in the algorithm to find tasks is to map these \emph{Helices}
+into program regions. The algorithm goes through the Dependence Graph looking for \emph{Helices}
+and then finds the minimal covering region for each \emph{Helix}. These minimal regions
+are later going to be annotated as tasks in the original program, should they fit a cost model.
+
+After finding potential task regions, next is the \emph{expansion} step. We expand the region to a larger 
+one as long as two requisites are met:
+
+\begin{enumerate}  
+\item Input and output dependencies are never increased;
+\item The potential parallelism is never reduced.
+\end{enumerate}
+
 \begin{figure}[t!]

### 2018-01-08 docs/ACM/paper.tex
Adding some of Guido's remarks to the paper.

@@
 Such challenges and benefits have guided the design and implementation of the
-techniques \rmv{that we discuss} \new{described in} ection~\ref{sec:sol}.
-\guido{The techniques or the advantages/difficulties? Ambiguous.} 
-In the rest of this section \ed{we discuss such advantage and difficulties.}
+techniques described in Section~\ref{sec:sol}.
+In the rest of this section we discuss such advantage and difficulties.
 
@@
 
-\guido{The runtime is a consequence; the main advantage is the possibility of leaving to a
-runtime the task of handling dependences dynamically.} 
-The main advantage of using OpenMP \new{annotations} to split a program into parallel tasks is
-\new{the ability  of leaving the job of  handling dependences to a runtime.}
-\new{The OpenMP runtime maintains a task dependence graph which dynamically exposes more parallelism 
-opportunities than those resulting from a conservative  compile-time  analysis.}
-\new{In particular, the} runtime lets us circumvent the shortcomings that pointer aliasing
+The main advantage of using OpenMP annotations to split a program into parallel
+tasks is
+the ability  of leaving the job of  handling dependences to a runtime.
+The OpenMP runtime maintains a task dependence graph which dynamically exposes more parallelism 
+opportunities than those resulting from a conservative  compile-time  analysis.
+In particular, the runtime lets us circumvent the shortcomings that pointer aliasing
 impose on the automatic parallelization of code.

### 2018-01-11 Task.cpp
changed some stuff

@@ -44,23 +44,37 @@ std::string Task::accessTypeToStr(AccessType T)
 	}
 }
 
+raw_ostream& Task::printPrivateValues(raw_ostream &os) const
+{
+	os << "\nPRIVATE VALUES:\n";
+	for (auto v : privateValues)
+	{
+		os << "\t";
+		v->print(os);
+		os << "\n";
+	}
+}
+
 raw_ostream& Task::printLiveSets(raw_ostream& os) const
 {
-	os << "\nIN:\n\t";
+	os << "\nIN:\n";
 	for (auto &in : liveIN)
 	{
+		os << "\t";
 		in->print(os);
 		os << "\n";
 	}
 	os << "OUT:\n\t";
 	for (auto &out : liveOUT)
 	{
+		os << "\t";
 		out->print(os);
 		os << "\n";
 	}
 	os << "INOUT:\n\t";
 	for (auto &inout : liveINOUT)
 	{
+		os << "\t";
 		inout->print(os);
 		os << "\n";
 	}
@@ -72,6 +86,7 @@ raw_ostream& Task::print(raw_ostream& os) const
 {
 	if (hasLoadInstructionInDependence())
 		os << "\nTASK HAS LOAD INSTRUCTION IN DEPENDENCIES\n";
+	printPrivateValues(os);
 	return printLiveSets(os);
 }
 
@@ -90,9 +105,39 @@ bool Task::hasLoadInstructionInDependence() const
 	return false;
 }
 
+Function* Task::getParentFunction()
+{
+	if (bbs.empty())
+		return nullptr;
+
+	return (*(bbs.begin()))->getParent();
+}
+
 bool Task::resolvePrivateValues()
 {
-
+	Function* F = getParentFunction();
+	for (Function::iterator ft = F->begin(); ft != F->end(); ft++)
+	{
+		for (BasicBlock::iterator bt = ft->begin(); bt != ft->end(); bt++)
+		{
+			Instruction *i = bt;
+		  BasicBlock* p = i->getParent();
+		  if (bbs.find(p) == bbs.end())
+		  {
+		     for (auto &u : i->uses())
+		     {
+		     	 if (Instruction* inst = dyn_cast<Instruction>(u.get()))
+		     	 {
+			       BasicBlock* pu = inst->getParent();
+			       if (bbs.find(pu) != bbs.end())
+			       {
+			         privateValues.insert(i);
+			       }		     	 	
+		     	 }
[…]

### 2018-01-11 Task.h

@@ -53,8 +53,9 @@ namespace llvm
 		std::set<Value*> getLiveINOUT() const;
 		std::set<BasicBlock*> getbbs() const;
 		CostModel getCost() const { return CM; }
-		std::list<Value*> getPrivateValues() { return privateValues; };
-		void addPrivateValue(Value* V) { privateValues.push_back(V); };
+		std::set<Value*> getPrivateValues() { return privateValues; };
+		void addPrivateValue(Value* V) { privateValues.insert(V); };
+		Function* getParentFunction();
 
 		//Methods
 		virtual bool resolveInsAndOutsSets() { return false; }
@@ -67,10 +68,11 @@ namespace llvm
 		//Printing to output stream methods
 		virtual raw_ostream& print(raw_ostream& os) const;
 		raw_ostream& printLiveSets(raw_ostream& os) const;
+		raw_ostream& printPrivateValues(raw_ostream& os) const;
 
 	private:
 		const TaskKind kind;
-		std::list<Value*> privateValues;
+		std::set<Value*> privateValues;
 
 	protected:
 		//Cost model

### 2018-01-11 docs/ACM/paper.tex

@@
 
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/Absolute_speedups}
+\caption{Speedup comparisons -- automatic annotations compare favourably against
+manual interventions, and lead to great performance gains.
+The Y-axis shows the speedup of either manual intervention, or automatic
+annotation (this paper) onto the original programs.}
+\label{fig:Absolute_speedups}
+\end{center}
+\end{figure}
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/Opt_Speedups}
+\caption{The benefit of our optimizations.
+Each optimization (profitability analysis and recursion bounds) lead to
+non-trivial speedups.}
+\label{fig:Opt_Speedups}
+\end{center}
+\end{figure}
+
 \section{Related Work}

### 2018-01-16 tests/benchmarks/toys/bookfilter/bookfilter.c
toys tests updated. added quadtree.

@@ -1,161 +1,173 @@
 #include <stdlib.h>
 #include <stdio.h>
 #include <string.h>
-#define DEBUG
+#include <math.h>
+#include <time.h>
+#include "../../include/time_common.h"
+// #define DEBUG
+#define CHECK_RESULTS
 
 typedef struct Book Book;
 
-struct Book {
-  int numLines;
-  int numCharsPerLine;
-  char **lines;
+struct Book
+{
+	int numLines;
+	unsigned long long int numCharsPerLine;
+	char** lines;
 };
 
-Book *readBook(char *filename);
+Book* readBook(int lines, unsigned long long int chars);
 
-void printBook(Book *b);
+void printBook(Book* b);
 
-void freeBook(Book *b);
+void freeBook(Book* b);
 
-void filterLines(Book b, char *word, int wordSize, int *occurrences,
-                 int *alphabet);
+void filterLines(Book b, char* word,  int wordSize, int* occurrences, int* alphabet);
 
-void filterLine(char *line, int lineSize, char *word, int wordSize,
-                int *occurrences, int *alphabet);
+void filterLine( char* line,  int lineSize,  char* word,  int wordSize, int* occurrences, int* alphabet);
 
-int main(int argc, char *argv[]) {
-  if (argc < 3) {
-    printf("Not enough arguments to main. <BOOK> <WORD> \n");
-    return 0;
-  }
-  Book *book;
-  if ((book = readBook(argv[1])) == NULL) {
-    printf("Could not open file.\n");
-    return 0;
-  }
+int main(int argc, char  *argv[])
+{
+	if (argc < 3)
+	{
+		printf("Not enough arguments to main. <LINES> <SIZE> <WORD>  \n");
+		return 0;
+	}
 
-  int *filtered = (int *)malloc(book->numLines * sizeof(int));
-  int *alphabet = (int *)malloc(book->numLines * sizeof(int));
-  memset(filtered, 0, sizeof(int) * book->numLines);
-  memset(alphabet, 0, sizeof(int) * book->numLines);
+	Instance* I = newInstance(100);
+  clock_t beg, end;
+	int lines = atoi(argv[1]);
+	unsigned long long chars = atoi(argv[2]);
 
-  char *word = argv[2];
-  int wordSize = strlen(word);
+	Book* book;
[…]

### 2018-01-16 tests/benchmarks/toys/bookfilter/bookfilter_MI.c

@@ -125,7 +125,7 @@ void filterLine(char* line, int lineSize, char* word,  int wordSize, int* occurr
 			(*alphabet)++;		
 	}
 
-	for (int i = 0 + *occurrences; i < lineSize; i++);
+	// for (int i = 0 + *occurrences; i < lineSize; i++);
 		// for (int j = *occurrences; j < lineSize; j++);
 }
 

### 2018-01-16 tests/benchmarks/toys/bookfilter_alter/bookfilter.c

@@ -26,19 +26,16 @@ int main(int argc, char *argv[]) {
   // char** lines = getLines(argv[1], &numLines, &(*size));
 
   char *lines;
-  FILE *in;
-  in = fopen(argv[1], "r");
-  fscanf(in, "%d\n", &(numLines));
-  fscanf(in, "%d\n", &numChars);
+  numLines = atoi(argv[1]);
+  numChars = atoi(argv[2]);
   size = (int *)malloc((numLines) * sizeof(int));
   lines = (char *)malloc((numLines * numChars + 1) * sizeof(char *));
   for (int i = 0; i < (numLines); i++) {
     size[i] = numChars;
     // lines[i] = (char*)malloc((numChars+1)*sizeof(char));
     for (int j = 0; j < numChars; j++) {
-      fscanf(in, "%c", &lines[i * numChars + j]);
+    	lines[i * numChars + j] =  'a' + (rand() % 26);
     }
-    fscanf(in, "\n", NULL);
   }
 
   int *filtered = (int *)malloc(numLines * sizeof(int));
@@ -150,8 +147,8 @@ void filterLine(char *line, int lineSize, char *word, int wordSize,
     }
   }
 
-  for (int i = 0 + *occurrences; i < lineSize; i++) {
-    for (int j = *occurrences; j < lineSize; j++) {
-    }
-  }
+  // for (int i = 0 + *occurrences; i < lineSize; i++) {
+  //   for (int j = *occurrences; j < lineSize; j++) {
+  //   }
+  // }
 }

### 2018-01-16 tests/benchmarks/toys/bookfilter_alter/bookfilter_MI.c

@@ -2,235 +2,158 @@
 #include <stdio.h>
 #include <string.h>
 #include <omp.h>
-#define DEBUG
+// #define DEBUG
 
-// Line* getLines( char* name, int* numLines);
+// Line* getLines(char* name, int* numLines);
 
-char** getLines( char* name, int* numLines, int* size);
+char **getLines(char *name, int *numLines, int *size);
 
-void printLines(char* lines,  int numLines,  int numChars);
+void printLines(char *lines, int numLines, int numChars);
 
-// void filterLine( Line l,  char* word, int wordSize, int* occurrences, int* alphabet);
+void filterLines(char *lines, int *size, int numLines, int numChars, char *word,
+                 int wordSize, int *occurrences, int *alphabet);
 
-void filterLines(char* lines, int* size, int numLines, int numChars, char* word,  int wordSize, int* occurrences, int* alphabet);
+void filterLine(char *line, int lineSize, char *word, int wordSize,
+                int *occurrences, int *alphabet);
 
-void filterLine( char* line,  int lineSize,  char* word,  int wordSize, int* occurrences, int* alphabet);
+int main(int argc, char *argv[]) {
+  if (argc < 3) {
+    printf("Not enough arguments to main. <BOOK> <WORD> \n");
+    return 0;
+  }
 
-int main(int argc, char  *argv[])
-{
-	omp_set_dynamic(1);
-	if (argc < 3)
-	{
-		printf("Not enough arguments to main. <BOOK> <WORD> \n");
-		return 0;
-	}
+  unsigned long long numLines;
+  unsigned long long numChars;
+  int *size;
+  // char** lines = getLines(argv[1], &numLines, &(*size));
 
-	int numLines, numChars;
-	int* size;
-	// char** lines = getLines(argv[1], &numLines, &(*size));
+  char *lines;
+  numLines = atoi(argv[1]);
+  numChars = atoi(argv[2]);
+  size = (int *)malloc((numLines) * sizeof(int));
+  lines = (char *)malloc((numLines * numChars + 1) * sizeof(char *));
+  for (int i = 0; i < (numLines); i++) {
+    size[i] = numChars;
[…]

### 2018-01-16 tests/benchmarks/toys/bookfilter_alter/bookfilter_SER.c

@@ -1,8 +1,7 @@
-#include <omp.h>
 #include <stdlib.h>
 #include <stdio.h>
 #include <string.h>
-#define DEBUG
+// #define DEBUG
 
 // Line* getLines(char* name, int* numLines);
 
@@ -17,34 +16,28 @@ void filterLine(char *line, int lineSize, char *word, int wordSize,
                 int *occurrences, int *alphabet);
 
 int main(int argc, char *argv[]) {
-  if (argc < 3) {
-    printf("Not enough arguments to main. <BOOK> <WORD> \n");
-    return 0;
-  }
+	if (argc < 4)
+	{
+		printf("Not enough arguments to main. <LINES> <SIZE> <WORD>  \n");
+		return 0;
+	}
 
-  int numLines, numChars;
+  unsigned long long numLines;
+  unsigned long long numChars;
   int *size;
   // char** lines = getLines(argv[1], &numLines, &(*size));
 
   char *lines;
-  FILE *in;
-  in = fopen(argv[1], "r");
-  fscanf(in, "%d\n", &(numLines));
-  fscanf(in, "%d\n", &numChars);
+  numLines = atoi(argv[1]);
+  numChars = atoi(argv[2]);
   size = (int *)malloc((numLines) * sizeof(int));
   lines = (char *)malloc((numLines * numChars + 1) * sizeof(char *));
-  #pragma omp parallel
-  #pragma omp single
   for (int i = 0; i < (numLines); i++) {
-    #pragma omp task depend(in:numLines,numChars,alphabet[i],argv[2],filtered[i]) depend(out:size[i],filtered[i],alphabet[i])
-    {
     size[i] = numChars;
     // lines[i] = (char*)malloc((numChars+1)*sizeof(char));
     for (int j = 0; j < numChars; j++) {
-      fscanf(in, "%c", &lines[i * numChars + j]);
+    	lines[i * numChars + j] =  'a' + (rand() % 26);
     }
-    fscanf(in, "\n", NULL);
-  }
   }
 
   int *filtered = (int *)malloc(numLines * sizeof(int));
@@ -102,11 +95,7 @@ char **getLines(char *name, int *numLines, int *size) {
   fscanf(in, "%d\n", &(*numLines));
   size = (int *)malloc((*numLines) * sizeof(int));
   lines = (char **)malloc((*numLines) * sizeof(char *));
-  #pragma omp parallel
-  #pragma omp single
   for (int i = 0; i < (*numLines); i++) {
[…]

### 2018-01-16 tests/benchmarks/toys/boruvka/boruvka_MI.c

@@ -1,6 +1,6 @@
 #include <stdlib.h>
 #include <stdio.h>
-#define SIZE 10000
+#include <omp.h>
 
 void fillgraph(int* G, int N)
 {
@@ -8,7 +8,7 @@ void fillgraph(int* G, int N)
 	{
 		for (long unsigned j = 0; j < N; j++)
 		{
-			*(G + i*N + j) = (i == j) ? 0 : rand()%50;
+			*(G + i*N + j) = rand()%5;
 		}
 	}
 }
@@ -34,7 +34,7 @@ struct edge
 typedef struct edge edgeType;
 
 edgeType* edgeTab;
-int numVertices, numEdges, usefulEdges;
+int numVertices, numEdges;
 int *parent, *weight, numTrees;
 int* bestEdgeNum;
 int* G;
@@ -49,36 +49,15 @@ int find(int x)
   
   /* path compression */
   for (i = x; parent[i] != i; )
-  {
   	j = parent[i];
   	parent[i] = root;
-  	i = j;  	
-  }
-
+  	i = j;
+  
   return root;
-}
-
-void findRootsOfEdge(int i)
-{
-	int root1, root2;
-  root1 = find(edgeTab[i].src);
-  root2 = find(edgeTab[i].dst);
-  if (root1 != root2)
-  {
-    usefulEdges++;
-    if (bestEdgeNum[root1] == (-1) ||
-        edgeTab[bestEdgeNum[root1]].weight > edgeTab[i].weight)
-      bestEdgeNum[root1] = i;  // Have a new best edge from this component
-
-    if (bestEdgeNum[root2] == (-1) ||
-        edgeTab[bestEdgeNum[root2]].weight > edgeTab[i].weight)
-      bestEdgeNum[root2] = i;  // Have a new best edge from this component
-  }
 }
 
 void union_(int i, int j)
 {
-	// printf("Union of %d and %d\n", i, j);
   if (weight[i] > weight[j])
   {
     parent[j] = i;
@@ -92,11 +71,13 @@ void union_(int i, int j)
   numTrees--;
 }
 
-int main()
+int main(int argc, char* argv[])
 {
   int i, j, MSTweight = 0;
   int root1, root2;
+  int usefulEdges;
 
+  int SIZE = atoi(argv[1]);
   edgeTab = (edgeType*)malloc(SIZE*SIZE* sizeof(edgeType));
   parent = (int*)malloc(SIZE * sizeof(int));
   weight = (int*)malloc(SIZE * sizeof(int));
[…]

### 2018-01-16 tests/benchmarks/toys/boruvka/boruvka_SER.c

@@ -1,6 +1,6 @@
 #include <stdlib.h>
 #include <stdio.h>
-#define SIZE 10000
+// #define SIZE 10000
 
 void fillgraph(int* G, int N)
 {
@@ -8,7 +8,7 @@ void fillgraph(int* G, int N)
 	{
 		for (long unsigned j = 0; j < N; j++)
 		{
-			*(G + i*N + j) = rand()%5;
+			*(G + i*N + j) = rand()%50 + 1;
 		}
 	}
 }
@@ -34,7 +34,7 @@ struct edge
 typedef struct edge edgeType;
 
 edgeType* edgeTab;
-int numVertices, numEdges;
+int numVertices;
 int *parent, *weight, numTrees;
 int* bestEdgeNum;
 int* G;
@@ -71,12 +71,14 @@ void union_(int i, int j)
   numTrees--;
 }
 
-int main()
+int main(int argc, char* argv[])
 {
   int i, j, MSTweight = 0;
   int root1, root2;
   int usefulEdges;
 
+  int SIZE = atoi(argv[1]);
+  numVertices = SIZE;
   edgeTab = (edgeType*)malloc(SIZE*SIZE* sizeof(edgeType));
   parent = (int*)malloc(SIZE * sizeof(int));
   weight = (int*)malloc(SIZE * sizeof(int));
@@ -84,7 +86,8 @@ int main()
   G = (int*)malloc(SIZE*SIZE*sizeof(int));
 
   fillgraph(G, SIZE);
-  // printGraph(G, SIZE);
+  if (SIZE < 20)
+	  printGraph(G, SIZE);
 
   //fillEdgeInfo
   for (i = 0; i < SIZE; i++)
@@ -138,11 +141,11 @@ int main()
         if (root1 == root2)
           continue;  // This round has already connected these components.
         MSTweight += edgeTab[bestEdgeNum[i]].weight;
-        // printf("%d %d %d included in MST\n", edgeTab[bestEdgeNum[i]].src,
-               // edgeTab[bestEdgeNum[i]].dst, edgeTab[bestEdgeNum[i]].weight);
+        printf("%d %d %d included in MST\n", edgeTab[bestEdgeNum[i]].src,
+               edgeTab[bestEdgeNum[i]].dst, edgeTab[bestEdgeNum[i]].weight);
         union_(root1, root2);
       }
-    // printf("numTrees is %d\n", numTrees);
+    printf("numTrees is %d\n", numTrees);
   }
 
   if (numTrees != 1)

### 2018-01-16 tests/benchmarks/toys/quadtree/arvorequad.c

@@ -1,0 +1,288 @@
+#include "arvorequad.h"
+#include <stdlib.h>
+#include <stdio.h>
+// #define DEBUG
+
+void imprimePesoDeTodosOsQuadrantes(Quadrante* Q, int index)
+{
+	if (Q == NULL)
+		return;
+	imprimePesoDeTodosOsQuadrantes(Q->NE, index*4 + 1);
+	imprimePesoDeTodosOsQuadrantes(Q->NW, index*4 + 2);
+	imprimePesoDeTodosOsQuadrantes(Q->SW, index*4 + 3);
+	imprimePesoDeTodosOsQuadrantes(Q->SE, index*4 + 4);
+	Q->peso = getPesoTotalDoQuadrante(Q);
+	printf("(%d, %d) %d\n", Q->centro.x, Q->centro.y, Q->peso);
+}
+
+int main(int argc, char const *argv[])
+{
+	int maxLargura, x, y, peso, pesototal=0;
+	unsigned numPontos;
+	scanf("%d", &maxLargura);
+	scanf("%d", &numPontos);
+	ArvoreQuad* A = criaNovaArvoreQuad(maxLargura);
+	while (numPontos > 0)
+	{
+		x = rand()%maxLargura;
+		y = rand()%maxLargura;
+		peso = rand()%100;
+		// scanf("%d %d %d", &x, &y, &peso);
+		Ponto P;
+		P.x = x;
+		P.y = y;
+		if (addNovaEstrelaNoPontoX(P, peso, A))
+			pesototal += peso;
+		numPontos--;
+	}
+
+	#ifdef DEBUG
+		imprimePesoDeTodosOsQuadrantes(A->raiz, 0);
+		if (pesototal != getPesoTotalDoQuadrante(A->raiz))
+			printf("PESO INCORRETO\n");
+	#endif
+
+	liberaMemoriaEmArvore(A);
+	return 0;
+}
+
+Estrela* novaEstrela(Ponto P, int peso)
+{
+	Estrela* star = (Estrela*) malloc(sizeof(Estrela));
+	star->p = P;
+	star->peso = peso;
+
+	return star;
+}
+
+Quadrante* criaNovoQuadranteVazio(Ponto NE, Ponto NW, Ponto SE, Ponto SW)
+{
+	Quadrante* Q = (Quadrante*) malloc(sizeof(Quadrante));
+	Q->NE = NULL;
+	Q->NW = NULL;
[…]

### 2018-01-16 tests/benchmarks/toys/quadtree/arvorequad.h

@@ -1,0 +1,136 @@
+/*
+UNIVERSIDADE FEDERAL DE MINAS GERAIS
+DEstarAMENTO DE CIÊNCIA DA COMPUTAÇÃO
+ALGORITMOS E ESTRUTURAS DE DADOS II
+======================================
+TP2: ÁRVORE QUADRUPLA
+PROFESSORES: 	Fernando Magno Q. Pereira
+							Luiz Chaimowicz
+							Raquel Minardi
+MONITOR: Pedro Ramos (Sala 2301)
+======================================
+
+Módulo: arvorequad.h
+
+Este cabeçalho contém a declaração dos métodos do módulo arvorequad.c, bem
+como a definição das estruturas a serem utilizadas nesse trablho. Muita atenção
+à estrutura: qualquer modificação na mesma pode interferir no resultado esperado
+na rotina "imprimeArvoreEmArquivoDot(ArvoreQuad* )". 
+
+Neste trabalho vocês irão implementar uma árvore quádrupla. Não se desesperem!
+Uma árvore quádrupla é aquela em que cada nó possui 4 filhos. Dessa vez,
+queremos dividir starículas num espaço 2D em quadrantes. Quando X ou mais
+starículas ocupam o mesmo quadrante no espaço 2D, o mesmo é dividido em outros
+4 subquadrantes filhos, e a starícula é então movida para o subquadrante 
+filho em que ela se situa.
+
+Cada quadrante é classificado de acordo com o centro do quadrante pai. Há, 
+então, 4 quadrantes para um centro do quadrante pai:
+NE -> Quadrante Nordeste ao centro 
+NW -> Quadrante Noroeste ao centro 
+SE -> Quadrante Sudeste ao centro 
+SW -> Quadrante Sudoeste ao centro 
+
+Estes quadrantes (e seus filhos, e os filhos de seus filhos...) podem ser
+representados por uma árvore quádrupla. Quando uma starícula nova é adicionada
+à árvore, você deve checar se ela vai entrar em um quadrante que já contém
+o número máximo de starículas permitido. Se isso ocorrer, você deve starir
+este quadrante em mais 4 subquadrantes e mover as starículas para baixo,
+atualizando o peso e o centro de cada novo subquadrante.
+
+*/
+#ifndef __ARVORE_QUAD_H__
+#define __ARVORE_QUAD_H__
+
[…]

### 2018-01-16 tests/benchmarks/toys/quadtree/arvorequad_MI.c

@@ -1,0 +1,312 @@
+#include "arvorequad.h"
+#include <stdlib.h>
+#include <stdio.h>
+#include <math.h>
+#include <omp.h>
+// #define DEBUG
+
+void imprimePesoDeTodosOsQuadrantes(Quadrante* Q, int index)
+{
+	if (Q == NULL)
+		return;
+	imprimePesoDeTodosOsQuadrantes(Q->NE, index*4 + 1);
+	imprimePesoDeTodosOsQuadrantes(Q->NW, index*4 + 2);
+	imprimePesoDeTodosOsQuadrantes(Q->SW, index*4 + 3);
+	imprimePesoDeTodosOsQuadrantes(Q->SE, index*4 + 4);
+	Q->peso = getPesoTotalDoQuadrante(Q);
+	printf("(%d, %d) %d\n", Q->centro.x, Q->centro.y, Q->peso);
+}
+
+int main(int argc, char const *argv[])
+{
+	int maxLargura, x, y, peso, pesototal=0, ans;
+	unsigned numPontos;
+	scanf("%d", &maxLargura);
+	scanf("%d", &numPontos);
+	int debug = 0;
+	if (numPontos < 20)
+	{
+		debug = 1;
+	}
+	ArvoreQuad* A = criaNovaArvoreQuad(maxLargura);
+	#pragma omp parallel
+	#pragma omp single
+	while (numPontos > 0)
+	{
+		x = rand()%maxLargura;
+		y = rand()%maxLargura;
+		peso = rand()%100;
+		// scanf("%d %d %d", &x, &y, &peso);
+		Ponto P;
+		P.x = x;
+		P.y = y;
+		ans = addNovaEstrelaNoPontoX(P, peso, A);
+		if (ans)
+		{
+			#pragma omp critical
+			pesototal += peso;
+		}
+		numPontos--;
+	}
+
+	#pragma omp taskwait
+
+	if (debug) imprimePesoDeTodosOsQuadrantes(A->raiz, 0);
+	#ifdef DEBUG
+		if (pesototal != getPesoTotalDoQuadrante(A->raiz))
+			printf("PESO INCORRETO\n");
+	#endif
+
+	liberaMemoriaEmArvore(A);
+	return 0;
+}
+
+Estrela* novaEstrela(Ponto P, int peso)
+{
+	Estrela* star = (Estrela*) malloc(sizeof(Estrela));
+	star->p = P;
+	star->peso = peso;
+
+	return star;
+}
[…]

### 2018-01-16 tests/benchmarks/toys/quadtree/arvorequad_SER.c

@@ -1,0 +1,295 @@
+#include "arvorequad.h"
+#include <stdlib.h>
+#include <stdio.h>
+#include <math.h>
+// #define DEBUG
+
+void imprimePesoDeTodosOsQuadrantes(Quadrante* Q, int index)
+{
+	if (Q == NULL)
+		return;
+	imprimePesoDeTodosOsQuadrantes(Q->NE, index*4 + 1);
+	imprimePesoDeTodosOsQuadrantes(Q->NW, index*4 + 2);
+	imprimePesoDeTodosOsQuadrantes(Q->SW, index*4 + 3);
+	imprimePesoDeTodosOsQuadrantes(Q->SE, index*4 + 4);
+	Q->peso = getPesoTotalDoQuadrante(Q);
+	printf("(%d, %d) %d\n", Q->centro.x, Q->centro.y, Q->peso);
+}
+
+int main(int argc, char const *argv[])
+{
+	int maxLargura, x, y, peso, pesototal=0;
+	unsigned numPontos;
+	scanf("%d", &maxLargura);
+	scanf("%d", &numPontos);
+	int debug = 0;
+	if (numPontos < 20)
+	{
+		debug = 1;
+	}
+	ArvoreQuad* A = criaNovaArvoreQuad(maxLargura);
+	while (numPontos > 0)
+	{
+		x = rand()%maxLargura;
+		y = rand()%maxLargura;
+		peso = rand()%100;
+		// scanf("%d %d %d", &x, &y, &peso);
+		Ponto P;
+		P.x = x;
+		P.y = y;
+		if (addNovaEstrelaNoPontoX(P, peso, A))
+			pesototal += peso;
+		numPontos--;
+	}
+
+	
+	if (debug) imprimePesoDeTodosOsQuadrantes(A->raiz, 0);
+	#ifdef DEBUG
+		if (pesototal != getPesoTotalDoQuadrante(A->raiz))
+			printf("PESO INCORRETO\n");
+	#endif
+
+	liberaMemoriaEmArvore(A);
+	return 0;
+}
+
+Estrela* novaEstrela(Ponto P, int peso)
+{
+	Estrela* star = (Estrela*) malloc(sizeof(Estrela));
+	star->p = P;
+	star->peso = peso;
+
+	return star;
+}
+
+Quadrante* criaNovoQuadranteVazio(Ponto NE, Ponto NW, Ponto SE, Ponto SW)
+{
[…]

### 2018-01-18 docs/ACM/paper.tex
toys tests updated. added quadtree.
Section 2.

@@
 
-\section{Advantages and Difficulties}
+\section{Challenges}
 \label{sec:ovf}
 
-The use of OpenMP pragmas as the concrete means to explore, without human
-intervention, task parallelism in programs presents difficulties and
-advantages. 
-Such challenges and benefits have guided the design and implementation of the
-techniques described in Section~\ref{sec:sol}.
-In the rest of this section we discuss such advantage and difficulties.
+This paper presents a tool that annotates source C code with OpenMP task
+directives.
+This tool uses novel techniques to fulfill its purpose.
+Such techniques solve four challenges, which Section~\ref{sub:dif}
+illustrates with examples.
+However, before we dive into these challenges, the reader must understand
+the main benefits of using a runtime environment such as OpenMP's, for
+such advantages have guided most of our designing decisions.
+Section~\ref{sub:adv} introduces this discussion.
 
-\subsection{The Advantages}
+\subsection{The OpenMP Runtime System}
 \label{sub:adv}
@@
 it already checks for dependencies among tasks, and dispatches them in a
-correct order~\cite{LaGrone11}. \ed{To achieve that, OpenMP runtime uses task descriptors that contain}
-\guido{The descriptor does not keep task status; this is done in the runtime.}
-\rmv{task's status (running, waiting)} \ed{a task identifier and  a list of memory addresses corresponding to the task input /output arguments.}
+correct order~\cite{LaGrone11}.
 
-The process of checking for dependencies can be as simple as checking if an
-incoming task accesses a memory address already in use by \ed{an in-flight task}.
-It can also be complex, involving checks over long ranges of addresses
-(in case the runtime system supports dependence checking for memory ranges).
-This process can also include memory labelling and renaming (in case the
+Dependence tracking can be complex, involving checks over ranges of addresses
+(if the runtime system treats dependencies across memory ranges).
+It can also include memory labelling and renaming (if the
 runtime system is able to remove false dependencies).
@@
 dependences between them.
-Tasks are dispatched for execution according to a \new{dynamic} topological ordering of this
-graph~\cite{Planas15}.
+Tasks are dispatched for execution according to a dynamic topological ordering of
+this graph~\cite{Planas15}.
 
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{images/ex_book_filter}
+\includegraphics[width=1\columnwidth]{images/ex_book_filter}
 \caption{The benefits of the OpenMP runtime environment.
@@
 
-\guido{Now it is clear the relevance for irregular programs.}
-\ed{The OpenMP runtime} support allows the parallelization of irregular applications,
+The OpenMP runtime support allows the parallelization of irregular applications,
 such as programs that traverse data-structures formed by a mesh of pointers.
-\guido{A litte bit more details: }
-\new{In such programs, control construcs (e.g. {\tt if} statement) make the execution 
-of certain pieces of code  dependent on the program input. When using 
-task parallelism the runtime can capture such dependences. This is not possible 
-otherwise, since compile-time dependence analyzers must be conservative and eventually
-skip some parallelization opportunity.}
-
+In such programs, control constructs like {\tt if} statements make the
+execution  of certain pieces of code dependent on the program's input.
+The runtime can capture such dependences, in contrast to static analysis tools.
 As an example, Figure~\ref{fig:ex_book_filter} shows an application that
@@
 to process each line.
-Figure~\ref{fig:ex_book_filter} has been annotated automatically by \rmv{the}
+Figure~\ref{fig:ex_book_filter} has been annotated automatically by
 \Taskminer.
 The OpenMP execution environment ensures the correct scheduling of the tasks
-created at lines 9 and 11, \ed{by}  \guido{This is vague:} \rmv{runtime checks.} 
-\new{assuring that the annotated input dependencies {\tt line} and {\tt pattern}  are 
-respected at runtime.}
-\guido{Not clear. Need more details here. Adding:} \new{Pointer-based dependencies
-can address various memory regions. Hence, in order to enable the automatic
-synthesis of task annotations a system must be able to precisely define which 
-memory region a pointer dependency is pointing to.}
-\guido{Not clear why it is not important for correctness.}
-Therefore, the ability to disambiguate memory regions statically is not
-essential for correctness, although it is important for efficiency reasons,
-as we will mention in Challenge~\ref{ch:Regions}.
+created at lines 9 and 11, by assuring that the annotated input dependencies
+{\tt line} and {\tt pattern}  are 
+respected at runtime.
 
-\subsection{The Difficulties}
+\subsection{Challenges}
 \label{sub:dif}
 
-The automatic insertion of effective OpenMP annotations into C/C++ programs
-required us to deal with a number of challenges.
-If left unsolved, these challenges would restrict our interventions in programs
-to trivial annotations, which would hardly be of any use.
+As seen in Section~\ref{sub:adv}, the OpenMP runtime liberates us
+from the burden of having to track dependences between pointers statically.
+However, the automatic insertion of effective task annotations into
+programs still required us to deal with a number of challenges.
+If left unsolved, these challenges would restrict our interventions
+to trivial annotations -- hardly be of any use.
 Our first challenge is inherent to any automatic parallelization system.
 
-\begin{figure}[h!]
+\begin{Challenge}
+\label{ch:Regions}
+Identify the memory region covered by a task.
+\end{Challenge}
+
+\begin{figure}[b!]
 \begin{center}
-\includegraphics[width=0.95\columnwidth]{images/ex_Regions}
+\includegraphics[width=1\columnwidth]{images/ex_Regions}
 \caption{Challenges~\ref{ch:Regions} and~\ref{ch:cost}: identifying memory regions
@@
 
-\begin{Challenge}
-\label{ch:Regions}
-Identify the memory region covered by a task.
-\end{Challenge}
-
 Figure~\ref{fig:ex_Regions} illustrates Challenge~\ref{ch:Regions}, and shows
-how we solve it\footnote{Figures~\ref{fig:ex_Regions}-\ref{fig:ex_cutoff} shows
-programs that we have annotated without any human intervention.
-Statements in black font are part of the original program.
-Annotations appear in grey.}.
+how we solve it\footnote{Whenever we show code, statements in black font are part
+of the original program.
+The annotations that we create automatically appear in grey.}.
 That program receives an $\mathsf{M}\times\mathsf{N}$ matrix \textsf{V}, in
@@
 The creation of tasks involves a heavy runtime cost due to allocation,
-scheduling and real-time management of the task dependence graph.
+scheduling and real-time management of the dependence graph
+(see Sec.~\ref{sub:adv}).
 Ideally, this cost should be paid only for tasks that perform an amount of work
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{images/ex_cutoff}
+\includegraphics[width=1\columnwidth]{images/ex_cutoff}
 \caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks with
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{images/alg_main}
+\includegraphics[width=1\columnwidth]{images/alg_main}
 \caption{The main steps of our code generator.}
@@
 detected iteration dependence, so it arises with loops or with recursive patterns (when the Graph is
-interprocedural).  \Figure \ref{fig:helix}  shows what represents a \emph{Helix}.
+interprocedural).  Figure~\ref{fig:helix}  shows what represents a \emph{Helix}.
 The insight behind \emph{Helices} is that they represent instructions that are deemed
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{images/expand_alg}
+\includegraphics[width=1\columnwidth]{images/expand_alg}
 \caption{Discovery of tasks via expansion of hammock regions.}
@@
 \label{sec:eval}
-
-%We aimed to show that our tool exceeded in three main aspects that surround parallel programming. Thus our work evaluation stands on these 3 pillars:
-
 % In section 4.
@@
 
-%\begin{itemize}
+We performed a thorough evaluation on \Taskminer{}'s applicability in real programs. Our test framework is divided in five aspects:
 
-%\item Practicality
-%\item Applicability
-%\item Performance
+\begin{itemize}
+\item Performance
+\item Optimizations
+\item Versatility
+\item Applicability
+\item Practicality
+\end{itemize}
 
-%\end{itemize}
-
-%\textbf{\textit{Practicality}}.
-Programming in a parallel pattern is deemed difficult by programmers mainly because of the complexity of its data structures and algorithms.
-We show that our tool is simple and practical, for it does not involve changing the code and data structures in order to fit in a parallel pattern.
-The code is simply annotated by compiler directives.
-
-%\textbf{\textit{Applicability}}.
-
-%\textbf{\textit{Performance}}.
-When it comes to parallel computing, it is undeniable that the main achievable goal should be performance.
-There's no reason why programmers would opt for parallelism other than the desire for faster programs.
-Therefore, we ought to show that the programs annotated with TaskMiner are faster than their serial counterparts.
+%PERFORMANCE
+%Here, we show the results for our small benchmarks (toys & bots)
+\textbf{\textit{Performance}}.
 
@@
 
+%OPTIMIZATIONS
+%Here, we show the results on two big optimizations: recursion depth and cost model.
+%We can use the same benchmarks as above.
+\textbf{\textit{Optimizations}}.
+
 \begin{figure}[t!]
@@
 \end{figure}
+
+%VERSATILITY
+%The goal here is to show that TaskMiner is a versatile tool, capable of finding many types of task parallelism in the code. 
+%And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
+\textbf{\textit{Versatility}}.
+
+%APPLICABILITY
+%We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
+\textbf{\textit{Versatility}}.
+
+%PRACTICALITY
+%The main objective here is to show that TaskMiner can be easily utilized by a programmer to find tasks in their source code. 
+%We'll test TaskMiner's running time.
+\textbf{\textit{Practicality}}.
 

### 2018-01-20 docs/ACM/paper.tex
Adding first definitions.

@@
 
-\title[Automatic Identification and Annotation of Parallel Tasks in Structured
+\title[Automatic Identification and Annotation of Tasks in Structured
 Programs]
-{Automatic Identification and Annotation of Parallel Tasks in Structured Programs}
+{Automatic Identification and Annotation of Tasks in Structured Programs}
 
@@
 
-\begin{figure}[t!]
+Figure~\ref{fig:alg_main} provides a high-level view of a source-to-source
+compiler that incorporates the techniques discussed in this paper.
+This pseudo-code uses several concepts well-known in the compiler's
+literature, such as control flow graphs~\cite{Kildall73} and
+dependence graphs~\cite{Ferrante87}.
+We built on top of such concepts, as well as others, like
+symbolic range analysis~\cite{Blume94}, and natural loops~\cite{Allen70}.
+In the rest of this section we explain how we have combined this previous
+knowledge in order to delimit and annotate tasks in structured programs.
+Our presentation focus on the new elements that we had to add onto known
+techniques, in order to adapt them to our purposes.
+
+\begin{figure}[h]
 \begin{center}
@@
 \end{figure}
+
+\paragraph{The syntax that we handle.}
+Our goal is to identify {\em tasks} in {\em structured} programs.
+Definition~\ref{def:task} formalizes the notion of task.
+A structured program is a program that can be partitioned in {\em hammock
+regions}, a concept introduced by Ferrante {\em et al.}~\cite{Ferrante87} in
+the middle 80's.
+The structure of this program is described by a a Control Flow Graph $G$ --
+a directed graph with a starting node $s$, and an exit node $x$.
+A hammock region is a subgraph $G' \subseteq G$, with a special node
+$h$, which {\em dominates}\footnote{A node $n_1 \in G$ dominates another node
+$n_2 \in G$ if every path from  $S$ to $n_2$ goes across $n_1$.
+Inversely, $n_1$ post-dominates $n_2$ if every path from $n_2$ to $x$ must
+go across $n_1$.} every other node in $G'$.
+Additionally, there exists a node $w \in G$, $w \notin G'$, such that
+$w$ {\em post-dominates} every node in $G'$.
+In this definition, $h$ is the {\em entry point}, and $w$ is the {\em exit point}
+of $G'$.
+
+\begin{definition}[Task]
+\label{def:task}
+Given a program $P$, a task $T$ is a tuple $(G', M)$ formed by a hammock region
+$G'$, plus a set $M$ of memory regions that represent the dependences of $T$.
+\end{definition}
+
+Definition~\ref{def:task} uses the concept of {\em memory region}.
+Syntactically, memory regions are described by program variables and/or pointers
+plus ranges of offsets that these pointers are allowed to dereference.
+If a task $(T_1, M_1)$ writes onto a memory region $m$, and task
+$(T_2, M_2)$ contains code that reads $m$, then $m \in M_1$, to ensure that
+dependences are respected.
+If a program $P$ is partitioned into a set of $n$ tasks $\{(T_1, M_1),
+\ldots (T_n, M_n)\}$, then this partition is said to be {\em correct} if any
+topological ordering of the tasks, as determined by dependence relations, always
+leads to the same results as the sequential execution of $P$.
+
+\paragraph{The annotations that we use.}
 
@@
 \includegraphics[width=1\columnwidth]{images/expand_alg}
-\caption{Discovery of tasks via expansion of hammock regions.}
+\caption{Task discovery via expansion of hammock regions.}
 \label{fig:expand_alg}

### 2018-01-20 docs/ACM/paper.tex
Working on Section 3.

@@
 \label{def:task}
-Given a program $P$, a task $T$ is a tuple $(G', M)$ formed by a hammock region
-$G'$, plus a set $M$ of memory regions that represent the dependences of $T$.
+Given a program $P$, a task $T$ is a tuple $(G', M_i, M_o)$ formed by a hammock
+region $G'$, plus a set $M_i$ of memory regions representing data that $T$ reads,
+and a set $M_o$ of memory regions representing data that $T$ writes.
 \end{definition}
@@
 plus ranges of offsets that these pointers are allowed to dereference.
-If a task $(T_1, M_1)$ writes onto a memory region $m$, and task
-$(T_2, M_2)$ contains code that reads $m$, then $m \in M_1$, to ensure that
-dependences are respected.
-If a program $P$ is partitioned into a set of $n$ tasks $\{(T_1, M_1),
-\ldots (T_n, M_n)\}$, then this partition is said to be {\em correct} if any
-topological ordering of the tasks, as determined by dependence relations, always
-leads to the same results as the sequential execution of $P$.
+Given two tasks: $T_1 = (G_1, M_{i1}, M_{o1})$ and $T_2 = (G_2, M_{i2}, M_{o2})$,
+if $M_{o1} \cap M_{i2} \neq \emptyset$, then we say that $T_2$ {\em depends} on
+$T_1$.
+If a program $P$ is partitioned into a set of $n$ tasks, then this partition is
+said to be {\em correct} if: (i) it does not contain cyclic dependence relations;
+and (ii) any topological ordering of the tasks, as determined by dependence
+relations, leads to the same results as the sequential execution of $P$.
 

### 2018-01-20 docs/ACM/paper.tex
Adding some text in the intro of Section 3.

@@
 %% Packages that we are using in this version of the work:
+\usepackage{amsmath}
 \usepackage{hyperref}
-\usepackage{amsmath}
+\usepackage{paralist}
 
@@
 
-\paragraph{The syntax that we handle.}
+\paragraph{Tasks: syntax and scope:}
 Our goal is to identify {\em tasks} in {\em structured} programs.
@@
 If a program $P$ is partitioned into a set of $n$ tasks, then this partition is
-said to be {\em correct} if: (i) it does not contain cyclic dependence relations;
-and (ii) any topological ordering of the tasks, as determined by dependence
+said to be {\em correct} if it abides by Definition~\ref{def:correctness}.
+
+\begin{definition}[Correctness]
+\label{def:correctness}
+A set $T$ of $n$ tasks is a correct parallelization of a program $P$ if:
+\begin{compactitem}
+\item $T$ does not contain cyclic dependence relations;
+\item the execution of the tasks in $T$ in any ordering determined by dependence
 relations, leads to the same results as the sequential execution of $P$.
+\end{compactitem}
+\end{definition}
 
-\paragraph{The annotations that we use.}
+\begin{example}[Memory Regions]
+\label{ex:regions}
+\fer{XX Add an example to describe the notions of regions and dependences.
+The best is to modify one of the programs in Section 2, so that we can refer to
+that program.
+Pedro, can you think about it and propose something?}
+\end{example}
+
+\paragraph{The annotation zoo.}
+Our equipment of choice to reveal task parallelism in programs is OpenMP 3.0.
+This annotation system provides us with a rich set of pragmas that we can use
+to indicate to compiler and runtime environment which tasks must be created.
+We describe below which annotations we are using, and explain, informally, their
+semantics.
+A full overview of the syntax and semantics of these annotations is publicly
+available\footnote{For a quick overview, we refer the reader to the leaflet
+``Summary of OpenMP 3.0 C/C++ Syntax", which is made available by the OpenMP
+group.}.
+
+\begin{compactitem}
+\item \textsf{task} {\em clauses}: creates a new task, according to the
+parameters specified in the {\em clauses} list:
+\begin{compactitem}
+\item \textsf{default([shared/private])}: indicates that variables are either
+shared or replicated among tasks.
+\item \textsf{firstprivate($v$)}: indicates that $v$ must be replicated among
+tasks, and initialized with its value at the point where the annotation is
+executed.
+\item \fer{Pedro/Gleison: can you guys continue this list?}
+\end{compactitem}
+\item \textsf{taskwait}: forces tasks to synchronize at the point of annotation.
+\end{compactitem}
 

### 2018-01-23 docs/ACM/paper.tex
Adding discussion about clauses.

@@
 Our equipment of choice to reveal task parallelism in programs is OpenMP 3.0.
-This annotation system provides us with a rich set of pragmas that we can use
-to indicate to compiler and runtime environment which tasks must be created.
+This annotation system provides us with a set of pragmas that indicate to compiler
+and runtime environment when and how tasks must be created.
 We describe below which annotations we are using, and explain, informally, their
 semantics.
-A full overview of the syntax and semantics of these annotations is publicly
+Full overviews of the syntax and semantics of these annotations is publicly
 available\footnote{For a quick overview, we refer the reader to the leaflet
 ``Summary of OpenMP 3.0 C/C++ Syntax", which is made available by the OpenMP
-group.}.
-
+group.}; hence, we shall not dive into their details.
+%
 \begin{compactitem}
-\item \textsf{task} {\em clauses}: creates a new task, according to the
-parameters specified in the {\em clauses} list:
+\item \textsf{parallel} (\textit{clauses}): forms a team of threads
+which will execute the marked program region in parallel.
+\item \textsf{single} (\textit{clauses}): specifies that a
+program region must be executed by one thread in the team.
+\item \textsf{task} (\textit{clauses}): creates a new task.
+\item \textsf{taskwait}: defines a synchronization point where
+threads must wait for the completion of child tasks.
+\end{compactitem}
+%
+Some pragmas are associated with lists of clauses.
+There are several of these clauses available in OpenMP 3.0; however, we only use
+the following:
 \begin{compactitem}
@@
 executed.
-\item \fer{Pedro/Gleison: can you guys continue this list?}
-\end{compactitem}
-\item \textsf{taskwait}: forces tasks to synchronize at the point of annotation.
+\item \textsf{untied}: if a task has this modifier, then its associated code can
+be executed by more than one thread; e.g., threads might alternate execution due
+to preemption.
+\item \textsf{depend}($\mathit{in}/\mathit{out}/\mathit{inout}$):
+determine if data is read ($\mathit{in}$), written ($\mathit{out}$) or both
+within a task region; thus, effectively setting dependences among tasks.
+\item \textsf{depend}({\em condition}): this clause defines the conditions
+under which a task is allowed to create threads.
+We use it to enforce the cost model.
 \end{compactitem}

### 2018-01-24 docs/ACM/paper.tex
worked on section 3.1 of the paper

@@
 \paragraph{The annotation zoo.}
-Our equipment of choice to reveal task parallelism in programs is OpenMP 3.0.
+Our equipment of choice to reveal task parallelism in programs is OpenMP 4.0.
 This annotation system provides us with a set of pragmas that indicate to compiler
@@
 available\footnote{For a quick overview, we refer the reader to the leaflet
-``Summary of OpenMP 3.0 C/C++ Syntax", which is made available by the OpenMP
+``Summary of OpenMP 4.0 C/C++ Syntax", which is made available by the OpenMP
 group.}; hence, we shall not dive into their details.
@@
 Some pragmas are associated with lists of clauses.
-There are several of these clauses available in OpenMP 3.0; however, we only use
+There are several of these clauses available in OpenMP 4.0; however, we only use
 the following:
@@
 be executed by more than one thread; e.g., threads might alternate execution due
-to preemption.
+to preemption and load balancing.
 \item \textsf{depend}($\mathit{in}/\mathit{out}/\mathit{inout}$):
@@
 within a task region; thus, effectively setting dependences among tasks.
-\item \textsf{depend}({\em condition}): this clause defines the conditions
+\item \textsf{if}({\em condition}): this clause defines the conditions
 under which a task is allowed to create threads.
@@
 the \emph{Program Dependence Graph (PDG)}. The key intuition behind
-finding potential tasks relies on a concept that we call \emph{Helices}. A \emph{Helix}
-is a set of nodes in the PDG that depend on a Strong Connected Component (SCC) but \emph{do not
-integrate the SCC}. Strong Connected Components in the Dependence Graph represent statically
-detected iteration dependence, so it arises with loops or with recursive patterns (when the Graph is
-interprocedural).  Figure~\ref{fig:helix}  shows what represents a \emph{Helix}.
-The insight behind \emph{Helices} is that they represent instructions that are deemed
-to repeat more than once and, since they do not have a cycle, they can be executed in parallel.
+finding potential tasks relies on a concept that we call \emph{Helices}.
 
-Therefore, the first step in the algorithm to find tasks is to map these \emph{Helices}
+\begin{definition}[Helix]
+\label{def:helix}
+Given a set $S$ of strongly connected nodes in the Dependence Graph $G$, a set of nodes $H$ is a Helix if, and only if:
+\begin{itemize}
+\item $H \subset \bigcup_i N_i[S]$;
+\item $H  \cap S = \emptyset$;
+\item $H$ is connected and maximal.
+\end{itemize}
+\end{definition}
+
+We can view a \emph{Helix} as a set of nodes in the PDG that depends on a Strongly Connected Component
+(SCC) but \emph{do not integrate the SCC}. That means helices are all those subgraphs that depend on
+the SCC and do not form a cyclic dependence with the SCC itself.
+
+Statically, a Strongly Connected Component in the PDG represents iteration dependence, so it
+arises due to loops or recursive patterns, should the PDG is interprocedural. The insight behind 
+\emph{Helices} is that they represent instructions that are deemed to be executed more than once
+for they depend on a cyclic dependence (the SCC), and, since they do not integrate the SCC, they can
+be executed in parallel.
+
+Thus, the first step in the algorithm to find tasks is to map these \emph{Helices}
 into program regions. The algorithm goes through the Dependence Graph looking for \emph{Helices}
@@
 
-After finding potential task regions, next is the \emph{expansion} step. We expand the region to a larger 
-one as long as two requisites are met:
+After finding potential task regions, the next critical step is the \emph{expansion}.
 
-\begin{enumerate}  
-\item Input and output dependencies are never increased;
-\item The potential parallelism is never reduced.
-\end{enumerate}
+\begin{definition}[Region expansion]
+\label{def:expansion}
+A task region $R$ can be expanded into a larger region $R'$ if, and only if:
+\begin{itemize}
+\item $|M(R')| \leq |M(R)|$, in which $M(R)$ and $M(R')$ are the set of input and output memory
+dependences in regions $R$ and $R'$ respectively.
+\item $R'$ is still inside a loop or a cyclic construct.
+\end{itemize}
+\end{definition}
 
@@
 
-\begin{itemize}
-\item Performance
-\item Optimizations
-\item Versatility
-\item Applicability
-\item Practicality
-\end{itemize}
+\begin{compactitem}
+\item \textsf{Performance}: we run \Taskminer on the BOTS Benchmark and show that the programs annotated by taskminer are sometimes as fast as programs annotated manually, and never slower than their sequential counterparts, thus proving it to be a conservative and useful technique.
+\item \textsf{Optimizations}: we show some optimizations that can be applied to \Taskminer in order to improve performance of the annotated programs.
+\item \textsf{Versatility}: we demonstrate \Taskminer's versatility when it is able to find tasks in several different program paradigms.
+\item \textsf{Applicability}: we run \Taskminer on larger benchmarks to show the potential of finding task parallelism in big applications.
+\item \textsf{Practicality}: here we present \Taskminer's runtime and show that it can be easily used by a programmer to find task parallelism in applications.
+We evidence \Taskminer's practicality when compared to the method of manually finding parallelism, determining data dependences annotating the program.
+\end{compactitem}
 
@@
 %We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
-\textbf{\textit{Versatility}}.
+\textbf{\textit{Applicability}}.
 

### 2018-01-24 TaskMiner.cpp

@@ -36,6 +36,9 @@ static cl::opt<int> NUMBER_OF_THREADS("N_THREADS",
 static cl::opt<int> RUNTIME_COST("RUNTIME_COST",
   cl::desc("Minimum cost per task (in instructions) in the runtime"), cl::NotHidden);
 
+static cl::opt<bool, false> ALLOW_NONVOID("ALLOW_NONVOID",
+  cl::desc("Allow non-void function calls to be turned into tasks."), cl::NotHidden);
+
 STATISTIC(NTASKS, "Total number of tasks");
 STATISTIC(NFCALLTASKS, "Total number of function call (non-recursive) tasks");
 STATISTIC(NRECURSIVETASKS, "Total number of recursive tasks");
@@ -44,7 +47,6 @@ STATISTIC(NINSTSTASKS, "Total number of task instruction costs");
 STATISTIC(NINDEPS, "Total number of task input dep costs");
 STATISTIC(NOUTDEPS, "Total number of task output dep costs");
 STATISTIC(NMODULEINSTS, "Total number of module instructions");
-
 
 void TaskMiner::getAnalysisUsage(AnalysisUsage &AU) const
 {
@@ -292,8 +294,8 @@ void	TaskMiner::mineFunctionCallTasks()
 			auto srcRW = e->getSrc()->getItem();
 			auto dstRW = e->getDst()->getItem();
 			indirectRecursion=false;
-			//Check if they're indirect recursion 
-			//(if both src and dst are in the same SCC)
+			// Check if they're indirect recursion 
+			// (if both src and dst are in the same SCC)
 			for (auto scc : SCCs)
 			{
 				if ((scc->getNodeIndex(srcRW) != -1)
@@ -306,22 +308,24 @@ void	TaskMiner::mineFunctionCallTasks()
 			CallInst* CI = callInsts[e];
 
 			if (!CI)
-				continue;
-			
+				continue;			
+
 			if (function_tasks.find(CI->getParent()->getParent()) != function_tasks.end())
 				continue;
 
 			if (topLevelRecCalls.find(CI) != topLevelRecCalls.end())
+				continue;
+		
+			if (!CI->getCalledFunction()->getReturnType()->isVoidTy())
 				continue;
 
 			bool hasLoop = srcRW->hasLoop;
 			if ((srcRW->F != dstRW->F)
 				&& (hasLoop)
 				&& (!indirectRecursion)
[…]

### 2018-01-24 tests/benchmarks/sample/expansion/expansion.c

@@ -1,0 +1,76 @@
+
+#include <stdlib.h>
+#include <stdio.h>
+
+
+void g();
+void f();
+
+//loop expansion
+void loop(int* V, int N)
+{
+	int i, j;
+	for (i = 0; i< N; i++)
+	{
+		for (j = 0; j < N; j++)
+		{
+			V[i] = j%i | 0x0000FFFF;
+		}
+		//eventual computations
+		V[i] += i*j;
+	}
+}
+
+//region expansion
+void region(int* V, int N)
+{
+	int i;
+	for (i = 0; i< N; i++)
+	{
+		if (V[i]%i > 3)
+		{
+			V[i] -= i;
+		}
+		else
+		{
+			V[i] -= 2*i;
+		}
+		V[i] += i*i;
+	}
+}
+
+//fcallexpansion case 1
+void fcall_1(int* V, int N)
+{
+	int i, j;
+	for (i = 0; i< N; i++)
+	{
+		for (j = 0; j < N; j++)
+		{
+			g();
+		}
+		V[i] += i*j + i%j;
+	}
+}
+
+//fcallexpansion case 2
+void fcall_2(int* V, int N)
+{
+	int i, j;
+	for (i = 0; i< N; i++)
+	{
+		g();
+		for (j = 0; j < N; j++)
+		{
+			f();
+			V[i] += i*j;
+		}
+	}
+}
+
+int main(int argc, char const *argv[])
+{
+
+
+}
+

### 2018-01-24 tests/benchmarks/sample/memregions/memregions.c

@@ -1,7 +1,7 @@
 #include <stdlib.h>
 #include <stdio.h>
 
-int foo(int* U, int* V, int N, int M) 
+int goo(int* U, int* V, int N, int M) 
 {
 	int i, j;
 	for(i = 0; i < N; i++) 
@@ -16,13 +16,48 @@ int foo(int* U, int* V, int N, int M)
 	return 1;
 }
 
+int foo(int* v, int i)
+{
+	if (i%4)
+	{
+		*v = v || i;
+		return i;
+	}
+	else
+	{
+		*v = v || 4;
+		return 4;
+	}
+}
+
+void doax5(int N) {
+	int v[N];
+	int i, x=0;
+	v[0] = 0;
+	v[1] = 1;
+	for (i=2; i<N; i++)
+	{
+		if (i % 2)
+		{
+			x = foo(&v[i-1], i);
+		}
+		else
+		{
+			x = foo(&v[i-2], i);
+		}
+		v[i] = foo(&v[i-1], x);
+	}
+}
+
+
 int main(int argc, char const *argv[])
 {
 	int N = 100;
 	int M = 100;
 	int* U = (int*) malloc(sizeof(int)*M);
 	int* V = (int*) malloc(sizeof(int)*N*M);
-	foo(U, V, N, M);
+	goo(U, V, N, M);
+	doax5(N);
 
 	return 0;
 }

### 2018-01-24 tests/benchmarks/sample/memregions/memregions_MI.c

@@ -1,8 +1,8 @@
-#include <omp.h>
 #include <stdlib.h>
 #include <stdio.h>
+#include <omp.h>
 
-int foo(int* U, int* V, int N, int M) 
+int goo(int* U, int* V, int N, int M) 
 {
 	int i, j;
 	#pragma omp parallel
@@ -20,13 +20,52 @@ int foo(int* U, int* V, int N, int M)
 	return 1;
 }
 
+int foo(int* v, int i)
+{
+	if (i%4)
+	{
+		*v = v || i;
+		return i;
+	}
+	else
+	{
+		*v = v || 4;
+		return 4;
+	}
+}
+
+void doax5(int N)
+{
+	int v[N];
+	int i, x=0;
+	v[0] = 0;
+	v[1] = 1;
+	for (i=2; i<N; i++)
+	{
+		if (i % 2)
+		{
+			#pragma omp task untied depend(in: v[i-1]) default(shared)
+			foo(&v[i-1], i);
+		}
+		else
+		{
+			#pragma omp task untied depend(in: v[i-2]) default(shared)
+			foo(&v[i-2], i);
+		}
+		#pragma omp task untied depend(in: v[i-1]) depend(out: v[i]) default(shared)
+		v[i] = foo(&v[i-1], i);
+	}
+}
+
+
 int main(int argc, char const *argv[])
 {
 	int N = 100;
 	int M = 100;
 	int* U = (int*) malloc(sizeof(int)*M);
 	int* V = (int*) malloc(sizeof(int)*N*M);
-	foo(U, V, N, M);
+	goo(U, V, N, M);
+	doax5(N);
 
 	return 0;
 }

### 2018-01-24 tests/temp/doax/doax5.cpp

@@ -8,17 +8,29 @@ using namespace std;
 
 #define N 		100
 
+int foo(int* v);
+
+int goo(int* v);
+
 void doax5() {
 	int v[N];
 
 	v[0] = 0;
 	v[1] = 1;
-	for (int i=2, x=0; i<N; i++) {
+	for (int i=2, x=0; i<N; i++)
+	{
 		if (i % 2)
-			x = v[i-1];
+		{
+			#pragma omp task depend(in:v[i-1]) default(shared)
+			x = foo(&v[i-1]);
+		}
 		else
-			x = v[i-2];
+		{
+			#pragma omp task depend(in:v[i-2]) default(shared)
+			x = foo(&v[i-2]);
+		}
 
-		v[i] = x;
+		#pragma omp task depend(in:v[i-2]) depend(out:v[i]) default(shared)
+		v[i] = goo(&v[i-1]);
 	}
 }

### 2018-01-26 docs/ACM/paper.tex
added section 3.1

@@
 
-The algorithm to find tasks is illustrated in Figure \ref{fig:alg_main}. It uses
-information of two abstract program structures: the \emph{Control Flow Graph (CFG)} and
-the \emph{Program Dependence Graph (PDG)}. The key intuition behind
-finding potential tasks relies on a concept that we call \emph{Helices}.
+The {\Taskminer} algorithm is illustrated in FIgure \ref{fig:alg_main}. 
+It uses information from both the \emph{Control Flow Graph} and
+the \emph{Dependence Graph}. It relies on the concepts of
+\emph{windmills} and \emph{helices} (Definitions \ref{def:helix} and \ref{def:windmill}).
+
+\begin{definition}[Windmill]
+\label{def:windmill}
+Given a set $S$ of strongly connected nodes in the program \emph{Dependence Graph} $G$, 
+a windmill $W$ is defined as:
+$$W = \bigcup_i N_i[S]$$
+\end{definition}
+
+Statically, a strongly connected set $S$ in the  \emph{Dependence Graph} $G$ represents cyclic dependence between instructions in any iterative construct.
+It arises from a loop in the program or, if $G$ is interprocedural,
+from a recursive pattern.
+
+Let $L = \{S_{1}, S_{2}, ..., S_{n}\} \subset W$ be the list of $n$ strongly connected sets contained
+in a windmill $W$. We call $S_{b}$ to be a \emph{windmill base} if $\forall S_{i} \subset L$, $S_{b} \geq S_{i}$ in any topological sorting of $G$.
 
@@
 \label{def:helix}
-Given a set $S$ of strongly connected nodes in the Dependence Graph $G$, a set of nodes $H$ is a Helix if, and only if:
+Given a windmill $W$  and a windmill base $S \subset W$ in the \emph{Dependence Graph} $G$, a set of nodes $H$ is a Helix if, and only if:
 \begin{itemize}
-\item $H \subset \bigcup_i N_i[S]$;
-\item $H  \cap S = \emptyset$;
+\item $H \subset W$;
+\item $H  \cap S_{b} = \emptyset$;
 \item $H$ is connected and maximal.
@@
 
-We can view a \emph{Helix} as a set of nodes in the PDG that depends on a Strongly Connected Component
-(SCC) but \emph{do not integrate the SCC}. That means helices are all those subgraphs that depend on
-the SCC and do not form a cyclic dependence with the SCC itself.
+We can view a \emph{Helix} as a set of nodes in the \emph{Dependence Graph}
+that depends on a strongly connected set which is a \emph{windmill base}.
+That means helices are all those subgraphs that depend on
+the \emph{windmill base} but do not form a cyclic dependence with it.
+Figure \ref{fig:helix} illustrates both concepts.
 
-Statically, a Strongly Connected Component in the PDG represents iteration dependence, so it
-arises due to loops or recursive patterns, should the PDG is interprocedural. The insight behind 
-\emph{Helices} is that they represent instructions that are deemed to be executed more than once
-for they depend on a cyclic dependence (the SCC), and, since they do not integrate the SCC, they can
-be executed in parallel.
+The insight behind  \emph{Helices} is that they represent instructions that 
+are deemed to be executed more than once, for they depend on a cyclic
+dependence (\emph{windmill base}), and, since they do not form a strongly
+connected set itself, they can be executed in parallel.
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=1\columnwidth]{images/helix}
+\caption{\emph{Windmills} and \emph{Helices} corresponding to the sample code above.
+We see the \emph{windmill} 
+$W = \{A, B, C, D, E, F, G, H\}$, the windmill base $S_{b} = \{A, B, C\}$ 
+and two \emph{helices} $H_{1} = \{H\}$ and $H_{2} = \{D, E, F, G\}$.  Note
+that there are more than one strongly connected, but only of them is a
+base, which is the one at the top topologically.}
+\label{fig:helix}
+\end{center}
+\end{figure}
 
 Thus, the first step in the algorithm to find tasks is to map these \emph{Helices}
-into program regions. The algorithm goes through the Dependence Graph looking for \emph{Helices}
-and then finds the minimal covering region for each \emph{Helix}. These minimal regions
-are later going to be annotated as tasks in the original program, should they fit a cost model.
+into program regions. The algorithm scans through the \emph{Dependence Graph}
+looking for \emph{Helices} and then finds the minimal covering region for each \emph{Helix}.
+These minimal regions are later going to be annotated as tasks in the original
+program, should they fit a cost model.
 
@@
 
-\begin{figure}[t!]
+Figure \ref{fig:expand_alg} illustrate the algorithm of expansion. It simply tries to expand while
+all the conditions in Definition \ref{def:expansion} are met, and then halts
+when they are not. After this process, {\Taskminer} ends up with a list
+of potential \emph{task regions}, which will then pass under
+a series of operations prior to the annotation to source code, the 
+ultimate step.
+
+\begin{figure}[h]
 \begin{center}
@@
 
+%I don't know much of this part. I asked gleison to write me a paragraph and
+%then I'll review it and try to write something here.
+
 \subsection{Estimating the Profitability of Tasks}
 \label{sub:profit}
+
+%We need to discuss the THRESHOLD. Are we going to use
+%César's experiments at Unicamp concerning the different runtimes? 
+%Because if yes we need to think on how to write it.
 
@@
 
+%I can work on that on the weekend!
+
 \subsection{Separating Private from Shared Variables}
@@
 
+%I can work on that on the weekend!
+
 \subsection{Mapping IR onto Source Code}
 \label{sub:ir}
+
+%I asked gleison and he'll sit with me to explain everything ,
+%how it's done, and then I'll write it here.
 

### 2018-01-26 tests/benchmarks/sample/format/format.c

@@ -1,0 +1,16 @@
+#include <stdlib.h>
+
+void veryHugeFunction(int a, int b, int c, int d, int e, int f, int g, int h, int j, int *s, char ch);
+
+void veryHugeFunction(int a, int b, int c, int d, int e, int f, int g, int h, int j, int *s, char ch) {
+  if (a == 0 || d == 10 || a + b + c + d + e + f + g + h + j != s[1] || ch != 's') // comment
+  {
+    return;
+  }
+
+  int hugevariabletextlength = b + c + e;
+
+  veryHugeFunction(a--, b--, c--, d++, hugevariabletextlength, f++, g--, h--, j--, s, ch);
+}
+
+int main(int argc, char const *argv[]) { return 0; }

### 2018-01-26 docs/ACM/paper.tex
added comments

@@
 
-%I don't know much of this part. I asked gleison to write me a paragraph and
-%then I'll review it and try to write something here.
+\pedro{I don't know much of this part. I asked gleison to write me a paragraph and
+then I'll review it and try to write something here.}
 
@@
 
-%We need to discuss the THRESHOLD. Are we going to use
-%César's experiments at Unicamp concerning the different runtimes? 
-%Because if yes we need to think on how to write it.
+\pedro{We need to discuss the THRESHOLD. Are we going to use
+César's experiments at Unicamp concerning the different runtimes? 
+Because if yes we need to think on how to write it.}
 
@@
 
-%I can work on that on the weekend!
-
 \subsection{Separating Private from Shared Variables}
 \label{sub:variance}
-
-%I can work on that on the weekend!
 
@@
 
-%I asked gleison and he'll sit with me to explain everything ,
-%how it's done, and then I'll write it here.
+\pedro{I asked gleison and he'll sit with me to explain everything ,
+how it's done, and then I'll write it here.}
 

### 2018-01-27 docs/ACM/paper.tex
Definition of Windmill.

@@
 
-\begin{figure}[h]
+\begin{figure}[b]
 \begin{center}
@@
 Syntactically, memory regions are described by program variables and/or pointers
-plus ranges of offsets that these pointers are allowed to dereference.
+plus ranges of dereferensable offsets.
 Given two tasks: $T_1 = (G_1, M_{i1}, M_{o1})$ and $T_2 = (G_2, M_{i2}, M_{o2})$,
@@
 A set $T$ of $n$ tasks is a correct parallelization of a program $P$ if:
-\begin{compactitem}
+\begin{compactenum}
 \item $T$ does not contain cyclic dependence relations;
@@
 relations, leads to the same results as the sequential execution of $P$.
-\end{compactitem}
+\end{compactenum}
 \end{definition}
@@
 \label{ex:regions}
-\fer{XX Add an example to describe the notions of regions and dependences.
-The best is to modify one of the programs in Section 2, so that we can refer to
-that program.
-Pedro, can you think about it and propose something?}
+Below we have two tasks, $T_{\mathit{foo}} = (\mathsf{foo}, \{\mathsf{v[i - 1]}\},
+\{v[i]\})$ and $T_{\mathit{bar}} = (\mathsf{bar}, \{v[i]\}, \{\})$.
+Dependencies are identified via the \textsf{depend} clause.
+In this example, each SESE region is formed by one function call:
 \end{example}
+
+\includegraphics[width=1\columnwidth]{images/ex_depends}
 
@@
 
-The {\Taskminer} algorithm is illustrated in FIgure \ref{fig:alg_main}. 
-It uses information from both the \emph{Control Flow Graph} and
-the \emph{Dependence Graph}. It relies on the concepts of
-\emph{windmills} and \emph{helices} (Definitions \ref{def:helix} and \ref{def:windmill}).
+% Windmills and vanes
+A {\em task candidate} is a program region that can run in parallel with the
+rest of the program.
+To identify task candidates, we rely on the structure of the program's
+control flow graph.
+To this end, we identify, subgraphs in the CFG called {\em windmills}, a term
+coined by Rideau {\em et al.}~\cite{Rideau08} to describe structural relations
+between register copies.
+We adopt a slightly more general definition than Rideaus'; however, the
+graphical shape of our graphs remain similar:
 
@@
 \label{def:windmill}
-Given a set $S$ of strongly connected nodes in the program \emph{Dependence Graph} $G$, 
-a windmill $W$ is defined as:
-$$W = \bigcup_i N_i[S]$$
+A windmill is a graph $G_w = G_c \cup G_{v1} \cup \ldots \cup G_{vn}$ formed by
+a strongly connected component $G_c$, its center, plus $n$ components (not
+necessarily strong) $G_{vi}$, the vanes, such that:
+\begin{compactenum}
+\item for any topological ordering of $G_w$, and nodes $n_c \in G_c$,
+$n_v \in G_{vi}$, we have $n_c$ ahead of $n_v$;
+\item for any $i$ and $j$, $1 \leq i < j \leq n$, $G_{vi}$ and $G_{vj}$ do not
+share vertices.
+\end{compactenum}
 \end{definition}

### 2018-01-28 docs/ACM/paper.tex
Adding discussion about windmills.

@@
 % Windmills and vanes
-A {\em task candidate} is a program region that can run in parallel with the
-rest of the program.
-To identify task candidates, we rely on the structure of the program's
-control flow graph.
-To this end, we identify, subgraphs in the CFG called {\em windmills}, a term
-coined by Rideau {\em et al.}~\cite{Rideau08} to describe structural relations
-between register copies.
+A {\em task candidate} is a set of program statements that can run in parallel
+with the rest of the program.
+To identify task candidates, we rely on the program's
+{\em Dependence Graph}.
+For completeness, Definition~\ref{def:pdg} revisits this notion.
+
+\begin{definition}[Program Dependence Graph -- \cite{Ferrante87}]
+\label{def:pdg}
+Given a program $P$, its PDG contains one vertex for each statement $s \in P$.
+There exists an edge from $s_1$ to $s_2$ if the latter depends on the former.
+Statement $s_2$ is {\em data-dependent} on $s_1$ if it reads data that $s_1$
+writes.
+It is {\em control dependent} on $s_1$ if $s_1$ determines the outcome of a
+branch, and depending on this outcome, we might execute $s_2$ or not.
+\end{definition}
+
+Task candidates are vanes in windmills.
+{\em Windmills} are a family of graphs.
+To the best of our knowledge, the term was coined by Rideau
+{\em et al.}~\cite{Rideau08} to describe structural relations between register
+copies.
+Our windmills exist as subgraphs of the program's dependence graph.
 We adopt a slightly more general definition than Rideaus'; however, the
-graphical shape of our graphs remain similar:
+metaphor that gave origin to the name: the shape of the graphs, is still
+unmistakable:
 
-\begin{definition}[Windmill]
+\begin{definition}[Windmill -- \cite{Rideau08}]
 \label{def:windmill}
@@
 
-Statically, a strongly connected set $S$ in the  \emph{Dependence Graph} $G$ represents cyclic dependence between instructions in any iterative construct.
-It arises from a loop in the program or, if $G$ is interprocedural,
-from a recursive pattern.
-
-Let $L = \{S_{1}, S_{2}, ..., S_{n}\} \subset W$ be the list of $n$ strongly connected sets contained
-in a windmill $W$. We call $S_{b}$ to be a \emph{windmill base} if $\forall S_{i} \subset L$, $S_{b} \geq S_{i}$ in any topological sorting of $G$.
-
-\begin{definition}[Helix]
-\label{def:helix}
-Given a windmill $W$  and a windmill base $S \subset W$ in the \emph{Dependence Graph} $G$, a set of nodes $H$ is a Helix if, and only if:
-\begin{itemize}
-\item $H \subset W$;
-\item $H  \cap S_{b} = \emptyset$;
-\item $H$ is connected and maximal.
-\end{itemize}
-\end{definition}
-
-We can view a \emph{Helix} as a set of nodes in the \emph{Dependence Graph}
-that depends on a strongly connected set which is a \emph{windmill base}.
-That means helices are all those subgraphs that depend on
-the \emph{windmill base} but do not form a cyclic dependence with it.
-Figure \ref{fig:helix} illustrates both concepts.
-
-The insight behind  \emph{Helices} is that they represent instructions that 
-are deemed to be executed more than once, for they depend on a cyclic
-dependence (\emph{windmill base}), and, since they do not form a strongly
-connected set itself, they can be executed in parallel.
-
-\begin{figure}[t!]
+\begin{figure}[h]
 \begin{center}
-\includegraphics[width=1\columnwidth]{images/helix}
-\caption{\emph{Windmills} and \emph{Helices} corresponding to the sample code above.
-We see the \emph{windmill} 
-$W = \{A, B, C, D, E, F, G, H\}$, the windmill base $S_{b} = \{A, B, C\}$ 
-and two \emph{helices} $H_{1} = \{H\}$ and $H_{2} = \{D, E, F, G\}$.  Note
-that there are more than one strongly connected, but only of them is a
-base, which is the one at the top topologically.}
-\label{fig:helix}
+\includegraphics[width=1\columnwidth]{images/ex_windmill}
+\caption{Examples of program dependence graphs.
+Nodes that form centers of windmills are coloured in gray.
+Data-dependence edges are solid; control-dependence edges are dashed.
+Vanes of windmills appear within dotted boxes.
+(a) PDG for Figure~\ref{fig:ex_book_filter};
+(b) PDG for Figure~\ref{fig:ex_Regions}}
+\label{fig:ex_windmill}
 \end{center}
@@
 
-Thus, the first step in the algorithm to find tasks is to map these \emph{Helices}
-into program regions. The algorithm scans through the \emph{Dependence Graph}
-looking for \emph{Helices} and then finds the minimal covering region for each \emph{Helix}.
-These minimal regions are later going to be annotated as tasks in the original
-program, should they fit a cost model.
+Figure~\ref{fig:ex_windmill} shows two program dependence graphs, highlighting
+windmills and their vanes.
+The structure of windmills naturally leads to task candidates.
+Vanes correspond to program parts that are likely to be executed
+several times, because they sprout from a loop -- the center of the windmill.
+Two different executions of the same vane can run in parallel.
+This is a property of the PDG, and one of the original motivations behind its
+design.
+These two different executions can be seen as two instances of the same
+structure (the vane), coming out of the same windmill center.
+A topological ordering of the dependence graph does not impose any order among
+these two hypothetical replicas of the same structure.
 
-After finding potential task regions, the next critical step is the \emph{expansion}.
+Windmills gives us structural properties to identify tasks.
+We can easily find them via a depth-search traversal of the program dependence
+graph, for instance.
+However, not every windmill lead us to profitable tasks.
+Furthermore, some windmills simply cannot be annotated, due to structural 
+incompatibilities between the program dependence graph and its source code.
+We deal with the first shortcoming in Section~\ref{sub:profit}; the latter is
+the subject of Section~\ref{sub:ir}.
+
+\subsection{Finding Symbolic Bounds of Arrays}
+\label{sub:symb}
+
+\pedro{I don't know much of this part. I asked gleison to write me a paragraph and
+then I'll review it and try to write something here.}
+
+\subsection{Estimating the Profitability of Tasks}
+\label{sub:profit}
+
+\pedro{We need to discuss the THRESHOLD. Are we going to use
+César's experiments at Unicamp concerning the different runtimes? 
+Because if yes we need to think on how to write it.}
+
+\subsection{Limiting the Creation of Recursive Tasks}
+\label{sub:rec}
+
+\subsection{Separating Private from Shared Variables}
+\label{sub:variance}
+
+\subsection{Mapping IR onto Source Code}
+\label{sub:ir}
 
@@
 \end{figure}
-
-\subsection{Finding Symbolic Bounds of Arrays}
-\label{sub:symb}
-
-\pedro{I don't know much of this part. I asked gleison to write me a paragraph and
-then I'll review it and try to write something here.}
-
-\subsection{Estimating the Profitability of Tasks}
-\label{sub:profit}
-
-\pedro{We need to discuss the THRESHOLD. Are we going to use
-César's experiments at Unicamp concerning the different runtimes? 
-Because if yes we need to think on how to write it.}
-
-\subsection{Limiting the Creation of Recursive Tasks}
-\label{sub:rec}
-
-\subsection{Separating Private from Shared Variables}
-\label{sub:variance}
-
-\subsection{Mapping IR onto Source Code}
-\label{sub:ir}
-
-\pedro{I asked gleison and he'll sit with me to explain everything ,
-how it's done, and then I'll write it here.}
 

### 2018-01-28 docs/ACM/paper.tex
Adding discussion about symbolic range analysis.

@@
 
-\pedro{I don't know much of this part. I asked gleison to write me a paragraph and
-then I'll review it and try to write something here.}
+% Why this is necessary
+To produce the annotations that will lead to the creation of a task $T = (G, M_i,
+M_o)$, we need to determine the memory regions $M_i$ that $T$ reads, and the
+memory regions $M_o$ that it writes.
+Memory regions consist of pointers, plus ranges of addresses that these pointers
+can dereference.
+Example~\ref{ex:mem_reg} illustrates this notion.
+To determine precise bounds to memory regions, we resort to an old ally of
+compiler writers: the {\em Symbolic Range Analysis}, a concept that
+Definition~\ref{def:sra} formalizes.
+
+\begin{example}[Memory Region]
+\label{ex:mem_reg}
+The statement \textsf{U[i] += V[i*N + j]}, at line 9 of
+Figure~\ref{fig:ex_Regions} contains two memory accesses: \textsf{U[i]} and
+\textsf{V[i*N + j]}.
+The first covers the memory region $[\mathtt{\&}\mathsf{U},
+\mathtt{\&}\mathsf{U} + (\mathsf{M} - 1) \times \mathsf{sizeof}(\mathtt{int})]$.
+The other covers the region
+$[\mathtt{\&}\mathsf{V} + \mathsf{N} \times \mathsf{sizeof}(\mathtt{int}), \mathtt{\&}\mathsf{V} + ((\mathsf{i} \times \mathsf{M} + j) - 1) \times \mathsf{sizeof}(\mathtt{int})]$.
+There is no code in Figure~\ref{fig:ex_Regions} that depends on the
+loop in lines 8-10.
+Thus, a task annotation must only account for the input dependence, e.g., the
+access on \textsf{V}.
+That is why the \textsf{depend} clause in line 6 contains a reference to this
+region.
+\end{example}
+
+\begin{definition}[Symbolic Range Analysis]
+\label{def:sra}
+This is a form of abstract interpretation that associates
+an integer variable $v$ with a {\em Symbolic Interval} $R(v) = [l, u]$, where
+$l$ and $u$ are {\em Symbolic Expressions}.
+A symbolic expression $E$ is defined by the grammar below, where $s$ is a
+{\em program symbol}:
+\renewcommand{\arraystretch}{0.9}
+\[
+\begin{array}{rcl}
+E & ::= & z \ \ | \ \ s \ \ | E + E \ \ | \ \ E \times E \ \ | \ \  \mbox{min}(E, E) \ \ | \\
+&  & \mbox{max}(E, E) \ \ | -\infty \ \ | \ \ +\infty
+\end{array}
+\]
+\end{definition}
+
+% How we do it.
+The program symbols mentioned in Definition~\ref{def:sra} are names that cannot be
+reconstruct as functions of other names.
+Examples include global variables, function arguments, and values returned by
+external functions.
+Symbolic range analysis is not a contribution of this paper.
+There are several different implementations publicly available, and we have
+adopted the one in the \dawn{} compiler~\cite{Mendonca17}, which, itself,
+reuses work from Blume {\em et al.}~\cite{Blume94}.
+The only extensions that we have added into \dawn's implementation was
+the ability to handle \textsf{structs}.
+Therefore, we shall not provide further details about part of our work.
+To understand the rest of this paper, it suffices to know that this implementation
+is sufficiently solid to handle the entire C99 language, always terminates, and
+runs in time linear on the size of the program's dependence graph.
+Thus, in the worst case, it is quadratic on the number of program variables.
+If a program contains an array access $\textsf{V}[E]$, and we have that
+$R(E) = [l, u]$, then the memory region covered by this access is, at least,
+$[\mathtt{\&}\textsf{V} + l, \mathtt{\&}\textsf{V} + u]$.
+The example below clarifies this observation.
+
+\begin{example}
+\label{ex:sra}
+Symbolic range analysis, when applied onto Figure~\ref{fig:sra}, gives us
+$R(\mathsf{i}) = [0, \mathsf{N} - 1]$, and $R(\mathsf{j}) = [0, \mathsf{M} - 1]$.
+The memory access \textsf{V[i*N + j]} at line 9, when combined with this
+information, yields the symbolic region that appears in the task annotation at
+line 6 of Figure~\ref{fig:ex_Regions}.
+\end{example}
 

### 2018-01-30 docs/ACM/paper.tex
Adding discussion about cost model.

@@
 \usepackage{paralist}
+\usepackage{mathpartir}
 
@@
 
+% Explain the tension between large and small tasks.
+The benefit of creating tasks depend on two factors:
+runtime cost, and parallelism.
+These two factors lead to a sweet spot in the size of tasks, where size is
+measured as the amount of code they contain.
+The smaller the tasks are, the more parallel they tend to be, as a consequence
+of less dependencies.
+However, if tasks are too small, then the performance gained by the extra
+parallelism might not be enough to pay for the cost of managing them.
+On the other hand, if tasks are too big, then we might not obtain enough
+parallelism, because individual tasks still execute sequentially.
+In this paper, we extract the smallest thread above the runtime cost.
+To bestow meaning into this last statement, in what follows we define more
+formally the notions of task size and runtime cost.
+
+\paragraph{Estimating the Size of Tasks.}
+The size of a task is given by its workload, i.e., the number of instructions that
+such task executes.
+The same program region might lead to the creation of tasks with different sizes.
+Therefore, the actual size of a task is only known after the threads finishes
+execution.
+However, to judge if the creation of a task is worth its cost, we must be able to
+approximate its size statically.
+With this goal, we define the notion of static workload estimate:
+
+\begin{definition}[Static Workload Estimate (SWE)]
+\label{def:swe}
+Let $G = G_1 \cup G_2 \cup \ldots \cup G_n$ be a partition of a program's control
+flow graph $G$ into $n$ {\em maximal} hammock regions.
+We define the static workload estimate ($W(G)$) as a real number, such that
+$W(G) = W(G_1) + W(G_2) + \ldots + W(G_n)$.
+\end{definition}
+
+\begin{figure}[t!]
+\begin{small}
+\begin{eqnarray*}
+\begin{tabular}{lc}
+\mbox{(Instruction)} &
+W(\mbox{instr}) = 1
+\\\\
+\mbox{(Sequence)} &
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_2}
+\\\\
+\mbox{(Branch)} &
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
+{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + w_2 + w_3}
+\\\\
+\mbox{(Unknown Lp)} &
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = \mbox{?}}
+{W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
+\\\\
+\mbox{(Known Loop)} &
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = E}
+{W(\mbox{while} (S_1) \ S_2;) = E \times (w_1 + w_2)}
+\end{tabular}
+\end{eqnarray*}
+\end{small}
+\caption{\label{fig:swe}Estimating the cost of tasks.}
+\end{figure}
+
+% Explain how we use symbolic information to compute costs.
+
+% Discuss the expansion algorithm.
+\paragraph{The Task Expansion Algorithm.}
+
 \pedro{We need to discuss the THRESHOLD. Are we going to use

### 2018-01-30 docs/ACM/paper.tex
Adding discussion about cost model.

@@
 
-\section{Solution}
+\section{Solutions}
 \label{sec:sol}
@@
 However, if tasks are too small, then the performance gained by the extra
-parallelism might not be enough to pay for the cost of managing them.
+parallelism might not compensate the cost of managing them.
 On the other hand, if tasks are too big, then we might not obtain enough
@@
 In this paper, we extract the smallest thread above the runtime cost.
-To bestow meaning into this last statement, in what follows we define more
+To bestow meaning into this last statement, in what follows, we define more
 formally the notions of task size and runtime cost.
@@
 The same program region might lead to the creation of tasks with different sizes.
-Therefore, the actual size of a task is only known after the threads finishes
-execution.
+Therefore, the actual size of a task is only known after it finishes execution.
 However, to judge if the creation of a task is worth its cost, we must be able to
 approximate its size statically.
-With this goal, we define the notion of static workload estimate:
+With this goal, we define the notion of {\em Static Workload Estimate}:
 
@@
 Let $G = G_1 \cup G_2 \cup \ldots \cup G_n$ be a partition of a program's control
-flow graph $G$ into $n$ {\em maximal} hammock regions.
-We define the static workload estimate ($W(G)$) as a real number, such that
-$W(G) = W(G_1) + W(G_2) + \ldots + W(G_n)$.
+flow graph $G$ into $n$ {\em disjoint} hammock regions.
+We define the static workload estimate ($W(G)$) as a non-negative real number,
+such that $W(G) = W(G_1) + W(G_2) + \ldots + W(G_n)$.
 \end{definition}
+
+Definition~\ref{def:swe} is too unconstrained: a function $W(G) = 0$ for any $G$
+satisfies it.
+Naturally, we would like to construct $W$ in such a way to approximate the 
+dynamic behavior of programs.
+The compiler-related literature contains heuristics to implement $W$.
+Perhaps, the best-known among these heuristics is the static profiler of
+Wu and Larus~\cite{Wu94}.
+In this paper, we adopted a different approach: we reuse the symbolic range
+analysis of Section~\ref{sub:sra} to augment static data with dynamic information.
+In other words, we use symbolic range analysis to construct expressions that
+represent the number of iterations of loops.
+Similar approach has already been used to decide when to migrate virtual memory
+pages in NUMA architectures~\cite{Piccoli14}.
+OpenMP 3.0 contains syntax to enable the conditional creation of tasks.
+Our symbolic analysis lets us build predicates for such conditional expressions.
+
+\begin{example}
+\label{ex:cond_task}
+The condition in line 7 of Figure~\ref{fig:ex_Regions} determines that tasks will
+only be created if the expression \textsf{5 $\times$ M $<$ WORK\_CUTOOF}
+holds.
+The expression \textsf{5 $\times$ M} is an approximation for the size of the
+task that comprises the loop at lines 8-10.
+\end{example}
 
@@
 \begin{tabular}{lc}
-\mbox{(Instruction)} &
-W(\mbox{instr}) = 1
+\textsc{[Instr]} &
+W(\mbox{instr}) = \mbox{given by the spec.}
 \\\\
-\mbox{(Sequence)} &
+\textsc{[Seq]} &
 \inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_2}
 \\\\
-\mbox{(Branch)} &
+\textsc{[Branch]} &
 \inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
@@
 \\\\
-\mbox{(Unknown Lp)} &
-\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = \mbox{?}}
+\textsc{[LoopInf]} &
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = \infty}
 {W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
 \\\\
-\mbox{(Known Loop)} &
+\textsc{[LoopExp]} &
 \inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = E}
@@
 % Explain how we use symbolic information to compute costs.
+The declarative rules in Figure~\ref{fig:swe} sketches the heuristics that
+we use to compute the SWE for a given hammock region $S$.
+The only rules that deserves comments are \textsc{LoopInf} and
+\textsc{LoopExp}.
+The former applies on loops whose number of iterations we cannot bound via some
+symbolic expression computed statically.
+The latter represents loops that we can analyze using our Symbolic Range Analysis.
+The auxiliary function $X(S)$ returns a symbolic expression that represents
+the range of values covered by the code $S$ that controls the number of
+iterations of the loop.
 

### 2018-02-01 docs/ACM/paper.tex
Added references, citations and skeleton to section 3.4

@@
 Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
-to substantial performance gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
+to substantial performance gains~\cite{Sura16Performance, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
 %\guido{Suppport what?}
@@
 
-% Discuss the expansion algorithm.
-\paragraph{The Task Expansion Algorithm.}
-
 \pedro{We need to discuss the THRESHOLD. Are we going to use
@@
 
-\subsection{Limiting the Creation of Recursive Tasks}
-\label{sub:rec}
-
-\subsection{Separating Private from Shared Variables}
-\label{sub:variance}
-
-\subsection{Mapping IR onto Source Code}
-\label{sub:ir}
+% Discuss the expansion algorithm.
+\paragraph{The Task Expansion Algorithm.}
 
@@
 \end{figure}
+
+\subsection{Limiting the Creation of Recursive Tasks}
+\label{sub:rec}
+
+Although the OpenMP runtime guarantees correctness, its scheduling policy
+is heavily jeopardized by the excessive queueing up of tasks. Specifically, algorithms
+such as \emph{SparseLU} and \emph{FFT} can suffer bloat because of
+too many tasks in the Task Graph.  \cite{Kenjiro17}.
+
+\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
+(1) the parent is a long for loop creating a large number of children, 
+all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
+(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
+It imposes an upper bound for the ready task queue of a worker; a worker 
+is discouraged to create too many tasks ready on the queue"}.
+
+To solve this problem, we conservatively limit the number of tasks
+that can be created tied to the same Task Region. We do that by two means:
+(1) limiting the creation of recursive tasks by depth; (2) limiting the creation of 
+tasks in the whole program.
+
+Consider the FFT example, shown in Figure X.
+
+\pedro{Show FFT example}
+
+\pedro{Explain that the setting is conservative and thus the parameter of control
+(max recursion depth and total number of tasks) can be easily switched by the
+user, or even completely disabled.}
+
+\subsection{Separating Private from Shared Variables}
+\label{sub:variance}
+
+\subsection{Mapping IR onto Source Code}
+\label{sub:ir}
 
@@
 
+\pedro{As future work, we plan on performing Autotuning on {\Taskminer} to find good default parameters.
+Autotuning works for data-flow applications have been already done in \cite{Trancoso17, Emani15}}.
+
 \bibliography{references}

### 2018-02-02 docs/ACM/paper.tex
Normalizing references.

@@
 Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
-to substantial performance gains~\cite{Sura16Performance, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
+to substantial performance gains~\cite{Martineau16, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
 %\guido{Suppport what?}
@@
 such as \emph{SparseLU} and \emph{FFT} can suffer bloat because of
-too many tasks in the Task Graph.  \cite{Kenjiro17}.
+too many tasks in the Task Graph\cite{Huynh17}.
 

### 2018-02-02 docs/ACM/paper.tex
Adding one more citation to Sura.

@@
 Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
-to substantial performance gains~\cite{Martineau16, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
+to substantial performance gains~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Samuel16,Wienke12}.
 %\guido{Suppport what?}

### 2018-02-02 docs/ACM/paper.tex
Adding description of implementation.

@@
 
+\paragraph{On the Implementation of \Taskminer.}
+We have implemented all the techniques described in this paper in
+LLVM~\cite{Lattner04}.
+This decision was motivated by two factors.
+First, the possibility to reuse all the infra-structure already
+available in LLVM to infer symbolic bounds of integer
+expressions~\cite{Mendonca17}.
+Second, given the state-of-the-art support that LLVM already provides to the
+compilation of OpenMP~\cite{Bertolli14,Martineau16,Samuel16}.
+
 We performed a thorough evaluation on \Taskminer{}'s applicability in real programs. Our test framework is divided in five aspects:

### 2018-02-02 docs/ACM/paper.tex
Talking a bit about task expansion.

@@
 the middle 80's.
+For completeness, we re-state it in Definition~\ref{def:hammock}.
 The structure of this program is described by a a Control Flow Graph $G$ --
 a directed graph with a starting node $s$, and an exit node $x$.
-A hammock region is a subgraph $G' \subseteq G$, with a special node
-$h$, which {\em dominates}\footnote{A node $n_1 \in G$ dominates another node
+
+\begin{definition}[Hammock Region~\cite{Ferrante87}]
+\label{def:hammock}
+A hammock region $G'$ from a CFG $G$ is a subgraph $G' \subseteq G$, with a
+node $h$, that {\em dominates}\footnote{A node $n_1 \in G$ dominates another node
 $n_2 \in G$ if every path from  $S$ to $n_2$ goes across $n_1$.
 Inversely, $n_1$ post-dominates $n_2$ if every path from $n_2$ to $x$ must
-go across $n_1$.} every other node in $G'$.
+go across $n_1$.} the other nodes in $G'$.
 Additionally, there exists a node $w \in G$, $w \notin G'$, such that
@@
 of $G'$.
+\end{definition}
 
@@
 parallelism, because individual tasks still execute sequentially.
-In this paper, we extract the smallest thread above the runtime cost.
+In this paper, {\em we extract the smallest thread above the runtime cost}.
 To bestow meaning into this last statement, in what follows, we define more
-formally the notions of task size and runtime cost.
+formally the notions of task size and task expansion.
 
@@
 The condition in line 7 of Figure~\ref{fig:ex_Regions} determines that tasks will
-only be created if the expression \textsf{5 $\times$ M $<$ WORK\_CUTOOF}
+only be created if the expression \textsf{5 $\times$ M $<$ WORK\_CUTOFF}
 holds.
@@
 task that comprises the loop at lines 8-10.
+The constant \textsf{WORK\_CUTOFF} represents the cost of creating a thread
+in the OpenMP runtime, and it is determined empirically.
 \end{example}
@@
 \paragraph{The Task Expansion Algorithm.}
+Task expansion consists in finding the smallest task that is large enough to
+pay for the thread creation cost.
+Figure \ref{fig:expand_alg} shows the algorithm that performs this activity.
+We start this algorithm by setting \textsf{REGION} to be a hammock graph $H$
+that is contained entirely within a windmill $W$.
+The hammock decomposition of a structured program forms a tree~\cite{Ferrante87},
+such that vertices in this tree represent hammock graphs.
+$H_1$ is a child of $H_2$ in this tree if $H_1 \subset H_2$, and for any other
+node $H_x$, $H_1 \subset H_x \Rightarrow H_2 \subset H_x$.
+In this context, we call $H_2$ the \textsf{PARENT} of $H_1$.
 

### 2018-02-06 docs/ACM/paper.tex
Changing the main algorithm.

@@
 
-The OpenMP runtime support allows the parallelization of irregular applications,
+OpenMP's runtime support allows the parallelization of irregular applications,
 such as programs that traverse data-structures formed by a mesh of pointers.
 In such programs, control constructs like {\tt if} statements make the
-execution  of certain pieces of code dependent on the program's input.
+execution of some statements dependent on the program's input.
 The runtime can capture such dependences, in contrast to static analysis tools.
 As an example, Figure~\ref{fig:ex_book_filter} shows an application that
-finds patterns in lines of a book.
-The book is given as an array of pointers; each pointer leads to a
-string representing a --potentially-- different line.
-The natural parallelization of this program consists in firing off a task
+finds patterns in lines of a book\footnote{Whenever we show code, statements in
+black font are part of the original program.
+The annotations that we create automatically appear in grey.
+The meaning of the pragmas used in the examples is explained in
+Section~\ref{sec:sol}}.
+The book is given as an array of pointers.
+Each pointer leads to a string representing a potentially different line.
+Out parallelization of this program consists in firing off a task
 to process each line.
-Figure~\ref{fig:ex_book_filter} has been annotated automatically by
+Figure~\ref{fig:ex_book_filter} has been annotated by
 \Taskminer.
 The OpenMP execution environment ensures the correct scheduling of the tasks
-created at lines 9 and 11, by assuring that the annotated input dependencies
-{\tt line} and {\tt pattern}  are 
-respected at runtime.
+created at lines 9 and 11, by assuring that the annotated dependencies
+{\tt line} and {\tt pattern}
+are respected at runtime.
 
@@
 Figure~\ref{fig:ex_Regions} illustrates Challenge~\ref{ch:Regions}, and shows
-how we solve it\footnote{Whenever we show code, statements in black font are part
-of the original program.
-The annotations that we create automatically appear in grey.}.
+how we solve it.
 That program receives an $\mathsf{M}\times\mathsf{N}$ matrix \textsf{V}, in
@@
 \includegraphics[width=1\columnwidth]{images/alg_main}
-\caption{The main steps of our code generator.}
+\caption{The main steps of our code generator.
+Grey boxes show sections in this paper where each phase is discussed.}
 \label{fig:alg_main}
@@
 pages in NUMA architectures~\cite{Piccoli14}.
-OpenMP 3.0 contains syntax to enable the conditional creation of tasks.
+OpenMP 4.0 contains syntax to enable the conditional creation of tasks.
 Our symbolic analysis lets us build predicates for such conditional expressions.

### 2018-02-06 docs/ACM/paper.tex
Fixed Jacobi analysis

--- 2018-02-02 docs/ACM/paper.tex
@@
 
-\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
-(1) the parent is a long for loop creating a large number of children, 
-all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
-(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
-It imposes an upper bound for the ready task queue of a worker; a worker 
-is discouraged to create too many tasks ready on the queue"}.
+%\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
+%(1) the parent is a long for loop creating a large number of children, 
+%all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
+%(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
+%It imposes an upper bound for the ready task queue of a worker; a worker 
+%is discouraged to create too many tasks ready on the queue"}.
 
@@
 
-Consider the FFT example, shown in Figure X.
+Consider the FIB
 
@@
 
+\begin{table}[h]
+\centering
+\caption{Different kinds of tasks among the BOTS benchmarks. {\Taskminer}'s versaitily allows the user to define which type of tasks should be mined, annotated or cared for.}
+\label{tab:types}
+\begin{tabular}{|r|c|c|c|}
+\hline
+                   & \textbf{Recursive} & \textbf{FunctionCall} & \textbf{Region} \\ \hline
+\textbf{fft}       & \checkmark         &                       & \checkmark      \\ \hline
+\textbf{fib}       & \checkmark         &                       &                 \\ \hline
+\textbf{floorplan} & \checkmark         &                       & \checkmark      \\ \hline
+\textbf{sort}      & \checkmark         &                       & \checkmark      \\ \hline
+\textbf{sparselu}  &                    & \checkmark            & \checkmark      \\ \hline
+\textbf{strassen}  & \checkmark         &                       & \checkmark      \\ \hline
+\textbf{uts}       & \checkmark         &                       &                 \\ \hline
+\textbf{nqueens}   & \checkmark         &                       & \checkmark      \\ \hline
+\textbf{knapsack}  & \checkmark         &                       & \checkmark      \\ \hline
+\textbf{health}    & \checkmark         & \checkmark            & \checkmark      \\ \hline
+\textbf{jacobi}    &                    &                       &                 \\ \hline
+\end{tabular}
+\end{table}
+
 %APPLICABILITY

### 2018-02-06 tests/benchmarks/bots/jacobi/poisson_AI.h
Jacobi

@@ -1,0 +1,133 @@
+#include <omp.h>
+#ifndef taskminerutils
+#define taskminerutils
+static int taskminer_depth_cutoff = 0;
+#define DEPTH_CUTOFF omp_get_num_threads()
+char cutoff_test = 0;
+#endif
+#ifndef KASTORS_POISSON_H
+#define KASTORS_POISSON_H
+# include <assert.h>
+
+typedef struct user_parameters user_parameters;
+
+struct user_parameters {
+    int check;
+    int succeed;
+    char* string2display;
+    int niter;
+    int titer;
+    int matrix_size;
+    int submatrix_size;
+    int blocksize;
+    int iblocksize;
+    int cutoff_depth;
+    int cutoff_size;
+};
+
+extern double run(struct user_parameters* params);
+#pragma omp parallel
+#pragma omp single
+
+/******************************************************************************/
+/*
+  Purpose:
+cutoff_test = (taskminer_depth_cutoff < DEPTH_CUTOFF);
+#pragma omp task untied default(shared) depend(in:unew_) depend(out:u_)
+
+  SWEEP carries out one step of the Jacobi iteration.
+#pragma omp taskwait
+
+  Discussion:
+
+  Assuming DX = DY, we can approximate
+
+  cutoff_test = (taskminer_depth_cutoff < DEPTH_CUTOFF);
+  #pragma omp task untied default(shared) depend(in:f_,u_) depend(out:unew_)
+  - (d/dx d/dx + d/dy d/dy) U(X,Y)
+
+  by
+#pragma omp taskwait
+
+  (U(i-1,j) + U(i+1,j) + U(i,j-1) + U(i,j+1) - 4*U(i,j)) / dx / dy
+
+  The discretization employed below will not be correct in the general
+  case where DX and DY are not equal.  It's only a little more complicated
+  to allow DX and DY to be different, but we're not going to worry about
+  that right now.
+
+  Licensing:
+
+  This code is distributed under the GNU LGPL license.
+
+  Modified:
+
+  14 December 2011
+
+  Author:
+
+  John Burkardt
+
+  Parameters:
+
+  Input, int NX, NY, the X and Y grid dimensions.
+
+  Input, double DX, DY, the spacing between grid points.
+
+  Input, double F[NX][NY], the right hand side data.
+
+  Input, int ITOLD, the iteration index on input.
+
+  Input, int ITNEW, the desired iteration index
+  on output.
+
+  Input, double U[NX][NY], the solution estimate on
+  iteration ITNEW-1.
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Parboil/common/polybenchUtilFuncts-AI.h
Unibench available.

@@ -1,0 +1,50 @@
+//polybenchUtilFuncts.h
+//Scott Grauer-Gray (sgrauerg@gmail.com)
+//Functions used across hmpp codes
+
+#ifndef POLYBENCH_UTIL_FUNCTS_H
+#define POLYBENCH_UTIL_FUNCTS_H
+
+//define a small float value
+#define SMALL_FLOAT_VAL 0.00000001f
+
+double rtclock()
+{
+    struct timezone Tzp;
+    struct timeval Tp;
+    int stat;
+    stat = gettimeofday (&Tp, &Tzp);
+    if (stat != 0) printf("Error return from gettimeofday: %d",stat);
+    return(Tp.tv_sec + Tp.tv_usec*1.0e-6);
+}
+
+
+float absVal(float a)
+{
+	if(a < 0)
+	{
+		return (a * -1);
+	}
+   	else
+	{ 
+		return a;
+	}
+}
+
+
+
+float percentDiff(double val1, double val2)
+{
+	if ((absVal(val1) < 0.01) && (absVal(val2) < 0.01))
+	{
+		return 0.0f;
+	}
+
+	else
+	{
+    		return 100.0f * (absVal(absVal(val1 - val2) / absVal(val1 + SMALL_FLOAT_VAL)));
+	}
+} 
+
+#endif //POLYBENCH_UTIL_FUNCTS_H
+

### 2018-02-06 tests/UniBenchBack/benchmarks/Parboil/mri-q/src/computeQ-AI.cc

@@ -1,0 +1,101 @@
+/***************************************************************************
+ *cr
+ *cr            (C) Copyright 2007 The Board of Trustees of the
+ *cr                        University of Illinois
+ *cr                         All Rights Reserved
+ *cr
+ ***************************************************************************/
+
+#define PI   3.1415926535897932384626433832795029f
+#define PIx2 6.2831853071795864769252867665590058f
+
+#define MIN(X,Y) ((X) < (Y) ? (X) : (Y))
+#define K_ELEMS_PER_GRID 2048
+
+struct kValues {
+  float Kx;
+  float Ky;
+  float Kz;
+  float PhiMag;
+};
+
+inline
+void 
+ComputePhiMagCPU(int numK, 
+                 float* phiR, float* phiI, float* phiMag) {
+  int indexK = 0;
+  #pragma omp parallel for
+  for (indexK = 0; indexK < numK; indexK++) {
+    //float real = phiR[indexK];
+    //float imag = phiI[indexK];
+    phiMag[indexK] = phiR[indexK]*phiR[indexK] + phiI[indexK]*phiI[indexK];
+  }
+}
+
+inline
+void
+ComputeQGPU(int numK, int numX,
+            struct kValues *kVals,
+            float* x, float* y, float* z,
+            float *Qr, float *Qi) {
+//  float expArg;
+//  float cosArg;
+//  float sinArg;
+
+  int indexK, indexX;
+	#pragma omp target device(1)
+  #pragma omp target map(to: kVals[:numK], x[:numX], y[:numX], z[:numX]) map(tofrom: Qr[:numX], Qi[:numX])
+  for (indexK = 0; indexK < numK; indexK++) {
+    #pragma omp parallel for
+    for (indexX = 0; indexX < numX; indexX++) {
+      float expArg = PIx2 * (kVals[indexK].Kx * x[indexX] +
+                       kVals[indexK].Ky * y[indexX] +
+                       kVals[indexK].Kz * z[indexX]);
+
+      float cosArg = cos(expArg);
+      float sinArg = sin(expArg);
+
+      float phi = kVals[indexK].PhiMag;
+      Qr[indexX] += phi * cosArg;
+      Qi[indexX] += phi * sinArg;
+    }
+  }
+}
+
+inline
+void
+ComputeQCPU(int numK, int numX,
+            struct kValues *kVals,
+            float* x, float* y, float* z,
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Parboil/mri-q/src/main.c

@@ -1,0 +1,276 @@
+/***************************************************************************
+ *cr
+ *cr            (C) Copyright 2007 The Board of Trustees of the
+ *cr                        University of Illinois
+ *cr                         All Rights Reserved
+ *cr
+ ***************************************************************************/
+
+/*
+ * C code for creating the Q data structure for fast convolution-based
+ * Hessian multiplication for arbitrary k-space trajectories.
+ *
+ * Inputs:
+ * kx - VECTOR of kx values, same length as ky and kz
+ * ky - VECTOR of ky values, same length as kx and kz
+ * kz - VECTOR of kz values, same length as kx and ky
+ * x  - VECTOR of x values, same length as y and z
+ * y  - VECTOR of y values, same length as x and z
+ * z  - VECTOR of z values, same length as x and y
+ * phi - VECTOR of the Fourier transform of the spatial basis
+ *      function, evaluated at [kx, ky, kz].  Same length as kx, ky, and kz.
+ *
+ * recommended g++ options:
+ *  -O3 -lm -ffast-math -funroll-all-loops
+ */
+
+#include <stdio.h>
+#include <math.h>
+#include <stdlib.h>
+#include <string.h>
+#include <sys/time.h>
+#include <malloc.h>
+
+#include "../../common/parboil.h"
+
+#include "file.h"
+#include "computeQ.cc"
+
+#include "../../common/polybenchUtilFuncts.h"
+
+#define ERROR_THRESHOLD 0.1
+#define GPU_DEVICE 1
+double t_start, t_end, t_start_GPU, t_end_GPU;
+
+float *Qr_GPU, *Qi_GPU; /* Q signal (complex) */
+float *Qr_CPU, *Qi_CPU; /* Q signal (complex) */
+int N;
+
+typedef float DATA_TYPE;
+
+void compareResults(DATA_TYPE *A, DATA_TYPE *A_GPU, DATA_TYPE *B,
+                    DATA_TYPE *B_GPU) {
+  int i, fail = 0;
+
+  for (i = 0; i < N; i++) {
+    if (percentDiff(A[i], A_GPU[i]) > ERROR_THRESHOLD) {
+      fail++;
+    }
+  }
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Parboil/spmv/src/convert_dataset-AI.c

@@ -1,0 +1,337 @@
+/*
+*   NOTES:
+*
+*   1) Matrix Market files are always 1-based, i.e. the index of the first
+*      element of a matrix is (1,1), not (0,0) as in C.  ADJUST THESE
+*      OFFSETS ACCORDINGLY when reading and writing 
+*      to files.
+*
+*   2) ANSI C requires one to use the "l" format modifier when reading
+*      double precision floating point numbers in scanf() and
+*      its variants.  For example, use "%lf", "%lg", or "%le"
+*      when reading doubles, otherwise errors will occur.
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "mmio.h"
+#include "convert_dataset.h"
+
+
+
+typedef struct _mat_entry {
+    int row, col; /* i,j */
+    float val;
+} mat_entry;
+
+typedef struct _row_stats { // stats on each row
+    int index;
+    int size;
+    int start;
+    int padding;
+} row_stats;
+
+int sort_rows(const void* a, const void* b) {
+    return (((mat_entry*)a)->row - ((mat_entry*)b)->row);
+}
+int sort_cols(const void* a, const void* b) {
+    return (((mat_entry*)a)->col - ((mat_entry*)b)->col);
+}
+/* sorts largest by size first */
+int sort_stats(const void* a, const void* b) {
+    return(((row_stats*)b)->size - ((row_stats*)a)->size);
+}
+
+/*
+ * COO to JDS matrix conversion.
+ *
+ * Needs to output both column and row major JDS formats
+ * with the minor unit padded to a multiple of `pad_minor`
+ * and the major unit arranged into groups of `group_size`
+ *
+ * Major unit is col, minor is row. Each block is either a scalar or vec4
+ *
+ * Inputs:
+ *   mtx_filename - the file in COO format
+ *   pad_rows - multiple of packed groups to pad each row to
+ *   warp_size - each group of `warp_size` cols is padded to the same amount
+ *   pack_size - number of items to pack
+ *   mirrored - is the input mtx file a symmetric matrix? The other half will be
+ *   	filled in if this is =1
+ *   binary - does the sparse matrix file have values in the format "%d %d"
+ *   	or "%d %d %lg"?
+ *   debug_level - 0 for no output, 1 for simple JDS data, 2 for visual grid
+ * Outputs:
+ *   data - the raw data, padded and grouped as requested
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Parboil/spmv/src/main.c

@@ -1,0 +1,309 @@
+/***************************************************************************
+ *cr
+ *cr            (C) Copyright 2010 The Board of Trustees of the
+ *cr                        University of Illinois
+ *cr                         All Rights Reserved
+ *cr
+ ***************************************************************************/
+
+#include "../../common/parboil.h"
+#include <stdio.h>
+#include <stdlib.h>
+#include <sys/time.h>
+
+#include "file.h"
+#include "convert_dataset.h"
+
+#include "../../common/polybenchUtilFuncts.h"
+
+#define ERROR_THRESHOLD 0.05
+#define GPU_DEVICE 1
+double t_start, t_end, t_start_GPU, t_end_GPU;
+
+float *h_Ax_vector_GPU, *h_Ax_vector_CPU;
+int N;
+
+typedef float DATA_TYPE;
+
+void compareResults(DATA_TYPE *A, DATA_TYPE *A_GPU) {
+  int i, fail = 0;
+
+  for (i = 0; i < N; i++) {
+    if (percentDiff(A[i], A_GPU[i]) > ERROR_THRESHOLD) {
+      fail++;
+    }
+  }
+
+  // print results
+  printf("Non-Matching CPU-GPU Outputs Beyond Error Threshold of %4.2f "
+         "Percent: %d\n",
+         ERROR_THRESHOLD, fail);
+}
+
+static int generate_vector(float *x_vector, int dim) {
+  srand(54321);
+  int i;
+  for (i = 0; i < dim; i++) {
+    x_vector[i] = (rand() / (float)RAND_MAX);
+  }
+  return 0;
+}
+
+/*
+void jdsmv(int height, int len, float* value, int* perm, int* jds_ptr, int*
+col_index, float* vector,
+        float* result){
+        int i;
+        int col,row;
+        int row_index =0;
+        int prem_indicator=0;
+        for (i=0; i<len; i++){
+                if (i>=jds_ptr[prem_indicator+1]){
+                        prem_indicator++;
+                        row_index=0;
+                }
+                if (row_index<height){
+                col = col_index[i];
+                row = perm[row_index];
+                result[row]+=value[i]*vector[col];
+                }
+
+                row_index++;
+        }
+        return;
+}
+*/
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Parboil/stencil/src/kernels.c

@@ -1,0 +1,50 @@
+/***************************************************************************
+ *cr
+ *cr            (C) Copyright 2010 The Board of Trustees of the
+ *cr                        University of Illinois
+ *cr                         All Rights Reserved
+ *cr
+ ***************************************************************************/
+
+#include "common.h"
+
+void cpu_stencilGPU(float c0, float c1, float *A0, float *Anext, const int nx,
+                    const int ny, const int nz) {
+
+  int i, j, k;
+
+  map(tofrom : Anext[:nx * ny * nz]) for (k = 1; k < nz - 1; k++) {
+    for (j = 1; j < ny - 1; j++) {
+      for (i = 1; i < nx - 1; i++) {
+        Anext[Index3D(nx, ny, i, j, k)] = (A0[Index3D(nx, ny, i, j, k + 1)] +
+                                           A0[Index3D(nx, ny, i, j, k - 1)] +
+                                           A0[Index3D(nx, ny, i, j + 1, k)] +
+                                           A0[Index3D(nx, ny, i, j - 1, k)] +
+                                           A0[Index3D(nx, ny, i + 1, j, k)] +
+                                           A0[Index3D(nx, ny, i - 1, j, k)]) *
+                                              c1 -
+                                          A0[Index3D(nx, ny, i, j, k)] * c0;
+      }
+    }
+  }
+}
+
+void cpu_stencilCPU(float c0, float c1, float *A0, float *Anext, const int nx,
+                    const int ny, const int nz) {
+
+  int i, j, k;
+  for (k = 1; k < nz - 1; k++) {
+    for (j = 1; j < ny - 1; j++) {
+      for (i = 1; i < nx - 1; i++) {
+        Anext[Index3D(nx, ny, i, j, k)] = (A0[Index3D(nx, ny, i, j, k + 1)] +
+                                           A0[Index3D(nx, ny, i, j, k - 1)] +
+                                           A0[Index3D(nx, ny, i, j + 1, k)] +
+                                           A0[Index3D(nx, ny, i, j - 1, k)] +
+                                           A0[Index3D(nx, ny, i + 1, j, k)] +
+                                           A0[Index3D(nx, ny, i - 1, j, k)]) *
+                                              c1 -
+                                          A0[Index3D(nx, ny, i, j, k)] * c0;
+      }
+    }
+  }
+}

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/2DCONV/src/2DConvolution-AI.c

@@ -1,0 +1,160 @@
+/**
+ * 2DConvolution.c: This file was adapted from PolyBench/GPU 1.0 test suite
+ * to run on GPU with OpenMP 4.0 pragmas and OpenCL driver.
+ *
+ * http://www.cse.ohio-state.edu/~pouchet/software/polybench/GPU 
+ *
+ * Contacts: Marcio M Pereira <mpereira@ic.unicamp.br>
+ *           Rafael Cardoso F Sousa <rafael.cardoso@students.ic.unicamp.br>
+ *	     Luís Felipe Mattos <ra107822@students.ic.unicamp.br>
+ */
+
+#include <unistd.h>
+#include <stdio.h>
+#include <time.h>
+#include <sys/time.h>
+#include <stdlib.h>
+#include <stdarg.h>
+#include <string.h>
+//include <omp.h>
+
+#include "../../common/polybenchUtilFuncts.h"
+
+//define the error threshold for the results "not matching"
+#define ERROR_THRESHOLD 0.05
+
+#define GPU_DEVICE 1
+
+/* Problem size */
+#define NI 8192
+#define NJ 8192
+
+/* Can switch DATA_TYPE between float and double */
+typedef float DATA_TYPE;
+
+void conv2D(DATA_TYPE* A, DATA_TYPE* B)
+{
+  int i, j;
+  DATA_TYPE c11, c12, c13, c21, c22, c23, c31, c32, c33;
+
+  c11 = +0.2;  c21 = +0.5;  c31 = -0.8;
+  c12 = -0.3;  c22 = +0.6;  c32 = -0.9;
+  c13 = +0.4;  c23 = +0.7;  c33 = +0.10;
+
+  #pragma acc data copy(B[8193:67108863],A[0:67117056])
+  #pragma acc kernels
+  #pragma acc loop independent
+  for (i = 1; i < NI - 1; ++i) // 0
+    {
+      for (j = 1; j < NJ - 1; ++j) // 1
+	{
+	  B[i*NJ + j] = c11 * A[(i - 1)*NJ + (j - 1)]  +  c12 * A[(i + 0)*NJ + (j - 1)]  +  c13 * A[(i + 1)*NJ + (j - 1)]
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/ATAX/src/atax-AI.c

@@ -1,0 +1,189 @@
+/**
+ * atax.c: This file was adapted from PolyBench/GPU 1.0 test suite
+ * to run on GPU with OpenMP 4.0 pragmas and OpenCL driver.
+ *
+ * http://www.cse.ohio-state.edu/~pouchet/software/polybench/GPU 
+ *
+ * Contacts: Marcio M Pereira <mpereira@ic.unicamp.br>
+ *           Rafael Cardoso F Sousa <rafael.cardoso@students.ic.unicamp.br>
+ *	     Luís Felipe Mattos <ra107822@students.ic.unicamp.br>
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+//include <omp.h>
+
+#include "../../common/polybenchUtilFuncts.h"
+
+//define the error threshold for the results "not matching"
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.5
+
+/* Problem size. */
+#define NX 8192
+#define NY 8192
+
+#define GPU_DEVICE 1
+
+#ifndef M_PI
+#define M_PI 3.14159
+#endif
+
+/* Can switch DATA_TYPE between float and double */
+typedef float DATA_TYPE;
+
+void init_array(DATA_TYPE *x, DATA_TYPE *A)
+{
+  int i, j;
+
+  #pragma acc data copy(A[0:67117056],x[0:8192])
+  #pragma acc kernels
+  #pragma acc loop independent
+  for (i = 0; i < NX; i++)
+    {
+      x[i] = i * M_PI;
+      for (j = 0; j < NY; j++)
+	{
+	  A[i*NY + j] = ((DATA_TYPE) i*(j)) / NX;
+	}
+    }
+}
+
+void compareResults(DATA_TYPE *z, DATA_TYPE *z_outputFromGpu)
+{
+  int i, fail;
+  fail = 0;
+
+  #pragma acc data copy(z[0:8192],z_outputFromGpu[0:8192])
+  #pragma acc kernels
+  #pragma acc loop independent
+  for (i=0; i<NY; i++)
+    {
+      if (percentDiff(z[i], z_outputFromGpu[i]) > PERCENT_DIFF_ERROR_THRESHOLD)
+	{
+	  fail++;
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/ATAX/src/atax.c

@@ -1,0 +1,145 @@
+/**
+ * atax.c: This file was adapted from PolyBench/GPU 1.0 test suite
+ * to run on GPU with OpenMP 4.0 pragmas and OpenCL driver.
+ *
+ * http://www.cse.ohio-state.edu/~pouchet/software/polybench/GPU
+ *
+ * Contacts: Marcio M Pereira <mpereira@ic.unicamp.br>
+ *           Rafael Cardoso F Sousa <rafael.cardoso@students.ic.unicamp.br>
+ *	     Luís Felipe Mattos <ra107822@students.ic.unicamp.br>
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+// include <omp.h>
+
+#include "../../common/polybenchUtilFuncts.h"
+
+// define the error threshold for the results "not matching"
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.5
+
+/* Problem size. */
+#define NX 8192
+#define NY 8192
+
+#define GPU_DEVICE 1
+
+#ifndef M_PI
+#define M_PI 3.14159
+#endif
+
+/* Can switch DATA_TYPE between float and double */
+typedef float DATA_TYPE;
+
+void init_array(DATA_TYPE *x, DATA_TYPE *A) {
+  int i, j;
+
+  for (i = 0; i < NX; i++) {
+    x[i] = i * M_PI;
+    for (j = 0; j < NY; j++) {
+      A[i * NY + j] = ((DATA_TYPE)i * (j)) / NX;
+    }
+  }
+}
+
+void compareResults(DATA_TYPE *z, DATA_TYPE *z_outputFromGpu) {
+  int i, fail;
+  fail = 0;
+
+  for (i = 0; i < NY; i++) {
+    if (percentDiff(z[i], z_outputFromGpu[i]) > PERCENT_DIFF_ERROR_THRESHOLD) {
+      fail++;
+    }
+  }
+
+  // print results
+  printf("Non-Matching CPU-GPU Outputs Beyond Error Threshold of %4.2f "
+         "Percent: %d\n",
+         PERCENT_DIFF_ERROR_THRESHOLD, fail);
+}
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/CORR/src/correlation_AI_ipmacc.cu

@@ -1,0 +1,502 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <assert.h>
+#include <openacc.h>
+#define IPMACC_MAX1(A)   (A)
+#define IPMACC_MAX2(A,B) (A>B?A:B)
+#define IPMACC_MAX3(A,B,C) (A>B?(A>C?A:(B>C?B:C)):(B>C?C:B))
+#ifdef __cplusplus
+#include "openacc_container.h"
+#endif
+
+#include <cuda.h>
+
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <sys/time.h>
+
+
+#include "../../common/polybenchUtilFuncts.h"
+
+
+#define ERROR_THRESHOLD 1.05
+
+#define GPU_DEVICE 1
+
+
+#define M 1024
+#define N 1024
+
+#define sqrt_of_array_cell(x, j) sqrt(x [j])
+
+#define FLOAT_N 3214212.01f
+#define EPS 0.005f
+
+
+typedef float DATA_TYPE;
+
+void init_arrays(DATA_TYPE* data)
+{
+  int i, j;
+
+  for (i = 0; i < (M + 1); i++) {
+    for (j = 0; j < (N + 1); j++) {
+      data [i * (N + 1) + j] = ((DATA_TYPE)i * j) / (M + 1);
+    }
+  }
+}
+
+void CPU__correlation(DATA_TYPE* data, DATA_TYPE* mean, DATA_TYPE* stddev, DATA_TYPE* symmat)
+{
+  int i, j, j1, j2;
+
+  
+  for (j = 1; j < (M + 1); j++) {
+    mean [j] = 0.0;
+
+    for (i = 1; i < (N + 1); i++) {
+      mean [j] += data [i * (M + 1) + j];
+    }
+
+    
+    mean [j] /= (DATA_TYPE)FLOAT_N;
+  }
+
+  
+  for (j = 1; j < (M + 1); j++) {
+    stddev [j] = 0.0;
+
+    for (i = 1; i < (N + 1); i++) {
+      stddev [j] += (data [i * (M + 1) + j] - mean [j]) * (data [i * (M + 1) + j] - mean [j]);
+    }
+
+    stddev [j] /= FLOAT_N;
+    stddev [j] = sqrt_of_array_cell(stddev, j);
+    stddev [j] = stddev [j] <= EPS ? 1.0 : stddev [j];
+  }
+
+  
+  
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/FDTD-2D/src/fdtd2d.c

@@ -1,0 +1,217 @@
+/**
+ * fdtd2d.c: This file was adapted from PolyBench/GPU 1.0 test suite
+ * to run on GPU with OpenMP 4.0 pragmas and OpenCL driver.
+ *
+ * http://www.cse.ohio-state.edu/~pouchet/software/polybench/GPU
+ *
+ * Contacts: Marcio M Pereira <mpereira@ic.unicamp.br>
+ *           Rafael Cardoso F Sousa <rafael.cardoso@students.ic.unicamp.br>
+ *           Luís Felipe Mattos <ra107822@students.ic.unicamp.br>
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+// include <omp.h>
+
+#include "../../common/polybenchUtilFuncts.h"
+
+// define the error threshold for the results "not matching"
+#define PERCENT_DIFF_ERROR_THRESHOLD 10.05
+
+#define GPU_DEVICE 1
+
+/* Problem size */
+#define tmax 500
+#define NX 2048
+#define NY 2048
+
+/* Can switch DATA_TYPE between float and double */
+typedef float DATA_TYPE;
+
+void init_arrays(DATA_TYPE *_fict_, DATA_TYPE *ex, DATA_TYPE *ey,
+                 DATA_TYPE *hz) {
+  int i, j;
+
+  for (i = 0; i < tmax; i++) {
+    _fict_[i] = (DATA_TYPE)i;
+  }
+
+  for (i = 0; i < NX; i++) {
+    for (j = 0; j < NY; j++) {
+      ex[i * NY + j] = ((DATA_TYPE)i * (j + 1) + 1) / NX;
+      ey[i * NY + j] = ((DATA_TYPE)(i - 1) * (j + 2) + 2) / NX;
+      hz[i * NY + j] = ((DATA_TYPE)(i - 9) * (j + 4) + 3) / NX;
+    }
+  }
+}
+
+void init_array_hz(DATA_TYPE *hz) {
+  int i, j;
+
+  for (i = 0; i < NX; i++) {
+    for (j = 0; j < NY; j++) {
+      hz[i * NY + j] = ((DATA_TYPE)(i - 9) * (j + 4) + 3) / NX;
+    }
+  }
+}
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/MVT/src/mvt.c

@@ -1,0 +1,155 @@
+/**
+ * mvt.c: This file was adapted from PolyBench/GPU 1.0 test suite
+ * to run on GPU with OpenMP 4.0 pragmas and OpenCL driver.
+ *
+ * http://www.cse.ohio-state.edu/~pouchet/software/polybench/GPU
+ *
+ * Contacts: Marcio M Pereira <mpereira@ic.unicamp.br>
+ *           Rafael Cardoso F Sousa <rafael.cardoso@students.ic.unicamp.br>
+ *           Luís Felipe Mattos <ra107822@students.ic.unicamp.br>
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+// include <omp.h>
+
+#include "../../common/polybenchUtilFuncts.h"
+
+// define the error threshold for the results "not matching"
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.05
+
+#define GPU_DEVICE 1
+
+/* Problem size */
+#define N 4096
+
+/* Can switch DATA_TYPE between float and double */
+typedef float DATA_TYPE;
+
+void init_array(DATA_TYPE *A, DATA_TYPE *x1, DATA_TYPE *x2, DATA_TYPE *y1,
+                DATA_TYPE *y2, DATA_TYPE *x1_gpu, DATA_TYPE *x2_gpu) {
+  int i, j;
+
+  for (i = 0; i < N; i++) {
+    x1[i] = ((DATA_TYPE)i) / N;
+    x2[i] = ((DATA_TYPE)i + 1) / N;
+    x1_gpu[i] = x1[i];
+    x2_gpu[i] = x2[i];
+    y1[i] = ((DATA_TYPE)i + 3) / N;
+    y2[i] = ((DATA_TYPE)i + 4) / N;
+    for (j = 0; j < N; j++) {
+      A[i * N + j] = ((DATA_TYPE)i * j) / N;
+    }
+  }
+}
+
+void runMvt(DATA_TYPE *a, DATA_TYPE *x1, DATA_TYPE *x2, DATA_TYPE *y1,
+            DATA_TYPE *y2) {
+  int i, j;
+
+  for (i = 0; i < N; i++) {
+    for (j = 0; j < N; j++) {
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Polybench/SYR2K/src/syr2k-AI.c

@@ -1,0 +1,177 @@
+/**
+ * syr2k.c: This file was adapted from PolyBench/GPU 1.0 test suite
+ * to run on GPU with OpenMP 4.0 pragmas and OpenCL driver.
+ *
+ * http://www.cse.ohio-state.edu/~pouchet/software/polybench/GPU 
+ *
+ * Contacts: Marcio M Pereira <mpereira@ic.unicamp.br>
+ *           Rafael Cardoso F Sousa <rafael.cardoso@students.ic.unicamp.br>
+ *           Luís Felipe Mattos <ra107822@students.ic.unicamp.br> 
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+//include <omp.h>
+
+#include "../../common/polybenchUtilFuncts.h"
+
+//define the error threshold for the results "not matching"
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.05
+
+/* Problem size */
+#define N 2048
+#define M 2048
+
+#define GPU_DEVICE 1
+
+/* Declared constant values for ALPHA and BETA (same as values in PolyBench 2.0) */
+#define ALPHA 12435
+#define BETA 4546
+
+/* Can switch DATA_TYPE between float and double */
+typedef float DATA_TYPE;
+
+void init_arrays(DATA_TYPE *A, DATA_TYPE *B, DATA_TYPE *C, DATA_TYPE *C_GPU)
+{
+  int i, j;
+  
+  #pragma acc data copy(C[0:4196352],C_GPU[0:4196352],B[0:4196352],A[0:4196352])
+  #pragma acc kernels
+  #pragma acc loop independent
+  for (i = 0; i < N; i++)
+    {
+      for (j = 0; j < N; j++)
+	{
+	  C[i*N + j] = ((DATA_TYPE) i*j + 2) / N;
+	  C_GPU[i*N + j] = C[i*N + j];
+	}
+      	
+      for (j = 0; j < M; j++)
+	{
+	  A[i*N + j] = ((DATA_TYPE) i*j) / N;
+	  B[i*N + j] = ((DATA_TYPE) i*j + 1) / N;
+	}
+    }
+}
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/ReadStatistics.cpp

@@ -1,0 +1,110 @@
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include <cstdlib>
+#include <cstdio>
+
+using namespace std;
+
+#define NTargets 6
+
+std::string getName (char *argv[]) {
+  std::string tmp;
+  int i = 0;
+  for (int i = 0; argv[1][i] != '\0'; i++) 
+    tmp += argv[1][i];
+  return tmp;
+}
+
+std::string extract (std::string str, std::string input) {
+  int pos = input.find(str);
+  std::string tmp;
+  if (str != "Writing output to file") {
+    for (int i = 0; i < pos; i++)
+      tmp += input[i];
+    return tmp;
+  }
+  pos = input.rfind("/");
+  for (int i = pos + 1; input[i] != '.'; i++)
+    tmp += input[i];
+  return tmp;
+}
+
+void createCSV (vector <vector <string> > & data) {
+  ofstream file ("benchmarksStatistics.csv");
+  if (!file.is_open()) {
+    printf("Error to create the benchmarksStatistics.csv file.\n");
+    return;
+  }
+  for (int i = 0, ie = data.size(); i != ie; i++) {
+    if (data[i].size() == 1)
+      continue;
+    for (int j = 0, je = data[i].size() - 1; j != je; j++)
+      file << data[i][j] << ",";
+    if (data[i].size() != NTargets)
+      for (int j = data[i].size(); j < NTargets; j++)
+        file << "0,";
+    file << data[i][(data[i].size() - 1)] << ","; 
+    file << "\n";
+  }
+  printf("Wrote!!!\n");
+  file.close();
+}
+
+void readFile (std::string name) {
+  ifstream file(name);
+  if (!file.is_open()) {
+    printf("Error to try open the file\n");
+    return;
+  }
+  string line;
+  vector <vector <string> > found;
+  vector <string> targets;
+  vector <string> tmp; 
+  // The headers to find.
+  targets.push_back("Writing output to file");
+  targets.push_back("PTRRangeAnalysis - Number of memory access");
+  targets.push_back("PTRRangeAnalysis - Number of memory analyzed access");
+  targets.push_back("writeExpressions - Number of analyzable loops");
+  targets.push_back("writeExpressions - Number of annotated loops");
+  targets.push_back("writeExpressions - Number of loops");
+  // The headers to write.
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Rodinia/b+tree/src/kernel/kernel_cpu_AI.c

@@ -1,0 +1,196 @@
+// #ifdef __cplusplus
+// extern "C" {
+// #endif
+
+//========================================================================================================================================================================================================200
+//	DEFINE/INCLUDE
+//========================================================================================================================================================================================================200
+
+//======================================================================================================================================================150
+//	LIBRARIES
+//======================================================================================================================================================150
+
+// include <omp.h>									// (in directory
+// known to compiler)			needed by openmp
+#include <stdlib.h> // (in directory known to compiler)			needed by malloc
+#include <stdio.h> // (in directory known to compiler)			needed by printf, stderr
+
+//======================================================================================================================================================150
+//	COMMON
+//======================================================================================================================================================150
+
+#include "../common.h" // (in directory provided here)
+
+//======================================================================================================================================================150
+//	UTILITIES
+//======================================================================================================================================================150
+
+#include "../util/timer/timer.h" // (in directory provided here)
+
+#define GPU_DEVICE 1
+
+//========================================================================================================================================================================================================200
+//	KERNEL_CPU FUNCTION
+//========================================================================================================================================================================================================200
+
+void kernel_gpu(int cores_arg,
+
+                record *records, knode *knodes, long knodes_elem,
+                long records_elem,
+
+                int order, long maxheight, int count,
+
+                long *currKnode, long *offset, int *keys, record *ans) {
+
+  //======================================================================================================================================================150
+  //	MCPU SETUP
+  //======================================================================================================================================================150
+
+  int max_nthreads;
+  max_nthreads = omp_get_max_threads();
+  // printf("max # of threads = %d\n", max_nthreads);
+  omp_set_num_threads(cores_arg);
+  // printf("set # of threads = %d\n", cores_arg);
+
+  int threadsPerBlock;
+  threadsPerBlock = order < 1024 ? order : 1024;
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Rodinia/b+tree/src/util/timer/timer-AI.c

@@ -1,0 +1,38 @@
+#ifdef __cplusplus
+extern "C" {
+#endif
+
+//===============================================================================================================================================================================================================200
+//	TIMER CODE
+//===============================================================================================================================================================================================================200
+
+//======================================================================================================================================================150
+//	INCLUDE/DEFINE
+//======================================================================================================================================================150
+
+#include <stdlib.h>
+
+
+//======================================================================================================================================================150
+//	FUNCTIONS
+//======================================================================================================================================================150
+
+//====================================================================================================100
+//	DISPLAY TIME
+//====================================================================================================100
+
+ // Returns the current system time in microseconds
+long long get_time() {
+	struct timeval tv;
+	gettimeofday(&tv, NULL);
+	return (tv.tv_sec * 1000000) + tv.tv_usec;
+}
+
+//===============================================================================================================================================================================================================200
+//	END TIMER CODE
+//===============================================================================================================================================================================================================200
+
+#ifdef __cplusplus
+}
+#endif
+

### 2018-02-06 tests/UniBenchBack/benchmarks/Rodinia/backprop/src/facetrain-AI.c

@@ -1,0 +1,50 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "backprop.h"
+//include "omp.h"
+
+extern char *strcpy();
+extern void exit();
+
+int layer_size = 0;
+
+backprop_face()
+{
+  BPNN *net;
+  int i;
+  float out_err, hid_err;
+  net = bpnn_create(layer_size, 16, 1); // (16, 1 can not be changed)
+  printf("Input layer size : %d\n", layer_size);
+  load(net);
+  //entering the training kernel, only one iteration
+  printf("Starting training kernel\n");
+
+
+  bpnn_train_kernel(net, &out_err, &hid_err);
+  
+
+  bpnn_free(net);
+  printf("Training done\n");
+}
+
+int setup(argc, argv)
+int argc;
+char *argv[];
+{
+  if(argc!=2){
+  fprintf(stderr, "usage: backprop <num of input elements>\n");
+  exit(0);
+  }
+
+  layer_size = atoi(argv[1]);
+  
+  int seed;
+
+  seed = 7;   
+  bpnn_initialize(seed);
+  backprop_face();
+
+  exit(0);
+}
+

### 2018-02-06 tests/UniBenchBack/benchmarks/Rodinia/lud/src/lud.c

@@ -1,0 +1,150 @@
+/*
+ * =====================================================================================
+ *
+ *       Filename:  suite.c
+ *
+ *    Description:  The main wrapper for the suite
+ *
+ *        Version:  1.0
+ *        Created:  10/22/2009 08:40:34 PM
+ *       Revision:  none
+ *       Compiler:  gcc
+ *
+ *         Author:  Liang Wang (lw2aw), lw2aw@virginia.edu
+ *        Company:  CS@UVa
+ *
+ * =====================================================================================
+ */
+
+#include <stdio.h>
+#include <unistd.h>
+#include <getopt.h>
+#include <stdlib.h>
+#include <assert.h>
+#include <sys/time.h>
+#include "../../common/rodiniaUtilFunctions.h"
+
+#include "common/common.h"
+
+static int do_verify = 0;
+
+static struct option long_options[] = {
+    /* name, has_arg, flag, val */
+    {"input", 1, NULL, 'i'},
+    {"size", 1, NULL, 's'},
+    {"verify", 0, NULL, 'v'},
+    {0, 0, 0, 0}};
+
+extern void lud_omp(float *m, int matrix_dim);
+
+int main(int argc, char *argv[]) {
+  int matrix_dim = 32; /* default size */
+  int opt, option_index = 0;
+  func_ret_t ret;
+  const char *input_file = NULL;
+  float *m_cpu, *m_gpu, *mm;
+  stopwatch sw;
+
+  while ((opt = getopt_long(argc, argv, "::vs:i:", long_options,
+                            &option_index)) != -1) {
+    switch (opt) {
+    case 'i':
+      input_file = optarg;
+      break;
+    case 'v':
+      do_verify = 1;
+      break;
+    case 's':
+      matrix_dim = atoi(optarg);
+      printf("Generate input matrix internally, size =%d\n", matrix_dim);
+      // fprintf(stderr, "Currently not supported, use -i instead\n");
+      // fprintf(stderr, "Usage: %s [-v] [-s matrix_size|-i input_file]\n",
+      // argv[0]);
+      // exit(EXIT_FAILURE);
+      break;
+    case '?':
+      fprintf(stderr, "invalid option\n");
+      break;
+    case ':':
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Rodinia/lud/src/tools/gen_input_AI.c

@@ -1,0 +1,140 @@
+#include <omp.h>
+#ifndef taskminerutils
+#define taskminerutils
+static int taskminer_depth_cutoff = 0;
+#define DEPTH_CUTOFF omp_get_num_threads()
+char cutoff_test = 0;
+#endif
+#include <time.h>
+#include <stdlib.h>
+#include <stdio.h>
+
+#ifdef FP_NUMBER
+typedef double FP_NUMBER;
+#else
+typedef float FP_NUMBER;
+#endif
+
+#define GET_RAND_FP \
+  ((FP_NUMBER)rand() / ((FP_NUMBER)(RAND_MAX) + (FP_NUMBER)(1)))
+char L_FNAME[32], U_FNAME[32], A_FNAME[32];
+
+int main(int argc, char **argv) {
+  int i, j, k, MatrixDim;
+  FP_NUMBER sum, **L, **U, **A;
+  FILE *fl, *fu, *fa;
+
+  if (argc < 2) {
+    printf("./gen_input [Matrix_Dimension_size]\n");
+    return 1;
+  }
+
+  MatrixDim = atoi(argv[1]);
+  L = (FP_NUMBER **)malloc(sizeof(FP_NUMBER *) * MatrixDim);
+  U = (FP_NUMBER **)malloc(sizeof(FP_NUMBER *) * MatrixDim);
+  A = (FP_NUMBER **)malloc(sizeof(FP_NUMBER *) * MatrixDim);
+
+  if (!L || !U || !A) {
+    printf("Can not allocate memory\n");
+    if (L)
+      free(L);
+    if (U)
+      free(U);
+    if (A)
+      free(A);
+    return 1;
+  }
+
+  srand(time(NULL));
+
+  sprintf(L_FNAME, "l-%d.dat", MatrixDim);
+  fl = fopen(L_FNAME, "wb");
+  if (fl == NULL) {
+    printf("Cannot open file %s\n", L_FNAME);
+    return 1;
+  }
+
+  sprintf(U_FNAME, "u-%d.dat", MatrixDim);
+  fu = fopen(U_FNAME, "wb");
+  if (fu == NULL) {
+    printf("Cannot open file %s\n", U_FNAME);
+    return 1;
+  }
+
+  sprintf(A_FNAME, "%d.dat", MatrixDim);
+  fa = fopen(A_FNAME, "wb");
+  if (!fa) {
+    printf("Cannot open file %s\n", A_FNAME);
+    return 1;
+  }
+
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/Rodinia/srad/src/resize-AI.c

@@ -1,0 +1,71 @@
+//====================================================================================================100
+//====================================================================================================100
+//	RESIZE FUNCTION
+//====================================================================================================100
+//====================================================================================================100
+#include "define.c"
+
+void resize(	fp* input, 
+					int input_rows,
+					int input_cols,
+					fp* output,
+					fp* output_cpu,
+					int output_rows,
+					int output_cols,
+					int major){
+
+	//================================================================================80
+	//	VARIABLES
+	//================================================================================80
+
+	int i, j;
+	int i2, j2;
+
+	//================================================================================80
+	//	COMPUTATION
+	//================================================================================80 
+
+	//============================================================60
+	//	ROW MAJOR
+	//============================================================60
+
+	if(major == 0){																												// do if data is saved row major
+
+		for(i=0, i2=0; i<output_rows; i++, i2++){
+			if(i2>=input_rows){
+				i2 = i2 - input_rows;
+			}
+			for(j=0, j2=0; j<output_cols; j++, j2++){
+				if(j2>=input_cols){
+					j2 = j2 - input_cols;
+				}
+				output[i*output_cols+j] = input[i2*input_cols+j2];
+				output_cpu[i*output_cols+j] = input[i2*input_cols+j2];
+			}
+		}
+
+	}
+
+	//============================================================60
+	//	COLUMN MAJOR
+	//============================================================60
+
+	else{																															// do if data is saved column major
+
+		for(j=0, j2=0; j<output_cols; j++, j2++){
+			if(j2>=input_cols){
+				j2 = j2 - input_cols;
+			}
+			for(i=0, i2=0; i<output_rows; i++, i2++){
+				if(i2>=input_rows){
+					i2 = i2 - input_rows;
+				}
+				output[j*output_rows+i] = input[j2*input_rows+i2];
+				output_cpu[j*output_rows+i] = input[j2*input_rows+i2];
+			}
+		}
+
+	}
+
+}
+

### 2018-02-06 tests/UniBenchBack/benchmarks/clear_all.sh

@@ -1,0 +1,184 @@
+#!/bin/bash
+THIS=`pwd`
+
+#cd /home/gleison/lge/llvm-3.7-src/build-debug/bin 
+
+#rm out.txt
+
+#cd -
+
+#rm out.txt benchmarksStatistics.csv
+
+# List of benchmarks available to use our techinic
+list=(
+    #OMPSpec Benchmarks
+    'OMPSpec/target-3c/src/target-3c'
+    'OMPSpec/target-data-1c/src/target-data-1c'
+    'OMPSpec/target-data-2c/src/target-data-2c'
+    'OMPSpec/target-data-6c/src/target-data-6c'
+    #Parboil Benchmarks
+    'Parboil/common/parboil'
+    'Parboil/mri-q/src/main'
+    'Parboil/mri-q/src/file'
+    'Parboil/sgemm/src/io'
+    'Parboil/sgemm/src/main'
+    'Parboil/sgemm/src/sgemm_kernel'
+    'Parboil/spmv/src/convert_dataset'
+    'Parboil/spmv/src/file'
+    'Parboil/spmv/src/main'
+    'Parboil/spmv/src/mmio'
+    'Parboil/stencil/src/file'
+    'Parboil/stencil/src/kernels'
+    'Parboil/stencil/src/main'
+    #Polybench Benchmarks
+    'Polybench/2DCONV/src/2DConvolution'
+    'Polybench/2MM/src/2mm'
+    'Polybench/3DCONV/src/3DConvolution'
+    'Polybench/3MM/src/3mm'
+    'Polybench/ATAX/src/atax'
+    'Polybench/BICG/src/bicg'
+    'Polybench/CORR/src/correlation'
+    'Polybench/COVAR/src/covariance'
+    'Polybench/FDTD-2D/src/fdtd2d'
+    'Polybench/GEMM/src/gemm'
+    'Polybench/GESUMMV/src/gesummv'
+    'Polybench/GRAMSCHM/src/gramschmidt'
+    'Polybench/MVT/src/mvt'
+    'Polybench/SYR2K/src/syr2k'
+    'Polybench/SYRK/src/syrk'
+    'Polybench/SYRK_M/src/syrk_m'
+    #Rodinia 
+    'Rodinia/backprop/src/backprop'
+    'Rodinia/backprop/src/backprop_kernel'
+    'Rodinia/backprop/src/facetrain'
+    'Rodinia/backprop/src/imagenet'
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/mgBench/cholesky/src/cholesky_gpu-AI.c

@@ -1,0 +1,181 @@
+/*
+   This program performs cholesky decomposition on the GPU with 
+   dynamically allocated matrices.
+    
+    Author: Gleison Souza Diniz Mendon?a 
+    Date: 04-01-2015
+    version 2.0
+    
+    Run:
+    ipmacc cholesky_gpu.c -o cholesky
+    ./cholesky matrix-size
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+#include "../../common/mgbenchUtilFunctions.h"
+
+#define SIZE 1000
+#define GPU_DEVICE 0
+#define ERROR_THRESHOLD 0.05
+
+
+// Initialize matrices.
+void init_arrays(float *A, float *B_GPU, float *B_CPU) 
+{
+    int i, j, q;
+    q = SIZE * SIZE;
+    
+    #pragma acc data copy(B_GPU[0:1001000],B_CPU[0:1001000],A[0:1001000])
+    #pragma acc kernels
+    #pragma acc loop independent
+    for (i = 0; i < SIZE; ++i) 
+    {
+        for (j = 0; j < SIZE; ++j) 
+        {
+            A[i * SIZE + j] = (float)(q-(10*i)-(5*j));
+            B_GPU[i * SIZE + j] = 0.0f;
+            B_CPU[i * SIZE + j] = 0.0f;
+        }
+    }
+}
+
+
+/// Cholesky algorithm GPU
+/// s = size of matrix
+void cholesky_GPU(float *A, float *B) 
+{
+    int i,j,k,l;
+    
+    float t;
+
+    #pragma omp target device(GPU_DEVICE)
+    #pragma omp target map(to: A[0:SIZE*SIZE]) map(tofrom: B[0:SIZE*SIZE])
+    {
+	#pragma omp parallel for collapse(1)
+        for(i = 0; i < SIZE; i++)
+        {
+            for(j = 0; j <= i; j++) 
+            {
+                t = 0.0f;
+                for (k = 0; k < j; k++)
+                {
+                    if(B[i*SIZE+k]!=0.0f && B[j*SIZE+k]!=0.0f)
+                    {
+                        t += B[i*SIZE+k] * B[j*SIZE+k];
+                    }
+                    else
+                    {
+                        k--;
+                    }
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/mgBench/collinear-list/src/collinear-list_gpu.c

@@ -1,0 +1,170 @@
+/*
+    This program checks the collinearity of points.
+    It receives an input a vector with points and returns the mathematical
+   functions that pass these points. It have a list to store answers.
+    This program create a csv file with the time execution results for each
+   function(CPU,GPU) in this format: size of vector, cpu with list time, gpu
+   with list time.
+
+    Author: Gleison Souza Diniz Mendon?a
+    Date: 04-05-2015
+    version 2.0
+
+    Run:
+    folder_ipmacc/ipmacc folder_archive/colinear_v2.c
+    ./a.out
+*/
+#include <stdlib.h>
+#include <stdio.h>
+#include <math.h>
+#include <limits.h>
+#include <string.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+#include "../../common/mgbenchUtilFunctions.h"
+
+#define SIZE 1024
+#define GPU_DEVICE 0
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.05
+
+typedef struct point {
+  int x;
+  int y;
+} point;
+
+point *points;
+
+void generate_points() {
+  int i;
+  for (i = 0; i < SIZE; i++) {
+    points[i].x = (i * 777) % 11;
+    points[i].y = (i * 777) % 13;
+  }
+}
+
+/// colinear list algorithm GPU
+/// N = size of vector
+int colinear_list_points_GPU() {
+  int i, j, k, p, val;
+  val = 0;
+  p = 10000;
+
+  int *parallel_lines;
+  parallel_lines = (int *)malloc(sizeof(int) * p);
+  for (i = 0; i < p; i++) {
+    parallel_lines[i] = 0;
+  }
+
+  map(tofrom : parallel_lines [0:p]) {
+    for (i = 0; i < SIZE; i++) {
+      for (j = 0; j < SIZE; j++) {
+        for (k = 0; k < SIZE; k++) {
+          /// to understand if is colinear points
+          int slope_coefficient, linear_coefficient;
+          int ret;
+          ret = 0;
+          slope_coefficient = points[j].y - points[i].y;
+          if ((points[j].x - points[i].x) != 0) {
+            slope_coefficient = slope_coefficient / (points[j].x - points[i].x);
+            linear_coefficient =
+                points[i].y - (points[i].x * slope_coefficient);
+            if (slope_coefficient != 0 && linear_coefficient != 0 &&
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/mgBench/mat-mul/src/mat-mul_gpu_AI_ipmacc.cu

@@ -1,0 +1,453 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <assert.h>
+#include <openacc.h>
+#define IPMACC_MAX1(A)   (A)
+#define IPMACC_MAX2(A,B) (A>B?A:B)
+#define IPMACC_MAX3(A,B,C) (A>B?(A>C?A:(B>C?B:C)):(B>C?C:B))
+#ifdef __cplusplus
+#include "openacc_container.h"
+#endif
+
+#include <cuda.h>
+
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+#include "../../common/mgbenchUtilFunctions.h"
+
+#define SIZE 1000
+#define GPU_DEVICE 0
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.01
+
+
+ __device__ float __accelerator_absVal( float a );
+__device__ float __accelerator_percentDiff( double val1 , double val2 );
+ __global__ void __generated_kernel_region_0(float * a,float * c_cpu,float * c_gpu,float * b);
+ 
+void init(float *a, float *b, float *c_cpu, float *c_gpu)
+{
+  int i, j;
+    
+
+	ipmacc_prompt((char*)"IPMACC: memory allocation c_cpu\n");
+acc_present_or_create((void*)c_cpu,(999999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory allocation c_gpu\n");
+acc_present_or_create((void*)c_gpu,(999999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory allocation b\n");
+acc_present_or_create((void*)b,(999999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory allocation a\n");
+acc_present_or_create((void*)a,(999999+0)*sizeof(float ));
+	ipmacc_prompt((char*)"IPMACC: memory copyin c_cpu\n");
+acc_pcopyin((void*)c_cpu,(999999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory copyin c_gpu\n");
+acc_pcopyin((void*)c_gpu,(999999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory copyin b\n");
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/mgBench/mat-sum/src/mat-sum_gpu-AI.c

@@ -1,0 +1,143 @@
+/*
+   This program performs matrix sum on the GPU with 
+   dynamically allocated matrices.
+    
+    Author: Gleison Souza Diniz Mendonça 
+    Date: 04-01-2015
+    version 2.0
+    
+    Run:
+    ipmacc mat-sum_gpu.c -o mat
+    ./mat matrix-size
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+#include "../../common/mgbenchUtilFunctions.h"
+
+#define SIZE 1000
+#define GPU_DEVICE 0
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.01
+
+// Initialize matrices.
+void init(float *a, float *b, float *c_cpu, float *c_gpu) 
+{
+    int i, j;
+    #pragma acc data copy(c_cpu[0:1001000],c_gpu[0:1001000],b[0:1001000],a[0:1001000])
+    #pragma acc kernels
+    #pragma acc loop independent
+    for (i = 0; i < SIZE; ++i)
+    {
+	for (j = 0; j < SIZE; ++j)
+	{
+	    a[i * SIZE + j] = (float)i + j;
+	    b[i * SIZE + j] = (float)i + j;
+	    c_cpu[i * SIZE + j] = 0.0f;
+	    c_gpu[i * SIZE + j] = 0.0f;
+	}
+    }
+}
+
+/// matrix sum algorithm GPU
+/// s = size of matrix
+void sum_GPU(float *a, float *b, float *c) 
+{
+    int i, j;
+
+    #pragma omp target device (GPU_DEVICE)
+    #pragma omp target map(to: a[0:SIZE*SIZE], b[0:SIZE*SIZE]) map(tofrom: c[0:SIZE*SIZE])
+    {
+	#pragma omp parallel for collapse(2)
+        #pragma acc data copy(a[0:1001000],b[0:1001000],c[0:1001000])
+        #pragma acc kernels
+        #pragma acc loop independent
+        for (i = 0; i < SIZE; ++i)
+        {
+	    for (j = 0; j < SIZE; ++j)
+	    {
+		c[i * SIZE + j] = a[i * SIZE + j] + b[i * SIZE + j];	
+	    }
+        }
+    }
+}
+
+
+/// matrix sum algorithm CPU
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/mgBench/search-vector/src/search-vector_gpu-AI.c

@@ -1,0 +1,113 @@
+/*
+    This program searche a values in unordered vector and returns if find or not
+    This program create a csv file with the time execution results for each function(CPU,GPU) in this format: size of vector,cpu time,gpu time.
+    
+    Author: Kezia Andrade
+    Date: 04-07-2015
+    version 1.0
+    
+    Run:
+    folder_ipmacc/ipmacc folder_archive/search_in_vector.c
+    ./a.out
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+#include "../../common/mgbenchUtilFunctions.h"
+
+#define SIZE 1000
+#define GPU_DEVICE 0
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.01
+
+
+void init(float *a) 
+{
+	int i;
+	#pragma acc data copy(a[0:1000])
+	#pragma acc kernels
+	#pragma acc loop independent
+	for (i = 0; i < SIZE; ++i)
+	{
+        	a[i] = 2*i+7;
+	}
+}
+
+int search_GPU(float *a, float c)
+{
+    int i;
+    int find = -1;
+	int *find2;
+
+	find2 = &find;
+
+    #pragma omp target device (GPU_DEVICE)
+    #pragma omp target map(to: a[:SIZE]) map(from: find2[:1])
+    {
+        #pragma omp parallel for
+        for (i = 0; i < SIZE; ++i)
+        {
+	    if(a[i] == c)
+	    {
+	        find2[0] = i;
+	        i=SIZE;
+	    }
+        }
+    }
+
+    return find;
+}
+
+int search_CPU(float *a, float c)
+{
+	int i;
+    	int find = -1;
+
+	for (i = 0; i < SIZE; ++i)
+	{
+        	if(a[i] == c)
+        	{
+            	    find = i;
+	    	    i=SIZE;
+        	}
+	}
+
+	return find;
+}
+
+int main(int argc, char *argv[]) {
+    double t_start, t_end;
+    float *a, c;
+    int find_cpu, find_gpu;
+
+    a = (float *) malloc(sizeof(float) * SIZE);
+    c = (float) SIZE-5;
+
+    init(a);
+
+    fprintf(stdout, "<< Search Vector >>\n");
+
+    t_start = rtclock();
+    find_gpu = search_GPU(a, c);
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/mgBench/vector-product/src/vector-product_gpu_AI_ipmacc.cu

@@ -1,0 +1,404 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <assert.h>
+#include <openacc.h>
+#define IPMACC_MAX1(A)   (A)
+#define IPMACC_MAX2(A,B) (A>B?A:B)
+#define IPMACC_MAX3(A,B,C) (A>B?(A>C?A:(B>C?B:C)):(B>C?C:B))
+#ifdef __cplusplus
+#include "openacc_container.h"
+#endif
+
+#include <cuda.h>
+
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+#include <unistd.h>
+#include <sys/time.h>
+#include "../../common/mgbenchUtilFunctions.h"
+
+#define SIZE 1000
+#define GPU_DEVICE 0
+#define PERCENT_DIFF_ERROR_THRESHOLD 0.05
+
+
+ __device__ float __accelerator_absVal( float a );
+__device__ float __accelerator_percentDiff( double val1 , double val2 );
+ __global__ void __generated_kernel_region_0(float * A,float * B);
+ 
+void init_arrays(float *A, float *B)
+{
+  int i;
+    
+
+	ipmacc_prompt((char*)"IPMACC: memory allocation B\n");
+acc_present_or_create((void*)B,(999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory allocation A\n");
+acc_present_or_create((void*)A,(999+0)*sizeof(float ));
+	ipmacc_prompt((char*)"IPMACC: memory copyin B\n");
+acc_pcopyin((void*)B,(999+0)*sizeof(float ));
+ipmacc_prompt((char*)"IPMACC: memory copyin A\n");
+acc_pcopyin((void*)A,(999+0)*sizeof(float ));
+
+
+{
+
+
+    
+
+
+/* kernel call statement [0, -1]*/
+{
+if (getenv("IPMACC_VERBOSE")) printf("IPMACC: Launching kernel 0 > gridDim: %d\tblockDim: %d\n",(((abs((int)((SIZE))-(0+0)))/(1)))/256+(((((abs((int)((SIZE))-(0+0)))/(1)))%(256))==0?0:1),256);
+__generated_kernel_region_0<<<(((abs((int)((SIZE))-(0+0)))/(1)))/256+(((((abs((int)((SIZE))-(0+0)))/(1)))%(256))==0?0:1),256>>>(
[…]

### 2018-02-06 tests/UniBenchBack/benchmarks/removePrag.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+
+sed -i '/device(GPU_DEVICE)/d' $1
+sed -i '/pragma omp/d' $1 
+sed -i '/pragma target/d' $1 

### 2018-02-07 docs/ACM/paper.tex
Adding changes up to 3.4

--- 2018-02-06 docs/ACM/paper.tex
@@
 Second, it determines symbolic bounds to the memory blocks accessed within
-those regions (Section~\ref{sub:symb}).
+those regions (Section~\ref{sub:sra}).
 Third, it extracts parameters from the code to estimate when it is profitable to
@@
 which we have borrowed from the compiler-related literature, as we
-explain in Section~\ref{sub:symb}.
+explain in Section~\ref{sub:sra}.
 Figure~\ref{fig:ex_Regions} also introduces the second challenge that we
@@
 compiler that incorporates the techniques discussed in this paper.
+The many parts of this algorithm shall be explained throughout this section.
 This pseudo-code uses several concepts well-known in the compiler's
@@
 dependence graphs~\cite{Ferrante87}.
-We built on top of such concepts, as well as others, like
-symbolic range analysis~\cite{Blume94}, and natural loops~\cite{Allen70}.
 In the rest of this section we explain how we have combined this previous
-knowledge in order to delimit and annotate tasks in structured programs.
+knowledge to delimit and annotate tasks in structured programs.
 Our presentation focus on the new elements that we had to add onto known
@@
 Our goal is to identify {\em tasks} in {\em structured} programs.
-Definition~\ref{def:task} formalizes the notion of task.
 A structured program is a program that can be partitioned in {\em hammock
@@
 For completeness, we re-state it in Definition~\ref{def:hammock}.
-The structure of this program is described by a a Control Flow Graph $G$ --
-a directed graph with a starting node $s$, and an exit node $x$.
+Definition~\ref{def:task} formalizes the notion of task.
 
@@
 \label{def:hammock}
-A hammock region $G'$ from a CFG $G$ is a subgraph $G' \subseteq G$, with a
-node $h$, that {\em dominates}\footnote{A node $n_1 \in G$ dominates another node
+A Control Flow Graph $G$ is a directed graph with a starting node $s$, and an
+exit node $x$.
+A hammock region $G$ is a subgraph of $G$ with a node $h$ that
+{\em dominates}\footnote{A node $n_1 \in G$ dominates another node
 $n_2 \in G$ if every path from  $S$ to $n_2$ goes across $n_1$.
@@
 Dependencies are identified via the \textsf{depend} clause.
-In this example, each SESE region is formed by one function call:
+In this example, each hammock region is formed by one function call:
 \end{example}
@@
 Our equipment of choice to reveal task parallelism in programs is OpenMP 4.0.
-This annotation system provides us with a set of pragmas that indicate to compiler
-and runtime environment when and how tasks must be created.
+%This annotation system lets us indicate to compiler
+%and runtime environment when and how tasks must be created.
 We describe below which annotations we are using, and explain, informally, their
@@
 
-\subsection{Mapping Program Regions to Tasks}
-\label{sub:identification}
-
-% Windmills and vanes
-A {\em task candidate} is a set of program statements that can run in parallel
-with the rest of the program.
-To identify task candidates, we rely on the program's
-{\em Dependence Graph}.
-For completeness, Definition~\ref{def:pdg} revisits this notion.
-
-\begin{definition}[Program Dependence Graph -- \cite{Ferrante87}]
-\label{def:pdg}
-Given a program $P$, its PDG contains one vertex for each statement $s \in P$.
-There exists an edge from $s_1$ to $s_2$ if the latter depends on the former.
-Statement $s_2$ is {\em data-dependent} on $s_1$ if it reads data that $s_1$
-writes.
-It is {\em control dependent} on $s_1$ if $s_1$ determines the outcome of a
-branch, and depending on this outcome, we might execute $s_2$ or not.
-\end{definition}
-
-Task candidates are vanes in windmills.
-{\em Windmills} are a family of graphs.
-To the best of our knowledge, the term was coined by Rideau
-{\em et al.}~\cite{Rideau08} to describe structural relations between register
-copies.
-Our windmills exist as subgraphs of the program's dependence graph.
-We adopt a slightly more general definition than Rideaus'; however, the
-metaphor that gave origin to the name: the shape of the graphs, is still
-unmistakable:
-
-\begin{definition}[Windmill -- \cite{Rideau08}]
-\label{def:windmill}
-A windmill is a graph $G_w = G_c \cup G_{v1} \cup \ldots \cup G_{vn}$ formed by
-a strongly connected component $G_c$, its center, plus $n$ components (not
-necessarily strong) $G_{vi}$, the vanes, such that:
-\begin{compactenum}
-\item for any topological ordering of $G_w$, and nodes $n_c \in G_c$,
-$n_v \in G_{vi}$, we have $n_c$ ahead of $n_v$;
-\item for any $i$ and $j$, $1 \leq i < j \leq n$, $G_{vi}$ and $G_{vj}$ do not
-share vertices.
-\end{compactenum}
-\end{definition}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1\columnwidth]{images/ex_windmill}
-\caption{Examples of program dependence graphs.
-Nodes that form centers of windmills are coloured in gray.
-Data-dependence edges are solid; control-dependence edges are dashed.
-Vanes of windmills appear within dotted boxes.
-(a) PDG for Figure~\ref{fig:ex_book_filter};
-(b) PDG for Figure~\ref{fig:ex_Regions}}
-\label{fig:ex_windmill}
-\end{center}
-\end{figure}
-
-Figure~\ref{fig:ex_windmill} shows two program dependence graphs, highlighting
-windmills and their vanes.
-The structure of windmills naturally leads to task candidates.
-Vanes correspond to program parts that are likely to be executed
-several times, because they sprout from a loop -- the center of the windmill.
-Two different executions of the same vane can run in parallel.
-This is a property of the PDG, and one of the original motivations behind its
-design.
-These two different executions can be seen as two instances of the same
-structure (the vane), coming out of the same windmill center.
-A topological ordering of the dependence graph does not impose any order among
-these two hypothetical replicas of the same structure.
-
-Windmills gives us structural properties to identify tasks.
-We can easily find them via a depth-search traversal of the program dependence
-graph, for instance.
-However, not every windmill lead us to profitable tasks.
-Furthermore, some windmills simply cannot be annotated, due to structural 
-incompatibilities between the program dependence graph and its source code.
-We deal with the first shortcoming in Section~\ref{sub:profit}; the latter is
-the subject of Section~\ref{sub:ir}.
-
 \subsection{Finding Symbolic Bounds of Arrays}
-\label{sub:symb}
+\label{sub:sra}
 
 % Why this is necessary
-To produce the annotations that will lead to the creation of a task $T = (G, M_i,
-M_o)$, we need to determine the memory regions $M_i$ that $T$ reads, and the
-memory regions $M_o$ that it writes.
+To produce the annotations that create a task $T = (G, M_i, M_o)$, we need to
+determine the memory regions $M_i$ that $T$ reads, and the memory regions $M_o$
+that it writes.
 Memory regions consist of pointers, plus ranges of addresses that these pointers
@@
 \label{ex:sra}
-Symbolic range analysis, when applied onto Figure~\ref{fig:sra}, gives us
+Symbolic range analysis, when applied onto Figure~\ref{fig:ex_Regions}, gives us
 $R(\mathsf{i}) = [0, \mathsf{N} - 1]$, and $R(\mathsf{j}) = [0, \mathsf{M} - 1]$.
@@
 
+\subsection{Mapping Program Regions to Tasks}
+\label{sub:identification}
+
+% Windmills and vanes
+A {\em task candidate} is a set of program statements that can run in parallel
+with the rest of the program.
+To identify task candidates, we rely on the program's
+{\em Dependence Graph}.
+For completeness, Definition~\ref{def:pdg} revisits this notion.
+
+\begin{definition}[Program Dependence Graph -- \cite{Ferrante87}]
+\label{def:pdg}
+Given a program $P$, its PDG contains one vertex for each statement $s \in P$.
+There exists an edge from $s_1$ to $s_2$ if the latter depends on the former.
+Statement $s_2$ is {\em data-dependent} on $s_1$ if it reads data that $s_1$
+writes.
+It is {\em control dependent} on $s_1$ if $s_1$ determines the outcome of a
+branch, and depending on this outcome, we might execute $s_2$ or not.
+\end{definition}
+
+Task candidates are vanes in windmills.
+{\em Windmills} are a family of graphs.
+To the best of our knowledge, the term was coined by Rideau
+{\em et al.}~\cite{Rideau08} to describe structural relations between register
+copies.
+Our windmills exist as subgraphs of the program's dependence graph.
+We adopt a slightly more general definition than Rideaus'; however, the
+metaphor that gave origin to the name: the shape of the graphs, is still
+unmistakable:
+
+\begin{definition}[Windmill -- \cite{Rideau08}]
+\label{def:windmill}
+A windmill is a graph $G_w = G_c \cup G_{v1} \cup \ldots \cup G_{vn}$ formed by
+a strongly connected component $G_c$, its center, plus $n$ components (not
+necessarily strong) $G_{vi}$, the vanes, such that:
+\begin{compactenum}
+\item for any topological ordering of $G_w$, and nodes $n_c \in G_c$,
+$n_v \in G_{vi}$, we have $n_c$ ahead of $n_v$;
+\item for any $i$ and $j$, $1 \leq i < j \leq n$, $G_{vi}$ and $G_{vj}$ do not
+share vertices (thus, sharing edges is also impossible).
+\end{compactenum}
+\end{definition}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=1\columnwidth]{images/ex_windmill}
+\caption{Examples of program dependence graphs.
+Nodes that form centers of windmills are coloured in gray.
+Data-dependence edges are solid; control-dependence edges are dashed.
+Vanes of windmills appear within dotted boxes.
+(a) PDG for Figure~\ref{fig:ex_book_filter};
+(b) PDG for Figure~\ref{fig:ex_Regions}}
+\label{fig:ex_windmill}
+\end{center}
+\end{figure}
+
+Figure~\ref{fig:ex_windmill} shows two program dependence graphs, highlighting
+windmills and their vanes.
+The structure of windmills naturally leads to task candidates.
+Vanes correspond to program parts that are likely to be executed
+several times, because they sprout from a loop -- the center of the windmill.
+Two different executions of the same vane can run in parallel.
+This is a property of the PDG, and one of the original motivations behind its
+design.
+These two different executions can be seen as two instances of the same
+structure (the vane), coming out of the same windmill center.
+A topological ordering of the dependence graph does not impose any order among
+these two hypothetical replicas of the same structure.
+
+Windmills gives us structural properties to identify tasks.
+We can find them via a depth-search traversal of the program's dependence
+graph.
+Function \textsf{findVanes}, in Figure~\ref{fig:alg_main} implements this
+search.
+However, not every windmill lead us to profitable tasks.
+Furthermore, some windmills cannot be annotated, due to the inability of
+range analysis to find bounds to the memory they access.
+We deal with these shortcomings in the next two sections.
+
 \subsection{Estimating the Profitability of Tasks}
@@
 runtime cost, and parallelism.
-These two factors lead to a sweet spot in the size of tasks, where size is
-measured as the amount of code they contain.
+This tension leads to a sweet spot in the size of tasks, where size is
+measured as the amount of code they execute.
 The smaller the tasks are, the more parallel they tend to be, as a consequence
@@
 parallelism, because individual tasks still execute sequentially.
-In this paper, {\em we extract the smallest thread above the runtime cost}.
-To bestow meaning into this last statement, in what follows, we define more
-formally the notions of task size and task expansion.
+In this paper, we mark as tasks {\em the first maximal analyzable vane above the
+runtime cost}.
+To imbue this last statement with meaning, in what follows, we define more
+formally the notions of task size.
+We leave the concept of maximal analyzable vane for Section~\ref{sub:expansion}.
 
 \paragraph{Estimating the Size of Tasks.}
-The size of a task is given by its workload, i.e., the number of instructions that
-such task executes.
+The size of a task is given by its workload, i.e., the number of instructions 
+that such task executes.
 The same program region might lead to the creation of tasks with different sizes.
@@
 satisfies it.
-Naturally, we would like to construct $W$ in such a way to approximate the 
+Naturally, we would like $W$ to approximate the 
 dynamic behavior of programs.
-The compiler-related literature contains heuristics to implement $W$.
+The literature contains heuristics to implement $W$.
 Perhaps, the best-known among these heuristics is the static profiler of
@@
 \label{ex:cond_task}
-The condition in line 7 of Figure~\ref{fig:ex_Regions} determines that tasks will
-only be created if the expression \textsf{5 $\times$ M $<$ WORK\_CUTOFF}
+The condition in line 7 of Fig.~\ref{fig:ex_Regions} determines that tasks can be
+created if \textsf{5 $\times$ M $<$ WORK\_CUTOFF}
 holds.
@@
 iterations of the loop.
-
-\pedro{We need to discuss the THRESHOLD. Are we going to use
-César's experiments at Unicamp concerning the different runtimes? 
-Because if yes we need to think on how to write it.}
+In Figure~\ref{fig:alg_main}, these rules are implemented by function
+\textsf{profitabilityAnalysis}.
+
+\paragraph{The Cost Model.}
+A static workload estimate is only meaningful in the context of a {\em cost
+model}.
+A cost model is a collection of parameters that determine the impact of the
+underlying computer architecture onto the creation and management of tasks.
+The literature contains examples of techniques used to build cost models,
+be it analytically~\cite{Baghsorkhi10}, or empirically~\cite{Poesia17}.
+The automatic construction of a cost model is not the goal of this paper.
+Instead, the reader shall notice that Figure~\ref{fig:alg_main} receives a
+cost model as a parameter.
+For the experiments in Section~\ref{sec:eval}, we have determined a small
+collection of constants related to the creation of threads in our target
+architecture, including the value of \textsf{WORK\_CUTOFF}, seen in
+Example~\ref{ex:cond_task}.
 
 % Discuss the expansion algorithm.
-\paragraph{The Task Expansion Algorithm.}
+\subsection{Task Expansion}
+\label{sub:expansion}
+
 Task expansion consists in finding the smallest task that is large enough to

### 2018-02-17 docs/ACM/paper.tex
Adding example to section 3.4.

@@
 \label{ex:cond_task}
-The condition in line 7 of Fig.~\ref{fig:ex_Regions} determines that tasks can be
-created if \textsf{5 $\times$ M $<$ WORK\_CUTOFF}
-holds.
+The condition in line 7 of Fig.~\ref{fig:ex_Regions} determines that tasks are
+created if \textsf{5 $\times$ M $<$ WORK\_CUTOFF}.
+\textsf{M} is a program symbol, i.e., a variable passed as argument to
+function \textsf{foo}.
 The expression \textsf{5 $\times$ M} is an approximation for the size of the
@@
 \textsc{[LoopInf]} &
-\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = \infty}
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = \infty}
 {W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
@@
 \textsc{[LoopExp]} &
-\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = E}
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = E}
 {W(\mbox{while} (S_1) \ S_2;) = E \times (w_1 + w_2)}
@@
 we use to compute the SWE for a given hammock region $S$.
-The only rules that deserves comments are \textsc{LoopInf} and
-\textsc{LoopExp}.
-The former applies on loops whose number of iterations we cannot bound via some
-symbolic expression computed statically.
-The latter represents loops that we can analyze using our Symbolic Range Analysis.
-The auxiliary function $X(S)$ returns a symbolic expression that represents
+Rule \textsc{LoopInf} applies on loops whose number of iterations we cannot bound
+via some symbolic expression computed statically.
+Rule \textsc{LoopExp} represents loops that we can analyze using our Symbolic
+Range Analysis.
+The auxiliary function $\mathit{Iter}(S)$ returns a symbolic expression that
+represents
 the range of values covered by the code $S$ that controls the number of
@@
 We start this algorithm by setting \textsf{REGION} to be a hammock graph $H$
-that is contained entirely within a windmill $W$.
+that corresponds to a vane within a windmill $W$.
 The hammock decomposition of a structured program forms a tree~\cite{Ferrante87},
 such that vertices in this tree represent hammock graphs.
-$H_1$ is a child of $H_2$ in this tree if $H_1 \subset H_2$, and for any other
-node $H_x$, $H_1 \subset H_x \Rightarrow H_2 \subset H_x$.
-In this context, we call $H_2$ the \textsf{PARENT} of $H_1$.
-
-\begin{definition}[Region expansion]
-\label{def:expansion}
-A task region $R$ can be expanded into a larger region $R'$ if, and only if:
-\begin{itemize}
-\item $|M(R')| \leq |M(R)|$, in which $M(R)$ and $M(R')$ are the set of input and output memory
-dependences in regions $R$ and $R'$ respectively.
-\item $R'$ is still inside a loop or a cyclic construct.
-\end{itemize}
-\end{definition}
-
-Figure \ref{fig:expand_alg} illustrate the algorithm of expansion. It simply tries to expand while
-all the conditions in Definition \ref{def:expansion} are met, and then halts
-when they are not. After this process, {\Taskminer} ends up with a list
-of potential \emph{task regions}, which will then pass under
-a series of operations prior to the annotation to source code, the 
-ultimate step.
+$H_1$ is a child of $H_2$ in this tree if two conditions apply:
+(i) $H_1 \subset H_2$, and (ii) for any 
+other node $H_x$, if $H_1 \subset H_x$ then $H_2 \subset H_x$.
+In this context, we call $H_2$ the {\em parent} of $H_1$.
 
@@
 \includegraphics[width=1\columnwidth]{images/expand_alg}
-\caption{Task discovery via expansion of hammock regions.}
+\caption{Task discovery via expansion of hammock regions.
+\textsf{COST} is the overhead of creating and scheduling threads, as determined
+by a cost model.}
 \label{fig:expand_alg}
@@
 \end{figure}
+
+The boolean \textsf{CanExpand} in Figure~\ref{fig:expand_alg} is determined by
+the routine \textsf{checkExpansion}.
+This function remains true for as long as the following conditions apply with
+respect to its input \textsf{VANE}:
+(i) \textsf{VANE} is a hammock region with the structural properties of a
+windmill's vane, i.e., it is contained within a windmill $W$;
+(ii) we can analyze all the memory regions within \textsf{VANE} using the
+symbolic range analysis of Section~\ref{sub:sra};
+(iii) \textsf{VANE} does not depend on another vane inside the same windmill $W$.
+In the rest of this section, we shall use Figure~\ref{fig:ex_expansion} to
+explain these conditions.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=1\columnwidth]{images/ex_expansion}
+\caption{(a) Example of doubly nested loop that shall be analyzed by the 
+\Taskminer.
+(b) The dependence graph of the program.
+(c) The decomposition of this loop into windmills and vanes.
+$D$ is the set of variables the vane depends on.}
+\label{fig:ex_expansion}
+\end{center}
+\end{figure}
+
+The program in Figure~\ref{fig:ex_expansion} (a), which is a slight variation of
+the code earlier seen in Figure~\ref{fig:ex_regions}, contains two windmills.
+The first consists in the \textsf{for} loop at line 1.
+The second, nested in the first, is the \textsf{for} loop at line 2.
+The vanes that sprout from these windmills, are highlighted in the program
+dependence graph seen in Figure~\ref{fig:ex_expansion} (b).
+The figure shows that we have three task candidates, each one formed by a
+different vane.
+In order to find the actual tasks, we apply function \textsf{expand}
+(Fig.~\ref{fig:expand_alg}) onto the innermost vanes: \textsf{Vane-2} and
+\textsf{Vane-3}.
+The latter cannot be further expanded, because it depends on the former.
+On the other hand, \textsf{Vane-2} can be expanded to include also
+\textsf{Vane-3}, as this expansion does not create new dependences between vanes
+in the same windmill.
 

### 2018-02-19 docs/ACM/paper.tex
Section 3 finally concluded.

@@
 
-%\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
-%(1) the parent is a long for loop creating a large number of children, 
-%all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
-%(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
-%It imposes an upper bound for the ready task queue of a worker; a worker 
-%is discouraged to create too many tasks ready on the queue"}.
-
 To solve this problem, we conservatively limit the number of tasks
@@
 (1) limiting the creation of recursive tasks by depth; (2) limiting the creation of 
-tasks in the whole program.
-
-Consider the FIB
-
-\pedro{Show FFT example}
-
-\pedro{Explain that the setting is conservative and thus the parameter of control
-(max recursion depth and total number of tasks) can be easily switched by the
-user, or even completely disabled.}
+tasks in the whole program. We do that by setting up static variables to count up
+the depth level in recursive calls. When the depth reaches a certain level, which
+can be defined by the user, task dispatch will be halted, avoiding creation of tasks that are
+too small. This technique is illustrated in Figure \ref{fig:ex_cutoff}. 
+This parameter's default value is very conservative and so can be easily switched off
+or set by the user.
 
@@
 
+As described in Challenge \ref{ch:privatize}, the need for privatization of variables
+arises when tasks write on or read from variables that are shared among tasks but, instead,
+should be private for each task. To distinguish variables that should be replicated among tasks
+from those who shouldn't, we mapped this problem into a simple flow analysis, described
+as follows.
+
+\begin{definition}[Privatization]
+\label{def:privatize}
+A variable $X$ should be made private in a Task Region $T$ if the 
+\emph{Definition-Use Chain} of $X$ crosses
+the frontier of the task creation of $T$.
+\end{definition}
+
+This means that, if a variable $X$ is defined prior to the entry point of $T$, and then
+it is used (read/write) inside $T$, then it should be made private. Figure \ref{fig:ex_privatize}
+shows an example of privatization.
+
+We only privatize values, not pointers. And for a matter of conservativeness, we set all the
+variables shared by default, and then we run the privatization analysis afterwards to pin out
+variables that should be made private.
+
 \subsection{Mapping IR onto Source Code}
 \label{sub:ir}
+
+All the analyses and techniques described previously in this section are made upon
+an \emph{intermediate representation} (IR) of the program. None of our work would
+be made possible if we couldn't recover information from the IR back to Source Code.
+{\Taskminer} needs not only to insert \emph{pragmas}
+around task regions, but also recover array bounds information and preserve
+soundness regarding scope. The bridge between IR and Source Code information
+has 3 main obstacles to be crossed over:
+
+\begin{compactitem}
+\item \textsf{Source Code mapping}: The first problem is, given a set of instructions in the IR,
+how to map them back to the source code file. {\Taskminer} compiles the source code
+with debugging flags on, in order to extract debugging information that maps
+instructions to lines of code. With these lines of code in hands, we then have to deal
+with two more problems before annotation: scope breaking and array bounds information.
+
+\item \textsf{Array bounds}: To recover array bounds information, we rely on strong 
+alias analyses \pedro{References here?}. We link several kinds of instructions such as
+loads, stores, array indexing and other pointer arithmetic instructions to 
+trace back information to Source Code. We build a symbolic range analysis
+for each pointer, map them to all loads and stores in the program and then come up with
+lower and upper bounds for each. If we cannot properly define the range for all pointers 
+inside a task region, \emph{we don't annotate the task.}
+
+\item \textsf{Scope}: Once the task region is defined in terms of basic blocks in 
+the \emph{Control Flow Graph} in the IR, a problem of scope breaking arises when
+inserting \emph{pragmas} around code fragments in the Source Code. To work around
+this problem, we build a \emph{Scope Tree} in LLVM's front-end (Clang) and before
+we annotate the tasks, we check if the region mapped back to Source Code will break
+any scope in the original program. The scope-breaking risk appears when many instructions
+inside basic blocks map back to their definition (instead of their uses) in the source code,
+which sometimes are outsite the region defined as a task. When that happens, we opt 
+not to annotate the task, because we can't recover enough information to correctly annotate
+the original code.
+
+\end{compactitem}
 

### 2018-04-02 docs/ACM/paper.tex

--- 2018-02-17 docs/ACM/paper.tex
@@
 Our goal is to identify {\em tasks} in {\em structured} programs.
-A structured program is a program that can be partitioned in {\em hammock
-regions}, a concept introduced by Ferrante {\em et al.}~\cite{Ferrante87} in
-the middle 80's.
+In the context of this work, a structured program is a program that can be
+partitioned in {\em hammock regions}, a concept introduced by Ferrante
+{\em et al.}~\cite{Ferrante87} in the middle 80's.
 For completeness, we re-state it in Definition~\ref{def:hammock}.
@@
 exit node $x$.
-A hammock region $G$ is a subgraph of $G$ with a node $h$ that
+A hammock region $G'$ is a subgraph of $G$ with a node $h$ that
 {\em dominates}\footnote{A node $n_1 \in G$ dominates another node
@@
 \paragraph{The annotation zoo.}
-Our equipment of choice to reveal task parallelism in programs is OpenMP 4.0.
+Our equipment of choice to exploit task parallelism in programs is OpenMP 4.0.
 %This annotation system lets us indicate to compiler
@@
 The only extensions that we have added into \dawn's implementation was
-the ability to handle \textsf{structs}.
-Therefore, we shall not provide further details about part of our work.
+the ability to handle C-like \textsf{structs}.
+Therefore, we shall not provide further details about this part of our work.
 To understand the rest of this paper, it suffices to know that this implementation
@@
 A windmill is a graph $G_w = G_c \cup G_{v1} \cup \ldots \cup G_{vn}$ formed by
-a strongly connected component $G_c$, its center, plus $n$ components (not
-necessarily strong) $G_{vi}$, the vanes, such that:
+a strongly connected component $G_c$ (its center), plus $n$ components, not
+necessarily strong, $G_{vi}$, the vanes, such that:
 \begin{compactenum}
@@
 \caption{Task discovery via expansion of hammock regions.
-\textsf{COST} is the overhead of creating and scheduling threads, as determined
-by a cost model.}
+\textsf{COST} is the overhead of creating and scheduling threads.}
 \label{fig:expand_alg}
@@
 
-The boolean \textsf{CanExpand} in Figure~\ref{fig:expand_alg} is determined by
-the routine \textsf{checkExpansion}.
-This function remains true for as long as the following conditions apply with
-respect to its input \textsf{VANE}:
-(i) \textsf{VANE} is a hammock region with the structural properties of a
+The routine \textsf{checkExpansion} sets the boolean \textsf{CanExpand} in
+Figure~\ref{fig:expand_alg}.
+This function is true as long as the following conditions apply:
+(i) \textsf{VANE} has the structural properties of a
 windmill's vane, i.e., it is contained within a windmill $W$;
-(ii) we can analyze all the memory regions within \textsf{VANE} using the
+(ii) we can analyze the memory regions within \textsf{VANE} using the
 symbolic range analysis of Section~\ref{sub:sra};
 (iii) \textsf{VANE} does not depend on another vane inside the same windmill $W$.
-In the rest of this section, we shall use Figure~\ref{fig:ex_expansion} to
-explain these conditions.
 
@@
 The program in Figure~\ref{fig:ex_expansion} (a), which is a slight variation of
-the code earlier seen in Figure~\ref{fig:ex_regions}, contains two windmills.
+the code earlier seen in Figure~\ref{fig:ex_Regions}, contains two windmills.
 The first consists in the \textsf{for} loop at line 1.
@@
 
-\subsection{Limiting the Creation of Recursive Tasks}
-\label{sub:rec}
-
+\paragraph{Rational:}
+We expand tasks up to a certain threshold \textsf{COST}, which is determined
+by the cost model mentioned in Section~\ref{sub:profit}.
+If the profitability of a task is less than this constant, then parallelism
+might not pay off the cost of managing threads.
+However, if we expand tasks too much, then we might not have much parallelism,
+because code within a task is executed sequentially.
+Thus, determining \textsf{COST} is essential to the performance of our
+optimization.
+In this work, we have determined this parameter empirically for the
+runtime environment to be described in Section~\ref{sec:eval}.
+
+\subsection{Privatization}
+\label{sub:variance}
+
+\Taskminer{} bestow a parallel semantics on code that has been originally
+conceived to run sequentially.
+This semantic gap might lead to race conditions.
+Race conditions happen when annotations cause two or more threads to update
+values that, in the sequential program, are denoted by the same name.
+To avoid such situations, the insertion of annotations requires us to replicate
+some values, making them private to each task.
+We have named such replication {\em privatization}.
+
+\begin{example}[Privatization]
+\label{ex:priv}
+Variables \textsf{i} and \textsf{j} in Figure~\ref{fig:ex_privatize} need to be
+replicated among the tasks that the annotation at line 8 creates.
+The need to replicate \textsf{j} is more apparent: this variable is updated in
+the body of the task pragma, at line 9.
+In the absence of replication, we have a race condition.
+Variable \textsf{i} must also be replicated.
+Each iteration of the loop at line 9 reads a different value of \textsf{i}.
+Thus, each task should receive a different value in this variable.
+In the absence of replication, all the threads would read the same value;  hence,
+parallelization would change the semantics of the program.
+\end{example}
+
+\begin{definition}[The Private Requirement]
+\label{def:private}
+If a variable name has scalar type and contains at least one def-use chain that
+enters the frontier of a task, then this name is said to bear the {\em private
+requirement}.
+The frontier of a task is determined by the \textsf{expand} function seen in
+Figure~\ref{fig:expand_alg}.
+\end{definition}
+
+\begin{example}
+\label{ex:priv_2}
+Variable \textsf{i} must be privatized because it is defined at lines 2 and 10 of
+Figure~\ref{fig:ex_privatize}, and is used at line 9 -- the body of a new task.
+Moreover, this variable has a scalar type, e.g., \textsf{int}.
+Similarly, variable \textsf{j} is defined at line 6, and is used at line 9.
+This property -- the existence of def-use chains entering the task region --
+leads to the insertion of the \textsf{firstprivate} clause at line 8 of
+Figure~\ref{fig:ex_privatize}.
+\end{example}
+
+\noindent
+\paragraph{firstprivate vs depend:} according to Definition~\ref{def:private},
+only names representing scalar values are privatized.
+These names have {\em value semantics}, i.e., they are ``passed
+by copy" if used as actual arguments of functions.
+Memory regions, that is to say, regions whose access happens through pointers,
+are not privatized.
+These regions are, instead, marked as dependences of the task, through the
+\textsf{depend} clause.
+Memory regions are discovered via the symbolic region analysis of
+Section~\ref{sub:sra}.
+In addition to pointers, we do not privatize values defined within
+a task region, and used outside it.
+That is to say: we privatize incoming def-use chains, but do not privatize
+outgoing chains.
+Values having this ``outgoing chain property" are shared by default.
+We indicate this semantics via the \textsf{default(shared)} pragmas, as seen
+in line 8 of Figure~\ref{fig:ex_privatize}.
+
+\subsection{Mapping IR onto Source Code}
+\label{sub:ir}
+
+% Explain rational
+The analyses described in Sections~\ref{sub:sra}-\ref{sub:variance} have
+been implemented at the level of the LLVM intermediate representation.
+We chose to implement those techniques at that level to benefit from the support
+of several data-flow analyses already in place in the LLVM infra-structure.
+In particular, this decision lets us reuse LLVM's scalar
+evolution~\cite[p.18]{Grosser12}, from which we derive our symbolic analysis.
+Additionally, we could reuse LLVM's program dependence graph, and its suite of
+powerful alias analyses.
+This toolbox gave us the necessary means to disambiguate pointers, albeit
+conservatively, and estimate safe limits to memory regions.
+However, our annotations are still inserted in C programs.
+Having them in a high-level programming language has two main advantages:
+they are human-readable, and thus can be debugged, and they are compatible with
+compilers other than \textsf{clang}, such as \textsf{gcc}.
+Thus, a major part of this work was the engineering effort to map
+information from LLVM's intermediate representation back into C.
+
+% Explain machinery: scope tree and simplification
+\noindent
+\textbf{The Scope Tree:}
+To recover high-level information from the low-level IR, we have designed a
+supporting data-structure henceforth named the {\em scope tree}.
+The scope tree maps hammock regions into C constructions, such as
+\textsf{while} and \textsf{if-then-else} blocks.
+Each node of this graph represents a hammock region, augmented with
+meta-information, such as the program part that it represents.
+We keep track of these program parts via debugging information, which is
+appended into the LLVM IR via the \textsf{-g} flag passed to the \textsf{clang}
+compiler.
+We have an edge from node $s_1$ to node $s_2$ if region $s_2$ is nested
+within region $s_2$.
+In the absence of control-flow optimizations such as loop unrolling or
+dead-code elimination, each hammock region corresponds to some structured
+code block (code region delimitable by braces).
+Thus, we can find line numbers for each of the regions that we have marked
+as tasks after the expansion seen in Section~\ref{sub:expansion}.
+
+\noindent
+\textbf{Simplification:}
+before we annotate programs, we proceed to simplify these annotations.
+Simplification happens via a system of rewriting rules, which explores 
+identities.
+Typical identifies include, for instance, $x + 0 = x$,
+$\mathsf{max}(x, x) = x$ and $c \times \mathsf{max}(x, y) =
+\mathsf{max}(c \times x, c \times y)$.
+Identities are applied iteratively, until a fixed-point is reached.
+Because we do not support commutativity, a fixed-point is guaranteed to be
+always reached.
+Notice that the source code that we produce is not totally equivalent to the
+original program augmented with annotations.
+To be able to insert annotations, we format the original code.
+This operation involves, for instance, breaking lines containing multiple
+statements, and inserting delimiting braces within every block in the program,
+even one-liners.
+This said, it is still possible that a task, after expansion, maps to a single
+line that contains multiple statements, such as nested function calls.
+In this case, we do not annotate the target program.
+Section~\ref{sec:eval} provides data about \Taskminer's capacity to
+annotate real-world programs.
+
+\paragraph{Bounding Recursive Tasks}
 Although the OpenMP runtime guarantees correctness, its scheduling policy
@@
 (1) limiting the creation of recursive tasks by depth; (2) limiting the creation of 
-tasks in the whole program.
-
-Consider the FIB
-
-\pedro{Show FFT example}
-
-\pedro{Explain that the setting is conservative and thus the parameter of control
-(max recursion depth and total number of tasks) can be easily switched by the
-user, or even completely disabled.}
-
-\subsection{Separating Private from Shared Variables}
-\label{sub:variance}
-
-\subsection{Mapping IR onto Source Code}
-\label{sub:ir}
+tasks in the whole program. We do that by setting up static variables to count up
+the depth level in recursive calls. When the depth reaches a certain level, which
+can be defined by the user, task dispatch will be halted, avoiding creation of tasks that are
+too small. This technique is illustrated in Figure \ref{fig:ex_cutoff}. 
+This parameter's default value is very conservative and so can be easily switched off
+or set by the user.
 

### 2018-04-03 docs/ACM/paper.tex
Done with Section 3.

@@
 the creation of tasks (Section~\ref{sub:profit}) and limit their recursion
-depth (Section~\ref{sub:rec}).
+depth (Section~\ref{sub:ir}).
 Fourth, \Taskminer{} determines which program variables need to be 
@@
 \includegraphics[width=1\columnwidth]{images/ex_cutoff}
-\caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks with
-counter associated with function calls.}
+\caption{Challenge~\ref{ch:cutoff}: bounding the creation of recursive tasks.
+Example taken from~\cite[Fig.1]{Iwasaki16}.}
 \label{fig:ex_cutoff}
@@
 This observation is particularly true in the context of recursive, fine-grain,
-tasks, as we analyze in Section~\ref{sub:rec}.
+tasks, as we analyze in Section~\ref{sub:ir}.
 Figure~\ref{fig:ex_cutoff} provides an example.
@@
 
-The program in Figure~\ref{fig:ex_expansion} (a), which is a slight variation of
-the code earlier seen in Figure~\ref{fig:ex_Regions}, contains two windmills.
-The first consists in the \textsf{for} loop at line 1.
+The program in Figure~\ref{fig:ex_expansion} (a), a slight variation of
+the code seen in Figure~\ref{fig:ex_Regions}, contains two windmills.
+The first consists of the \textsf{for} loop at line 1.
 The second, nested in the first, is the \textsf{for} loop at line 2.
-The vanes that sprout from these windmills, are highlighted in the program
-dependence graph seen in Figure~\ref{fig:ex_expansion} (b).
-The figure shows that we have three task candidates, each one formed by a
+The vanes that sprout from these windmills are highlighted in the program
+dependence graph in Figure~\ref{fig:ex_expansion} (b).
+The figure shows that we have three task candidates, each formed by a
 different vane.
-In order to find the actual tasks, we apply function \textsf{expand}
+To find the actual tasks, we apply function \textsf{expand}
 (Fig.~\ref{fig:expand_alg}) onto the innermost vanes: \textsf{Vane-2} and
 \textsf{Vane-3}.
-The latter cannot be further expanded, because it depends on the former.
-On the other hand, \textsf{Vane-2} can be expanded to include also
+The latter cannot be expanded, as it depends on the former.
+On the other hand, \textsf{Vane-2} can be expanded to include
 \textsf{Vane-3}, as this expansion does not create new dependences between vanes
@@
 
-\paragraph{Rational:}
-We expand tasks up to a certain threshold \textsf{COST}, which is determined
-by the cost model mentioned in Section~\ref{sub:profit}.
+\noindent
+\textbf{Rational:}
+We expand tasks up to the \textsf{COST} threshold, which is determined
+by the cost model seen in Section~\ref{sub:profit}.
 If the profitability of a task is less than this constant, then parallelism
 might not pay off the cost of managing threads.
-However, if we expand tasks too much, then we might not have much parallelism,
-because code within a task is executed sequentially.
+However, if we expand tasks too much, then we might lose parallelism,
+as code in a task runs sequentially.
 Thus, determining \textsf{COST} is essential to the performance of our
 optimization.
-In this work, we have determined this parameter empirically for the
+In this work, we have set this parameter empirically for the
 runtime environment to be described in Section~\ref{sec:eval}.
@@
 \paragraph{Bounding Recursive Tasks}
-Although the OpenMP runtime guarantees correctness, its scheduling policy
-is heavily jeopardized by the excessive queueing up of tasks. Specifically, algorithms
-such as \emph{SparseLU} and \emph{FFT} can suffer bloat because of
-too many tasks in the Task Graph\cite{Huynh17}.
-
-To solve this problem, we conservatively limit the number of tasks
-that can be created tied to the same Task Region. We do that by two means:
-(1) limiting the creation of recursive tasks by depth; (2) limiting the creation of 
-tasks in the whole program. We do that by setting up static variables to count up
-the depth level in recursive calls. When the depth reaches a certain level, which
-can be defined by the user, task dispatch will be halted, avoiding creation of tasks that are
-too small. This technique is illustrated in Figure \ref{fig:ex_cutoff}. 
-This parameter's default value is very conservative and so can be easily switched off
-or set by the user.
+During the evaluation of the \Taskminer, we observed that recursive
+programs experienced performance regressions due to the excessive creation
+of tasks.
+To avoid this kind of slowdown, we currently give users the possibility to
+bound the number of threads ever in flight, via a command line option, e.g.,
+\textsf{./Taskminer -r 12} will limit the number of tasks to 12.
+We implement this feature directly at the source code level, as part of the
+final annotation of code.
+Our solution is simple, yet, as the reader shall perceive in
+Section~\ref{sec:eval}, it brings non-negligible benefits onto recursive
+benchmarks.
+Task bounding is implemented via a global variable, statically linked in the
+program.
+This variable is \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:ex_cutoff}.
+We insert code to increment it at the beginning of recursive functions that
+are invoked within task regions, and we insert code to decrement it at each
+return point of said functions.
+
+\begin{example}[Task Bounding]
+Figure~\ref{fig:ex_cutoff} illustrates the strategy that we
+use to limit the number of tasks in flight due to recursive function
+invocation.
+The parameter \textsf{DEPTH\_CUTOFF} is determined by \Taskminer's users.
+\end{example}
+
+There are more involved ways to bound the number of tasks.
+We believe that the state-of-the-art in the field today is the work of
+Iwasaki and Taura~\cite{Iwasaki16,Iwasaki16B}.
+These authors propose different techniques to limit the creation of tasks,
+be it through the replication of code, be it through the estimation of work,
+given function inputs.
+Pragmas for the conditional creation of tasks, such as the one seen in
+lines 7 and 10 of Figure~\ref{fig:ex_cutoff}, lets us obtain much of the benefit
+of code versioning, as proposed by Iwasaki and Taura.
+However, we found work estimation of recursive functions a task too difficult
+to accomplish in general.
+Quoting~\cite[p.355]{Iwasaki16}: ``{\em there are tasks which essentially do not
+have simple termination conditions (e.g., tasks traversing pointer-based
+trees)}".
+Thus, although simple, our recursion counters are general enough, handling even
+such tasks that are hard to bound symbolically.
+Nevertheless, we still would like to explore further ways to cut-off extremely
+fine-grained tasks in the future.
 

### 2018-04-04 docs/ACM/paper.tex
Adding reference to Antao's paper.

@@
 
-\paragraph{On the Implementation of \Taskminer.}
 We have implemented all the techniques described in this paper in
@@
 expressions~\cite{Mendonca17}.
-Second, given the state-of-the-art support that LLVM already provides to the
-compilation of OpenMP~\cite{Bertolli14,Martineau16,Samuel16}.
-
-We performed a thorough evaluation on \Taskminer{}'s applicability in real programs. Our test framework is divided in five aspects:
-
+Second, the state-of-the-art support that LLVM already provides to the
+compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16,Samuel16}.
+In this section, we evaluate this implementation, focusing on four research
+questions:
+%
 \begin{compactitem}
-\item \textsf{Performance}: we run \Taskminer on the BOTS Benchmark and show that the programs annotated by taskminer are sometimes as fast as programs annotated manually, and never slower than their sequential counterparts, thus proving it to be a conservative and useful technique.
-\item \textsf{Optimizations}: we show some optimizations that can be applied to \Taskminer in order to improve performance of the annotated programs.
-\item \textsf{Versatility}: we demonstrate \Taskminer's versatility when it is able to find tasks in several different program paradigms.
-\item \textsf{Applicability}: we run \Taskminer on larger benchmarks to show the potential of finding task parallelism in big applications.
-\item \textsf{Practicality}: here we present \Taskminer's runtime and show that it can be easily used by a programmer to find task parallelism in applications.
-We evidence \Taskminer's practicality when compared to the method of manually finding parallelism, determining data dependences annotating the program.
+\item \textsf{[Performance]}: how do our automatically annotated programs
+compare against their sequential counterparts, or against manually annotated
+versions?
+\item \textsf{[Optimizations]}: what is the impact of the cost model
+(Section~\ref{sub:profit}) and recursion bounding (Section~\ref{sub:ir}) onto
+the programs that we annotate?
+\item \textsf{[Versatility]}: how effective is \Taskminer{} in finding
+opportunities to annotate general benchmarks?
+\item \textsf{[Scalability]}: what is the runtime complexity of our
+implementation of \Taskminer?
 \end{compactitem}
@@
 %Here, we show the results for our small benchmarks (toys & bots)
-\textbf{\textit{Performance}}.
+\subsection{Performance}.
 
@@
 %We can use the same benchmarks as above.
-\textbf{\textit{Optimizations}}.
+\subsection{Optimizations}.
 
@@
 %And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
-\textbf{\textit{Versatility}}.
+\subsection{Versatility}.
 
@@
 %We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
-\textbf{\textit{Applicability}}.
-
-%PRACTICALITY
-%The main objective here is to show that TaskMiner can be easily utilized by a programmer to find tasks in their source code. 
-%We'll test TaskMiner's running time.
-\textbf{\textit{Practicality}}.
+\subsection{Scalability}.
 

### 2018-04-04 docs/ACM/paper.tex
Removing repeated reference to Antao's work.

@@
 Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
-to substantial performance gains~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Samuel16,Wienke12}.
+to substantial performance gains~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Antao16,Wienke12}.
 %\guido{Suppport what?}
@@
 Second, the state-of-the-art support that LLVM already provides to the
-compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16,Samuel16}.
+compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16}.
 In this section, we evaluate this implementation, focusing on four research

### 2018-04-05 docs/ACM/paper.tex
Adding reference to Ravishankar's work.

@@
 memory region -- either prevents parallelism altogether, or forces compilers to
-resort to complex runtime checks to ensure its correctness~\cite{Alves15,Rus02}.
+resort to complex runtime checks to ensure its
+correctness~\cite{Alves15,Ravishankar14}.
 The OpenMP runtime shields us from this problem, because

### 2018-04-07 docs/ACM/paper.tex
Adding related work session + new references.

@@
 
+Data-flow programming was originally proposed as a candidate to enable
+task-based parallelism \cite{agrawal:ipdps:2010, chan:spaa:2007,
+gupta:micro:2011}.  Agrawal et al. \cite{agrawal:ipdps:2010}  extended
+data-flow programming  with task input/otuput  specifications in  Cilk++.
+Vandierendonck et al.  \cite{vandierendonck:hotpar:2011} also extended Cilk++
+by adding dependency clauses that facilitated the design of complex
+parallelization patterns. Both works presented a unified scheduler based on
+fork-join parallelism \cite{vandierendonck:pact:2011} which enabled the
+execution of task-based dataflow applications. Other approaches have also used
+data-flow task graphs to exploit parallelism, like Data-Driven Tasks
+\cite{tasirlar:icpp:2011}, where the programmer can use put/await clauses to
+determine the task arguments before execution.  These works focused on
+data-flow programming  models and unfortunately  have not been adopted by most
+programmers. Function-based task parallelism was proposed by Gupta et al
+\cite{gupta:micro:2011} with the goal of using function arguments  as a way to
+specify task  dependencies. Although their work seemed sound, programming using
+such approach is a cumbersome task, when compared to modern directive-based
+parallelization.
+
+Many systems have been developed aiming at (semi) automatically extracting task
+parallelism from sequential programs. Examples of such systems are OSCAR
+(Optimally SCheduled Advanced multiprocessoR), Multigrain Parallelizing
+Compiler \cite{ishizaka:journal:2000, kasahara:iwlcpc:2000},  MAPS (MPSoC
+Application Programming  Studio) \cite{castrillon:tii:2013, ceng:dac:2008}, and
+DiscoPoP (Discovery of Potential Parallelism) \cite{discopop, li:jss:2016}.
+Although most of these systems have succeeded in achieving their goals, overall
+they have not managed to engage most programmers in using them. Besides
+parallelization systems, tools like Paraver \cite{extrae, paraver}, Aftermath
+\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, and TEMANEJO
+\cite{brinkmann:parco:2011, brinkmann:journal:2013, temanejo} were  designed to
+enable performance analysis, debugging, and vizualization of task programming
+executions.
+
+More recently, directive based sequential code annotation  standards have
+provided programmers with a very clean and easy to use parallel programming
+model. Task based extensions to these standards have resulted in OpenMP 4.X,
+StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
+tejedor:hpdc:2011} and OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}  which have
+been extensively used to task-parallelize a large number of applications. Such
+programming models have the support of tools that help programmers find the
+best annotations for their code. For example,  Tareador
+\cite{ayguade:wcae:2015} enables a programmer, by means of a simple API and a
+graphical representation,  to iteratively annotate sequential code, thus
+allowing the identification of potential task parallelization opportunities.
+Contrary to Tareador,  this paper proposes an approach that enables the
+automatic insertion OpenMP task annotations to relevant fragments of a
+sequential program.
+
 % Talk about annotations vs libraries, e.g., Wool, Intel TBB. See: "A Comparison of some recent Task-based Parallel Programming Models"

### 2018-04-08 docs/ACM/paper.tex
Working on Related Work.

--- 2018-04-05 docs/ACM/paper.tex
@@
 \bibliographystyle{ACM-Reference-Format}
-\citestyle{acmauthoryear}
+%\citestyle{acmauthoryear}
 
@@
 
+Mainstream compilers have only recently added support to OpenMP 4.0's task
+parallelism.
+An implementation of \textsf{clang} supporting tasks was released in March 14th,
+2014\footnote{\url{https://clang-omp.github.io/}}.
+A few weeks later, in April 22nd, 2014, such support was also announced in
+\textsf{gcc} 4.9.
+Thus, because the necessary infra-structure for the implementation of tasks is
+relatively new, currently there are no tools, other than the \Taskminer,
+that annotate programs automatically with these directives.
+Nevertheless, there exists a long string of research aiming at the automatic
+parallelization of programs.
+In this section, we examine some elements in this list that relate to our
+work.
+
+Directive-based code annotation standards provide programmers with an easy-to-use
+parallel programming model.
+Task-based extensions to these standards have resulted in OpenMP 4.X,
+StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
+tejedor:hpdc:2011} and OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}  which have
+been extensively used to task-parallelize applications. Such
+programming models come with tools that help programmers find the
+best annotations for their code. For example,  Tareador
+\cite{ayguade:wcae:2015} enables a programmer, by means of a graphical interface,
+to annotate sequential code, thus allowing the identification of potential task
+parallelization opportunities.
+Contrary to Tareador,  this paper proposes an approach that enables the
+automatic insertion of OpenMP task annotations to relevant fragments of a
+sequential program.
+
+The techniques that we use to map program regions to tasks is similar to
+analyses previously used in the generation of code for data-flow machines.
+Data-flow programming was originally proposed as a candidate to enable
+task-based parallelism \cite{agrawal:ipdps:2010, chan:spaa:2007,
+gupta:micro:2011}.  Agrawal et al. \cite{agrawal:ipdps:2010}  extended
+data-flow programming  with task input/output specifications in  Cilk++.
+Vandierendonck et al.  \cite{vandierendonck:hotpar:2011} further extended Cilk++
+with dependency clauses to facilitate the design of complex
+parallelization patterns. Both groups presented a unified scheduler based on
+fork-join parallelism \cite{vandierendonck:pact:2011} that enabled the
+execution of task-based applications. Other approaches have also used
+data-flow graphs to exploit parallelism, like Data-Driven Tasks
+\cite{tasirlar:icpp:2011}, where the programmer can use put/await clauses to
+determine task arguments before execution.
+Function-based task parallelism was proposed by Gupta {\em et al.}
+\cite{gupta:micro:2011} to use function arguments  as a way to
+specify task  dependencies.
+Notice that such research efforts focused on giving to programmers the tools to
+{\em construct} parallel programs.
+The automatic annotation of ordinary programs with data-flow constructs was not
+among their goals.
+
+Many systems have been developed to extract task parallelism from sequential
+programs (semi) automatically.
+Examples include OSCAR
+(Optimally SCheduled Advanced multiprocessoR), Multigrain Parallelizing
+Compiler \cite{ishizaka:journal:2000, kasahara:iwlcpc:2000},  MAPS (MPSoC
+Application Programming  Studio) \cite{castrillon:tii:2013, ceng:dac:2008}, and
+DiscoPoP (Discovery of Potential Parallelism) \cite{discopop, li:jss:2016}.
+Besides parallelization systems, tools like Paraver \cite{extrae, paraver},
+Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, and TEMANEJO
+\cite{brinkmann:parco:2011, brinkmann:journal:2013, temanejo} were  designed to
+enable performance analysis and visualization of task-based programs.
+Although these tools help the programmer in adapting code
+to run in parallel, they are not fully automatic.
+For instance, the work that is the closest of ours, in reach and effectiveness,
+in our opinion, is the suite of techniques proposed by Ravishankar {\em et
+al.}~\cite{Ravishankar14}.
+The type of irregular loops that they handle is impressive; however,
+the lack of the runtime support \`{a} la OpenMP 4.X still requires them to
+modify code before parallelization.
+In their words: ``{\em For all benchmarks and applications, all functions were 
+inlined, and arrays of structures were converted to structures of arrays for use
+with our prototype compiler.}"
+
 % Talk about annotations vs libraries, e.g., Wool, Intel TBB. See: "A Comparison of some recent Task-based Parallel Programming Models"

### 2018-04-08 docs/ACM/paper.tex
Small fix in paper.
Adding new references.

@@
 task parallelism.
-These techniques deal with problems such as the discovery and use of program
-symbols to estimate the profit of tasks, bound their recursive depth and limit
-the memory regions onto which they operate.
-These techniques have been implemented into the first source-to-source
-compiler able to insert OpenMP pragmas into C/C++ programs without human
-intervention.
-By building onto the solid collection of static analyses available in LLVM,
-and relying on OpenMP's runtime ability to disambiguate pointers, we show that
-we can annotate large and convoluted programs, often replicating the performance
-gains of handmade annotation.
+These techniques approximate the ranges covered by memory regions, bound
+recursive tasks and estimate the profitability of tasks.
+We have used these ideas to implement a source-to-source compiler that inserts 
+OpenMP pragmas into C/C++ programs without any human intervention.
+By building onto the static program analysis literature, and relying on OpenMP's
+runtime ability to disambiguate pointers, we show that we can annotate large and
+convoluted programs, often replicating the performance gains of handmade
+annotation.
+Furthermore, our techniques give us the means to discover, without any 
+development cost, opportunities of parallelism that remained buried in the syntax 
+of well-known benchmarks for many years.
 \end{abstract}
@@
 % How we do it.
-The program symbols mentioned in Definition~\ref{def:sra} are names that cannot be
-reconstruct as functions of other names.
+The program symbols mentioned in Definition~\ref{def:sra} are names that cannot 
+be reconstruct as functions of other names.
 Examples include global variables, function arguments, and values returned by
 external functions.
-Symbolic range analysis is not a contribution of this paper.
-There are several different implementations publicly available, and we have
-adopted the one in the \dawn{} compiler~\cite{Mendonca17}, which, itself,
+Symbolic range analysis is not a contribution of this paper: several
+implementations of it exist.
+We have adopted the one in the \dawn{} compiler~\cite{Mendonca17}, which, itself,
 reuses work from Blume {\em et al.}~\cite{Blume94}.
@@
 satisfies it.
-Naturally, we would like $W$ to approximate the 
-dynamic behavior of programs.
+However, we want $W$ to approximate the dynamic behavior of programs.
 The literature contains heuristics to implement $W$.
@@
 
-We have implemented all the techniques described in this paper in
-LLVM~\cite{Lattner04}.
-This decision was motivated by two factors.
-First, the possibility to reuse all the infra-structure already
-available in LLVM to infer symbolic bounds of integer
-expressions~\cite{Mendonca17}.
-Second, the state-of-the-art support that LLVM already provides to the
-compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16}.
+\noindent
+\textbf{Runtime Environment:}
+We have implemented the techniques described in this paper in
+LLVM 3.9~\cite{Lattner04}.
+All our experiments were performed in a 64-bits 12-core Intel(R) Xeon(R) CPU
+E5-2620 at 2.00GHz, with 32K of L1 cache, 256K of L2 cache, 15M of L3 cache and
+15Gb of main memory.
+We use OpenMP 4.5, from November of 2015.
+
+\noindent
+\textbf{Research Questions:}
 In this section, we evaluate this implementation, focusing on four research
@@
 
+\noindent
+\textbf{Benchmarking:}
+we have used different benchmarks in our experiments.
+In Sections~\ref{sub:performance} and~\ref{sub:optimizations} we use
+\textsf{BSC-Bots}\footnote{\url{https://github.com/bsc-pm/bots/tree/master/serial}} and \textsf{Swan}\footnote{\url{http://cuda.dcc.ufmg.br/swan/}}~\cite{Moreira17}.
+In Section~\ref{sub:versatility} we use the LLVM test suite, and in
+Section~\ref{sub:scalability} we use random programs produced with
+\textsf{CSmith}~\cite{Yang11}.
+Runtime numbers are averages of five executions.
+We have not changed manually any of the benchmarks.
+
 %PERFORMANCE
@@
 \subsection{Performance}.
-
-\begin{figure}[t!]
+\label{sub:performance}
+
+\begin{figure}[htb]
 \begin{center}
@@
 \subsection{Optimizations}.
-
-\begin{figure}[t!]
+\label{sub:optimizations}
+
+\begin{figure}[htb]
 \begin{center}
@@
 \subsection{Versatility}.
+\label{sub:versatility}
 
@@
 \subsection{Scalability}.
+\label{sub:scalability}
 
@@
 best annotations for their code. For example,  Tareador
-\cite{ayguade:wcae:2015} enables a programmer, by means of a graphical interface,
+\cite{Ayguade15} enables a programmer, by means of a graphical interface,
 to annotate sequential code, thus allowing the identification of potential task

### 2018-04-08 docs/ACM/paper.tex
Working on scalability.

@@
 \textsc{[Seq]} &
-\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_2}
+\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_1 + w_2}
 \\\\
@@
 %Here, we show the results for our small benchmarks (toys & bots)
-\subsection{Performance}.
+\subsection{Performance}
 \label{sub:performance}
@@
 %We can use the same benchmarks as above.
-\subsection{Optimizations}.
+\subsection{Optimizations}
 \label{sub:optimizations}
@@
 %And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
-\subsection{Versatility}.
+\subsection{Versatility}
 \label{sub:versatility}
@@
 %We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
-\subsection{Scalability}.
+\subsection{Scalability}
 \label{sub:scalability}
+
+The analyses that we have described in Section~\ref{sec:sol} have a worst-case
+quadratic time.
+This is the worst-case scenario of the symbolic range analysis of
+Section~\ref{sub:sra} and the task-expansion algorithm of
+Section~\ref{sub:expansion}.
+Nevertheless, our implementation is fast in practice.
+To support this statement, we have used \textsf{CSmith}~\cite{Yang11}, a random
+code generator, to produce 100 programs of varying sizes, which we then fed to
+the \Taskminer.
+Figure~\ref{fig:TM_Runtime} shows the result of this experiment.
+Our largest program had 4,999 lines of C, and \Taskminer{} could process it
+in 1.2 seconds.
+the $R^2$ of polynomials of degree 1, 2, 3 and 4 is, respectively, 0.795,
+0.890, 0.909 and 0.911, suggesting very small differences between polynomials
+of degree 2 or more.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/TM_Runtime}
+\caption{Runtime of \Taskminer{} vs size of input programs.
+Each dot represents one of the 100 program generated by \textsf{CSmit}.
+We have fit a degree-2 polynomial on this dataset.}
+\label{fig:TM_Runtime}
+\end{center}
+\end{figure}
 

### 2018-04-09 docs/ACM/paper.tex
filled sections 4.1 4.2 and 4.3

@@
 
-\begin{figure}[htb]
+\begin{figure}[h]
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{images/Absolute_speedups}
+\includegraphics[width=1.1\columnwidth]{images/EVAL1_bots_and_toys.png}
 \caption{Speedup comparisons -- automatic annotations compare favourably against
@@
 
+In order to evaluate {\Taskminer}'s performance, we picked the \textsf{BSC-Bots} along with
+five other single source programs\footnote{Toy benchmarks: Boruvka's MST algorithm;
+Bellman-Ford's shortest path algorithm; Book filter, an algorithm that performs operations on lines from
+a text; Private, the algorithm from Figure \ref{fig:ex_privatize}; and the Depth-first search algorithm.}
+and produced four versions for each single source file: the sequential original program; a parallel version
+of the program, annotated by hand; a parallel version automatically annotated by {\Taskminer}, without
+the task cost model; a parallel version annotated by {\Taskminer} with the cost model enabled. Figure
+\ref{fig:Absolute_speedups} show {\Taskminer}'s overall performance compared to the original
+sequential and manually annotated programs. For simplification purposes, we address
+the difference between the automatic samples in regards to the cost model in section
+\ref{sub:optimizations}.
+
+{\Taskminer}'s annotated programs were faster than their sequential counterparts in 13 of the 16
+programs. Most of the programs in these benchmarks were classic Divide and Conquer algorithms, such as \textit{Strassen}'s matrix multiplication, \textit{knapsack.c} and \textit{fft.c}.
+In 6 of them, the automatically annotated programs were close and sometimes even slightly
+above the manually annotated ones. In the programs \textit{fib.c}, \textit{floorplan.c} and
+\textit{bellmandford.c}, although the
+{\Taskminer}'s version fell behind the sequential ones, it was also faster than the manually annotated
+versions, which were clearly slower than the original programs. The manually annotated versions for all
+the \textsf{BSC-Bots} benchmarks were obtained from \cite{Duran09}. Regarding the \textit{bellmanford.c}
+benchmark, we believe that the slowdown was due to small tasks being dispatched. Even the cost model
+wasn't able to pay off for this difference.
+In the \textit{fib.c} program, both parallel versions (automatic and manual) were far slower than
+the original, specially for big entries. We believe that the compiler we utilized optimized the
+classic sequential fibonacci algorithm, while the \textsf{OpenMP} runtime didn't.
+Overall, {\Taskminer} has proven to be able to find all the tasks in the \textsf{BSC-Bots} benchmarks and
+its annotated versions even surpassed some of the original in performance.
+
 %OPTIMIZATIONS
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{images/Opt_Speedups}
+\includegraphics[width=1\columnwidth]{images/EVAL2_opt.png}
 \caption{The benefit of our optimizations.
-Each optimization (profitability analysis and recursion bounds) lead to
+Each optimization (cost model and recursion bounds) lead to
 non-trivial speedups.}
@@
 \end{figure}
+
+In most of the benchmarks, the presence of task cost estimates made little difference in performance of
+the automatically annotated programs. In some of them, the cost model was very decisive to 
+guarantee a speed up against the sequential versions, though. These can be seen in Figure \ref{fig:Opt_Speedups}.
+A coarse gain in speed up was noticed in the \textit{nqueens.c} program, in which the recursion bounding
+avoided the creation of smaller and exponentially increasing tasks, which caused a significant speed
+up in its execution. 
+If on one hand, the cost model is able to avoid the creation and the dispatch of tasks that are too small
+and are not going to pay off for the runtime cost, on the other hand computing the cost for tasks can add
+some overhead to the programs. This is easily seen in the \textit{bellmanford} program. For larger
+matrices, larger is the number of paths to be computed, so in this case, {\Taskminer} will try to
+compute the cost for every task, which we believe caused this minor slowdown. However, it's
+clear that the cost model greatly improved {\Taskminer}.
 
@@
 \label{sub:versatility}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=1\columnwidth]{images/EVAL3_test-suite.png}
+\caption{{\Taskminer}'s performance in the real world. This chart shows that our algorithm also performs
+well on programs that are not deemed inherently parallel, being able to find hidden parallelism
+in 20 programs from LLVM's Test Suite.}
+\label{fig:testsuite}
+\end{center}
+\end{figure}
+
+Our tool has also performed well on \textsf{LLVM's Test Suite}, being able to even find hidden parallelism.
+From a total of XX single source programs,
+{\Taskminer} automatically produced parallel annotated versions of 20 of them, as seen in Figure
+\ref{fig:testsuite}. We were able to not only find hidden parallelism in those programs, which are not
+considered inherently parallel, but also produce these parallel versions automatically. Amongst
+those programs, one caught our attention: \textit{misc/lowercase.c}, which applies a function to every
+string in the text. The automatically annotated version of this program was 3.5 times faster than
+the sequential one. We have also nice speed up numbers in \textit{misc/ffbench} and \textit{misc/mandel-2}.
 
@@
 \textbf{health}    & \checkmark         & \checkmark            & \checkmark      \\ \hline
-\textbf{jacobi}    &                    &                       &                 \\ \hline
+\textbf{jacobi}    &                    &  \checkmark                     &                 \\ \hline
 \end{tabular}
@@
 
-%APPLICABILITY
-%We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
+{\Taskminer}'s versatility also arises in regards to the diversity of types of task parallelism that it
+can find in a program. Table \ref{tab:types} shows all types of tasks found in our main benchmarks.
+There are 3 types of tasks: recursive, which arises from vanes in Divide and Conquer
+algorithms; function call, which arises within loops that are not clearly parallel; and region, which 
+are similar to function calls, but instead are entire fragments of code within loops that can be executed in
+parallel. We provide the user complete decision power to mine for any type of tasks they wish when
+running our tool.
+
+%SCALABILITY
 \subsection{Scalability}
 \label{sub:scalability}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{images/TM_Runtime}
+\caption{Runtime of \Taskminer{} vs size of input programs.
+Each dot represents one of the 100 program generated by \textsf{CSmit}.
+We have fit a degree-2 polynomial on this dataset.}
+\label{fig:TM_Runtime}
+\end{center}
+\end{figure}
 
@@
 of degree 2 or more.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{images/TM_Runtime}
-\caption{Runtime of \Taskminer{} vs size of input programs.
-Each dot represents one of the 100 program generated by \textsf{CSmit}.
-We have fit a degree-2 polynomial on this dataset.}
-\label{fig:TM_Runtime}
-\end{center}
-\end{figure}
 

### 2018-04-09 docs/ACM/paper.tex
Adding new figures.

@@
 In Sections~\ref{sub:performance} and~\ref{sub:optimizations} we use
-\textsf{BSC-Bots}\footnote{\url{https://github.com/bsc-pm/bots/tree/master/serial}} and \textsf{Swan}\footnote{\url{http://cuda.dcc.ufmg.br/swan/}}~\cite{Moreira17}.
+\textsf{BSC-Bots}\footnote{\url{https://github.com/bsc-pm/bots/tree/master/serial}}~\cite{Duran09} and
+\textsf{Swan}\footnote{\url{http://cuda.dcc.ufmg.br/swan/}}~\cite{Moreira17}.
 In Section~\ref{sub:versatility} we use the LLVM test suite, and in
@@
 \begin{center}
-\includegraphics[width=1.1\columnwidth]{images/EVAL1_bots_and_toys.png}
+\includegraphics[width=1\columnwidth]{images/TM_Performance}
 \caption{Speedup comparisons -- automatic annotations compare favourably against
@@
 annotation (this paper) onto the original programs.}
-\label{fig:Absolute_speedups}
+\label{fig:TM_Performance}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{images/EVAL2_opt.png}
+\includegraphics[width=1\columnwidth]{images/Stub}
 \caption{The benefit of our optimizations.
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{images/EVAL3_test-suite.png}
+\includegraphics[width=1\columnwidth]{images/Stub}
 \caption{{\Taskminer}'s performance in the real world. This chart shows that our algorithm also performs

### 2018-04-09 docs/ACM/paper.tex
Adding figure about versatility.

@@
 
+Figure~\ref{fig:TM_Performance} compares the runtime of programs produced by
+\Taskminer{} against either the original -- sequential -- program (the baseline,
+compiled with \textsf{clang} -O3)
+or versions of said programs annotated manually.
+In this experiment we use the two benchmarks mentioned in the beginning of this
+Section: \textsf{BSC-Bots}~\cite{Duran09} (\textsf{fft} to \textsf{jacobi}
+in Fig.~\ref{fig:TM_Performance}) and \textsf{Swan}~\cite{Moreira17}
+(\textsf{dfs} to \textsf{private}).
+Both these benchmarks come with sequential and parallel versions.
+
 \begin{figure}[h]
@@
 manual interventions, and lead to great performance gains.
-The Y-axis shows the speedup of either manual intervention, or automatic
-annotation (this paper) onto the original programs.}
+The Y-axis shows the speedup of either manual intervention or the \Taskminer{}
+(this paper) upon the original programs, in number of times.
+Small numbers in boxes show speedup achieved by \Taskminer.}
 \label{fig:TM_Performance}
@@
 
-In order to evaluate {\Taskminer}'s performance, we picked the \textsf{BSC-Bots} along with
-five other single source programs\footnote{Toy benchmarks: Boruvka's MST algorithm;
-Bellman-Ford's shortest path algorithm; Book filter, an algorithm that performs operations on lines from
-a text; Private, the algorithm from Figure \ref{fig:ex_privatize}; and the Depth-first search algorithm.}
-and produced four versions for each single source file: the sequential original program; a parallel version
-of the program, annotated by hand; a parallel version automatically annotated by {\Taskminer}, without
-the task cost model; a parallel version annotated by {\Taskminer} with the cost model enabled. Figure
-\ref{fig:Absolute_speedups} show {\Taskminer}'s overall performance compared to the original
-sequential and manually annotated programs. For simplification purposes, we address
-the difference between the automatic samples in regards to the cost model in section
-\ref{sub:optimizations}.
-
-{\Taskminer}'s annotated programs were faster than their sequential counterparts in 13 of the 16
-programs. Most of the programs in these benchmarks were classic Divide and Conquer algorithms, such as \textit{Strassen}'s matrix multiplication, \textit{knapsack.c} and \textit{fft.c}.
-In 6 of them, the automatically annotated programs were close and sometimes even slightly
-above the manually annotated ones. In the programs \textit{fib.c}, \textit{floorplan.c} and
-\textit{bellmandford.c}, although the
-{\Taskminer}'s version fell behind the sequential ones, it was also faster than the manually annotated
-versions, which were clearly slower than the original programs. The manually annotated versions for all
-the \textsf{BSC-Bots} benchmarks were obtained from \cite{Duran09}. Regarding the \textit{bellmanford.c}
-benchmark, we believe that the slowdown was due to small tasks being dispatched. Even the cost model
-wasn't able to pay off for this difference.
-In the \textit{fib.c} program, both parallel versions (automatic and manual) were far slower than
-the original, specially for big entries. We believe that the compiler we utilized optimized the
-classic sequential fibonacci algorithm, while the \textsf{OpenMP} runtime didn't.
-Overall, {\Taskminer} has proven to be able to find all the tasks in the \textsf{BSC-Bots} benchmarks and
-its annotated versions even surpassed some of the original in performance.
+The programs annotated by \Taskminer{} were faster than their sequential
+counterparts in 13 of the 16 samples.
+Most of the programs in these benchmarks were classic Divide and Conquer algorithms, such as \textsf{Strassen}'s matrix multiplication, \textsf{knapsack}
+and \textsf{fft}.
+In 6 of them, the automatically annotated programs were close and sometimes even 
+slightly above the manually annotated versions.
+In three examples where \Taskminer{} fell behind the original samples, e.g.,
+\textsf{fib}, \textsf{floorplan} and \textsf{bellmandford} (\textsf{bell-ford}),
+it produced code faster than the manually annotated competitor.
+Visual inspection of \textsf{bellmanford} shows that the version parallelized
+manually is dispatching an large number of small tasks.
+Our cost model can prune some of these small tasks, but not enough to win
+on the sequential version.
+We emphasize that the human-annotated versions of our benchmarks have not
+been tested originally in our architecture.
+For instance, \textsf{BSC-Bots} was evaluated on an SGI Altix 4700
+with 128 processors~\cite{Duran09}.
+Thus, this difference in hardware might be accountable for the slowdown in
+some of the manually annotated samples.
+Nevertheless, this experiment lets demonstrate that {\em \Taskminer{} can
+deliver non-negligible speedups comparable with sequential and manually
+annotated programs}.
 
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{images/Stub}
+\includegraphics[width=1\columnwidth]{images/TM_Versatility}
 \caption{{\Taskminer}'s performance in the real world. This chart shows that our algorithm also performs
@@
 in 20 programs from LLVM's Test Suite.}
-\label{fig:testsuite}
+\label{fig:TM_Versatility}
 \end{center}

### 2018-04-09 docs/ACM/paper.tex
Adding discussion on versatility.

@@
 
+The benchmarks used in Section~\ref{sub:performance} have been written to
+demonstrate the power of different parallel systems; hence, they have already
+been written in a way that simplifies the discovery of parallelism in programs.
+In this section, we address the following question: ``can \Taskminer" find
+parallelism in general programs?
+To answer it, we have applied \Taskminer{} onto the 219 C programs available in
+the LLVM test suite, and have compared the annotated version
+against the sequential version compiled with \textsf{clang} -O3.
+\Taskminer{} annotates a benchmark if it can find symbolic bounds to every
+memory access (load or store) used within a region marked as a task candidate.
+Under this constraint, we have been able to discover tasks in 63 benchmarks.
+Figure~\ref{fig:TM_Versatility} relates the number of tasks and the number of
+instructions in benchmarks.
+To avoid counting multiple C files for the same benchmark,
+Figure~\ref{fig:TM_Versatility} contains only benchmarks that are
+constituted by a single file (present in LLVM's \textsf{SingleSource} folder).
+As this experiment demonstrates, \Taskminer{} {\em can annotate a non-trivial
+number of real-world benchmarks}.
+
 \begin{figure}[htb]
@@
 \includegraphics[width=1\columnwidth]{images/TM_Versatility}
-\caption{{\Taskminer}'s performance in the real world. This chart shows that our algorithm also performs
-well on programs that are not deemed inherently parallel, being able to find hidden parallelism
-in 20 programs from LLVM's Test Suite.}
+\caption{Relation between number of task regions and program size.
+Each benchmark is a complete C file.}
 \label{fig:TM_Versatility}
@@
 
-Our tool has also performed well on \textsf{LLVM's Test Suite}, being able to even find hidden parallelism.
-From a total of XX single source programs,
-{\Taskminer} automatically produced parallel annotated versions of 20 of them, as seen in Figure
-\ref{fig:testsuite}. We were able to not only find hidden parallelism in those programs, which are not
-considered inherently parallel, but also produce these parallel versions automatically. Amongst
-those programs, one caught our attention: \textit{misc/lowercase.c}, which applies a function to every
-string in the text. The automatically annotated version of this program was 3.5 times faster than
-the sequential one. We have also nice speed up numbers in \textit{misc/ffbench} and \textit{misc/mandel-2}.
-
-\begin{table}[h]
-\centering
-\caption{Different kinds of tasks among the BOTS benchmarks. {\Taskminer}'s versaitily allows the user to define which type of tasks should be mined, annotated or cared for.}
-\label{tab:types}
-\begin{tabular}{|r|c|c|c|}
-\hline
-                   & \textbf{Recursive} & \textbf{FunctionCall} & \textbf{Region} \\ \hline
-\textbf{fft}       & \checkmark         &                       & \checkmark      \\ \hline
-\textbf{fib}       & \checkmark         &                       &                 \\ \hline
-\textbf{floorplan} & \checkmark         &                       & \checkmark      \\ \hline
-\textbf{sort}      & \checkmark         &                       & \checkmark      \\ \hline
-\textbf{sparselu}  &                    & \checkmark            & \checkmark      \\ \hline
-\textbf{strassen}  & \checkmark         &                       & \checkmark      \\ \hline
-\textbf{uts}       & \checkmark         &                       &                 \\ \hline
-\textbf{nqueens}   & \checkmark         &                       & \checkmark      \\ \hline
-\textbf{knapsack}  & \checkmark         &                       & \checkmark      \\ \hline
-\textbf{health}    & \checkmark         & \checkmark            & \checkmark      \\ \hline
-\textbf{jacobi}    &                    &  \checkmark                     &                 \\ \hline
-\end{tabular}
-\end{table}
-
-{\Taskminer}'s versatility also arises in regards to the diversity of types of task parallelism that it
-can find in a program. Table \ref{tab:types} shows all types of tasks found in our main benchmarks.
-There are 3 types of tasks: recursive, which arises from vanes in Divide and Conquer
-algorithms; function call, which arises within loops that are not clearly parallel; and region, which 
-are similar to function calls, but instead are entire fragments of code within loops that can be executed in
-parallel. We provide the user complete decision power to mine for any type of tasks they wish when
-running our tool.
+Most of the benchmarks, e.g., 27, that have been automatically annotated did not
+give us speedups, because the regions marked as tasks were too small to influence
+the program's runtime.
+We have observed slowdowns in 17 benchmarks.
+In this case, interactions between data-structures end up forcing the OpenMP
+runtime to serialize execution of tasks.
+And we have measured speedups above 5\% in 19 benchmarks.
+In one case, \textsf{Misc/lowercase}, the speedup is above 3.5x, and in
+three cases, it goes beyond 1.5x.
+Figure~\ref{fig:TM_GeneralProgs} summarizes these findings.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=1\columnwidth]{images/TM_GeneralProgs}
+\caption{20 best speedups obtained by \Taskminer{} when applied onto the LLVM
+test suite.
+The larger the bar, the better.
+\textbf{LoC} stands for ``Lines of C".}
+\label{fig:TM_GeneralProgs}
+\end{center}
+\end{figure}
+
+%{\Taskminer}'s versatility also arises in regards to the diversity of types of task parallelism that it
+%can find in a program. Table \ref{tab:types} shows all types of tasks found in our main benchmarks.
+%There are 3 types of tasks: recursive, which arises from vanes in Divide and Conquer
+%algorithms; function call, which arises within loops that are not clearly parallel; and region, which 
+%are similar to function calls, but instead are entire fragments of code within loops that can be executed in
+%parallel. We provide the user complete decision power to mine for any type of tasks they wish when
+%running our tool.
 

### 2018-04-10 docs/ACM/paper.tex
Fixing caption of Figure 13.
Adding Description of optimizations.

@@
 In Sections~\ref{sub:performance} and~\ref{sub:optimizations} we use
-\textsf{BSC-Bots}\footnote{\url{https://github.com/bsc-pm/bots/tree/master/serial}}~\cite{Duran09} and
-\textsf{Swan}\footnote{\url{http://cuda.dcc.ufmg.br/swan/}}~\cite{Moreira17}.
+\textsf{BSC-Bots} (\url{https://github.com/bsc-pm/bots/tree/master/serial})~\cite{Duran09} and
+\textsf{Swan} (\url{http://cuda.dcc.ufmg.br/swan/})~\cite{Moreira17}.
 In Section~\ref{sub:versatility} we use the LLVM test suite, and in
@@
 \textsf{CSmith}~\cite{Yang11}.
-Runtime numbers are averages of five executions.
-We have not changed manually any of the benchmarks.
-
-%PERFORMANCE
-%Here, we show the results for our small benchmarks (toys & bots)
+Runtimes are averages of five executions.
+No benchmark has been changed manually.
+
 \subsection{Performance}
@@
 
-Figure~\ref{fig:TM_Performance} compares the runtime of programs produced by
-\Taskminer{} against either the original -- sequential -- program (the baseline,
-compiled with \textsf{clang} -O3)
-or versions of said programs annotated manually.
-In this experiment we use the two benchmarks mentioned in the beginning of this
-Section: \textsf{BSC-Bots}~\cite{Duran09} (\textsf{fft} to \textsf{jacobi}
-in Fig.~\ref{fig:TM_Performance}) and \textsf{Swan}~\cite{Moreira17}
-(\textsf{dfs} to \textsf{private}).
-Both these benchmarks come with sequential and parallel versions.
-
-\begin{figure}[h]
+\begin{figure}[b!]
 \begin{center}
@@
 \end{figure}
+
+Figure~\ref{fig:TM_Performance} compares the runtime of programs produced by
+\Taskminer{} against either the original program (the baseline,
+compiled with \textsf{clang} -O3)
+or versions of said programs annotated manually.
+In this experiment we use the benchmarks \textsf{BSC-Bots}~\cite{Duran09} (\textsf{fft} to \textsf{jacobi}
+in Fig.~\ref{fig:TM_Performance}) and \textsf{Swan}~\cite{Moreira17}
+(\textsf{dfs} to \textsf{private}).
+Both these benchmarks come with sequential and parallel (manually
+annotated) versions.
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[b!]
 \begin{center}
-\includegraphics[width=1\columnwidth]{images/Stub}
-\caption{The benefit of our optimizations.
-Each optimization (cost model and recursion bounds) lead to
-non-trivial speedups.}
-\label{fig:Opt_Speedups}
+\includegraphics[width=1\columnwidth]{images/Optimizations}
+\caption{Benefit of task pruning (Secs.~\ref{sub:profit} and~\ref{sub:ir}).
+\textbf{RFC}: tasks created within \underline{R}ecursive \underline{F}unction
+\underline{C}alls.
+\textbf{NRC}: interprocedural tasks created around
+\underline{N}on-\underline{R}ecursive function \underline{C}alls.
+\underline{Reg}: tasks involving \underline{Reg}ions without function calls.
+}
+\label{fig:Optimizations}
 \end{center}
@@
 
-In most of the benchmarks, the presence of task cost estimates made little difference in performance of
-the automatically annotated programs. In some of them, the cost model was very decisive to 
-guarantee a speed up against the sequential versions, though. These can be seen in Figure \ref{fig:Opt_Speedups}.
-A coarse gain in speed up was noticed in the \textit{nqueens.c} program, in which the recursion bounding
-avoided the creation of smaller and exponentially increasing tasks, which caused a significant speed
-up in its execution. 
-If on one hand, the cost model is able to avoid the creation and the dispatch of tasks that are too small
-and are not going to pay off for the runtime cost, on the other hand computing the cost for tasks can add
-some overhead to the programs. This is easily seen in the \textit{bellmanford} program. For larger
-matrices, larger is the number of paths to be computed, so in this case, {\Taskminer} will try to
-compute the cost for every task, which we believe caused this minor slowdown. However, it's
-clear that the cost model greatly improved {\Taskminer}.
+This paper describes two ways to optimize task placement.
+Both these techniques are based on the idea of ``task pruning": we avoid
+creating tasks if we deem them unprofitable.
+The first technique prunes tasks judged unprofitable by the cost-model of
+Section~\ref{sub:profit}; the second prunes tasks that are too deep in the
+recursion stack, as described in Section~\ref{sub:ir}.
+Figure~\ref{fig:Optimizations} illustrates the benefits of these two techniques.
+We show the gains -- in terms of speedup over the baseline -- of the three
+benchmarks that
+benefit the most from each type of task pruning, among those earlier seen in
+Figure~\ref{fig:TM_Performance}.
+
+In three benchmarks, \textsf{private}, \textsf{boruvka} and
+\textsf{bellman-ford}, the cost model avoids creating tasks around loops that
+initialize data-structures.
+For instance, the following loop, in line 75 of \textsf{bellmanford.c}, would be
+parallelized by \Taskminer, were it not for the cost-model marking it as
+unprofitable:
+
+\begin{verbatim}
+  for (long unsigned i = 0; i < N; i++)
+    for (long unsigned j = 0; j < N; j++)
+      *(G + i * N + j) = rand();
+\end{verbatim}
+
+Similarly, recursion bounding (Sec.~\ref{sub:ir}), although
+simple, is effective in eliminating the excessive number of tasks.
+Figure~\ref{fig:Optimizations} shows the effect of this optimization upon
+three \textsf{BSC-Bots} benchmarks: \textsf{health}, \textsf{nqueens} and
+\textsf{strassen}.
+These programs were designed to illustrate the parallelization of
+divide-and-conquer algorithms~\cite{Duran09}, and contain a large number of
+recursive calls (see \textbf{RFC}) in Figure~\ref{fig:Optimizations}.
+Pruning at higher levels of the recursion tree lets them deliver
+non-negligible speedups onto the baseline programs.
+Were pruning absent, then we would observe slowdowns in \textsf{health}
+and \textsf{nqueens}.
 
@@
 \includegraphics[width=1\columnwidth]{images/TM_GeneralProgs}
-\caption{20 best speedups obtained by \Taskminer{} when applied onto the LLVM
+\caption{Speedups obtained by \Taskminer{} when applied onto the LLVM
 test suite.

### 2018-04-10 docs/ACM/paper.tex
Adding conclusion to Sec. 5.

@@
 \inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
-{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + w_2 + w_3}
+{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + \mbox{max}(w_2 + w_3)}
 \\\\
@@
 and \textsf{nqueens}.
+This experiment shows that {\em our optimizations are effective to
+improve the quality of the code that we generate}.
 
@@
 
-The benchmarks used in Section~\ref{sub:performance} have been written to
-demonstrate the power of different parallel systems; hence, they have already
+The benchmarks used in Section~\ref{sub:performance} have been coded to
+demonstrate the power of parallel systems; hence, they have
 been written in a way that simplifies the discovery of parallelism in programs.
@@
 Figure~\ref{fig:TM_Versatility} relates the number of tasks and the number of
-instructions in benchmarks.
+instructions in the 30 largest benchmarks that we analyze.
 To avoid counting multiple C files for the same benchmark,
-Figure~\ref{fig:TM_Versatility} contains only benchmarks that are
-constituted by a single file (present in LLVM's \textsf{SingleSource} folder).
+Figure~\ref{fig:TM_Versatility} contains only benchmarks that
+consists of a single file (present in LLVM's \textsf{SingleSource} folder).
 As this experiment demonstrates, \Taskminer{} {\em can annotate a non-trivial
@@
 runtime to serialize execution of tasks.
-And we have measured speedups above 5\% in 19 benchmarks.
-In one case, \textsf{Misc/lowercase}, the speedup is above 3.5x, and in
-three cases, it goes beyond 1.5x.
+Most of these slowdowns were inferior to 10\%.
+In one case, \textsf{MiBench/office-stringsearch}, our program was 11x slower.
+Nevertheless, we have measured speedups above 5\% in 19 benchmarks.
+In \textsf{Misc/lowercase}, the speedup is above 3.5x, and in
+three cases, it is above 1.5x.
 Figure~\ref{fig:TM_GeneralProgs} summarizes these findings.
-
-\begin{figure}[htb]
+We emphasize that this experiment did not involve any human intervention.
+Hence, {\em \Taskminer{} enables the discovery of parallelism at
+zero programming cost}.
+
+\begin{figure}[t!]
 \begin{center}
 \includegraphics[width=1\columnwidth]{images/TM_GeneralProgs}
-\caption{Speedups obtained by \Taskminer{} when applied onto the LLVM
-test suite.
+\caption{Speedups (in number of times) obtained by \Taskminer{} when applied onto
+the LLVM test suite.
 The larger the bar, the better.

### 2018-04-10 docs/ACM/paper.tex
Fixing the paper in 11 pages.

@@
 \begin{abstract}
-This paper reports the design and implementation of a suit of static analyses
+This paper describes the design and implementation of a suit of static analyses
 and code generation techniques to annotate programs with OpenMP pragmas for
@@
 To fulfil this goal, \Taskminer{} solves different challenges.
-First, it finds program regions, e.g., loops or functions, that can be
+First, it determines symbolic bounds to the memory blocks accessed within
+programs (Section~\ref{sub:sra}).
+Second, it finds program regions, e.g., loops or functions, that can be
 effectively mapped onto tasks (Section~\ref{sub:identification}).
-Second, it determines symbolic bounds to the memory blocks accessed within
-those regions (Section~\ref{sub:sra}).
 Third, it extracts parameters from the code to estimate when it is profitable to
@@
 the time to annotate programs.
+In Section~\ref{sec:eval}, we show that we have been able to achieve almost
+four-fold speedups onto standard benchmarks (not-used in parallel programming),
+with zero programming cost.
 \Taskminer{} receives as input C code, and produces, as output, a C
@@
 Some of these programs, such as those taken from the
-Kastor~\cite{Virouleau14} or Bots~\cite{Duran09}
-benchmark suites, are large and complex; thus, their manual annotation is a
-time consuming and error prone task.
+Kastor~\cite{Virouleau14}, Bots~\cite{Duran09} or the LLVM~\cite{Lattner04} test
+suites, are large and complex.
 Yet, our automatically annotated programs not only approximate the execution
 times of the parallel versions of those benchmarks, but are much faster than
-\guido{Numbers?}
-their sequential --unannotated-- versions, as we report in Section~\ref{sec:eval}.
+their sequential --unannotated-- versions, as we report in
+Section~\ref{sec:eval}.
 
@@
 three cases, it is above 1.5x.
-Figure~\ref{fig:TM_GeneralProgs} summarizes these findings.
+Figure~\ref{fig:TM_GeneralProgs} shows our 10 largest speedups.
 We emphasize that this experiment did not involve any human intervention.
@@
 
-The analyses that we have described in Section~\ref{sec:sol} have a worst-case
-quadratic time.
+The analyses described in Section~\ref{sec:sol} have a worst-case quadratic time.
 This is the worst-case scenario of the symbolic range analysis of
@@
 An implementation of \textsf{clang} supporting tasks was released in March 14th,
-2014\footnote{\url{https://clang-omp.github.io/}}.
+2014.
 A few weeks later, in April 22nd, 2014, such support was also announced in
@@
 
-\pedro{As future work, we plan on performing Autotuning on {\Taskminer} to find good default parameters.
-Autotuning works for data-flow applications have been already done in \cite{Trancoso17, Emani15}}.
+This paper has described a methodology to annotate programs with task
+parallel pragmas, which we could demonstrate to be effective
+on general programs.
+This methodology does not introduce any fundamentally new static analysis or code 
+optimization; in this field, we claim no contribution.
+Instead, our contributions lay into the overall design that eventually
+emerged from a two-years long effort to combine existing compilation techniques
+towards the goal of profiting from the powerful runtime system that OpenMP's
+task parallelism brings forward.
+During this period, we went through many dead-ends; too many, indeed, for a
+11-pages report.
+Nevertheless, this experience lets us single out a few elements from the
+compiler literature, such as symbolic range analysis and windmills, which we
+could use to solve challenges related to automatic code annotation.
+Much work is still left to be done, until we can reach a stage in which
+automatic annotations can beat consistently manual interventions.
+In particular, our methodology asks for more aggressive tuning strategies.
+Techniques such as Trancoso's~\cite{Trancoso17}, Iwasaki's~\cite{Iwasaki16B}
+or Emani's~\cite{Emani15} have already been shown to be effective in this
+domain, and we want to explore them further.
+More specifically, a future release of \Taskminer{} is already expected to
+feature Iwasaki's cut-off~\cite{Iwasaki16B}.
 

### 2018-04-11 docs/ACM/paper.tex
bibtex formatted

@@
 Such fact is unfortunate, since much of the power of current annotation
-systems lays on their ability to create tasks~\cite{Ayguade09}.
+systems lies in their ability to create tasks~\cite{Ayguade09}.
 %\guido{Why the ability to create tasks makes such programs similar to irregular code?
@@
 parallelism in C/C++ programs.
-To fulfil this goal, \Taskminer{} solves different challenges.
+To fulfill this goal, \Taskminer{} solves different challenges.
 First, it determines symbolic bounds to the memory blocks accessed within
@@
 the main benefits of using a runtime environment such as OpenMP's, for
-such advantages have guided most of our designing decisions.
+such advantages have guided most of our design decisions.
 Section~\ref{sub:adv} introduces this discussion.
@@
 Each pointer leads to a string representing a potentially different line.
-Out parallelization of this program consists in firing off a task
+Our parallelization of this program consists in firing off a task
 to process each line.
@@
 The OpenMP execution environment ensures the correct scheduling of the tasks
-created at lines 9 and 11, by assuring that the annotated dependencies
+created at lines 9 and 11, by reassuring that the annotated dependencies
 {\tt line} and {\tt pattern}
@@
 If left unsolved, these challenges would restrict our interventions
-to trivial annotations -- hardly be of any use.
+to trivial annotations, which would hardly be of any use.
 Our first challenge is inherent to any automatic parallelization system.
@@
 We use the runtime value of \textsf{M} to determine, during the execution of the
-program, if we create a task, or not.
+program, if we create a task or not.
 Such test is carried out by the guard at line 7 of the figure, which is part of
@@
 created}"~\cite{Duran08b}.
-This observation is particularly true in the context of recursive, fine-grain,
+This observation is particularly true in the context of recursive, fine-grained
 tasks, as we analyze in Section~\ref{sub:ir}.
@@
 tasks created at line 5 of Figure~\ref{fig:ex_privatize}.
-Because \textsf{j} is written within these tasks, race conditions would
+Because \textsf{j} is written to within these tasks, race conditions would
 ensue.
@@
 The many parts of this algorithm shall be explained throughout this section.
-This pseudo-code uses several concepts well-known in the compiler's
+This pseudo-code uses several concepts well-known in the compilers
 literature, such as control flow graphs~\cite{Kildall73} and
@@
 knowledge to delimit and annotate tasks in structured programs.
-Our presentation focus on the new elements that we had to add onto known
+Our presentation focuses on the new elements that we had to add onto known
 techniques, in order to adapt them to our purposes.
@@
 partitioned in {\em hammock regions}, a concept introduced by Ferrante
-{\em et al.}~\cite{Ferrante87} in the middle 80's.
+{\em et al.}~\cite{Ferrante87} in the middle 1980's.
 For completeness, we re-state it in Definition~\ref{def:hammock}.
@@
 Syntactically, memory regions are described by program variables and/or pointers
-plus ranges of dereferensable offsets.
+plus ranges of dereferenceable offsets.
 Given two tasks: $T_1 = (G_1, M_{i1}, M_{o1})$ and $T_2 = (G_2, M_{i2}, M_{o2})$,
@@
 \item the execution of the tasks in $T$ in any ordering determined by dependence
-relations, leads to the same results as the sequential execution of $P$.
+relations leads to the same results as the sequential execution of $P$.
 \end{compactenum}
@@
 semantics.
-Full overviews of the syntax and semantics of these annotations is publicly
+Full overviews of the syntax and semantics of these annotations are publicly
 available\footnote{For a quick overview, we refer the reader to the leaflet
@@
 \item \textsf{single} (\textit{clauses}): specifies that a
-program region must be executed by one thread in the team.
+program region must be executed by a single thread in the team.
 \item \textsf{task} (\textit{clauses}): creates a new task.
@@
 The program symbols mentioned in Definition~\ref{def:sra} are names that cannot 
-be reconstruct as functions of other names.
+be reconstructed as functions of other names.
 Examples include global variables, function arguments, and values returned by
@@
 reuses work from Blume {\em et al.}~\cite{Blume94}.
-The only extensions that we have added into \dawn's implementation was
+The only extensions that we have added into \dawn 's implementation was
 the ability to handle C-like \textsf{structs}.
@@
 \label{ex:sra}
-Symbolic range analysis, when applied onto Figure~\ref{fig:ex_Regions}, gives us
+Symbolic range analysis, when applied onto Figure~\ref{fig:ex_Regions}, give us
 $R(\mathsf{i}) = [0, \mathsf{N} - 1]$, and $R(\mathsf{j}) = [0, \mathsf{M} - 1]$.
@@
 Windmills gives us structural properties to identify tasks.
-We can find them via a depth-search traversal of the program's dependence
+We can find them via a depth-first search traversal of the program's dependence
 graph.
@@
 search.
-However, not every windmill lead us to profitable tasks.
+However, not every windmill leads us to profitable tasks.
 Furthermore, some windmills cannot be annotated, due to the inability of
@@
 % Explain the tension between large and small tasks.
-The benefit of creating tasks depend on two factors:
+The benefit of creating tasks depends on two factors:
 runtime cost, and parallelism.
@@
 represent the number of iterations of loops.
-Similar approach has already been used to decide when to migrate virtual memory
+A similar approach has already been used to decide when to migrate virtual memory
 pages in NUMA architectures~\cite{Piccoli14}.
@@
 by the cost model seen in Section~\ref{sub:profit}.
-If the profitability of a task is less than this constant, then parallelism
+If the profitability of a task is smaller than this constant, then parallelism
 might not pay off the cost of managing threads.
@@
 
-\Taskminer{} bestow a parallel semantics on code that has been originally
+\Taskminer{} bestows a parallel semantics on code that has been originally
 conceived to run sequentially.
@@
 of several data-flow analyses already in place in the LLVM infra-structure.
-In particular, this decision lets us reuse LLVM's scalar
+In particular, this decision let us reuse LLVM's scalar
 evolution~\cite[p.18]{Grosser12}, from which we derive our symbolic analysis.
@@
 Visual inspection of \textsf{bellmanford} shows that the version parallelized
-manually is dispatching an large number of small tasks.
+manually is dispatching a large number of small tasks.
 Our cost model can prune some of these small tasks, but not enough to win
@@
 some of the manually annotated samples.
-Nevertheless, this experiment lets demonstrate that {\em \Taskminer{} can
+Nevertheless, this experiment demonstrates that {\em \Taskminer{} can
 deliver non-negligible speedups comparable with sequential and manually
@@
 to run in parallel, they are not fully automatic.
-For instance, the work that is the closest of ours, in reach and effectiveness,
+For instance, the work that is the closest to ours, in reach and effectiveness,
 in our opinion, is the suite of techniques proposed by Ravishankar {\em et

### 2018-04-11 docs/ACM/paper.tex
Adding Gabriel's suggestions to paper.

@@
 annotation.
-Furthermore, our techniques give us the means to discover, without any 
-development cost, opportunities of parallelism that remained buried in the syntax 
-of well-known benchmarks for many years.
+Furthermore, our techniques give us the means to discover opportunities of
+parallelism that remained buried in the syntax  of well-known benchmarks for many
+years -- sometimes leading to up to four-fold speedups on a 12-core machine at
+zero programming cost.
 \end{abstract}
@@
 Yet, our automatically annotated programs not only approximate the execution
-times of the parallel versions of those benchmarks, but are much faster than
-their sequential --unannotated-- versions, as we report in
+times of the parallel versions of those benchmarks, but are in general faster
+than their sequential --unannotated-- versions, as we report in
 Section~\ref{sec:eval}.
@@
 \caption{Examples of program dependence graphs.
-Nodes that form centers of windmills are coloured in gray.
+Nodes that form centers of windmills are colored in gray.
 Data-dependence edges are solid; control-dependence edges are dashed.
@@
 (a) PDG for Figure~\ref{fig:ex_book_filter};
-(b) PDG for Figure~\ref{fig:ex_Regions}}
+(b) PDG for Figure~\ref{fig:ex_Regions}.}
 \label{fig:ex_windmill}
@@
 \inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
-{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + \mbox{max}(w_2 + w_3)}
+{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + \mbox{max}(w_2, w_3)}
 \\\\
@@
 invocation.
-The parameter \textsf{DEPTH\_CUTOFF} is determined by \Taskminer's users.
+The parameter \textsf{DEPTH\_ CUTOFF} is determined by \Taskminer's users.
 \end{example}
@@
 Each dot represents one of the 100 program generated by \textsf{CSmit}.
-We have fit a degree-2 polynomial on this dataset.}
+We have fit a degree-2 polynomial on this dataset.
+We cannot control the size of programs produced by CSmith; hence, it is
+difficult to push the limit above 5,000 LoC.}
 \label{fig:TM_Runtime}
@@
 \textsf{gcc} 4.9.
-Thus, because the necessary infra-structure for the implementation of tasks is
-relatively new, currently there are no tools, other than the \Taskminer,
-that annotate programs automatically with these directives.
-Nevertheless, there exists a long string of research aiming at the automatic
+Because the necessary infra-structure for the implementation of tasks is
+new, currently there are no tools, other than \Taskminer,
+that annotate programs with these directives.
+Nevertheless, there exist much research aiming at the automatic
 parallelization of programs.
-In this section, we examine some elements in this list that relate to our
+This section examines elements in this list related to our
 work.
@@
 StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
-tejedor:hpdc:2011} and OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}  which have
-been extensively used to task-parallelize applications. Such
-programming models come with tools that help programmers find the
+tejedor:hpdc:2011} and OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}.
+Such programming models come with tools that help programmers to find the
 best annotations for their code. For example,  Tareador

### 2018-04-11 docs/ACM/paper.tex
Adding subject descriptors.

@@
 <concept>
+<concept_id>10010147.10010169.10010175</concept_id>
+<concept_desc>Computing methodologies~Parallel programming languages</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10010147.10011777.10011014</concept_id>
+<concept_desc>Computing methodologies~Concurrent programming languages</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
 <concept_id>10011007.10011006.10011041</concept_id>
@@
 </concept>
-<concept>
-<concept_id>10011007.10011006.10011008.10011024.10011035</concept_id>
-<concept_desc>Software and its engineering~Procedures, functions and subroutines</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10003752.10003766.10003776</concept_id>
-<concept_desc>Theory of computation~Regular languages</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10003752.10010124.10010131.10010134</concept_id>
-<concept_desc>Theory of computation~Operational semantics</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
 </ccs2012>
@@
 
+\ccsdesc[500]{Computing methodologies~Parallel programming languages}
+\ccsdesc[500]{Computing methodologies~Concurrent programming languages}
 \ccsdesc[500]{Software and its engineering~Compilers}
-\ccsdesc[300]{Software and its engineering~Procedures, functions and subroutines}
-\ccsdesc[300]{Theory of computation~Regular languages}
-\ccsdesc[300]{Theory of computation~Operational semantics}
 
@@
 Figure~\ref{fig:TM_Performance} compares the runtime of programs produced by
-\Taskminer{} against either the original program (the baseline,
-compiled with \textsf{clang} -O3)
+\Taskminer{} against either the original program
 or versions of said programs annotated manually.
@@
 annotated) versions.
+Baseline and annotated sources are compiled with gcc-6.
 
@@
 the LLVM test suite, and have compared the annotated version
-against the sequential version compiled with \textsf{clang} -O3.
+against the sequential version compiled.
 \Taskminer{} annotates a benchmark if it can find symbolic bounds to every

### 2018-04-14 docs/ACM/paper.tex

@@
 OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
-Tareador~\cite{Ayguade15}.
+OmpSs~\cite{bueno:icpp:2011, duran:ppl:2011}.
 Annotations work as a meta-language: they let developers grant parallel
@@
 OpenMP 4.0 contains syntax to enable the conditional creation of tasks.
-Our symbolic analysis lets us build predicates for such conditional expressions.
+Our symbolic analysis lets us build predicates for such conditionals.
 
@@
 % Explain how we use symbolic information to compute costs.
-The declarative rules in Figure~\ref{fig:swe} sketches the heuristics that
-we use to compute the SWE for a given hammock region $S$.
+The declarative rules in Figure~\ref{fig:swe} sketch the heuristics that
+we use to compute the SWE for a hammock region $S$.
 Rule \textsc{LoopInf} applies on loops whose number of iterations we cannot bound
 via some symbolic expression computed statically.
+We assume that loops execute 10 times, following previous
+statistics~\cite{Wu94}.
 Rule \textsc{LoopExp} represents loops that we can analyze using our Symbolic
@@
 collection of constants related to the creation of threads in our target
-architecture, including the value of \textsf{WORK\_CUTOFF}, seen in
-Example~\ref{ex:cond_task}.
+architecture.
+As an example, the value of \textsf{WORK\_CUTOFF}, seen in
+Example~\ref{ex:cond_task}, in our setting, is roughly 500 cycles.
 
@@
 against the sequential version compiled.
-\Taskminer{} annotates a benchmark if it can find symbolic bounds to every
-memory access (load or store) used within a region marked as a task candidate.
-Under this constraint, we have been able to discover tasks in 63 benchmarks.
+\Taskminer{} annotates a benchmark if:
+(i) it can find symbolic bounds to every
+memory access used in a vane; and
+(ii) the vane is large enough to pay for the cost of creating threads.
+Under these constraints, we have discovered tasks in 63 benchmarks.
 Figure~\ref{fig:TM_Versatility} relates the number of tasks and the number of
-instructions in the 30 largest benchmarks that we analyze.
+instructions in the 30 largest benchmarks that we have used.
 To avoid counting multiple C files for the same benchmark,

### 2018-05-14 docs/SBLP/paper.tex
Added SBLP paper

%% For double-blind review submission
\documentclass[sigplan,10pt,review]{acmart}
\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

\makeatletter\if@ACM@journal\makeatother

%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother

%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[PL'17]{IEEE}{2018}{Planet Earh}
\acmYear{2017}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

\newcommand{\fer}[1]{\textcolor{red}{#1}}

%% For review submission
\setcopyright{none}

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%\citestyle{acmauthoryear}

%% Packages that we are using in this version of the work:
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{paralist}
\usepackage[brazil]{babel}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}

% To turn comments OFF simply comment out the \Commentstrue line
\newif\ifComments\Commentstrue

\ifComments
\newcommand{\marcio}[1]{\noindent\textcolor{violet}{Marcio: {#1}}}
\newcommand{\guido}[1]{\noindent\textcolor{magenta}{Guido: {#1}}}
\newcommand{\fernando}[1]{\noindent\textcolor{brown}{Fernando: {#1}}}
\newcommand{\cesar}[1]{\noindent\textcolor{magenta}{Cesar: {#1}}}
\newcommand{\pedro}[1]{\noindent\textcolor{brown}{Pedro: {#1}}}
\newcommand{\rmv}[1]{\noindent\textcolor{gray}{Removed: {#1}}}
\newcommand{\new}[1]{\noindent\textcolor{blue}{ {#1}}}
\newcommand{\ed}[1]{\noindent\textcolor{red}{ {#1}}}
\else
\newcommand{\marcio}[1]{}
\newcommand{\guido}[1]{}
\newcommand{\fernando}[1]{}
\newcommand{\cesar}[1]{}
\newcommand{\pedro}[1]{}
\newcommand{\rmv}[1]{}
\newcommand{\new}[1]{#1}
\newcommand{\ed}[1]{}
\fi
\newcommand\dawn{\mbox{\textsf{DawnCC}}}
\newcommand\Taskminer{\mbox{\textsf{TaskMiner}}}

\newtheorem{Challenge}{Challenge}[section]

\begin{document}

\title[Automatic Identification and Annotation of Tasks in Structured
Programs]
{TaskMiner: Identificação Automática de Tarefas}

\author{Pedro Henrique Ramos Costa}
\authornote{with author1 note}          %% \authornote is optional;
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Researcher}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{pedroramos@dcc.ufmg.br}

\author{Gleison Souza Diniz Mendonc\c{c}a}
\authornote{with author1 note}          %% \authornote is optional;
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Researcher}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{gleison.mendonca@dcc.ufmg.br}

\author{Guilherme Mendes Leobas}
\authornote{with author1 note}          %% \authornote is optional;
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Researcher}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{guihermel@dcc.ufmg.br}

\author{Fernando M Q Pereira}
\authornote{with author1 note}
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Professor}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{fernando@dcc.ufmg.br}          %% \email is recommended

\begin{abstract}
Este artigo apresenta \Taskminer{}, uma ferramenta capaz de encontrar paralelismo de tarefas
em código C automaticamente. \Taskminer{} lida com problemas clássicos de paralelismo irregular como
encontrar os limites simbólicos de acesso à memória em tempo de execução, remoção de dependências
estáticas espúrias, contornar condições de corrida ao transformar código sequencial em código paralelo, e
principalmente, encontrar o equilíbrio entre tamanho de uma tarefa e excesso de paralelismo, em contraste com
o custo de manutenção de tarefas pelo ambiente de execução. Para contornar esses problemas,
\Taskminer{} implementa uma série de otimizações e análises em representação intermediária do LLVM, resultando
em um compilador fonte-a-fonte capaz de analisar código C e inserir no mesmo anotações OpenMP automaticamente. \Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente, além de encontrar paralelismo escondido em programas sequenciais, absolutamente sem intervenção humana.
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010169.10010175</concept_id>
<concept_desc>Computing methodologies~Parallel programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10011777.10011014</concept_id>
<concept_desc>Computing methodologies~Concurrent programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011041</concept_id>
<concept_desc>Software and its engineering~Compilers</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Parallel programming languages}
\ccsdesc[500]{Computing methodologies~Concurrent programming languages}
\ccsdesc[500]{Software and its engineering~Compilers}

\keywords{Parallelism, Tasks, OpenMP}

\maketitle

\section{Introdu\c{c}\~{a}o}
\label{sec:intro}

É inegável que computação paralela e distribuída é hoje a alternativa mais procurada por 
desenvolvedores em sua busca por desempenho. Programadores tem cada vez mais investido
em paradigmas paralelos, visando maior eficiência e velocidade. Nesse contexto, sistemas de
anotação como OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} e
OmpSs~\cite{bueno:icpp:2011, duran:ppl:2011}
atuam como metalinguagem, conferindo ao programador
poder semântico para transformar um programa originalmente sequencial
em um programa paralelo. Tais sistemas mostram-se muito promissores quando
combinados com aceleradores como GPUs e FPGAs~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Antao16,Wienke12}.
Entretanto, apesar de conveniente, o uso desses sistemas não é automático e
requer exaustiva escrutinação de olho humano para garantia de corretude e eficiência.

Embora já existam ferramentas que inserem anotações automaticamente 
em programas~\cite{Amini12,Guelton12,Mendonca16,Pingali11,Nugteren14},
todas essas tecnologias exploram somente paralelismo de dados.  Porém, grande
parte do poder de sistemas de anotação provém da capacidade de se criar \textit{tarefas}
durante a execução do programa~\cite{Ayguade09}. Dessa forma, o propósito desse trabalho
é apresentar um algoritmo capaz de minerar oportunidades para paralelismo de tarefas
em programas sequênciais e anotá-los automaticamente. Como descrito na seção \ref{sec:ovf},
essas anotações conferem ao programa irregular semântica de algoritmos em grafos e/ou \textit{worklists}~\cite{Ben-Nun17,Kulkarni11,Pingali11}.

O presente artigo descreve {\Taskminer}, um compilador fonte-a-fonte que expõe
paralelismo de tarefas em programas C/C++. {\Taskminer} lida com diversos desafios 
do universo do paralelismo irregular. Primeiro, deve-se determinar os limites
simbólicos dos blocos de memória acessados dentro de cada programa. Depois,
encontra-se regiões ou fragmentos de código (laços ou funções) que podem 
ser efetivamente mapeados à tarefas. Então, deve-se extrair parâmetros capazes
de estimar o custo da tarefa em questão. Esses parâmetros estão dinamicamente atrelados
às anotações e são capazes de ativar ou desativar a criação de tarefas durante a execução do programa,
ou de limitar a profundidade de tarefas geradas recursivamente. Após feito isso, deve-se determinar
quais variáveis serão privatizadas em novas tarefas, ou compartilhadas por tarefas concorrentes.
Finalmente, deve-se mapear todas essas informações de volta ao código fonte, produzindo
anotações legíveis.

Este trabalho defende a tese de que a anotação automática de tarefas é útil à medida que
retira do programador o fardo de procurar, anotar e verificar as anotações, tornando seu
processo de desenvolvimento mais eficiente. A ferramenta {\Taskminer} é capaz
de alcançar ganhos de quase 4x em benchmarks não usualmente paralelos, como descrito em \ref{sec:eval}. {\Taskminer}
recebe como input um programa escrito em C e produz como output um programa também em C,
mas anotado com diretivas OpenMP legíveis. {\Taskminer} anota programas não triviais, envolvendo
todo tipo de construto da linguagem C como arranjos, estruturas, uniões e ponteiros para esses tipos.
Alguns desses programas provém de benchmarks complexos como Kastor~\cite{Virouleau14}, Bots~\cite{Duran09}  e a suíte de testes do LLVM~\cite{Lattner04}.
As versões anotadas pelo {\Taskminer} se aproximam das versões anotadas manualmente em
desempenho, e são mais rápidos que as versões sequenciais.

\section{Visão geral}
\label{sec:ovf}

A construção de um compilador como o \Taskminer{} envolve a superação de uma série de etapas e desafios.
\Taskminer{} recebe como entrada um programa escrito em C e retorna o mesmo programa anotado com 
diretivas OpenMP. Como descrito por LaGrone et al. ~\cite{LaGrone11}, 
o ambiente de execução OpenMP se encarrega de 
rastrear dependências entre ponteiros estaticamente. Entretanto, a inserção
automática das anotações é apenas a última etapa. Nesta Seção detalharemos os desafios e problemas
encontrados pelo \Taskminer{} no processo de mineração de tarefas. A solução para esses problemas será descrita 
posteriormente na Seção~\ref{sec:sol}.

\begin{figure}[b!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/ex_Regions}
\caption{Identificando limites de memória e o custo de uma tarefa.}
\label{fig:ex_Regions}
\end{center}
\end{figure}

O primeiro desafio encontrado pelo \Taskminer{} consiste em 
identificar regiões de memória cobertas por uma tarefa.
A Figura~\ref{fig:ex_Regions} ilustra esse problema e como resolvê-lo. Este programa recebe
uma matriz $\mathsf{M}\times\mathsf{N}$ identificada por  \textsf{V}, em formato linear,
e produz um vetor  \textsf{U} de forma que  \textsf{U[i]} contenha a soma de todos
os elementos na linha  \textsf{i} da matriz  \textsf{V}. {\Taskminer} determina que cada
iteração do laço mais externo pode se tornar uma tarefa. Então, cada tarefa neste programa
consiste no laço mais interno, e atravessa a região de memória entre os endereços  \textsf{\&V + i * N} e
 \textsf{\&V + i * N + M}. A identificação desses limites envolve o uso de álgebra simbólica baseada
 na literatura de compiladores.

A Figura~\ref{fig:ex_Regions} também apresenta um outro problema: {\em como estimar a rentabilidade de uma tarefa?}
A criação de tarefas envolve um custo alto por parte do ambiente de execução, causado por questões como
alocação, escalonamento, concorrência e gerenciamento em tempo real do grafo de dependências de tarefas.
Idealmente, são desejáveis tarefas que executem uma quantidade de trabalho
grande o suficiente para superar este custo. Como consta em \cite{Rice53}, a quantidade de trabalho executado
por uma tarefa não pode ser descoberta estaticamente. É possível aproximar-se dessa quantia utilizando-se
símbolos nativos do programa, que, em execução, serão substituídos por valores. 
Por exemplo, na figura~\ref{fig:ex_Regions}
é conhecido o número de instruções do laço interno. Então aproxima-se a quantidade de trabalho executado
com a expressão \textsf{5 * M}. Dessa forma, o valor de \textsf{M} durante a execução será determinante para
a criação da tarefa. Essa checagem é feita na linha 7 da Figura, 
e faz parte da sintaxe de OpenMP. Além disso, {\Taskminer} propõe
uma estimativa confiável a respeito do limite mínimo de custo 
que uma tarefa deve possuir para ser criada sem produzir
excesso de computação. Esse limite considera fatores como número de 
núcleos disponíveis e informações a respeito do ambiente
de execução em termos de instruções de máquina.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/ex_cutoff}
\caption{limitando a criação de tarefas recursivas.
Exemplo retirado de~\cite[Fig.1]{Iwasaki16}.}
\label{fig:ex_cutoff}
\end{center}
\end{figure}

No paralelismo de tarefas, um fator importante para bom desempenho
é o uso de cortes mínimos para o número de tarefas a serem criadas~\cite{Duran08b}. 
Observa-se esse fator explicitamente no contexto de tarefas recursivas. 
Para limitar a criação de tais tarefas, que tem uma granularidade menor,
uma variável de controle é inserida no código. 
Um exemplo é ilustrado na Figura~\ref{fig:ex_cutoff}. 
Um contador é associado à invocação de funções recursivas anotadas com diretiva de tarefas. 
A checagem na linha 7 certifica-se de que o limite
nunca é excedido. Esse limite é pré-determinado na fase de configuração do 
{\Taskminer}, assim como o limite de trabalho mínimo
por tarefa. Dessa forma, observa-se que a geração 
de código executada pelo {\Taskminer} é dependente de dois parâmetros,
\textsf{DEPTH\_CUTOFF} e \textsf{WORK\_CUTOFF}. 
Eles possuem valores por padrão, mas podem ser configurados pelo usuário.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/ex_privatize}
\caption{A variável \textsf{j} deve ser replicada em todas as tarefas para evitar condições de corrida.}
\label{fig:ex_privatize}
\end{center}
\end{figure}

Por fim,  um último problema surge ao transformar um programa originalmente
sequencial em um programa paralelo. Condições de corrida evidenciam
quais variáveis devem ser replicadas e
quais podem ser compartilhadas pelas tarefas. 
Assim como o problema de determinar os limites de acesso à memória, 
se não resolvido, esse problema pode levar à programas incorretos.
Esse processo de replicação de variáveis em todas as tarefas criadas se chama \textit{privatização}. 
Na Figura~\ref{fig:ex_privatize}, por exemplo,
a variávei \textsf{j} deve ser privatizada. 
Caso não seja, ela será compartilhada por todas as tarefas 
criadas na linha 5 da Figura~\ref{fig:ex_privatize}. 
{\Taskminer} utiliza uma técnica descrita na seção~\ref{sec:sol} 
para resolver esse problema.

\section{Solu\c{c}\~{a}o}
\label{sec:sol}

\begin{figure}[b]
\begin{center}
\includegraphics[width=1\columnwidth]{images/alg_main}
\caption{Os principais passos do algoritmo do TaskMiner.}
\label{fig:alg_main}
\end{center}
\end{figure}

A figura~\ref{fig:alg_main} descreve o algoritmo executado pela ferramenta {\Taskminer}. Ele utiliza conceitos conhecidos como
o grafo de dependências~\cite{Ferrante87} e o grafo de fluxo de controle~\cite{Kildall73}. O objetivo principal do {\Taskminer}
é identificar tarefas em programas estruturados. Programas estruturados podem ser particionados em regiões \textit{hammock}
\cite{Ferrante87}.

\begin{definition} [Região \textit{Hammock}]
\label{def:hammock}
Um grafo de fluxo de controle $G$ é um grafo direcionado com um nó de entrada
$s$ e um nó de saída $x$. Uma região \textit{hammock} $G'$ é um subgrafo de $G$ com um nó $h$ que {em domina}
\footnote{Um nó $n_1 \in G$ domina outro nó
$n_2 \in G$ de todo caminho de  $S$ até $n_2$ atravessa $n_1$.
Inversamente, $n_1$ pós-domina $n_2$ se todo caminho de $n_2$ até $x$ deve passar por $n_1$.} os outros nós em $G$.
Além disso, existe um nó $w \in G$, $w \notin G'$, tal que $w$ {\em pós-domina} todo nó em $G'$. Nessa definição,
$h$ é o nó de entrada e $w$ é o nó de saída de $G'$.  
\end{definition}

\begin{definition} [Tarefa]
\label{def:task}
Dado um programa $P$, uma tarefa $T$ é uma tupla $(G', M_i, M_o)$ formada
por uma região \textit{hammock} $G'$ e um conjunto $M_i$ de dependências de memória representando
os dados lidos por $T$ e um conjunto $M_o$ de regiões de memória que representam dados escritos por $T$.
\end{definition}

Sintaticamente, regiões de memória são descritas por variáveis do programa e/ou ponteiros com intervalos derefenciáveis.
Dadas duas tarefas $T_1 = (G_1, M_{i1}, M_{o1})$ e $T_2 = (G_2, M_{i2}, M_{o2})$, 
se $M_{o1} \cap M_{i2} \neq \emptyset$ então $T_2$ {\em depende} de $T_1$. Se um programa $P$ está particionado em um 
conjunto de $n$ tarefas, então ele deve respeitar a Definição \ref{def:corretude} para ser considerado correto:

\begin{definition} [Corretude]
\label{def:corretude}
Um conjunto $T$ de $n$ tarefas é uma paralelização correta de um programa $P$ se:
\begin{compactenum}
\item $T$ não contém dependências cíclicas;
\item A execução das tarefas em $T$ em qualquer ordem determinada pelas relações de dependência devem resultar
identicamente à execução sequencial de $P$.
\end{compactenum}
\end{definition}

Abaixo há um exemplo de como as regiões de memória são marcadas em uma anotação de tarefa.
Considere-se duas tarefas $T_{\mathit{foo}} = (\mathsf{foo}, \{\mathsf{v[i - 1]}\},
\{v[i]\})$ e $T_{\mathit{bar}} = (\mathsf{bar}, \{v[i]\}, \{\})$. Dependências são identificadas na cláusula \textit{depend}. 
Nesse exemplo, cada região \textit{hammock} é constituída por uma chamada de função:

\includegraphics[width=1\columnwidth]{images/ex_depends}

{\Taskminer} utiliza OpenMP 4.0 para explorar o paralelismo de tarefas. Detalhes da sintaxe e semântica
das anotações do OpenMP estão publicamente disponíveis\footnote{``Summary of OpenMP 4.0 C/C++ Syntax", disponibilizado
pelo grupo OpenMP}. As anotações utilizadas são:
%
\begin{compactitem}
\item \textsf{parallel}: compõe um time de \textit{threads}
para executar uma região do programa marcada como paralela.
\item \textsf{single}: especifica uma região que deve ser executada
por apenas uma \textit{thread} do time.
\item \textsf{task}: cria uma nova tarefa.
\item \textsf{taskwait}: define um ponto de sincronização para aquela
região paralela.
\end{compactitem}
%
Algumas dessas anotações são associadas a uma lista de cláusulas, a seguir:
\begin{compactitem}
\item \textsf{default([shared/private])}: indica que a variável é compartilhada ou replicada
entre tarefas.
\item \textsf{firstprivate($v$)}: indica que $v$ deve ser replicada entre tarefas e inicializada
com o valor corrente no ponto de execução da anotação.
\item \textsf{untied}: indica que uma tarefa não está associada firmemente à uma única \textit{thread},
permitindo ao ambiente balancemanto e preempção.
\item \textsf{depend}($\mathit{in}/\mathit{out}/\mathit{inout}$): determina se um dado é lido, escrito
ou ambos, efetivamente estabelecendo as dependências entre as tarefas.
\item \textsf{if}({\em condição}): define uma condição para que aquela anotação seja executada.
\end{compactitem}

\subsection{Encontrando limites simbólicos}
\label{sec:sra}

Para produzir uma anotação que criará uma tarefa $T = (G, M_i, M_o)$,
é necessário determinar as regiões de memória $M_i$ que $T$ lê, e as regiões
$M_o$ em que $T$ escreve. Para tal, recorre-se à análise de limites simbólicos.

 Por exemplo, a instrução \textsf{U[i] += V[i*N + j]}, na linha 9 da Figura~\ref{fig:ex_Regions}
 contém dois acessos à memória: \textsf{U[i]} e
\textsf{V[i*N + j]}.
 O primeiro cobre a região de memória $[\mathtt{\&}\mathsf{U},
\mathtt{\&}\mathsf{U} + (\mathsf{M} - 1) \times \mathsf{sizeof}(\mathtt{int})]$.
O segundo cobre a região 
$[\mathtt{\&}\mathsf{V} + \mathsf{N} \times \mathsf{sizeof}(\mathtt{int}), \mathtt{\&}\mathsf{V} + ((\mathsf{i} \times \mathsf{M} + j) - 1) \times \mathsf{sizeof}(\mathtt{int})]$.
Não há código na Figura~\ref{fig:ex_Regions} que dependa do laço nas linhas 8-10.
Portanto, uma anotação de tarefa deve considerar apenas a dependência de entrada, ou seja,
o acesso à \textsf{V}. É por isso que a cláusula \textsf{depend} na linha 6 contém uma referência
a essa região.

\begin{definition} [Análise de Limites Simbólicos]
\label{def:limites}
É uma forma abstrata de interpretação que associa uma variável inteira $v$
a um intervalo simbólico $R(v) = [l, u]$ em que $l$ e $u$ são expressões simbólicas.
Uma expressão simbólica $E$ é definida pela gramática abaixo, em que $s$ é um 
símbolo do programa:
\renewcommand{\arraystretch}{0.9}
\[
\begin{array}{rcl}
E & ::= & z \ \ | \ \ s \ \ | E + E \ \ | \ \ E \times E \ \ | \ \  \mbox{min}(E, E) \ \ | \\
&  & \mbox{max}(E, E) \ \ | -\infty \ \ | \ \ +\infty
\end{array}
\]
\end{definition}

Símbolos de programa são nomes que não podem ser construídos como funções de
outros nomes. Exemplos incluem variáveis globais, argumentos de função e valores retornados
por funções externas. Análise de limtes simbólicos não é uma contribuição deste artigo. A técnica
escolhida para as análises do {\Taskminer} é aquela implementada no compilador \dawn{} \cite{Mendonca17},
que, por sua vez, reusa trabalho de Blume {\em et al.}~\cite{Blume94}. Para este trabalho, é apenas
suficiente saber que essa implementação é sólida o suficiente para lidar com toda a linguagem C99, sempre termina
e executa em tempo quadrático no número de variáveis do programa, no pior caso.

Por exemplo, se aplicada à Figura~\ref{fig:ex_Regions}, a análise de limites resulta em 
$R(\mathsf{i}) = [0, \mathsf{N} - 1]$, e $R(\mathsf{j}) = [0, \mathsf{M} - 1]$.
O acesso à memória \textsf{V[i*N + j]} na linha 9, combinado a essa informação, fornece
a região simbólica que aparece na anotação da linha 6 na Figura~\ref{fig:ex_Regions}.

\subsection{Mapeando regiões em tarefas}
\label{sub:identification}

% Windmills and vanes
Uma {\em tarefa candidata} é um conjunto de instruções que podem executar paralelamente.
Para identificá-las, {\Taskminer} faz uso do {\em Grafo de Dependências}.

\begin{definition} [Grafo de Dependências]~\cite{Ferrante87}
\label{def:pdg}
Dado um programa
$P$, seu PDG contém um vértice para cada instrução $s \in P$. Existe uma aresta de 
$s_1$ a $s_2$ se o último depende do primeiro. $s_2$ tem uma dependência de dados de $s_1$
se lê dados que $s_1$ escreve. $s_2$ tem uma dependência de controle de $s_1$ se $s_1$ controla
a execução de $s_2$ a partir do resultado de um \textit{branch}, por exemplo.
\end{definition}

Tarefas candidatas são \textbf{hélices em moinhos}. {\em Moinhos} são uma família de grafos ~\ref{Rideau08}.
Moinhos existem como subgrafos do grafo de dependências.

\begin{definition} [Moinho]
\label{def:moinho}
Um moinho é um grafo $G_w = G_c \cup G_{v1} \cup \ldots \cup G_{vn}$
formado por componentes fortemente conexos $G_c$ (centro do Moinho) e $n$ componentes, não necessariamente
fortes, $G_{vi}$ chamados de hélices, tais que:
\begin{compactenum}
\item para qualquer ordenação topológica de $G_w$, e os nós $n_c \in G_c$,
$n_v \in G_{vi}$, $n_c$ está à frente de $n_v$;
\item para qualquer $i$ e $j$, $1 \leq i < j \leq n$, $G_{vi}$ e $G_{vj}$ não
compartilham vértices (portanto, compartilhar arestas também é impossível).
\end{compactenum}
\end{definition}

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth]{images/ex_windmill}
\caption{Exemplos de grafos de dependências. Nós que formam centros de moinhos
são coloridos de cinza. Arestas sólidas representam dependências de dados; arestas pontilhadas
dependências de controle. Hélices de moinhos aparecem dentro de retângulos pontilhados.
Na imagem, vemos o grafo para a Figura~\ref{fig:ex_Regions} em (b).}
\label{fig:ex_windmill}
\end{center}
\end{figure}

A Figura ~\ref{fig:ex_windmill} mostra dois grafos de dependências, bem como seus
moinhos e hélices. A estrutura de moinhos naturalmente evidencia tarefas candidatas.
Hélices correspondem à partes do programa que tem alta probabilidade de serem
executadas diversas vezes, pois surgem de um laço: o centro do moinho. Duas execuções
de uma mesma hélice podem ser paralelas. Esta é uma propriedade do grafo de dependências, e uma 
das motivações originais para este trabalho. Essas duas execuções podem ser vistas como duas instâncias
da mesma estrutura: a hélice, partindo do mesmo centro do moinho. Uma ordenação topológica desse grafo não impõe
nenhuma ordem entre essas duas hipotéticas réplicas de uma mesma hélice.

Moinhos contém propriedades estruturais para identificação de tarefas. Moinhos são encontrados
em uma simples busca em profundidade no grafo de dependências. Entretanto, nem todo moinho
evidencia tarefas proveitosas. Além disso, alguns moinhos não podem ser anotados devido à inabiliadde 
da análise de ponteiros em encontrar limites de acesso à memória. As próximas seções tratam desses
problemas.

\subsection{Estimando a lucratividade de tarefas}
\label{sub:profit}

O benefício de criar tarefas depende de dois fatores: custo de execução e paralelismo.
A dificuldade surge em encontrar o ponto mediano entre tarefas grandes demais e tarefas pequenas.
Tarefas muito pequenas tendem a ser mais paralelas, pois tendem a ter menos dependências. Entretanto,
se uma tarefa é muito pequena, então os ganhos de performance são eclipsados pelo custo do ambiente de execução
em manter essa tarefa ativa, e o paralelismo extra não compensa o custo de gerenciamento desta tarefa.
Por outro lado, se tarefas são muito grandes, então não há paralelismo: tarefas individuais executarão sequencialmente.
{\Taskminer} marca como tarefa aquelas hélices que são maximais em termos de custo de execução, ou seja, as menores hélices
que estão acima do custo de execução no ambiente escolhido.

O tamanho de uma tarefa é dado pelo número de instruções contidas na mesma. A mesma região de um programa
pode levar à criação de tarefas com tamanhos diferentes. Portanto, o tamanho real de uma tarefa só é conhecido ao final 
da execução da mesma. Entretanto, para julgar se acriação de uma tarefa vale a pena, é necessário aproximar esse tamanho
estaticamente. Com esse objetivo em mente, define-se a noção de {\em Trabalho Estatico Estimado}:

% Explain the tension between large and small tasks.
\begin{definition}[Trabalho Estático Estimado (TEE)]
\label{def:swe}
Seja $G = G_1 \cup G_2 \cup \ldots \cup G_n$ uma partição de um grafo de controle
de um $G$ em $n$ regiões hammock {\em disjuntas}.
Trabalho Estático Estimado ($W(G)$) é definido como um número real não negativo,
tal que $W(G) = W(G_1) + W(G_2) + \ldots + W(G_n)$.
\end{definition}

O objetivo é obter um $W$ próximo ao comportamento dinâmico dos programas.
A heurística mais conhecida na literatura para a proximação de $W$ é o 
\textit{profiler} estático implementado por Wu e Larus~\cite{Wu94}.
A heurística escolhida para este trabalho utiliza a análise de limites
descrita na Seção \ref{sub:sra} para inserir informações dinâmicas em ambiente estático,
através da construção de expressões simbólicas que representam o número de iterações
de laços, similar à técnica implantada para migração de memória virtual em arquiteturas NUMA
\cite{Piccoli14}. Essas expressões são inseridas em condicionais para a criação da
tarefa, como ilustrado na linha 7 da Figura \ref{fig:ex_Regions}.

\begin{figure}[t!]
\begin{small}
\begin{eqnarray*}
\begin{tabular}{lc}
\textsc{[Instr]} &
W(\mbox{instr}) = \mbox{given by the spec.}
\\\\
\textsc{[Seq]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_1 + w_2}
\\\\
\textsc{[Branch]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + \mbox{max}(w_2, w_3)}
\\\\
\textsc{[LoopInf]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = \infty}
{W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
\\\\
\textsc{[LoopExp]} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ \mathit{Iter}(S_1) = E}
{W(\mbox{while} (S_1) \ S_2;) = E \times (w_1 + w_2)}
\end{tabular}
\end{eqnarray*}
\end{small}
\caption{\label{fig:swe}Estimando o custo das tarefas.}
\end{figure}

% Explain how we use symbolic information to compute costs.
As regras declarativas da Figura~\ref{fig:swe} esboçam as heurísticas
utilizadas para computar o TEE para uma região hammock $S$.
A regra \textsc{LoopInf} aplica-se a laços cujo número de iterações não
pode ser limitado por uma expressão simbólica computada estaticamente.
Assume-se que laços executam ao menos 10 vezes~\cite{Wu94}.
A regra \textsc{LoopExp} representa laços que não podem ser analisados 
com a análise de limites simbólicos. A função auxiliar $\mathit{Iter}(S)$ 
retorna uma expressão simbólica que representa a variedade de valores
cobertos pelo código em $S$ que controla o número de iterações do laço.
Essas regras são implementadas durante o passo de estimativa da lucratividade.

\paragraph{O Modelo de Custo.}
Um modelo de custo é uma coleção de parâmetros que determinam o impacto
da criação e manutenção de tarefas em uma determinada arquitetura.
A literatura lista técnicas analíticas~\cite{Baghsorkhi10} e empíricas~\cite{Poesia17}
para a construção do modelo. Um modelo de custo automático não é o objetivo deste trabalho.
Pelo contrário, o algoritmo do {\Taskminer} recebe um modelo de custo como parâmetro.
Para os experimentos descritos na Seção ~\ref{sec:eval}, utilizou-se constantes
relacionadas à criação de {\em threads} em uma determinada arquitetura. Por exemplo,
a criação de tarefas foi estimada em 500 ciclos para a arquitetura em que os experimentos
foram realizados.

% Discuss the expansion algorithm.
\subsection{Expansão de tarefas}
\label{sub:expansion}

Expansão de tarefas consiste em encontrar a menor tarefa que é grande o suficiente
para compensar o custo de criação de {\em threads}. A figura \ref{fig:expand_alg}
mostra o algoritmo de expansão. Inicia-se o algoritmo atribuindo \textsf{REGIÃO} a
um grafo hammock $H$ que corresponde a uma hélice em um moinho $W$.
A decomposição hammock de um programa estruturado forma uma árvore~\cite{Ferrante87},
em que os vértices representam grafos hammock.
$H_1$ é filho de $H_2$ na árvore se:
(i) $H_1 \subset H_2$, e (ii) para qualquer 
nó $H_x$, se $H_1 \subset H_x$ então $H_2 \subset H_x$.
Nese contexto, $H_2$ é {\em pai} de $H_1$.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth]{images/expand_alg}
\caption{Descoberta de tarefas em regiões hammock.
\textsf{CUSTO} é o custo de criação e escalonamento de {\em threads}.}
\label{fig:expand_alg}
\end{center}
\end{figure}

A cada nova expansão, checa-se se a expansão é válida. A expansão é válida se:
(i) \textsf{HÉLICE} está contida em um moinho $W$;
(ii) as regiões de memória em \textsf{HÉLICE} podem ser analisadas de acordo com
a seção \ref{sub:sra};
(iii) \textsf{HÉLICE} não depende de uma outra hélice no mesmo moinho $W$.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth]{images/ex_expansion}
\caption{(a) Exemplo de laço duplamente aninhando analisado pelo {\Taskminer}.
(b) O Grafo de Dependências do programa.
(c) A decomposição desse laço em moinhos e hélices. $D$ é o conjunto de variáveis
das quais as hélices dependem.}
\label{fig:ex_expansion}
\end{center}
\end{figure}

O programa na Figura~\ref{fig:ex_expansion} (a) contém dois moinhos.
O primeiro consiste do laço da linha 1. O outro, aninhado, é o laço da linha 2.
As hélices que surgem desses moinhos estão evidenciadas na Figura~\ref{fig:ex_expansion} (b).
Na Figura, há 3 tarefas candidatas, cada uma formada por uma hélice diferente.
Para encontrar as tarefas, aplica-se a função de expansão (Fig.~\ref{fig:expand_alg})
nas hélices mais internas: \textsf{Hélice-2} pode ser expandida para incluir \textsf{Hélice-3}.

A expansão ocorre até o limite definido pelo \textsf{CUSTO}, que é determinado pelo modelo de custo
da Seção~\ref{sub:profit}. Se a lucratividade é menor que este custo, então
a criação da tarefa não é desejável. Porém, se a tarefa é expandida demais, 
há perda de paralelismo: o código executa sequencialmente. Portanto, determinar o \textsf{CUSTO}
é essencial para o desempenho do {\Taskminer}.

\subsection{Privatização de variáveis}
\label{sub:variance}

Para evitar condições de corrida, a inserção de anotações com semântica paralela
em programas sequenciais exige a replicação de alguns valores, tornando-os privados para cada tarefa.
Essa medida é chamada de {\em privatização}.

Se uma variável escalar contém pelo menos uma cadeia de definição-e-uso que entra
a fronteira de uma tarefa, então essa variável deve ser privatizada. A fronteira de uma 
tarefa é determinada pela função de expansão vista na Figura~\ref{fig:expand_alg}.

\begin{example}[Privatização]
\label{ex:priv}
Variáveis \textsf{i} e \textsf{j} na Figura~\ref{fig:ex_privatize} devem ser replicadas
nas tarefas indicadas pela anotação na linha 8.
A variável \textsf{i} é definida nas linhas 2 e 10, e utilizada na linha 9, que faz
parte do corpo de uma nova tarefa; \textsf{j} é definida na linha 6 e utilizada na linha 9.
Dessa forma, ambas possuem uma cadeia de definição-e-uso que ultrapassa a fronteira
de uma tarefa. Cada iteração do laço na linha 9 lê um valor diferente para \textsf{i}; portanto,
cada tarefa deve receber um valor diferente nesta variável. Na ausência de privatização, cada {\em thread}
leria o mesmo valor, de forma que a paralelização desse código o tornaria incorreto.
A privatização de \textsf{i} e\textsf{j} evita as condições de corrida e mantém o programa correto.
\end{example}

\subsection{Anotando o código fonte}
\label{sub:ir}

As análises descritas até agora foram implementadas na representação intermediária
do LLVM devido à facilidade do uso de análises como evolução escalar~\cite[p.18]{Grosser12} e outras
análises de fluxo de dados.
Porém, as anotações são inseridas em código fonte C, então grande
parte deste trabalho foi o mapeamento de informações da representação intermediária do LLVM de volta
para código C.

% Explain machinery: scope tree and simplification
\noindent
\textbf{Árvore de escopos:}
A árvore de escopos é uma estrutura utilizada pelo {\Taskminer} para mapear regiões hammock em construtos C, como blocos
\textsf{while} e \textsf{if-then-else}. Cada nó nesta árvore contém {\em meta-dados}
provenientes de informação de depuração obtida durante a compilação para representação
intermediária do LLVM. Para manter esse tipo de informação de depuração, basta compilar o código com a flag
{\em -g}.
É possível achar o número da linha relacionada à cada nó na árvore de escopos, permitindo
ao {\Taskminer} a anotação das regiões hammock no código fonte de maneira precisa.

\paragraph{Limitando a criação de tarefas recursivas}
Para evitar a criação excessiva de tarefas muito pequenas, {\Taskminer} concede a opção
aos usuários de limitar a criação de tarefas. Por exemplo \textsf{./Taskminer -r 12} limita o número
de tarefas criadas um total de 12 tarefas. Essa solução é implementada diretamente no código-fonte,
na fase final. Embora simples, conforme experimentos (Sec.~\ref{sec:eval}), essa solução traz claros
benefícios em benchmarks recursivos. A variável, chamada de \textsf{taskminer\_depht\_cutoff} na Figura
\ref{fig:ex_cutoff}, é global e ligada estaticamente no programa. No começo de cada função recursiva,
esta variável é incrementada para indicar a criação de uma nova tarefa; e decrementada ao sair da mesma função.

\begin{example}[Limitação de tarefas]
A Figura~\ref{fig:ex_cutoff} ilustra a estratégia utilizada pelo {\Taskminer} para limitar
o número de tarefas criadas durante a invocação de uma função recursiva.
O parâmetro \textsf{DEPHT\_CUTOFF} é determinado pelo usuário.
\end{example}

Há outras formas de limitar o número de tarefas recursivas~\cite{Iwasaki16,Iwasaki16B}.
Porém, o trabalho de estimar funções recursivas é muito difícil e não é o foco deste trabalho.
Portanto, embora simples, essa medida é genérica o suficiente para lidar com tarefas difíceis de se
limitar simbolicamente. Como trabalho futuro, pretende-se explorar melhores maneiras de
limitar tarefas extremamente pequenas.

\section{Avalia\c{c}\~{a}o Experimental}
\label{sec:eval}

O {\Taskminer} foi implementado em LLVM 3.9~\cite{Lattner04}. Todos os experimentos
foram executados em uma máquina de 12 núcleos 64-bits Intel(R) Xeon(R) CPU E5-2620, 2.00GHz, com 32K de cache L1, 256K de cache L2 e 15M de cache L3, e 15Gb de memória RAM. Utilizou-se OpenMP 4.5, lançado em 
Novembro de 2015.

\subsection{Desempenho}
\label{sub:performance}

\begin{figure}[b!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/TM_Performance}
\caption{Comparações de performance. Anotações automáticas comparam-se favoralmente a intervenções
manuais, e levam à ganhos de desempenho. O eixo Y mostra o ganho de desempenho de cada versão anotada
pelo {\Taskminer} sobre a versão anotada manualmente. Os números nas pequenas caixas representam
o crescimento em velocidade obtido pelo {\Taskminer}.}
\label{fig:TM_Performance}
\end{center}
\end{figure}

A Figura~\ref{fig:TM_Performance} compara o tempo de execução de programas produzidos
pelo {\Taskminer} contra versões originais dos mesmos programas anotados manualmente.
Os {\em benchmarks} utilizados neste experimento são do \textsf{BSC-Bots}~\cite{Duran09} (\textsf{fft} até \textsf{jacobi}
na Fig.~\ref{fig:TM_Performance}) e do \textsf{Swan}~\cite{Moreira17}
(\textsf{dfs} até \textsf{private}).
Ambos vem com versões sequenciais e paralelas (anotadas manualmente). Os códigos foram compilados
com gcc-6.

As versões anotadas pelo \Taskminer{} foram mais velozes que as sequenciais em 13 dos 16 programas.
A maioria são algoritmos Dividir \& Conquistar clássicos como multiplicação de matrizes de \textsf{Strassen},
 \textsf{knapsack} (Problema da Mochila) e \textsf{fft}. Em 6 deles, as versões automáticas foram próximas e até
levemente acima das versões anotadas manualmente. Em 3 exemplos \Taskminer{} produziu versões piores que
as versões sequenciais: \textsf{fib}, \textsf{floorplan} e \textsf{bell-ford}. Entretanto, ainda assim produziu versões
mais rápidas que as anotadas manualmente. Uma inspeção visual de \textsf{bell-ford} indica que a versão
paralelizada manualmente dispara um número grande tarefas pequenas. O modelo de custo
do \Taskminer{} poda a criação de tarefas pequenas, mas não o suficiente para vencer o desempenho
da versão sequencial. Este experimento demonstra que \Taskminer{} pode trazer
ganhos consideráveis se comparados às versões sequenciais e manualmente anotadas.

%OPTIMIZATIONS
%Here, we show the results on two big optimizations: recursion depth and cost model.
%We can use the same benchmarks as above.
\subsection{Otimizações}
\label{sub:optimizations}

\begin{figure}[b!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/Optimizations}
\caption{Benefícios de limitar a criação de tarefas. (Secs.~\ref{sub:profit} e ~\ref{sub:ir}).
\textbf{CFR}: tarefas criadas em \underline{C}hamadas de \underline{F}unções \underline{R}ecursivas.
\textbf{CNR}: tarefas interprocedurais criadas ao redor de \underline{C}hamadas  \underline{N}ão-\underline{R}ecursivas.
\textbf{Reg}: tarefas envolvendo \underline{Reg}iões, sem chamadas de função.}
\label{fig:Optimizations}
\end{center}
\end{figure}

Este artigo descreve duas formas de otimizar a criação de tarefas. Ambas são baseadas na ideia de 
``poda de tarefas": evita-se a criação de tarefas consideradas não-lucrativas. A primeira técnica
corta criação de tarefas ditas não lucrativas de acordo com o modelo de custo, conforme explicado na 
Seção~\ref{sub:profit}; a segunda técnica corta criação de tarefas muito profundas na pilha de recursão, 
como descrito na Seção~\ref{sub:ir}. A Figura~\ref{fig:Optimizations} ilustra os benefícios dessas duas técnicas,
presentes em 6 dos benchmarks vistos anteriormente na Figura~\ref{fig:TM_Performance}.

Em 3 benchmarks, \textsf{private}, \textsf{boruvka} e
\textsf{bellman-ford}, o modelo de custo evita a criação de tarefas em laços que inicializam estruturas de dados.
Por exemplo, o laço a seguir, na linha 75 do programa \textsf{bellmanford.c}, seria paralelizado pelo
\Taskminer{}, caso o modelo de custo o marcasse como lucrativo:

\begin{verbatim}
  for (long unsigned i = 0; i < N; i++)
    for (long unsigned j = 0; j < N; j++)
      *(G + i * N + j) = rand();
\end{verbatim}

Similarmente, a limitação de tarefas recursivas (Sec.~\ref{sub:ir}), embora simples,
é efetiva em eliminar o excesso de tarefas pequenas. A Figura~\ref{fig:Optimizations} mostra o efeito
dessa otimização em três programas: \textsf{health}, \textsf{nqueens} e
\textsf{strassen}. Estes programas foram projetados para ilustrar paralelismo
em paradigma Dividir \& Conquistar ~\cite{Duran09}, e contém um grande número de chamadas
recursivas. A poda em níveis mais altos da árvore de recursão leva a ganhos de desempenho consideráveis
nestes programas. Caso não houvesse essa otimização de poda, então perda de desempenho seria observada
em  \textsf{health} e \textsf{nqueens}. Este experimento prova que as otimizações são efetivas
para melhorar a qualidade do código gerado pelo \Taskminer{}.

%VERSATILITY
%The goal here is to show that TaskMiner is a versatile tool, capable of finding many types of task parallelism in the code. 
%And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
\subsection{Versatilidade}
\label{sub:versatility}

Os benchmarks das seções anteriores foram projetados especialmente para o estudo de 
paralelismo irregular. Para determinar se o \Taskminer{} consegue encontrar paralelismo 
em programas comuns, executou-se o mesmo sobre 219 programas escritos em C disponíveis
na suíte de testes do LLVM, e comparou-se o desempenho da versão anotada automaticamente pelo
\Taskminer{} com a versão original sequencial. 
\Taskminer{} anota um programa se:
(i) consegue encontrar limites simbólicos para todos os acessos à memória que ocorrem em uma hélice; e
(ii) a hélice é ampla o suficiente para pagar pelo custo de criação de tarefas no ambiente de execução.
Sob essas circunstâncias, descobriu-se tarefas em 63 desses programas. A Figura~\ref{fig:TM_Versatility} relaciona
o número de tarefas ao número de instruções em 30 dos maiores programas utilizados.
Para evitar a contagem de múltiplos arquivos C para o mesmo benchmark, a Figura~\ref{fig:TM_Versatility} contém
somente benchmarks que consistem em arquivos {\em single-source}. Como demonstrado neste experimento,
\Taskminer{} é capaz de anotar um número não trivial de benchmarks reais.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=1\columnwidth]{images/TM_Versatility}
\caption{Relação entre o número de regiões de tarefas e tamanho do programa.
Cada programa é um arquivo C completo.}
\label{fig:TM_Versatility}
\end{center}
\end{figure}

Observa-se que 27 dos benchmarks anotados não demonstraram aumento de desempenho em 
relação à versão sequencial,
pois as tarefas anotadas eram demasiadamente pequenas e pouco influenciaram na execução total do programa.
Em 17 benchmarks, observou-se uma perda de velocidade: neste caso, interações entre estruturas de dados
forçaram ao ambiente de execução do OpenMP a serizalizar a execução das tarefas. Essas perdas foram 
inferiores à 10\%. Em um dos casos, \textsf{MiBench/office-stringsearch}, a versão paralela foi 11 vezes mais lenta.
Por outro lado, obteve-se aumento de desempenho acima de 5\% em 19 benchmarks. 
Em \textsf{Misc/lowercase}, o acréscimo de velocidade foi acima de 3.5x, e em 3 casos, acima de 1.5x.
A Figura~\ref{fig:TM_GeneralProgs} mostra os 10 maiores acréscimos de desempenho obtidos pelo \Taskminer{}.
É importante enfatizar que esse experimento {\em não contou com nenhum tipo de intervenção humana}.
Portanto, \Taskminer{} é capaz de encontrar paralelismo automaticamente sem custo de programação.

\begin{figure}[t!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/TM_GeneralProgs}
\caption{Melhorias de desempenho obtidas pelo \Taskminer{} quando aplicado à suíte de testes
do LLVM. Quanto maior a barra, maior o ganho de desempenho.
\textbf{LoC} significa ``Linhas de Código".}
\label{fig:TM_GeneralProgs}
\end{center}
\end{figure}

%{\Taskminer}'s versatility also arises in regards to the diversity of types of task parallelism that it
%can find in a program. Table \ref{tab:types} shows all types of tasks found in our main benchmarks.
%There are 3 types of tasks: recursive, which arises from vanes in Divide and Conquer
%algorithms; function call, which arises within loops that are not clearly parallel; and region, which 
%are similar to function calls, but instead are entire fragments of code within loops that can be executed in
%parallel. We provide the user complete decision power to mine for any type of tasks they wish when
%running our tool.

%SCALABILITY
\subsection{Escalabilidade}
\label{sub:scalability}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{images/TM_Runtime}
\caption{Tempo de execução do \Taskminer{} versus tamanho dos programas.
Cada ponto representa um dos 100 programas gerados pelo \textsf{CSmith}.
A curva é uma aproximação polinomial de grau 2. O tamanho máximo obtido 
nos programas gerados pelo CSmith foi de 5.000 LoC.}
\label{fig:TM_Runtime}
\end{center}
\end{figure}

As análises descritas neste artigo possuem complexidade de tempo quadrática no pior caso.
Para testar a complexidade do algoritmo implementado na ferramenta \Taskminer{}, 
utilizou-se \textsf{CSmith}~\cite{Yang11}, um gerador de código aleatório, para produzir 
100 programas de tamanhos variados, os quais foram alimentados ao \Taskminer{}. 
A Figura~\ref{fig:TM_Runtime} mostra o resultado desse experimento.
O maior programa obtido teve 4.999 linhas de código, as quais foram processadas
pelo \Taskminer{} em 1.2 segundos.

\section{Trabalhos Relacionados}
\label{sec:rw}

Compiladores modernos adicionaram suporte ao paralelismo de tarefas do OpenMP apenas recentemente. Uma implementação
do compilador \textsf{clang} com esse suporte foi lançado em Março de 2014, por exemplo. Uma vez que a infra-estrutura necessária para
a implementação de tarefas é nova, não existem ferramentas além do {\Taskminer} capazes de anotar programas
automaticamente com essas diretivas.
Padrões de anotação baseados em diretivas provém aos programadores um modelo de programação paralela prático e fácil. Exemplos
de modelos que permitem paralelismo de tarefas são OpenMP 4.X,
StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
tejedor:hpdc:2011} e OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}.
Por exemplo, Tareador \cite{Ayguade15} apresenta uma interface gráfica para identificação de potencial paralelismo e anotação de código sequencial.
Ao contrário do Tareador, {\Taskminer} executa essa tarefa automaticamente.

A técnica utilizada pelo {\Taskminer} para identificação de tarefas se assemelha às análises usadas durante
geração de código para máquinas de fluxo de dados. Programação de fluxo de dados foi originalmente proposta 
para facilitar paralelismo de tarefas~\cite{agrawal:ipdps:2010, chan:spaa:2007,
gupta:micro:2011}. Agrawal et al. \cite{agrawal:ipdps:2010} estendeu esse modelo
com inputs e outpus em Cilk++, que foi extendido novamente por ~\cite{vandierendonck:hotpar:2011} 
com cláusulas de dependência para facilitar
o projeto de padrões complexos de paralelsimo. Ambos apresentaram um escalonador unificado
baseado em paralelismo \textit{fork-join} \cite{vandierendonck:pact:2011} que permitiu
a execução de aplicações baseadas em tarefas. Outras abordagens também utilizaram grafos
de fluxo de dados para explorar paralelismo, como Tarefas Movidas à Dados \cite{tasirlar:icpp:2011},
em que o programador pode manipular cláusulas para determinar os argumentos da tarefa
antes de sua execução. Paralelismo baseado em função também foi proposto em \cite{gupta:micro:2011}
para utilizar argumentos de funções como especificadores de dependências entre tarefas.
Entretanto, a mineração e inserção automática dessas diretivas não consta como objetivo
em nenhum desses trabalhos.

Muitos sistemas foram desenvolvidos para extrair paralelismo de tarefas a partir de código sequencial.
Exemplos incluem OSCAR, Multigrain Parallelizing
Compiler \cite{ishizaka:journal:2000, kasahara:iwlcpc:2000},  MAPS \cite{castrillon:tii:2013, ceng:dac:2008}, e
DiscoPoP \cite{discopop, li:jss:2016}. Ferramentas como Paraver \cite{extrae, paraver},
Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, e TEMANEJO
\cite{brinkmann:parco:2011, brinkmann:journal:2013, temanejo} foram implementadas para 
permitir análise de desempenho e visualização de programas baseados em tarefas.
Apesar de ajudar o programar a adaptar o código paralelo, essas ferramentas não são 
inteiramente automáticas como o {\Taskminer}.

\section{Conclus\~{a}o}
\label{sec:conc}

\bibliography{references}

\end{document}

### 2018-05-18 docs/ACM/paper.tex
Added portuguese pictures to the sblp paper.

@@
 Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
-to substantial performance gains~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Antao16,Wienke12}.
+to substantial performance gains~\cite{Bertolli14,Mendonca17,Poesia17}.
 %\guido{Suppport what?}
@@
 There exist tools that insert automatic annotations in
-programs~\cite{Amini12,Guelton12,Mendonca16,Pingali11,Nugteren14}.
+programs~\cite{Mendonca16,Pingali11}.
 All these technologies explore data-parallelism -- the possibility of running
@@
 closer to irregular programs such as those that process graphs and
-worklists~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
+worklists~\cite{Pingali11}.
 The purpose of this work is to address this omission.
@@
 Some of these programs, such as those taken from the
-Kastor~\cite{Virouleau14}, Bots~\cite{Duran09} or the LLVM~\cite{Lattner04} test
+Kastor~\cite{Virouleau14}, Bots~\cite{Duran09} or the LLVM test
 suites, are large and complex.

### 2018-05-21 docs/SBLP/paper.tex

@@
 
-\author{Pedro Henrique Ramos Costa}
-\authornote{with author1 note}          %% \authornote is optional;
-\orcid{nnnn-nnnn-nnnn-nnnn}
+\author{Pedro Ramos*, Gleison Souza, Guilherme Leobas, Fernando M Q Pereira}
+%\authornote{with author1 note}          %% \authornote is optional;
+%\orcid{nnnn-nnnn-nnnn-nnnn}
 \affiliation{
-  \position{Researcher}
-  \department{DCC}
+  %\position{Researcher}
+  %\department{DCC}
   \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
+%  \streetaddress{6627 Antonio Carlos Avenue}
+%  \city{Belo Horizonte}
+%  \state{Minas Gerais}
+ % \postcode{31.270-213}
+ % \country{Brazil}
 }
-\email{pedroramos@dcc.ufmg.br}
+\email{ pedroramos, gleison, guilherme, fernando @dcc.ufmg.br}
 
-\author{Gleison Souza Diniz Mendonc\c{c}a}
-\authornote{with author1 note}          %% \authornote is optional;
-\orcid{nnnn-nnnn-nnnn-nnnn}
-\affiliation{
-  \position{Researcher}
-  \department{DCC}
-  \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
-}
-\email{gleison.mendonca@dcc.ufmg.br}
+%\author{Gleison Souza Diniz Mendonc\c{c}a}
+%\authornote{with author1 note}          %% \authornote is optional;
+%\orcid{nnnn-nnnn-nnnn-nnnn}
+%\affiliation{
+ % \position{Researcher}
+%  \department{DCC}
+ % \institution{UFMG}
+ % \streetaddress{6627 Antonio Carlos Avenue}
+%  \city{Belo Horizonte}
+%  \state{Minas Gerais}
+%  \postcode{31.270-213}
+%  \country{Brazil}
+%}
+%\email{gleison.mendonca@dcc.ufmg.br}
 
-\author{Guilherme Mendes Leobas}
-\authornote{with author1 note}          %% \authornote is optional;
-\orcid{nnnn-nnnn-nnnn-nnnn}
-\affiliation{
-  \position{Researcher}
-  \department{DCC}
-  \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
-}
-\email{guihermel@dcc.ufmg.br}
+%\author{Guilherme Mendes Leobas}
+%\authornote{with author1 note}          %% \authornote is optional;
+%\orcid{nnnn-nnnn-nnnn-nnnn}
+%\affiliation{
+%  \position{Researcher}
+%  \department{DCC}
+%  \institution{UFMG}
+%  \streetaddress{6627 Antonio Carlos Avenue}
+%  \city{Belo Horizonte}
+%  \state{Minas Gerais}
+%  \postcode{31.270-213}
+%  \country{Brazil}
+%}
+%\email{guihermel@dcc.ufmg.br}
 
-\author{Fernando M Q Pereira}
-\authornote{with author1 note}
-\orcid{nnnn-nnnn-nnnn-nnnn}
-\affiliation{
-  \position{Professor}
-  \department{DCC}
-  \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
-}
-\email{fernando@dcc.ufmg.br}          %% \email is recommended
+%\author{Fernando M Q Pereira}
+%\authornote{with author1 note}
+%\orcid{nnnn-nnnn-nnnn-nnnn}
+%affiliation{
+ % \position{Professor}
+ % \department{DCC}
+ % \institution{UFMG}
+ % \streetaddress{6627 Antonio Carlos Avenue}
+ % \city{Belo Horizonte}
+ % \state{Minas Gerais}
+ % \postcode{31.270-213}
+ % \country{Brazil}
+%}
+%\email{fernando@dcc.ufmg.br}          %% \email is recommended
 
@@
 encontrar os limites simbólicos de acesso à memória em tempo de execução, remoção de dependências
-estáticas espúrias, contornar condições de corrida ao transformar código sequencial em código paralelo, e
-principalmente, encontrar o equilíbrio entre tamanho de uma tarefa e excesso de paralelismo, em contraste com
-o custo de manutenção de tarefas pelo ambiente de execução. Para contornar esses problemas,
+estáticas espúrias, condições de corrida ao transformar código sequencial em código paralelo, e
+principalmente, encontrar o equilíbrio entre tamanho de uma tarefa e excesso de paralelismo, o eterno contraste entre tarefas grandes e sequenciais e tarefas pequenas e paralelas.
+Para contornar esses problemas,
 \Taskminer{} implementa uma série de otimizações e análises em representação intermediária do LLVM, resultando
 em um compilador fonte-a-fonte capaz de analisar código C e inserir no mesmo anotações OpenMP automaticamente.
-\Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente, além de encontrar paralelismo escondido em programas sequenciais, absolutamente sem intervenção humana.
+\Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente.
+A ferramenta também se mostra capaz de encontrar paralelismo escondido em programas sequenciais, absolutamente sem intervenção humana.
 \end{abstract}
@@
 OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} e
-OmpSs~\cite{bueno:icpp:2011, duran:ppl:2011}
+OmpSs~\cite{duran:ppl:2011}
 atuam como metalinguagem, conferindo ao programador
@@
 em um programa paralelo. Tais sistemas mostram-se muito promissores quando
-combinados com aceleradores como GPUs e FPGAs~\cite{Bertolli14,Martineau16,Mendonca17,Poesia17,Reyes12,Antao16,Wienke12}.
+combinados com aceleradores como GPUs e FPGAs~\cite{Mendonca17,Poesia17}.
 Entretanto, apesar de conveniente, o uso desses sistemas não é automático e
@@
 Embora já existam ferramentas que inserem anotações automaticamente 
-em programas~\cite{Amini12,Guelton12,Mendonca16,Pingali11,Nugteren14},
+em programas~\cite{Mendonca16,Pingali11},
 todas essas tecnologias exploram somente paralelismo de dados.  Porém, grande
@@
 em programas sequênciais e anotá-los automaticamente. Como descrito na seção \ref{sec:ovf},
-essas anotações conferem ao programa irregular semântica de algoritmos em grafos e/ou \textit{worklists}~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
+essas anotações conferem ao programa irregular semântica de algoritmos em grafos e/ou \textit{worklists}~\cite{Pingali11}.
 
@@
 todo tipo de construto da linguagem C como arranjos, estruturas, uniões e ponteiros para esses tipos.
-Alguns desses programas provém de benchmarks complexos como Kastor~\cite{Virouleau14}, Bots~\cite{Duran09}  e a suíte de testes do LLVM~\cite{Lattner04}.
+Alguns desses programas provém de benchmarks complexos como Kastor~\cite{Virouleau14}, Bots~\cite{Duran09}  e a suíte de testes do LLVM.
 As versões anotadas pelo {\Taskminer} se aproximam das versões anotadas manualmente em
@@
 de código executada pelo {\Taskminer} é dependente de dois parâmetros,
-\textsf{DEPTH\_CUTOFF} e \textsf{WORK\_CUTOFF}. 
+\textsf{PROFUNDIDADE\_MAX} e \textsf{CUSTO\_MIN}. 
 Eles possuem valores por padrão, mas podem ser configurados pelo usuário.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=1\columnwidth]{images/ex_privatize}
-\caption{A variável \textsf{j} deve ser replicada em todas as tarefas para evitar condições de corrida.}
-\label{fig:ex_privatize}
-\end{center}
-\end{figure}
-
-Por fim,  um último problema surge ao transformar um programa originalmente
-sequencial em um programa paralelo. Condições de corrida evidenciam
-quais variáveis devem ser replicadas e
-quais podem ser compartilhadas pelas tarefas. 
-Assim como o problema de determinar os limites de acesso à memória, 
-se não resolvido, esse problema pode levar à programas incorretos.
-Esse processo de replicação de variáveis em todas as tarefas criadas se chama \textit{privatização}. 
-Na Figura~\ref{fig:ex_privatize}, por exemplo,
-a variávei \textsf{j} deve ser privatizada. 
-Caso não seja, ela será compartilhada por todas as tarefas 
-criadas na linha 5 da Figura~\ref{fig:ex_privatize}. 
-{\Taskminer} utiliza uma técnica descrita na seção~\ref{sec:sol} 
-para resolver esse problema.
 
@@
 por funções externas. Análise de limtes simbólicos não é uma contribuição deste artigo. A técnica
-escolhida para as análises do {\Taskminer} é aquela implementada no compilador \dawn{} \cite{Mendonca17},
-que, por sua vez, reusa trabalho de Blume {\em et al.}~\cite{Blume94}. Para este trabalho, é apenas
+escolhida para as análises do {\Taskminer} é aquela implementada no compilador \dawn{} \cite{Mendonca17}.
+Para este trabalho, é apenas
 suficiente saber que essa implementação é sólida o suficiente para lidar com toda a linguagem C99, sempre termina
@@
 
-Tarefas candidatas são \textbf{hélices em moinhos}. {\em Moinhos} são uma família de grafos ~\ref{Rideau08}.
+Tarefas candidatas são \textbf{hélices em moinhos}. {\em Moinhos} são uma família de grafos ~\cite{Rideau08}.
 Moinhos existem como subgrafos do grafo de dependências.
@@
 da criação e manutenção de tarefas em uma determinada arquitetura.
-A literatura lista técnicas analíticas~\cite{Baghsorkhi10} e empíricas~\cite{Poesia17}
+A literatura lista técnicas analíticas e empíricas~\cite{Poesia17}
 para a construção do modelo. Um modelo de custo automático não é o objetivo deste trabalho.
@@
 
-\subsection{Privatização de variáveis}
-\label{sub:variance}
-
-Para evitar condições de corrida, a inserção de anotações com semântica paralela
-em programas sequenciais exige a replicação de alguns valores, tornando-os privados para cada tarefa.
-Essa medida é chamada de {\em privatização}.
-
-Se uma variável escalar contém pelo menos uma cadeia de definição-e-uso que entra
-a fronteira de uma tarefa, então essa variável deve ser privatizada. A fronteira de uma 
-tarefa é determinada pela função de expansão vista na Figura~\ref{fig:expand_alg}.
-
-\begin{example}[Privatização]
-\label{ex:priv}
-Variáveis \textsf{i} e \textsf{j} na Figura~\ref{fig:ex_privatize} devem ser replicadas
-nas tarefas indicadas pela anotação na linha 8.
-A variável \textsf{i} é definida nas linhas 2 e 10, e utilizada na linha 9, que faz
-parte do corpo de uma nova tarefa; \textsf{j} é definida na linha 6 e utilizada na linha 9.
-Dessa forma, ambas possuem uma cadeia de definição-e-uso que ultrapassa a fronteira
-de uma tarefa. Cada iteração do laço na linha 9 lê um valor diferente para \textsf{i}; portanto,
-cada tarefa deve receber um valor diferente nesta variável. Na ausência de privatização, cada {\em thread}
-leria o mesmo valor, de forma que a paralelização desse código o tornaria incorreto.
-A privatização de \textsf{i} e\textsf{j} evita as condições de corrida e mantém o programa correto.
-\end{example}
-
 \subsection{Anotando o código fonte}
@@
 o número de tarefas criadas durante a invocação de uma função recursiva.
-O parâmetro \textsf{DEPHT\_CUTOFF} é determinado pelo usuário.
+O parâmetro \textsf{PROFUNDIDADE\_MAX} é determinado pelo usuário.
 \end{example}
 
-Há outras formas de limitar o número de tarefas recursivas~\cite{Iwasaki16,Iwasaki16B}.
+Há outras formas de limitar o número de tarefas recursivas~\cite{Iwasaki16}.
 Porém, o trabalho de estimar funções recursivas é muito difícil e não é o foco deste trabalho.
@@
 
-O {\Taskminer} foi implementado em LLVM 3.9~\cite{Lattner04}. Todos os experimentos
+O {\Taskminer} foi implementado em LLVM 3.9. Todos os experimentos
 foram executados em uma máquina de 12 núcleos 64-bits Intel(R) Xeon(R) CPU E5-2620, 2.00GHz, com 32K de cache L1, 256K de cache L2 e 15M de cache L3, e 15Gb de memória RAM.
@@
 %SCALABILITY
-\subsection{Escalabilidade}
-\label{sub:scalability}
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{images/TM_Runtime}
-\caption{Tempo de execução do \Taskminer{} versus tamanho dos programas.
-Cada ponto representa um dos 100 programas gerados pelo \textsf{CSmith}.
-A curva é uma aproximação polinomial de grau 2. O tamanho máximo obtido 
-nos programas gerados pelo CSmith foi de 5.000 LoC.}
-\label{fig:TM_Runtime}
-\end{center}
-\end{figure}
-
-As análises descritas neste artigo possuem complexidade de tempo quadrática no pior caso.
-Para testar a complexidade do algoritmo implementado na ferramenta \Taskminer{}, 
-utilizou-se \textsf{CSmith}~\cite{Yang11}, um gerador de código aleatório, para produzir 
-100 programas de tamanhos variados, os quais foram alimentados ao \Taskminer{}. 
-A Figura~\ref{fig:TM_Runtime} mostra o resultado desse experimento.
-O maior programa obtido teve 4.999 linhas de código, as quais foram processadas
-pelo \Taskminer{} em 1.2 segundos.
 
@@
 
-Compiladores modernos adicionaram suporte ao paralelismo de tarefas do OpenMP apenas recentemente. Uma implementação
+Compiladores modernos adicionaram suporte ao paralelismo de tarefas do OpenMP apenas recentemente. Uma implementa-\c{c}\~{a}o
 do compilador \textsf{clang} com esse suporte foi lançado em Março de 2014, por exemplo. Uma vez que a infra-estrutura necessária para
@@
 de modelos que permitem paralelismo de tarefas são OpenMP 4.X,
-StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
-tejedor:hpdc:2011} e OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}.
+StarSs \cite{planas:hpca:2009} e OmpSs \cite{duran:ppl:2011}.
 Por exemplo, Tareador \cite{Ayguade15} apresenta uma interface gráfica para identificação de potencial paralelismo e anotação de código sequencial.
@@
 geração de código para máquinas de fluxo de dados. Programação de fluxo de dados foi originalmente proposta 
-para facilitar paralelismo de tarefas~\cite{agrawal:ipdps:2010, chan:spaa:2007,
-gupta:micro:2011}. Agrawal et al. \cite{agrawal:ipdps:2010} estendeu esse modelo
-com inputs e outpus em Cilk++, que foi extendido novamente por ~\cite{vandierendonck:hotpar:2011} 
+para facilitar paralelismo de tarefas~\cite{gupta:micro:2011}. Agrawal et al. \cite{agrawal:ipdps:2010} extendeu esse modelo
+com inputs e outpus em Cilk++, que foi extendido novamente ~\cite{vandierendonck:hotpar:2011} 
 com cláusulas de dependência para facilitar
 o projeto de padrões complexos de paralelsimo. Ambos apresentaram um escalonador unificado
-baseado em paralelismo \textit{fork-join} \cite{vandierendonck:pact:2011} que permitiu
+baseado em paralelismo \textit{fork-join} que permitiu
 a execução de aplicações baseadas em tarefas. Outras abordagens também utilizaram grafos
@@
 Exemplos incluem OSCAR, Multigrain Parallelizing
-Compiler \cite{ishizaka:journal:2000, kasahara:iwlcpc:2000},  MAPS \cite{castrillon:tii:2013, ceng:dac:2008}, e
-DiscoPoP \cite{discopop, li:jss:2016}. Ferramentas como Paraver \cite{extrae, paraver},
+Compiler \cite{kasahara:iwlcpc:2000},  MAPS \cite{ceng:dac:2008}, e
+DiscoPoP \cite{discopop, li:jss:2016}. Ferramentas como Paraver \cite{paraver},
 Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, e TEMANEJO
-\cite{brinkmann:parco:2011, brinkmann:journal:2013, temanejo} foram implementadas para 
+\cite{brinkmann:parco:2011} foram implementadas para 
 permitir análise de desempenho e visualização de programas baseados em tarefas.

### 2018-05-21 docs/SBLP/paper.tex
Shrinking intro.

@@
 
-\author{Pedro Ramos*, Gleison Souza, Guilherme Leobas, Fernando M Q Pereira}
+\author{Pedro Ramos, Gleison Souza, Guilherme Leobas, Fernando Magno Quint\~{a}o Pereira}
 %\authornote{with author1 note}          %% \authornote is optional;
@@
 }
-\email{ pedroramos, gleison, guilherme, fernando @dcc.ufmg.br}
+\email{[pedroramos, gleison, guilherme, fernando]@dcc.ufmg.br}
 
@@
 Este artigo apresenta \Taskminer{}, uma ferramenta capaz de encontrar paralelismo de tarefas
-em código C automaticamente. \Taskminer{} lida com problemas clássicos de paralelismo irregular como
-encontrar os limites simbólicos de acesso à memória em tempo de execução, remoção de dependências
-estáticas espúrias, condições de corrida ao transformar código sequencial em código paralelo, e
-principalmente, encontrar o equilíbrio entre tamanho de uma tarefa e excesso de paralelismo, o eterno contraste entre tarefas grandes e sequenciais e tarefas pequenas e paralelas.
-Para contornar esses problemas,
-\Taskminer{} implementa uma série de otimizações e análises em representação intermediária do LLVM, resultando
+em código C automaticamente. \Taskminer{} lida com problemas clássicos de paralelismo irregular 
+como a delimitação simbólica de regiões de memória, remoção de dependências
+estáticas espúrias, detecção de condições de corrida, e a estimativa de benefício de tarefas grandes porém sequenciais e tarefas pequenas porém paralelas. Para contornar esses problemas,
+\Taskminer{} implementa uma série de otimizações e análises em representa\-ção intermediária do LLVM, resultando
 em um compilador fonte-a-fonte capaz de analisar código C e inserir no mesmo anotações OpenMP automaticamente.
@@
 em paradigmas paralelos, visando maior eficiência e velocidade. Nesse contexto, sistemas de
-anotação como OpenMP~\cite{JaegerCP15},
-OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
-OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} e
-OmpSs~\cite{duran:ppl:2011}
-atuam como metalinguagem, conferindo ao programador
+anotação como OpenMP~\cite{JaegerCP15} e
+OpenACC~\cite{OpenACC20} atuam como metalinguagens, conferindo ao programador
 poder semântico para transformar um programa originalmente sequencial
@@
 
-Embora já existam ferramentas que inserem anotações automaticamente 
-em programas~\cite{Mendonca16,Pingali11},
-todas essas tecnologias exploram somente paralelismo de dados.  Porém, grande
+Embora existam ferramentas que anotem programas automaticamente~\cite{Mendonca16,Pingali11},
+essas tecnologias exploram somente paralelismo de dados.  Porém, grande
 parte do poder de sistemas de anotação provém da capacidade de se criar \textit{tarefas}
@@
 
-O presente artigo descreve {\Taskminer}, um compilador fonte-a-fonte que expõe
+Este artigo descreve {\Taskminer}, um compilador fonte-a-fonte que expõe
 paralelismo de tarefas em programas C/C++. {\Taskminer} lida com diversos desafios 
-do universo do paralelismo irregular. Primeiro, deve-se determinar os limites
+relacionados a paralelismo irregular. Primeiro, ele determinar os limites
 simbólicos dos blocos de memória acessados dentro de cada programa. Depois,
-encontra-se regiões ou fragmentos de código (laços ou funções) que podem 
-ser efetivamente mapeados à tarefas. Então, deve-se extrair parâmetros capazes
+ele encontra fragmentos de código (laços ou funções) que podem 
+ser efetivamente mapeados à tarefas. Então, ele extrai parâmetros capazes
 de estimar o custo da tarefa em questão. Esses parâmetros estão dinamicamente atrelados
 às anotações e são capazes de ativar ou desativar a criação de tarefas durante a execução do programa,
-ou de limitar a profundidade de tarefas geradas recursivamente. Após feito isso, deve-se determinar
-quais variáveis serão privatizadas em novas tarefas, ou compartilhadas por tarefas concorrentes.
-Finalmente, deve-se mapear todas essas informações de volta ao código fonte, produzindo
+ou de limitar a profundidade de tarefas geradas recursivamente. \Taskminer{} também determina
+quais variáveis serão replicadas em novas tarefas, ou compartilhadas por tarefas concorrentes.
+Finalmente, ele mapeia todas essas informações de volta ao código fonte, produzindo
 anotações legíveis.
@@
 todo tipo de construto da linguagem C como arranjos, estruturas, uniões e ponteiros para esses tipos.
-Alguns desses programas provém de benchmarks complexos como Kastor~\cite{Virouleau14}, Bots~\cite{Duran09}  e a suíte de testes do LLVM.
+Alguns desses programas provém de benchmarks complexos como Bots~\cite{Duran09}  e a coleção de testes do LLVM.
 As versões anotadas pelo {\Taskminer} se aproximam das versões anotadas manualmente em

### 2018-05-21 docs/SBLP/paper.tex
Removing one widow.

@@
 \begin{example}[Limitação de tarefas]
-A Figura~\ref{fig:ex_cutoff} ilustra a estratégia utilizada pelo {\Taskminer} para limitar
-o número de tarefas criadas durante a invocação de uma função recursiva.
+A Figura~\ref{fig:ex_cutoff} ilustra a limitação de tarefas criadas durante a invocação de uma
+função recursiva.
 O parâmetro \textsf{PROFUNDIDADE\_MAX} é determinado pelo usuário.

### 2018-05-23 docs/SBLP/paper.tex
Changing the title.
Finished paper.

@@
 \newtheorem{Challenge}{Challenge}[section]
+\newtheorem{Definicao}{Defini\c{c}\~{a}o}
 
@@
 
-\title[Automatic Identification and Annotation of Tasks in Structured
-Programs]
+\title[TaskMiner: Identifica\c{c}\~{a}o Autom\'{a}tica de Tarefas]
 {TaskMiner: Identificação Automática de Tarefas}
@@
 \begin{abstract}
-Este artigo apresenta \Taskminer{}, uma ferramenta capaz de encontrar paralelismo de tarefas
+Este artigo apresenta \Taskminer{}, uma ferramenta que encontra paralelismo de tarefas
 em código C automaticamente. \Taskminer{} lida com problemas clássicos de paralelismo irregular 
 como a delimitação simbólica de regiões de memória, remoção de dependências
-estáticas espúrias, detecção de condições de corrida, e a estimativa de benefício de tarefas grandes porém sequenciais e tarefas pequenas porém paralelas. Para contornar esses problemas,
-\Taskminer{} implementa uma série de otimizações e análises em representa\-ção intermediária do LLVM, resultando
-em um compilador fonte-a-fonte capaz de analisar código C e inserir no mesmo anotações OpenMP automaticamente.
+estáticas espúrias, detecção de condições de corrida, e principalmente avaliação do custo do paralelismo. Para solucioná-los,
+\Taskminer{} implementa uma série de otimizações em representa\-ção intermediária do LLVM, que analisam código C e inserem anotações OpenMP automaticamente.
 \Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente.
-A ferramenta também se mostra capaz de encontrar paralelismo escondido em programas sequenciais, absolutamente sem intervenção humana.
+\Taskminer{} também é capaz de encontrar paralelismo escondido em programas sequenciais, sem intervenção humana.
 \end{abstract}
@@
 
-É inegável que computação paralela e distribuída é hoje a alternativa mais procurada por 
-desenvolvedores em sua busca por desempenho. Programadores tem cada vez mais investido
+É inegável que computação paralela e distribuída é hoje uma alternativa muito procurada por 
+desenvolvedores na busca por desempenho. Programadores tem, cada vez mais, investido
 em paradigmas paralelos, visando maior eficiência e velocidade. Nesse contexto, sistemas de
@@
 parte do poder de sistemas de anotação provém da capacidade de se criar \textit{tarefas}
-durante a execução do programa~\cite{Ayguade09}. Dessa forma, o propósito desse trabalho
+durante a execução do programa~\cite{Ayguade09}. O propósito desse trabalho
 é apresentar um algoritmo capaz de minerar oportunidades para paralelismo de tarefas
 em programas sequênciais e anotá-los automaticamente. Como descrito na seção \ref{sec:ovf},
-essas anotações conferem ao programa irregular semântica de algoritmos em grafos e/ou \textit{worklists}~\cite{Pingali11}.
+essas anotações conferem ao programa irregular semântica de algoritmos em grafos e/ou \textit{worklists}~\cite{Pingali11}, paradigmas paralelos.
 
 Este artigo descreve {\Taskminer}, um compilador fonte-a-fonte que expõe
-paralelismo de tarefas em programas C/C++. {\Taskminer} lida com diversos desafios 
-relacionados a paralelismo irregular. Primeiro, ele determinar os limites
-simbólicos dos blocos de memória acessados dentro de cada programa. Depois,
-ele encontra fragmentos de código (laços ou funções) que podem 
-ser efetivamente mapeados à tarefas. Então, ele extrai parâmetros capazes
+paralelismo de tarefas em programas C/C++. {\Taskminer} lida com desafios 
+relacionados ao paralelismo irregular. Primeiro, ele determina os limites
+simbólicos dos blocos de memória acessados dentro de cada programa. Depois, encontra 
+fragmentos de código (laços ou funções) que podem 
+ser efetivamente mapeados à tarefas. Então, extrai parâmetros capazes
 de estimar o custo da tarefa em questão. Esses parâmetros estão dinamicamente atrelados
@@
 
-Este trabalho defende a tese de que a anotação automática de tarefas é útil à medida que
+Defende-se a tese de que a anotação automática de tarefas é útil à medida que
 retira do programador o fardo de procurar, anotar e verificar as anotações, tornando seu
@@
 
-A construção de um compilador como o \Taskminer{} envolve a superação de uma série de etapas e desafios.
+A construção de um compilador como o \Taskminer{} envolve a superação de uma série  de desafios.
 \Taskminer{} recebe como entrada um programa escrito em C e retorna o mesmo programa anotado com 
-diretivas OpenMP. Como descrito por LaGrone et al. ~\cite{LaGrone11}, 
-o ambiente de execução OpenMP se encarrega de 
-rastrear dependências entre ponteiros estaticamente. Entretanto, a inserção
-automática das anotações é apenas a última etapa. Nesta Seção detalharemos os desafios e problemas
-encontrados pelo \Taskminer{} no processo de mineração de tarefas. A solução para esses problemas será descrita 
+diretivas OpenMP. O ambiente de execução OpenMP se encarrega de 
+rastrear dependências entre ponteiros (~\cite{LaGrone11}). Entretanto, a inserção
+automática das anotações é apenas a última etapa. Nesta Seção detalha-se os problemas
+encontrados pelo \Taskminer{} no percalço de mineração de tarefas. A solução para esses problemas será descrita 
 posteriormente na Seção~\ref{sec:sol}.
@@
 O primeiro desafio encontrado pelo \Taskminer{} consiste em 
-identificar regiões de memória cobertas por uma tarefa.
-A Figura~\ref{fig:ex_Regions} ilustra esse problema e como resolvê-lo. Este programa recebe
-uma matriz $\mathsf{M}\times\mathsf{N}$ identificada por  \textsf{V}, em formato linear,
+identificar as regiões de memória cobertas por uma tarefa.
+A Figura~\ref{fig:ex_Regions} ilustra esse problema e como resolvê-lo. O programa
+uma matriz \textsf{V}, $\mathsf{M}\times\mathsf{N}$, em formato linear,
 e produz um vetor  \textsf{U} de forma que  \textsf{U[i]} contenha a soma de todos
@@
 
-A Figura~\ref{fig:ex_Regions} também apresenta um outro problema: {\em como estimar a rentabilidade de uma tarefa?}
+A Figura~\ref{fig:ex_Regions} apresenta um outro problema: {\em como estimar a rentabilidade de uma tarefa?}
 A criação de tarefas envolve um custo alto por parte do ambiente de execução, causado por questões como
-alocação, escalonamento, concorrência e gerenciamento em tempo real do grafo de dependências de tarefas.
+alocação, escalonamento, concorrência e gerenciamento em tempo real do grafo de dependências.
 Idealmente, são desejáveis tarefas que executem uma quantidade de trabalho
-grande o suficiente para superar este custo. Como consta em \cite{Rice53}, a quantidade de trabalho executado
-por uma tarefa não pode ser descoberta estaticamente. É possível aproximar-se dessa quantia utilizando-se
+grande o suficiente para superar este custo. A quantidade de trabalho executado
+por uma tarefa não pode ser descoberta estaticamente \cite{Rice53}. 
+É possível aproximar-se desse custo com
 símbolos nativos do programa, que, em execução, serão substituídos por valores. 
 Por exemplo, na figura~\ref{fig:ex_Regions}
-é conhecido o número de instruções do laço interno. Então aproxima-se a quantidade de trabalho executado
-com a expressão \textsf{5 * M}. Dessa forma, o valor de \textsf{M} durante a execução será determinante para
-a criação da tarefa. Essa checagem é feita na linha 7 da Figura, 
+sabe-se o número de instruções do laço interno. Então aproxima-se a quantidade de trabalho executado
+com a expressão \textsf{5 * M}. O valor de \textsf{M} durante a execução será determinante para
+a criação da tarefa. Essa checagem é feita na linha 7 da figura, 
 e faz parte da sintaxe de OpenMP. Além disso, {\Taskminer} propõe
@@
 é o uso de cortes mínimos para o número de tarefas a serem criadas~\cite{Duran08b}. 
-Observa-se esse fator explicitamente no contexto de tarefas recursivas. 
-Para limitar a criação de tais tarefas, que tem uma granularidade menor,
-uma variável de controle é inserida no código. 
-Um exemplo é ilustrado na Figura~\ref{fig:ex_cutoff}. 
-Um contador é associado à invocação de funções recursivas anotadas com diretiva de tarefas. 
+Observa-se esse fator no contexto de tarefas recursivas. 
+Uma variável de controle é inserida no código para controlar
+a criação de tarefas de baixa granularidade, como ilustrado na Figura~\ref{fig:ex_cutoff}. 
+Um contador é associado à invocação das funções recursivas anotadas como tarefas. 
 A checagem na linha 7 certifica-se de que o limite
@@
 {\Taskminer}, assim como o limite de trabalho mínimo
-por tarefa. Dessa forma, observa-se que a geração 
+por tarefa. Portanto, a geração 
 de código executada pelo {\Taskminer} é dependente de dois parâmetros,
 \textsf{PROFUNDIDADE\_MAX} e \textsf{CUSTO\_MIN}. 
-Eles possuem valores por padrão, mas podem ser configurados pelo usuário.
+Ambos possuem valores padrão, mas são passíveis de configuração.
 
@@
 
-A figura~\ref{fig:alg_main} descreve o algoritmo executado pela ferramenta {\Taskminer}. Ele utiliza conceitos conhecidos como
-o grafo de dependências~\cite{Ferrante87} e o grafo de fluxo de controle~\cite{Kildall73}. O objetivo principal do {\Taskminer}
-é identificar tarefas em programas estruturados. Programas estruturados podem ser particionados em regiões \textit{hammock}
+A figura~\ref{fig:alg_main} descreve o algoritmo executado pela ferramenta {\Taskminer}. 
+Ele utiliza conceitos  como
+o grafo de dependências~\cite{Ferrante87} e o 
+grafo de fluxo de controle~\cite{Kildall73}. {\Taskminer}
+identifica tarefas em programas estruturados que podem
+ser particionados em regiões \textit{hammock}
 \cite{Ferrante87}.
 
-\begin{definition} [Região \textit{Hammock}]
+\begin{Definicao} [Região \textit{Hammock}]
 \label{def:hammock}
@@
 $h$ é o nó de entrada e $w$ é o nó de saída de $G'$.  
-\end{definition}
+\end{Definicao}
 
-\begin{definition} [Tarefa]
+\begin{Definicao} [Tarefa]
 \label{def:task}
-Dado um programa $P$, uma tarefa $T$ é uma tupla $(G', M_i, M_o)$ formada
-por uma região \textit{hammock} $G'$ e um conjunto $M_i$ de dependências de memória representando
-os dados lidos por $T$ e um conjunto $M_o$ de regiões de memória que representam dados escritos por $T$.
-\end{definition}
+Em um programa $P$, uma tarefa $T$ é uma tupla $(G', M_i, M_o)$ formada
+por uma região \textit{hammock} $G'$ e dois conjuntos $M_i$ e $M_o$, dados de memória lidos e escritos por $T$ respectivamente.
+\end{Definicao}
 
-Sintaticamente, regiões de memória são descritas por variáveis do programa e/ou ponteiros com intervalos derefenciáveis.
-Dadas duas tarefas $T_1 = (G_1, M_{i1}, M_{o1})$ e $T_2 = (G_2, M_{i2}, M_{o2})$, 
+Regiões de memória são descritas por variáveis do programa ou ponteiros com intervalos derefenciáveis.
+Sejam duas tarefas $T_1 = (G_1, M_{i1}, M_{o1})$ e $T_2 = (G_2, M_{i2}, M_{o2})$, 
 se $M_{o1} \cap M_{i2} \neq \emptyset$ então $T_2$ {\em depende} de $T_1$. Se um programa $P$ está particionado em um 
@@
 
-\begin{definition} [Corretude]
+\begin{Definicao} [Corretude]
 \label{def:corretude}
@@
 \end{compactenum}
-\end{definition}
+\end{Definicao}
 
@@
 \item \textsf{parallel}: compõe um time de \textit{threads}
-para executar uma região do programa marcada como paralela.
+para executar a região anotada.
 \item \textsf{single}: especifica uma região que deve ser executada
-por apenas uma \textit{thread} do time.
+por apenas uma \textit{thread}.
 \item \textsf{task}: cria uma nova tarefa.
-\item \textsf{taskwait}: define um ponto de sincronização para aquela
-região paralela.
+\item \textsf{taskwait}: define um ponto de sincronização.
 \end{compactitem}
@@
 \begin{compactitem}
-\item \textsf{default([shared/private])}: indica que a variável é compartilhada ou replicada
+\item \textsf{default([shared/private])}: indica se a variável é compartilhada ou replicada
 entre tarefas.
-\item \textsf{firstprivate($v$)}: indica que $v$ deve ser replicada entre tarefas e inicializada
-com o valor corrente no ponto de execução da anotação.
-\item \textsf{untied}: indica que uma tarefa não está associada firmemente à uma única \textit{thread},
-permitindo ao ambiente balancemanto e preempção.
+\item \textsf{untied}: indica se uma tarefa não está associada à uma única \textit{thread},
+permitindo ao ambiente balancemanto.
 \item \textsf{depend}($\mathit{in}/\mathit{out}/\mathit{inout}$): determina se um dado é lido, escrito
-ou ambos, efetivamente estabelecendo as dependências entre as tarefas.
+ou ambos, explicitando as dependências entre as tarefas.
 \item \textsf{if}({\em condição}): define uma condição para que aquela anotação seja executada.
@@
 Para produzir uma anotação que criará uma tarefa $T = (G, M_i, M_o)$,
-é necessário determinar as regiões de memória $M_i$ que $T$ lê, e as regiões
+deve-se determinar as regiões de memória $M_i$ que $T$ lê, e as regiões
 $M_o$ em que $T$ escreve. Para tal, recorre-se à análise de limites simbólicos.
 
- Por exemplo, a instrução \textsf{U[i] += V[i*N + j]}, na linha 9 da Figura~\ref{fig:ex_Regions}
+A instrução \textsf{U[i] += V[i*N + j]}, na linha 9 da Figura~\ref{fig:ex_Regions}
 contém dois acessos à memória: \textsf{U[i]} e
@@
 Portanto, uma anotação de tarefa deve considerar apenas a dependência de entrada, ou seja,
-o acesso à \textsf{V}. É por isso que a cláusula \textsf{depend} na linha 6 contém uma referência
+o acesso à \textsf{V}. A cláusula \textsf{depend} na linha 6 contém uma referência
 a essa região.
 
-\begin{definition} [Análise de Limites Simbólicos]
+\begin{Definicao} [Análise de Limites Simbólicos]
 \label{def:limites}
@@
 \]
-\end{definition}
+\end{Definicao}
 
-Símbolos de programa são nomes que não podem ser construídos como funções de
-outros nomes. Exemplos incluem variáveis globais, argumentos de função e valores retornados
-por funções externas. Análise de limtes simbólicos não é uma contribuição deste artigo. A técnica
-escolhida para as análises do {\Taskminer} é aquela implementada no compilador \dawn{} \cite{Mendonca17}.
-Para este trabalho, é apenas
-suficiente saber que essa implementação é sólida o suficiente para lidar com toda a linguagem C99, sempre termina
-e executa em tempo quadrático no número de variáveis do programa, no pior caso.
+Exemplos de símbolos de programa incluem variáveis globais, argumentos de função e retornos de
+funções externas. A técnica
+escolhida para as análises do {\Taskminer} é a mesma do compilador \dawn{} \cite{Mendonca17}.
+Essa implementação é sólida o suficiente para lidar com toda a linguagem C99, sempre termina
+e executa em tempo quadrático no número de variáveis do programa.
 
@@
 
-\begin{definition} [Grafo de Dependências]~\cite{Ferrante87}
+\begin{Definicao} [Grafo de Dependências (PDG)]~\cite{Ferrante87}
 \label{def:pdg}
@@
 a execução de $s_2$ a partir do resultado de um \textit{branch}, por exemplo.
-\end{definition}
+\end{Definicao}
 
@@
 
-\begin{definition} [Moinho]
+\begin{Definicao} [Moinho]
 \label{def:moinho}
@@
 
-A Figura ~\ref{fig:ex_windmill} mostra dois grafos de dependências, bem como seus
-moinhos e hélices. A estrutura de moinhos naturalmente evidencia tarefas candidatas.
+A Figura ~\ref{fig:ex_windmill} mostra dois grafos de dependências e seus
+moinhos. A estrutura de moinhos naturalmente evidencia tarefas candidatas.
 Hélices correspondem à partes do programa que tem alta probabilidade de serem
 executadas diversas vezes, pois surgem de um laço: o centro do moinho. Duas execuções
-de uma mesma hélice podem ser paralelas. Esta é uma propriedade do grafo de dependências, e uma 
+de uma mesma hélice podem ser paralelas. Esta é uma propriedade do PDG, e uma 
 das motivações originais para este trabalho. Essas duas execuções podem ser vistas como duas instâncias
-da mesma estrutura: a hélice, partindo do mesmo centro do moinho. Uma ordenação topológica desse grafo não impõe
-nenhuma ordem entre essas duas hipotéticas réplicas de uma mesma hélice.
+da mesma estrutura: a hélice, partindo do mesmo centro do moinho. 
+Uma ordenação topológica desse grafo não impõe
+ordem entre as duas hipotéticas réplicas da mesma hélice.
 
-Moinhos contém propriedades estruturais para identificação de tarefas. Moinhos são encontrados
-em uma simples busca em profundidade no grafo de dependências. Entretanto, nem todo moinho
-evidencia tarefas proveitosas. Além disso, alguns moinhos não podem ser anotados devido à inabiliadde 
+Moinhos contém propriedades estruturais para identificação de tarefas e são encontrados
+em uma simples busca em profundidade no PDG. Entretanto, nem todo moinho
+evidencia tarefas boas. Ainda, alguns moinhos não podem ser anotados devido à inabiliadde 
 da análise de ponteiros em encontrar limites de acesso à memória. As próximas seções tratam desses
@@
 
-O benefício de criar tarefas depende de dois fatores: custo de execução e paralelismo.
-A dificuldade surge em encontrar o ponto mediano entre tarefas grandes demais e tarefas pequenas.
-Tarefas muito pequenas tendem a ser mais paralelas, pois tendem a ter menos dependências. Entretanto,
-se uma tarefa é muito pequena, então os ganhos de performance são eclipsados pelo custo do ambiente de execução
-em manter essa tarefa ativa, e o paralelismo extra não compensa o custo de gerenciamento desta tarefa.
-Por outro lado, se tarefas são muito grandes, então não há paralelismo: tarefas individuais executarão sequencialmente.
-{\Taskminer} marca como tarefa aquelas hélices que são maximais em termos de custo de execução, ou seja, as menores hélices
+O benefício de tarefas depende de dois fatores: custo de execução e paralelismo.
+A dificuldade surge em encontrar o ponto mediano entre tarefas grandes e tarefas pequenas.
+Tarefas muito pequenas são mais paralelas, pois tendem a ter menos dependências. 
+Entretanto, se uma tarefa é muito pequena, 
+então os ganhos de performance são eclipsados pelo custo do ambiente de execução
+em manter essa tarefa ativa, e o paralelismo extra não compensa.
+Por outro lado, se tarefas são muito grandes, então não há paralelismo: 
+tarefas individuais executarão sequencialmente.
+{\Taskminer} marca como tarefa as hélices que são maximais 
+em termos de custo de execução, ou seja, as menores hélices
 que estão acima do custo de execução no ambiente escolhido.
 
-O tamanho de uma tarefa é dado pelo número de instruções contidas na mesma. A mesma região de um programa
-pode levar à criação de tarefas com tamanhos diferentes. Portanto, o tamanho real de uma tarefa só é conhecido ao final 
-da execução da mesma. Entretanto, para julgar se acriação de uma tarefa vale a pena, é necessário aproximar esse tamanho
-estaticamente. Com esse objetivo em mente, define-se a noção de {\em Trabalho Estatico Estimado}:
+O tamanho de uma tarefa é dado pelo seu número de instruções. A mesma região de um programa
+pode levar à criação de tarefas com tamanhos diferentes. 
+Portanto, o tamanho real de uma tarefa só é conhecido ao final 
+de sua execução. Para julgar a rentabilidade de uma tarefa,
+deve-se aproximar esse tamanho
+estaticamente. Assim, define-se a noção de {\em Trabalho Estatico Estimado}:
 
@@
 O objetivo é obter um $W$ próximo ao comportamento dinâmico dos programas.
-A heurística mais conhecida na literatura para a proximação de $W$ é o 
-\textit{profiler} estático implementado por Wu e Larus~\cite{Wu94}.
 A heurística escolhida para este trabalho utiliza a análise de limites
-descrita na Seção \ref{sub:sra} para inserir informações dinâmicas em ambiente estático,
+descrita na Seção \ref{sub:sra} para inserir informações dinâmicas estaticamente,
 através da construção de expressões simbólicas que representam o número de iterações
-de laços, similar à técnica implantada para migração de memória virtual em arquiteturas NUMA
-\cite{Piccoli14}. Essas expressões são inseridas em condicionais para a criação da
-tarefa, como ilustrado na linha 7 da Figura \ref{fig:ex_Regions}.
+de laços. Essas expressões são inseridas em condicionais para a criação da
+tarefa, como na linha 7 da Figura \ref{fig:ex_Regions}.
 
@@
 cobertos pelo código em $S$ que controla o número de iterações do laço.
-Essas regras são implementadas durante o passo de estimativa da lucratividade.
 
 \paragraph{O Modelo de Custo.}
+O {\Taskminer} recebe um modelo de custo como parâmetro.
 Um modelo de custo é uma coleção de parâmetros que determinam o impacto
@@
 A literatura lista técnicas analíticas e empíricas~\cite{Poesia17}
-para a construção do modelo. Um modelo de custo automático não é o objetivo deste trabalho.
-Pelo contrário, o algoritmo do {\Taskminer} recebe um modelo de custo como parâmetro.
+para a construção do modelo. 
 Para os experimentos descritos na Seção ~\ref{sec:eval}, utilizou-se constantes
@@
 um grafo hammock $H$ que corresponde a uma hélice em um moinho $W$.
-A decomposição hammock de um programa estruturado forma uma árvore~\cite{Ferrante87},
+A decomposição hammock de um programa estruturado é uma árvore~\cite{Ferrante87},
 em que os vértices representam grafos hammock.
@@
 As hélices que surgem desses moinhos estão evidenciadas na Figura~\ref{fig:ex_expansion} (b).
-Na Figura, há 3 tarefas candidatas, cada uma formada por uma hélice diferente.
-Para encontrar as tarefas, aplica-se a função de expansão (Fig.~\ref{fig:expand_alg})
+Na Figura, há 3 tarefas candidatas, cada uma formada por uma hélice.
+Para encontrá-las, aplica-se a função de expansão (Fig.~\ref{fig:expand_alg})
 nas hélices mais internas: \textsf{Hélice-2} pode ser expandida para incluir \textsf{Hélice-3}.
@@
 da Seção~\ref{sub:profit}. Se a lucratividade é menor que este custo, então
-a criação da tarefa não é desejável. Porém, se a tarefa é expandida demais, 
+a criação da tarefa não é desejável. Se a tarefa é expandida demais, 
 há perda de paralelismo: o código executa sequencialmente. Portanto, determinar o \textsf{CUSTO}
@@
 
-As análises descritas até agora foram implementadas na representação intermediária
-do LLVM devido à facilidade do uso de análises como evolução escalar~\cite[p.18]{Grosser12} e outras
-análises de fluxo de dados.
+As análises deste artigo foram implementadas na representação intermediária (R.I.)
+do LLVM devido à facilidade do uso de análises como evolução escalar~\cite[p.18]{Grosser12} e outras.
 Porém, as anotações são inseridas em código fonte C, então grande
-parte deste trabalho foi o mapeamento de informações da representação intermediária do LLVM de volta
+parte deste trabalho é o mapeamento de informações da R.I. do LLVM de volta
 para código C.
@@
 \textsf{while} e \textsf{if-then-else}. Cada nó nesta árvore contém {\em meta-dados}
-provenientes de informação de depuração obtida durante a compilação para representação
-intermediária do LLVM. Para manter esse tipo de informação de depuração, basta compilar o código com a flag
-{\em -g}.
+provenientes de informação de depuração obtida durante a compilação para R.I.
 É possível achar o número da linha relacionada à cada nó na árvore de escopos, permitindo
@@
 \paragraph{Limitando a criação de tarefas recursivas}
-Para evitar a criação excessiva de tarefas muito pequenas, {\Taskminer} concede a opção
+Para evitar a criação excessiva de tarefas pequenas, {\Taskminer} dá a opção
 aos usuários de limitar a criação de tarefas. Por exemplo \textsf{./Taskminer -r 12} limita o número
-de tarefas criadas um total de 12 tarefas. Essa solução é implementada diretamente no código-fonte,
-na fase final. Embora simples, conforme experimentos (Sec.~\ref{sec:eval}), essa solução traz claros
-benefícios em benchmarks recursivos. A variável, chamada de \textsf{taskminer\_depht\_cutoff} na Figura
-\ref{fig:ex_cutoff}, é global e ligada estaticamente no programa. No começo de cada função recursiva,
-esta variável é incrementada para indicar a criação de uma nova tarefa; e decrementada ao sair da mesma função.
+de tarefas criadas a um total de 12 tarefas. Essa solução é implementada na fase de anotação. 
+Essa solução traz claros benefícios em benchmarks recursivos. 
+A variável, chamada de \textsf{taskminer\_depht\_cutoff} na Figura
+\ref{fig:ex_cutoff}, é global e ligada estaticamente. 
+No começo de cada função recursiva,
+esta variável é incrementada para indicar a criação de uma nova tarefa; 
+e decrementada ao sair da função.
+A Figura~\ref{fig:ex_cutoff} ilustra a limitação de tarefas 
+durante invocação recursiva.
+O parâmetro \textsf{PROFUNDIDADE\_MAX}
+é determinado pelo usuário.
 
-\begin{example}[Limitação de tarefas]
-A Figura~\ref{fig:ex_cutoff} ilustra a limitação de tarefas criadas durante a invocação de uma
-função recursiva.
-O parâmetro \textsf{PROFUNDIDADE\_MAX} é determinado pelo usuário.
-\end{example}
-
+Embora simples, a medida implementada é genérica o suficiente para lidar com 
+tarefas difíceis de se
+limitar simbolicamente. 
 Há outras formas de limitar o número de tarefas recursivas~\cite{Iwasaki16}.
-Porém, o trabalho de estimar funções recursivas é muito difícil e não é o foco deste trabalho.
-Portanto, embora simples, essa medida é genérica o suficiente para lidar com tarefas difíceis de se
-limitar simbolicamente. Como trabalho futuro, pretende-se explorar melhores maneiras de
-limitar tarefas extremamente pequenas.
+Futuramente, 
+pretende-se explorar melhores maneiras de
+limitar criação de tarefas pequenas.
 
@@
 
-O {\Taskminer} foi implementado em LLVM 3.9. Todos os experimentos
-foram executados em uma máquina de 12 núcleos 64-bits Intel(R) Xeon(R) CPU E5-2620, 2.00GHz, com 32K de cache L1, 256K de cache L2 e 15M de cache L3, e 15Gb de memória RAM.
-Utilizou-se OpenMP 4.5, lançado em
-Novembro de 2015.
+{\Taskminer} foi implementado em LLVM 3.9. Os experimentos
+foram executados em uma máquina de 12 núcleos 64-bits Intel(R) Xeon(R) CPU E5-2620, 2.00GHz, com 32K de cache L1, 256K de cache L2 e 15M de cache L3, e 15Gb de memória RAM. Utilizou-se OpenMP 4.5.
 
@@
 \caption{Comparações de performance. Anotações automáticas comparam-se favoralmente a intervenções
-manuais, e levam à ganhos de desempenho. O eixo Y mostra o ganho de desempenho de cada versão anotada
-pelo {\Taskminer} sobre a versão anotada manualmente. Os números nas pequenas caixas representam
-o crescimento em velocidade obtido pelo {\Taskminer}.}
+manuais, e levam à ganhos de desempenho. No eixo y, ganho de desempenho de cada versão anotada
+pelo {\Taskminer} sobre a versão anotada manualmente. Os números nas caixas representam
+o crescimento em velocidade obtido.}
 \label{fig:TM_Performance}
@@
 pelo {\Taskminer} contra versões originais dos mesmos programas anotados manualmente.
-Os {\em benchmarks} utilizados neste experimento são do \textsf{BSC-Bots}~\cite{Duran09} (\textsf{fft} até \textsf{jacobi}
-na Fig.~\ref{fig:TM_Performance}) e do \textsf{Swan}~\cite{Moreira17}
-(\textsf{dfs} até \textsf{private}).
+Os {\em benchmarks} utilizados neste experimento são do \textsf{BSC-Bots}~\cite{Duran09} 
+e do \textsf{Swan}~\cite{Moreira17}.
 Ambos vem com versões sequenciais e paralelas (anotadas manualmente). Os códigos foram compilados
@@
  \textsf{knapsack} (Problema da Mochila) e \textsf{fft}. Em 6 deles, as versões automáticas foram próximas e até
-levemente acima das versões anotadas manualmente. Em 3 exemplos \Taskminer{} produziu versões piores que
-as versões sequenciais: \textsf{fib}, \textsf{floorplan} e \textsf{bell-ford}. Entretanto, ainda assim produziu versões
-mais rápidas que as anotadas manualmente. Uma inspeção visual de \textsf{bell-ford} indica que a versão
+levemente acima das versões anotadas manualmente. Em 3, \Taskminer{} produziu versões piores que
+as versões sequenciais: \textsf{fib}, \textsf{floorplan} e \textsf{bell-ford}. Ainda assim, produziu versões
+mais rápidas que as anotadas manualmente. Uma inspeção de \textsf{bell-ford} indica que a versão
 paralelizada manualmente dispara um número grande tarefas pequenas. O modelo de custo
@@
 
-Este artigo descreve duas formas de otimizar a criação de tarefas. Ambas são baseadas na ideia de 
-``poda de tarefas": evita-se a criação de tarefas consideradas não-lucrativas. A primeira técnica
-corta criação de tarefas ditas não lucrativas de acordo com o modelo de custo, conforme explicado na 
-Seção~\ref{sub:profit}; a segunda técnica corta criação de tarefas muito profundas na pilha de recursão, 
+Ambas as formas de 
+otimizar a criação de tarefas descritas neste artigo são baseadas na ideia de 
+``poda": evita-se a criação de tarefas consideradas não-lucrativas. 
+Limita-se a criação de tarefas ditas não lucrativas de acordo com o modelo de custo, 
+conforme explicado na 
+Seção~\ref{sub:profit}; e limita-se a criação de tarefas muito profundas na pilha de recursão, 
 como descrito na Seção~\ref{sub:ir}. A Figura~\ref{fig:Optimizations} ilustra os benefícios dessas duas técnicas,
-presentes em 6 dos benchmarks vistos anteriormente na Figura~\ref{fig:TM_Performance}.
+presentes em 6 dos benchmarks vistos anteriormente (sec ~\ref{sub:performance}).
 
@@
 
-Similarmente, a limitação de tarefas recursivas (Sec.~\ref{sub:ir}), embora simples,
-é efetiva em eliminar o excesso de tarefas pequenas. A Figura~\ref{fig:Optimizations} mostra o efeito
-dessa otimização em três programas: \textsf{health}, \textsf{nqueens} e
+A limitação de tarefas recursivas (Sec.~\ref{sub:ir}), embora simples,
+é efetiva em eliminar o excesso de tarefas pequenas. 
+A Figura~\ref{fig:Optimizations} mostra esse impacto em três programas: \textsf{health}, \textsf{nqueens} e
 \textsf{strassen}. Estes programas foram projetados para ilustrar paralelismo
-em paradigma Dividir \& Conquistar ~\cite{Duran09}, e contém um grande número de chamadas
-recursivas. A poda em níveis mais altos da árvore de recursão leva a ganhos de desempenho consideráveis
-nestes programas. Caso não houvesse essa otimização de poda, então perda de desempenho seria observada
-em  \textsf{health} e \textsf{nqueens}. Este experimento prova que as otimizações são efetivas
-para melhorar a qualidade do código gerado pelo \Taskminer{}.
+em paradigma Dividir \& Conquistar, e contém muitas chamadas
+recursivas. A poda em níveis mais altos da árvore de recursão leva a bons ganhos de desempenho. 
+Caso não houvesse essa otimização de poda, então perda de desempenho seria observada
+em  \textsf{health} e \textsf{nqueens}, provando que as otimizações são eficazes e melhoram
+a qualidade do código gerado pelo \Taskminer{}.
 
@@
 paralelismo irregular. Para determinar se o \Taskminer{} consegue encontrar paralelismo 
-em programas comuns, executou-se o mesmo sobre 219 programas escritos em C disponíveis
+em programas comuns, executou-se o mesmo sobre 219 programas C disponíveis
 na suíte de testes do LLVM, e comparou-se o desempenho da versão anotada automaticamente pelo
@@
 (ii) a hélice é ampla o suficiente para pagar pelo custo de criação de tarefas no ambiente de execução.
-Sob essas circunstâncias, descobriu-se tarefas em 63 desses programas. A Figura~\ref{fig:TM_Versatility} relaciona
+Sob esses termos, descobriu-se tarefas em 63 desses programas. A Figura~\ref{fig:TM_Versatility} relaciona
 o número de tarefas ao número de instruções em 30 dos maiores programas utilizados.
-Para evitar a contagem de múltiplos arquivos C para o mesmo benchmark, a Figura~\ref{fig:TM_Versatility} contém
-somente benchmarks que consistem em arquivos {\em single-source}. Como demonstrado neste experimento,
+Como demonstrado neste experimento,
 \Taskminer{} é capaz de anotar um número não trivial de benchmarks reais.
@@
 
-Observa-se que 27 dos benchmarks anotados não demonstraram aumento de desempenho em 
+Dos benchmarks anotados, 27 não demonstraram aumento de desempenho em 
 relação à versão sequencial,
-pois as tarefas anotadas eram demasiadamente pequenas e pouco influenciaram na execução total do programa.
-Em 17 benchmarks, observou-se uma perda de velocidade: neste caso, interações entre estruturas de dados
-forçaram ao ambiente de execução do OpenMP a serizalizar a execução das tarefas. Essas perdas foram 
-inferiores à 10\%. Em um dos casos, \textsf{MiBench/office-stringsearch}, a versão paralela foi 11 vezes mais lenta.
-Por outro lado, obteve-se aumento de desempenho acima de 5\% em 19 benchmarks. 
-Em \textsf{Misc/lowercase}, o acréscimo de velocidade foi acima de 3.5x, e em 3 casos, acima de 1.5x.
+pois as tarefas anotadas eram muito pequenas e pouco influenciaram na execução total do programa.
+Em 17 deles, observou-se perda de velocidade: neste caso, interações entre estruturas de dados
+forçaram ao ambiente de execução do OpenMP a serizalizar a execução das tarefas. 
+Essas perdas foram 
+inferiores à 10\%.
+
+Obteve-se aumento de desempenho acima de 5\% em 19 programas. 
+Em \textsf{Misc/lowercase}, o fator de crescimento foi acima de 3.5x, e em 3 casos, acima de 1.5x.
 A Figura~\ref{fig:TM_GeneralProgs} mostra os 10 maiores acréscimos de desempenho obtidos pelo \Taskminer{}.
-É importante enfatizar que esse experimento {\em não contou com nenhum tipo de intervenção humana}.
+Enfatiza-se que esse experimento {\em não contou com nenhum tipo de intervenção humana}.
 Portanto, \Taskminer{} é capaz de encontrar paralelismo automaticamente sem custo de programação.
@@
 
-Compiladores modernos adicionaram suporte ao paralelismo de tarefas do OpenMP apenas recentemente. Uma implementa-\c{c}\~{a}o
-do compilador \textsf{clang} com esse suporte foi lançado em Março de 2014, por exemplo. Uma vez que a infra-estrutura necessária para
-a implementação de tarefas é nova, não existem ferramentas além do {\Taskminer} capazes de anotar programas
-automaticamente com essas diretivas.
-Padrões de anotação baseados em diretivas provém aos programadores um modelo de programação paralela prático e fácil. Exemplos
+Compiladores modernos adicionaram suporte ao paralelismo de tarefas 
+do OpenMP apenas recentemente. 
+Uma vez que a infra-estrutura necessária para
+a implementação de tarefas é nova, não existem ferramentas 
+além do {\Taskminer} capazes de anotar programas
+automaticamente com diretivas. Exemplos
 de modelos que permitem paralelismo de tarefas são OpenMP 4.X,
@@
 Por exemplo, Tareador \cite{Ayguade15} apresenta uma interface gráfica para identificação de potencial paralelismo e anotação de código sequencial.
-Ao contrário do Tareador, {\Taskminer} executa essa tarefa automaticamente.
 
 A técnica utilizada pelo {\Taskminer} para identificação de tarefas se assemelha às análises usadas durante
-geração de código para máquinas de fluxo de dados. Programação de fluxo de dados foi originalmente proposta 
-para facilitar paralelismo de tarefas~\cite{gupta:micro:2011}. Agrawal et al. \cite{agrawal:ipdps:2010} extendeu esse modelo
-com inputs e outpus em Cilk++, que foi extendido novamente ~\cite{vandierendonck:hotpar:2011} 
-com cláusulas de dependência para facilitar
-o projeto de padrões complexos de paralelsimo. Ambos apresentaram um escalonador unificado
-baseado em paralelismo \textit{fork-join} que permitiu
-a execução de aplicações baseadas em tarefas. Outras abordagens também utilizaram grafos
+geração de código para máquinas de fluxo de dados. Muitas abordagens utilizaram grafos
 de fluxo de dados para explorar paralelismo, como Tarefas Movidas à Dados \cite{tasirlar:icpp:2011},
@@
 para utilizar argumentos de funções como especificadores de dependências entre tarefas.
-Entretanto, a mineração e inserção automática dessas diretivas não consta como objetivo
-em nenhum desses trabalhos.
 
 Muitos sistemas foram desenvolvidos para extrair paralelismo de tarefas a partir de código sequencial.
-Exemplos incluem OSCAR, Multigrain Parallelizing
-Compiler \cite{kasahara:iwlcpc:2000},  MAPS \cite{ceng:dac:2008}, e
-DiscoPoP \cite{discopop, li:jss:2016}. Ferramentas como Paraver \cite{paraver},
-Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, e TEMANEJO
-\cite{brinkmann:parco:2011} foram implementadas para 
-permitir análise de desempenho e visualização de programas baseados em tarefas.
-Apesar de ajudar o programar a adaptar o código paralelo, essas ferramentas não são 
-inteiramente automáticas como o {\Taskminer}.
+Entretanto, a mineração e inserção automática dessas diretivas não consta como objetivo
+em nenhum desses trabalhos, e \Taskminer{} segue como primeira ferramenta capaz 
+de anotar código como paralelo
+automaticamente de maneira correta.
 
@@
 
+Este trabalho apresentou \Taskminer{}, uma ferramenta capaz de identificar automaticamente oportunidades de paralelismo de tarefas e anotá-las com diretivas OpenMP.
+\Taskminer{} implementa algoritmos de análise de código em representação intermediária do LLVM e contorna problemas clássicos no paralelismo irregular.
+Apesar das dificuldades, \Taskminer{} prova-se eficiente e competitivo, sendo capaz de anotar programas não triviais e encontrar paralelismo escondido sem custo adicional.
+
+Entretanto, ainda falha quando não consegue analisar os limites de memória estaticamente.
+Além disso, \Taskminer{} implementa uma heurística simples demais para estimar o custo de uma tarefa, que não é firme o suficiente para garantir a lucratividade de uma anotação.
+Como trabalho futuro, pretende-se implementar heurísticas de estimativa de custo que sejam mais precisas, para refinar o algoritmo do \Taskminer{}.
+
 \bibliography{references}

### 2018-05-23 docs/SBLP/paper.tex
Changing the conclusion of the paper a bit.

@@
 
-Entretanto, ainda falha quando não consegue analisar os limites de memória estaticamente.
-Além disso, \Taskminer{} implementa uma heurística simples demais para estimar o custo de uma tarefa, que não é firme o suficiente para garantir a lucratividade de uma anotação.
+Embora já possa ser usado em produção de código paralelo, \Taskminer{} ainda apresenta espaço
+para melhorias.
+Em particular, \Taskminer{} implementa uma heurística simples demais para estimar o custo de uma tarefa.
+Dada a sua simplicidade, essa heurística não é firme o suficiente para garantir a lucratividade de uma anotação.
 Como trabalho futuro, pretende-se implementar heurísticas de estimativa de custo que sejam mais precisas, para refinar o algoritmo do \Taskminer{}.

### 2018-06-05 docs/ACM/Rebuttal.txt
Adding reviews and rebuttal.

We thank the referees for all the time and expertise they have put into reviewing our work. We address individual comments below.

Review #124A

> The example in Figure 3 shows some limitations of the proposed
> TaskMiner approach as currently implemented. In particular, the
> generated code uses the if clause on the OpenMP task construct to
> limit generation of tasks. However, the if clause merely leads to the
> generation of an undeferred task. While the task must be executed
> immediately, most of the overheads of OpenMP task generation are still
> implied. In particular, the implementation must create a new data
> environment for the task. The correct way to end the task generation
> requires the use of the final clause, which leads to tasks that are
> mergeable and thus can be merged tasks, for which a data environment
> does not need to be created.

We agree with the referee: final tasking is a definitely better solution. However, none of the two compilers that we use support 'final+mergeable' (gcc and clang): they recognize the pragmas, but do not generate code for them. The 'if' clause is a temporary solution. Although not ideal, it brings noticeable runtime improvement. Fibonacci, our example in Figure 3 is 16x faster to calculate "fib 40" with the conditional pragma plus the task cutoff. Notice that our cost model already prevents the annotation of very small program regions.

> The authors do not discuss the restrictions of the depend clause on
> OpenMP Task constructs. In particular, "List items used in depend
> clauses of the same task or sibling tasks must indicate identical
> storage locations or disjoint storage locations." The implementation
> does not appear to consider this restriction so it is unclear if the
> automatically generated OpenMP tasking code is correct. This issue is
> significant as the proposed implementation may yield significantly
> higher parallelism as most OpenMP implementations only enforce
> dependencies based on the base address of an array section and will
> not detect that the restriction is violated (let alone enforce the
> intended dependences).

We consider the restriction on list items! We follow Section 2.13.9 of the standard. Even more, we only annotate a region if we can find symbolic limits for all the memory accesses used within that region. This restriction means that we only annotate arrays if we can determine their sections correctly. Another restriction is that a region must be profitable (see Page 10, Line 34, Column 1). Given these two restrictions, we found "annotable regions" in 63 out of 219 benchmarks in the LLVM test suite. All these benchmarks have sanity checks to certify correct behavior.

> Cilk++ is not annotation based. It's inclusion in the list of
> annotation systems in the first sentence of the introduction is
> incorrect.

The referee is right, and we shall fix the text.

> The default clause cannot be specified with the private parameter in C
> and C++. The private and firstprivate parameters are only permitted in
> Fortran.

We believe the referee refers to Page 4, Line 38, Column 2, where we wrote: "default([shared/private])". That was a bad way to write it. We do use private and firstprivate, but never within default. We shall fix that.

> The y-axis on Figure 10 needs to be labeled. What does the graph show?
> Runtime in seconds? Speedup? Compared to what? I think it is speedup
> compared to the sequential version of the program but it should be
> clearly indicated.

Yes, the referee's intuition is correct. We shall add labels to the figures.

> Including "bel-ford" as one of the three programs that most benefits
> from your cost model is not convincing since it appears to suffer from
> slowdown compared to the sequential version. That manual annotations
> provide even worse performance is irrelevant. Why doesn't your cost
> model determine that using tasks at all is a bad idea?

Some of the programs that we annotate do experiment slowdowns. That's a bit like compiling with gcc -O3, for instance: this optimization level slows downs some programs. The problem with bellman-ford, in particular, is not due to the cost model. This algorithm traverses a graph implemented as an array of arrays. The graph is not sparse, and dependences hinder parallelism. Actually dependences happen whenever two threads try to update the adjacent list of the same node. We experimented similar problems with other benchmarks that work with meshes of pointers (see Page 10, Line 53, Column 1).

Review #124B

> Comparing against manual parallel implementation makes sense, but I
> would appreciate to see alternative approaches as well (even ICC would
> at least give an idea).

We are comparing against gcc -O3, so, some of the benchmarks are vectorized by the compiler. The Swan benchmarks were taken from the Intel SPMD compiler. Thus, we can compare against them, if the referee wants. Notice that each one of these benchmarks is written in C and in SPMD. Only the latter is parallelized by ISPC (using vector instructions).

> In the evaluation section I would appreciate to see an evaluation of
> the cost model used in this work.

Figure 11 presented an evaluation in three benchmarks. We also would like to show numbers about some tuning of it. We did not do it due to lack of space, but we might include these results if we have one more page.

Review #124C

> Another thing that was not clear
> to me unless I miss something is how the algorithm determines where
> spawned tasks will be synchronized. The paper discusses how to find
> "program statements that can run in parallel with the rest of the
> program" (section 3.2), yet this notion is relative to when they
> synchronize with the rest of the program.

Yes, we acknowledge that we could have described it better. We use basically the same technique that nvcc uses to insert implicit barriers in programs: we synchronize at the post dominator of each parallel region.

### 2018-06-05 docs/ACM/Rebuttal.txt
Adding rebuttal.

@@
 
-> The example in Figure 3 shows some limitations of the proposed
-> TaskMiner approach as currently implemented. In particular, the
-> generated code uses the if clause on the OpenMP task construct to
-> limit generation of tasks. However, the if clause merely leads to the
-> generation of an undeferred task. While the task must be executed
-> immediately, most of the overheads of OpenMP task generation are still
-> implied. In particular, the implementation must create a new data
-> environment for the task. The correct way to end the task generation
-> requires the use of the final clause, which leads to tasks that are
-> mergeable and thus can be merged tasks, for which a data environment
-> does not need to be created.
+> The example in Figure 3 shows some limitations of the proposed TaskMiner approach as currently implemented.
+The generated code uses the if clause on the OpenMP task construct to limit generation of tasks.
+However, the if clause leads to the generation of an undeferred task.
+While the task must be executed immediately, most of the overheads of OpenMP task generation are still implied.
+The implementation must create a new data environment for the task.
+The correct way to end the task generation requires the use of the final clause, which leads to tasks that are mergeable and thus can be merged tasks, for which a data environment does not need to be created.
 
-We agree with the referee: final tasking is a definitely better solution.
-However, none of the two compilers that we use support 'final+mergeable' (gcc and clang): they recognize the pragmas, but do not generate code for them.
-The 'if' clause is a temporary solution.
-Although not ideal, it brings noticeable runtime improvement.
+We agree with the referee: final tasking is a better solution than conditional tasking.
+However, gcc-6 does not support 'final+mergeable': it recognizes the pragmas, but does not generate code for them.
+Notice that although not ideal, the 'if' clause is not incorrect, and it brings runtime improvement because it avoids checking dependences.
 Fibonacci, our example in Figure 3 is 16x faster to calculate "fib 40" with the conditional pragma plus the task cutoff.
-Notice that our cost model already prevents the annotation of very small program regions.
+Notice also that our cost model already prevents the annotation of very small program regions.
 
-> The authors do not discuss the restrictions of the depend clause on
-> OpenMP Task constructs. In particular, "List items used in depend
-> clauses of the same task or sibling tasks must indicate identical
-> storage locations or disjoint storage locations." The implementation
-> does not appear to consider this restriction so it is unclear if the
-> automatically generated OpenMP tasking code is correct. This issue is
-> significant as the proposed implementation may yield significantly
-> higher parallelism as most OpenMP implementations only enforce
-> dependencies based on the base address of an array section and will
-> not detect that the restriction is violated (let alone enforce the
-> intended dependences).
+> The authors do not discuss the restrictions of the depend clause on OpenMP Task constructs.
+"List items used in depend clauses of the same task or sibling tasks must indicate identical storage locations or disjoint storage locations." The implementation  does not appear to consider this restriction so it is unclear if the automatically generated OpenMP tasking code is correct.
+This issue is significant as the proposed implementation may yield significantly higher parallelism as most OpenMP implementations only enforce  dependencies based on the base address of an array section and will not detect that the restriction is violated (let alone enforce the intended dependences).
 
@@
 This restriction means that we only annotate arrays if we can determine their sections correctly.
+Also, whenever we annotate different sections within the same array, these sections are disjoint per task.
 Another restriction is that a region must be profitable (see Page 10, Line 34, Column 1).
@@
 
-> Cilk++ is not annotation based. It's inclusion in the list of
-> annotation systems in the first sentence of the introduction is
-> incorrect.
+> The approach should be able to generate taskloop and taskgroup constructs. Their addition of would significantly increase the overall contribution.
 
-The referee is right, and we shall fix the text.
+We agree, and we are working to accommodate task grouping.
 
-> The default clause cannot be specified with the private parameter in C
-> and C++. The private and firstprivate parameters are only permitted in
-> Fortran.
+> Cilk++ is not annotation based. It's inclusion in the list of  annotation systems in the first sentence of the introduction is incorrect.
+
+We shall fix the text.
+
+> The default clause cannot be specified with the private parameter in C and C++. The private and firstprivate parameters are only permitted in Fortran.
 
@@
 We shall fix that.
+Notice that in Page 8, Line 12, Column 1, we explain that 'shared' is the only default.
 
-> The y-axis on Figure 10 needs to be labeled. What does the graph show?
-> Runtime in seconds? Speedup? Compared to what? I think it is speedup
-> compared to the sequential version of the program but it should be
-> clearly indicated.
+> The y-axis on Figure 10 needs to be labeled. What does the graph show? I think it is speedup compared to the sequential version of the program but it should be clearly indicated.
 
@@
 
-> Including "bel-ford" as one of the three programs that most benefits
-> from your cost model is not convincing since it appears to suffer from
-> slowdown compared to the sequential version. That manual annotations
-> provide even worse performance is irrelevant. Why doesn't your cost
-> model determine that using tasks at all is a bad idea?
+> Including "bel-ford" as one of the three programs that most benefits from your cost model is not convincing since it appears to suffer from slowdown compared to the sequential version.
+Why doesn't your cost model determine that using tasks at all is a bad idea?
 
-Some of the programs that we annotate do experiment slowdowns.
-That's a bit like compiling with gcc -O3, for instance: this optimization level slows downs some programs.
-The problem with bellman-ford, in particular, is not due to the cost model.
+Some of the programs that we annotate experiment slowdowns.
+That's like compiling with gcc-O3, for instance: it slows down some programs, while speeding up others.
+The problem with bellman-ford is not due to the cost model.
 This algorithm traverses a graph implemented as an array of arrays.
-The graph is not sparse, and dependences hinder parallelism.
-Actually dependences happen whenever two threads try to update the adjacent list of the same node.
+Dependences hinder parallelism.
+Dependences happen whenever two threads try to update the adjacent list of the same node.
 We experimented similar problems with other benchmarks that work with meshes of pointers (see Page 10, Line 53, Column 1).
@@
 
-> Comparing against manual parallel implementation makes sense, but I
-> would appreciate to see alternative approaches as well (even ICC would
-> at least give an idea).
+> Comparing against manual parallel implementation makes sense, but I would appreciate to see alternative approaches as well.
 
-We are comparing against gcc -O3, so, some of the benchmarks are vectorized by the compiler.
-The Swan benchmarks were taken from the Intel SPMD compiler.
+We are comparing against gcc-O3, which vectorizes some benchmarks.
+The Swan benchmarks were taken from the Intel SPMD compiler (ISPC).
 Thus, we can compare against them, if the referee wants.
-Notice that each one of these benchmarks is written in C and in SPMD.
+Each one of these benchmarks is written in C and in SPMD.
 Only the latter is parallelized by ISPC (using vector instructions).
 
-> In the evaluation section I would appreciate to see an evaluation of
-> the cost model used in this work.
+> In the evaluation section I would appreciate to see an evaluation of the cost model used in this work.
 
-Figure 11 presented an evaluation in three benchmarks.
-We also would like to show numbers about some tuning of it.
-We did not do it due to lack of space, but we might include these results if we have one more page.
+Figure 11 presented an evaluation in three benchmarks. We also would like to show numbers about some tuning of it. We did not do it due to lack of space.
 
@@
 
-> Another thing that was not clear
-> to me unless I miss something is how the algorithm determines where
-> spawned tasks will be synchronized. The paper discusses how to find
-> "program statements that can run in parallel with the rest of the
-> program" (section 3.2), yet this notion is relative to when they
-> synchronize with the rest of the program.
+> How the algorithm determines where spawned tasks will be synchronized?
 
-Yes, we acknowledge that we could have described it better.
-We use basically the same technique that nvcc uses to insert implicit barriers in programs: we synchronize at the post dominator of each parallel region.
+We shall clarify it. We synchronize at the post dominator of each parallel region.
+
+Review #124D
+
+> The paper is well written, with clear motivation and easy to understand.
+The challenge with work like this is that while it provides a great tool with useful techniques, the chosen techniques by themselves are not very novel and therefore the insights generated may be limited.
+That said, the tool is quite valuable and the design and implementation of it will be useful to the community, especially when made available publicly.
+The paper will serve as a useful report of the workings and principles behind the tool but it is unclear whether the PACT audience will find it directly useful due to the limited novelty/insights.
+
+We thank the referee for the kind words.
+We agree that we are not providing any fundamentally new technique.
+We closed our paper with this remark: "This methodology does not introduce any fundamentally new static analysis or code optimization; in this field, we claim no contribution.
+Instead, our contributions lay into the overall design that eventually emerged from a two-years long effort to combine existing compilation techniques towards the goal of profiting from the powerful runtime system that OpenMP’s task parallelism brings forward".
+Thus, we would like to believe that PACT is the right community for our work, as it fits well the topic "Compilers and tools for parallel computer systems", which is available in the call for papers.

### 2018-06-06 docs/ACM/Rebuttal.txt
Adding rebuttal.

@@
 
-> The example in Figure 3 shows some limitations of the proposed TaskMiner approach as currently implemented.
+> The example in Fig-3 shows limitations of TaskMiner as currently implemented.
 The generated code uses the if clause on the OpenMP task construct to limit generation of tasks.
@@
 
-We agree with the referee: final tasking is a better solution than conditional tasking.
-However, gcc-6 does not support 'final+mergeable': it recognizes the pragmas, but does not generate code for them.
-Notice that although not ideal, the 'if' clause is not incorrect, and it brings runtime improvement because it avoids checking dependences.
-Fibonacci, our example in Figure 3 is 16x faster to calculate "fib 40" with the conditional pragma plus the task cutoff.
-Notice also that our cost model already prevents the annotation of very small program regions.
+We agree with the referee: 'final+mergeable' is better.
+Gcc did not support 'final' when we started the project (see, the last slide of https://openmp.org/wp-content/uploads/sc15-openmp-CT-MK-tasking.pdf).
+However, although not ideal, the 'if' clause is correct, and it brings runtime gains.
+We have moved into 'final' already (we use 'final' to limit recursion, and 'if' to implement the dynamic cost model).
+The fibonacci example in the paper finds the 40th fib number in:
+
+'omp-final': real=7.68s/user=14.25s;
+'omp-if': real=7.51s/user=37.48s;
+'omp+nothing, aka no-optimization': real=1m46.57s/user=11m16.72s
 
@@
 "List items used in depend clauses of the same task or sibling tasks must indicate identical storage locations or disjoint storage locations." The implementation does not appear to consider this restriction so it is unclear if the automatically generated OpenMP tasking code is correct.
-This issue is significant as the proposed implementation may yield significantly higher parallelism as most OpenMP implementations only enforce  dependencies based on the base address of an array section and will not detect that the restriction is violated (let alone enforce the intended dependences).
+This issue is significant as the proposed implementation may yield significantly higher parallelism.
 
-We consider the restriction on list items!
+We consider those restriction!
 We follow Section 2.13.9 of the standard.
-Even more, we only annotate a region if we can find symbolic limits for all the memory accesses used within that region.
-This restriction means that we only annotate arrays if we can determine their sections correctly.
-Also, whenever we annotate different sections within the same array, these sections are disjoint per task.
-Another restriction is that a region must be profitable (see Page 10, Line 34, Column 1).
-Given these two restrictions, we found "annotable regions" in 63 out of 219 benchmarks in the LLVM test suite.
-All these benchmarks have sanity checks to certify correct behavior.
+Even more, we only annotate a region if we can find symbolic limits for all the memory accesses used within it.
+We only annotate arrays if we can determine their sections.
+Whenever we annotate different sections within the same array, these sections are disjoint across tasks.
+Another restriction is that a region must be profitable (see Page10, Line34, Column1).
+Given these two restrictions, we found "annotable regions" in 63 out of 219 benchmarks in the test suite.
+Every benchmark contains sanity checks.
 
-> The approach should be able to generate taskloop and taskgroup constructs. Their addition of would significantly increase the overall contribution.
+> The approach should generate taskloop and taskgroup constructs.
 
@@
 
-> Cilk++ is not annotation based. It's inclusion in the list of  annotation systems in the first sentence of the introduction is incorrect.
+> Cilk++ is not annotation based. It's inclusion in the list in the introduction is incorrect.
 
-We shall fix the text.
+Ok.
 
-> The default clause cannot be specified with the private parameter in C and C++. The private and firstprivate parameters are only permitted in Fortran.
+> The default clause cannot be specified with the private parameter in C and C++.
 
-We believe the referee refers to Page 4, Line 38, Column 2, where we wrote: "default([shared/private])".
-That was a bad way to write it.
-We do use private and firstprivate, but never within default.
+We believe the referee refers to Page4, Line38, Column2, where we wrote: "default([shared/private])".
+That was bad writing.
+We use private and firstprivate, but never within default.
 We shall fix that.
-Notice that in Page 8, Line 12, Column 1, we explain that 'shared' is the only default.
+Notice that in Page8, Line12, Column1, we explain that 'shared' is the only default.
 
-> The y-axis on Figure 10 needs to be labeled. What does the graph show? I think it is speedup compared to the sequential version of the program but it should be clearly indicated.
+> The y-axis on Figure 10 needs a label. What does the graph show? I think it is speedup compared to the sequential version of the program.
 
-Yes, the referee's intuition is correct. We shall add labels to the figures.
+Yes, the referee's intuition is correct. We shall fix it.
 
 > Including "bel-ford" as one of the three programs that most benefits from your cost model is not convincing since it appears to suffer from slowdown compared to the sequential version.
-Why doesn't your cost model determine that using tasks at all is a bad idea?
+Why doesn't your cost model determine that using tasks is a bad idea?
 
@@
 This algorithm traverses a graph implemented as an array of arrays.
-Dependences hinder parallelism.
-Dependences happen whenever two threads try to update the adjacent list of the same node.
-We experimented similar problems with other benchmarks that work with meshes of pointers (see Page 10, Line 53, Column 1).
+Dependences hinder parallelism whenever two tasks receive the adjacent list of the same node.
+We experimented similar problems with other irregular benchmarks (see Page10, Line53, Column1).
 
@@
 
-> Comparing against manual parallel implementation makes sense, but I would appreciate to see alternative approaches as well.
+> Comparing against manual parallel implementation makes sense, but I would appreciate to see alternative approaches.
 
-We are comparing against gcc-O3, which vectorizes some benchmarks.
+We are comparing against gcc-O3, with vectorization enabled.
 The Swan benchmarks were taken from the Intel SPMD compiler (ISPC).
-Thus, we can compare against them, if the referee wants.
-Each one of these benchmarks is written in C and in SPMD.
+We can compare against them.
+However, each benchmark is written in C and in SPMD.
 Only the latter is parallelized by ISPC (using vector instructions).

### 2018-06-06 docs/ACM/Rebuttal.txt
Fixing one typo.

@@
 
-'omp-final': real=7.68s/user=14.25s;
-'omp-if': real=7.51s/user=37.48s;
+'omp+final': real=7.68s/user=14.25s;
+'omp+if': real=7.51s/user=37.48s;
 'omp+nothing, aka no-optimization': real=1m46.57s/user=11m16.72s
@@
 We follow Section 2.13.9 of the standard.
-Even more, we only annotate a region if we can find symbolic limits for all the memory accesses used within it.
-We only annotate arrays if we can determine their sections.
+We only annotate a region if we can find symbolic limits for all the memory accesses used within it.
 Whenever we annotate different sections within the same array, these sections are disjoint across tasks.
@@
 Every benchmark contains sanity checks.
+We will expand this discussion in the paper.
 
@@
 
-Figure 11 presented an evaluation in three benchmarks. We also would like to show numbers about some tuning of it. We did not do it due to lack of space.
+Figure 11 presented an evaluation in three benchmarks. We also would like to show numbers about some tuning of the cost model. We did not do it due to lack of space.
 

### 2018-06-06 docs/ACM/Rebuttal.txt
Adding comment for Ref 3.

@@
 
-> Including "bel-ford" as one of the three programs that most benefits from your cost model is not convincing since it appears to suffer from slowdown compared to the sequential version.
+> Including "bel-ford" as one of the programs that benefits from your cost model is not convincing since it suffers from slowdown compared to the sequential version.
 Why doesn't your cost model determine that using tasks is a bad idea?
 
-Some of the programs that we annotate experiment slowdowns.
-That's like compiling with gcc-O3, for instance: it slows down some programs, while speeding up others.
+TaskMiner is like compiling with gcc-O3, for instance: it slows down some programs, while speeding up others.
 The problem with bellman-ford is not due to the cost model.
@@
 
+> How the algorithm discovers accessed region of tasks involving recursive calls?
+
+We use an interprocedural dependence graph.
+
 > How the algorithm determines where spawned tasks will be synchronized?

### 2018-07-03 docs/SBLP/paper.tex
Fixed imgs on sblp paper

@@
 %% For double-blind review submission
-\documentclass[sigplan,10pt,review]{acmart}
+\documentclass[sigplan,10pt]{acmart}
 \settopmatter{printfolios=true}
@@
 %% Supplied to authors by publisher for camera-ready submission
-\acmConference[PL'17]{IEEE}{2018}{Planet Earh}
-\acmYear{2017}
+\acmConference[SBLP'18]{IEEE}{2018}{Brasil}
+\acmYear{2018}
 \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
@@
 }
-\email{[pedroramos, gleison, guilherme, fernando]@dcc.ufmg.br}
+\email{[pedroramos, gleison.mendonca, guilhermel, fernando]@dcc.ufmg.br}
 
@@
 como a delimitação simbólica de regiões de memória, remoção de dependências
-estáticas espúrias, detecção de condições de corrida, e principalmente avaliação do custo do paralelismo. Para solucioná-los,
+estáticas espúrias, detecção de condições de corrida, e, principalmente, a avaliação do custo do paralelismo. Para solucioná-los,
 \Taskminer{} implementa uma série de otimizações em representa\-ção intermediária do LLVM, que analisam código C e inserem anotações OpenMP automaticamente.
@@
 
-\ccsdesc[500]{Computing methodologies~Parallel programming languages}
-\ccsdesc[500]{Computing methodologies~Concurrent programming languages}
-\ccsdesc[500]{Software and its engineering~Compilers}
-
-\keywords{Parallelism, Tasks, OpenMP}
+\keywords{paralelismo, tarefas, OpenMP, compiladores}
 
@@
 desenvolvedores na busca por desempenho. Programadores tem, cada vez mais, investido
-em paradigmas paralelos, visando maior eficiência e velocidade. Nesse contexto, sistemas de
+em paradigmas paralelos visando maior eficiência e velocidade. Nesse contexto, sistemas de
 anotação como OpenMP~\cite{JaegerCP15} e
@@
 em programas sequênciais e anotá-los automaticamente. Como descrito na seção \ref{sec:ovf},
-essas anotações conferem ao programa irregular semântica de algoritmos em grafos e/ou \textit{worklists}~\cite{Pingali11}, paradigmas paralelos.
+essas anotações conferem ao programa irregular uma semântica de paradigmas paralelos,
+como aqueles em grafos e/ou em \textit{worklists}~\cite{Pingali11}.
 
@@
 fragmentos de código (laços ou funções) que podem 
-ser efetivamente mapeados à tarefas. Então, extrai parâmetros capazes
+ser efetivamente mapeados em tarefas. Então, extrai parâmetros capazes
 de estimar o custo da tarefa em questão. Esses parâmetros estão dinamicamente atrelados
@@
 ou de limitar a profundidade de tarefas geradas recursivamente. \Taskminer{} também determina
-quais variáveis serão replicadas em novas tarefas, ou compartilhadas por tarefas concorrentes.
+quais variáveis serão replicadas em novas tarefas ou compartilhadas por tarefas concorrentes.
 Finalmente, ele mapeia todas essas informações de volta ao código fonte, produzindo
@@
 processo de desenvolvimento mais eficiente. A ferramenta {\Taskminer} é capaz
-de alcançar ganhos de quase 4x em benchmarks não usualmente paralelos, como descrito em \ref{sec:eval}. {\Taskminer}
-recebe como input um programa escrito em C e produz como output um programa também em C,
+de alcançar ganhos de quase 4x em benchmarks não usualmente paralelos, como descrito na Seção \ref{sec:eval}. {\Taskminer}
+recebe como entrada um programa escrito em C e produz como saída um programa também em C,
 mas anotado com diretivas OpenMP legíveis. {\Taskminer} anota programas não triviais, envolvendo
-todo tipo de construto da linguagem C como arranjos, estruturas, uniões e ponteiros para esses tipos.
+todo tipo de construto da linguagem C, como arranjos, estruturas, uniões e ponteiros para esses tipos.
 Alguns desses programas provém de benchmarks complexos como Bots~\cite{Duran09}  e a coleção de testes do LLVM.
 As versões anotadas pelo {\Taskminer} se aproximam das versões anotadas manualmente em
-desempenho, e são mais rápidos que as versões sequenciais.
+desempenho e são mais rápidas que as versões sequenciais.
 
@@
 diretivas OpenMP. O ambiente de execução OpenMP se encarrega de 
-rastrear dependências entre ponteiros (~\cite{LaGrone11}). Entretanto, a inserção
+rastrear dependências entre ponteiros~\cite{LaGrone11}. Entretanto, a inserção
 automática das anotações é apenas a última etapa. Nesta Seção detalha-se os problemas
-encontrados pelo \Taskminer{} no percalço de mineração de tarefas. A solução para esses problemas será descrita 
-posteriormente na Seção~\ref{sec:sol}.
+encontrados pelo \Taskminer{} no percalço de mineração de tarefas. A solução para esses problemas é descrita na Seção~\ref{sec:sol}.
 
@@
 A Figura~\ref{fig:ex_Regions} ilustra esse problema e como resolvê-lo. O programa
-uma matriz \textsf{V}, $\mathsf{M}\times\mathsf{N}$, em formato linear,
+recebe uma matriz \textsf{V}, $\mathsf{M}\times\mathsf{N}$, em formato linear,
 e produz um vetor  \textsf{U} de forma que  \textsf{U[i]} contenha a soma de todos
@@
 grande o suficiente para superar este custo. A quantidade de trabalho executado
-por uma tarefa não pode ser descoberta estaticamente \cite{Rice53}. 
-É possível aproximar-se desse custo com
+por uma tarefa não pode ser descoberta estaticamente \cite{Rice53}. Contudo,
+é possível aproximar-se desse custo com
 símbolos nativos do programa, que, em execução, serão substituídos por valores. 
-Por exemplo, na figura~\ref{fig:ex_Regions}
-sabe-se o número de instruções do laço interno. Então aproxima-se a quantidade de trabalho executado
+Por exemplo, na Figura~\ref{fig:ex_Regions}
+sabe-se o número de instruções do laço interno. Então, aproxima-se a quantidade de trabalho executado
 com a expressão \textsf{5 * M}. O valor de \textsf{M} durante a execução será determinante para
-a criação da tarefa. Essa checagem é feita na linha 7 da figura, 
+a criação da tarefa. Essa checagem é feita na linha 7 do exemplo, 
 e faz parte da sintaxe de OpenMP. Além disso, {\Taskminer} propõe
@@
 \includegraphics[width=1\columnwidth]{images/ex_cutoff}
-\caption{limitando a criação de tarefas recursivas.
+\caption{Limitando a criação de tarefas recursivas.
 Exemplo retirado de~\cite[Fig.1]{Iwasaki16}.}
@@
 \textsf{PROFUNDIDADE\_MAX} e \textsf{CUSTO\_MIN}. 
-Ambos possuem valores padrão, mas são passíveis de configuração.
+Ambos possuem valores padrão, mas podem ser configurados pelo usuário.
 
@@
 
-A figura~\ref{fig:alg_main} descreve o algoritmo executado pela ferramenta {\Taskminer}. 
+A Figura~\ref{fig:alg_main} descreve o algoritmo executado pela ferramenta {\Taskminer}. 
 Ele utiliza conceitos  como
-o grafo de dependências~\cite{Ferrante87} e o 
+o grafo de dependências ~\cite{Ferrante87} e o 
 grafo de fluxo de controle~\cite{Kildall73}. {\Taskminer}
@@
 
-\begin{Definicao} [Região \textit{Hammock}]
+\begin{Definicao} [Região \textit{hammock}]
 \label{def:hammock}
 Um grafo de fluxo de controle $G$ é um grafo direcionado com um nó de entrada
-$s$ e um nó de saída $x$. Uma região \textit{hammock} $G'$ é um subgrafo de $G$ com um nó $h$ que {em domina}
+$s$ e um nó de saída $x$. Uma região \textit{hammock} $G'$ é um subgrafo de $G$ com um nó $h$ que {\em domina}
 \footnote{Um nó $n_1 \in G$ domina outro nó
-$n_2 \in G$ de todo caminho de  $S$ até $n_2$ atravessa $n_1$.
+$n_2 \in G$ se todo caminho de  $S$ até $n_2$ atravessa $n_1$.
 Inversamente, $n_1$ pós-domina $n_2$ se todo caminho de $n_2$ até $x$ deve passar por $n_1$.} os outros nós em $G$.
@@
 Em um programa $P$, uma tarefa $T$ é uma tupla $(G', M_i, M_o)$ formada
-por uma região \textit{hammock} $G'$ e dois conjuntos $M_i$ e $M_o$, dados de memória lidos e escritos por $T$ respectivamente.
+por uma região \textit{hammock} $G'$ e dois conjuntos $M_i$ e $M_o$, dados de memória lidos e escritos por $T$, respectivamente.
 \end{Definicao}
 
-Regiões de memória são descritas por variáveis do programa ou ponteiros com intervalos derefenciáveis.
+Regiões de memória são descritas por variáveis do programa ou ponteiros com intervalos derrefenciáveis.
 Sejam duas tarefas $T_1 = (G_1, M_{i1}, M_{o1})$ e $T_2 = (G_2, M_{i2}, M_{o2})$, 
@@
 
-{\Taskminer} utiliza OpenMP 4.0 para explorar o paralelismo de tarefas. Detalhes da sintaxe e semântica
-das anotações do OpenMP estão publicamente disponíveis\footnote{``Summary of OpenMP 4.0 C/C++ Syntax", disponibilizado
+{\Taskminer} utiliza OpenMP 4.5 para explorar o paralelismo de tarefas. Detalhes da sintaxe e semântica
+das anotações do OpenMP estão publicamente disponíveis\footnote{``Summary of OpenMP 4.5 C/C++ Syntax", disponibilizado
 pelo grupo OpenMP}. As anotações utilizadas são:
@@
 
-A instrução \textsf{U[i] += V[i*N + j]}, na linha 9 da Figura~\ref{fig:ex_Regions}
+A instrução \textsf{U[i] += V[i*N + j]} na linha 9 da Figura~\ref{fig:ex_Regions}
 contém dois acessos à memória: \textsf{U[i]} e
@@
 \begin{array}{rcl}
-E & ::= & z \ \ | \ \ s \ \ | E + E \ \ | \ \ E \times E \ \ | \ \  \mbox{min}(E, E) \ \ | \\
+E & ::= & z \ \ | \ \ s \ \ | \ \ E + E \ \ | \ \ E \times E \ \ | \ \  \mbox{min}(E, E) \ \ | \\
 &  & \mbox{max}(E, E) \ \ | -\infty \ \ | \ \ +\infty
@@
 
-\begin{Definicao} [Grafo de Dependências (PDG)]~\cite{Ferrante87}
+\begin{Definicao} [Grafo de Dependências (PDG) ~\cite{Ferrante87}]
 \label{def:pdg}
@@
 moinhos. A estrutura de moinhos naturalmente evidencia tarefas candidatas.
-Hélices correspondem à partes do programa que tem alta probabilidade de serem
+Hélices correspondem a partes do programa que tem alta probabilidade de serem
 executadas diversas vezes, pois surgem de um laço: o centro do moinho. Duas execuções
-de uma mesma hélice podem ser paralelas. Esta é uma propriedade do PDG, e uma 
+de uma mesma hélice podem ser paralelas. Esta é uma propriedade do PDG e também uma 
 das motivações originais para este trabalho. Essas duas execuções podem ser vistas como duas instâncias
@@
 
-Moinhos contém propriedades estruturais para identificação de tarefas e são encontrados
+Moinhos possuem propriedades estruturais para identifica-\c{c}\~{a}o de tarefas e são encontrados
 em uma simples busca em profundidade no PDG. Entretanto, nem todo moinho
-evidencia tarefas boas. Ainda, alguns moinhos não podem ser anotados devido à inabiliadde 
+evidencia tarefas rentáveis. Ainda, alguns moinhos não podem ser anotados devido à inabilidade 
 da análise de ponteiros em encontrar limites de acesso à memória. As próximas seções tratam desses
@@
 % Explain the tension between large and small tasks.
-\begin{definition}[Trabalho Estático Estimado (TEE)]
+\begin{Definicao}[Trabalho Estático Estimado (TEE)]
 \label{def:swe}
 Seja $G = G_1 \cup G_2 \cup \ldots \cup G_n$ uma partição de um grafo de controle
-de um $G$ em $n$ regiões hammock {\em disjuntas}.
+de um $G$ em $n$ regiões {\em hammock} {\em disjuntas}.
 Trabalho Estático Estimado ($W(G)$) é definido como um número real não negativo,
 tal que $W(G) = W(G_1) + W(G_2) + \ldots + W(G_n)$.
-\end{definition}
+\end{Definicao}
 
-O objetivo é obter um $W$ próximo ao comportamento dinâmico dos programas.
+O objetivo é obter um $TEE$ próximo ao comportamento dinâmico dos programas.
 A heurística escolhida para este trabalho utiliza a análise de limites
-descrita na Seção \ref{sub:sra} para inserir informações dinâmicas estaticamente,
+descrita na Seção \ref{sec:sra} para inserir informações dinâmicas estaticamente
 através da construção de expressões simbólicas que representam o número de iterações
@@
 \textsc{[Instr]} &
-W(\mbox{instr}) = \mbox{given by the spec.}
+W(\mbox{instr}) = \mbox{TEE, como especificado.}
 \\\\
@@
 As regras declarativas da Figura~\ref{fig:swe} esboçam as heurísticas
-utilizadas para computar o TEE para uma região hammock $S$.
+utilizadas para computar o TEE para uma região {\em hammock} $S$.
 A regra \textsc{LoopInf} aplica-se a laços cujo número de iterações não
@@
 Um modelo de custo é uma coleção de parâmetros que determinam o impacto
-da criação e manutenção de tarefas em uma determinada arquitetura.
-A literatura lista técnicas analíticas e empíricas~\cite{Poesia17}
-para a construção do modelo. 
+da criação e manuten-\c{c}\~{a}o de tarefas em uma determinada arquitetura.
+A literatura lista técnicas analíticas e empíricas
+para a construção do modelo~\cite{Poesia17}. 
 Para os experimentos descritos na Seção ~\ref{sec:eval}, utilizou-se constantes
@@
 Expansão de tarefas consiste em encontrar a menor tarefa que é grande o suficiente
-para compensar o custo de criação de {\em threads}. A figura \ref{fig:expand_alg}
-mostra o algoritmo de expansão. Inicia-se o algoritmo atribuindo \textsf{REGIÃO} a
-um grafo hammock $H$ que corresponde a uma hélice em um moinho $W$.
-A decomposição hammock de um programa estruturado é uma árvore~\cite{Ferrante87},
-em que os vértices representam grafos hammock.
+para compensar o custo de criação de {\em threads}. A Figura \ref{fig:expand_alg}
+mostra o algoritmo de expansão. Inicia-se o algoritmo atribuindo \textsf{REGIÃO\_PAI} a
+um grafo {\em hammock} $H$ que corresponde a uma hélice em um moinho $W$.
+A decomposição {\em hammock} de um programa estruturado é uma árvore~\cite{Ferrante87},
+em que os vértices representam grafos {\em hammock}.
 $H_1$ é filho de $H_2$ na árvore se:
@@
 \includegraphics[width=1\columnwidth]{images/expand_alg}
-\caption{Descoberta de tarefas em regiões hammock.
+\caption{Descoberta de tarefas em regiões {\em hammock}.
 \textsf{CUSTO} é o custo de criação e escalonamento de {\em threads}.}
@@
 \textbf{Árvore de escopos:}
-A árvore de escopos é uma estrutura utilizada pelo {\Taskminer} para mapear regiões hammock em construtos C, como blocos
-\textsf{while} e \textsf{if-then-else}. Cada nó nesta árvore contém {\em meta-dados}
+A árvore de escopos é uma estrutura utilizada pelo {\Taskminer} para mapear regiões {\em hammock} em construtos C, como blocos
+\textsf{while} e \textsf{if-then-else}. Cada nó nesta árvore contém {\em metadados}
 provenientes de informação de depuração obtida durante a compilação para R.I.
 É possível achar o número da linha relacionada à cada nó na árvore de escopos, permitindo
-ao {\Taskminer} a anotação das regiões hammock no código fonte de maneira precisa.
+ao {\Taskminer} a anotação das regiões {\em hammock} no código fonte de maneira precisa.
 
@@
 Para evitar a criação excessiva de tarefas pequenas, {\Taskminer} dá a opção
-aos usuários de limitar a criação de tarefas. Por exemplo \textsf{./Taskminer -r 12} limita o número
+aos usuários de limitar a criação de tarefas. Por exemplo, \textsf{./Taskminer -r 12} limita o número
 de tarefas criadas a um total de 12 tarefas. Essa solução é implementada na fase de anotação. 
-Essa solução traz claros benefícios em benchmarks recursivos. 
+Essa solução traz claros benefícios em benchmarks recursivos, como mostra-se na Seção \ref{sec:eval}. 
 A variável, chamada de \textsf{taskminer\_depht\_cutoff} na Figura
 \ref{fig:ex_cutoff}, é global e ligada estaticamente. 
-No começo de cada função recursiva,
-esta variável é incrementada para indicar a criação de uma nova tarefa; 
+No começo de cada função recursiva
+esta variável é incrementada para indicar a criação de uma nova tarefa, 
 e decrementada ao sair da função.
@@
 A maioria são algoritmos Dividir \& Conquistar clássicos como multiplicação de matrizes de \textsf{Strassen},
- \textsf{knapsack} (Problema da Mochila) e \textsf{fft}. Em 6 deles, as versões automáticas foram próximas e até
-levemente acima das versões anotadas manualmente. Em 3, \Taskminer{} produziu versões piores que
+ \textsf{knapsack} (Problema da Mochila) e \textsf{fft} (Transformada Rápida de Fourrier). Em 6 deles, as versões automáticas foram próximas e até
+levemente superiores às versões anotadas manualmente. Em 3, \Taskminer{} produziu versões piores que
 as versões sequenciais: \textsf{fib}, \textsf{floorplan} e \textsf{bell-ford}. Ainda assim, produziu versões
@@
 otimizar a criação de tarefas descritas neste artigo são baseadas na ideia de 
-``poda": evita-se a criação de tarefas consideradas não-lucrativas. 
+{\em poda}: evita-se a criação de tarefas consideradas não-lucrativas. 
 Limita-se a criação de tarefas ditas não lucrativas de acordo com o modelo de custo, 
@@
 Em 17 deles, observou-se perda de velocidade: neste caso, interações entre estruturas de dados
-forçaram ao ambiente de execução do OpenMP a serizalizar a execução das tarefas. 
+forçaram o ambiente de execução do OpenMP a serializar a execução das tarefas. 
 Essas perdas foram 
@@
 Obteve-se aumento de desempenho acima de 5\% em 19 programas. 
-Em \textsf{Misc/lowercase}, o fator de crescimento foi acima de 3.5x, e em 3 casos, acima de 1.5x.
+Em \textsf{Misc/lowercase}, o fator de crescimento foi acima de 3,5x, e em 3 casos, acima de 1.5x.
 A Figura~\ref{fig:TM_GeneralProgs} mostra os 10 maiores acréscimos de desempenho obtidos pelo \Taskminer{}.
@@
 além do {\Taskminer} capazes de anotar programas
-automaticamente com diretivas. Exemplos
+automaticamente com diretivas de tarefas. Exemplos
 de modelos que permitem paralelismo de tarefas são OpenMP 4.X,
@@
 A técnica utilizada pelo {\Taskminer} para identificação de tarefas se assemelha às análises usadas durante
-geração de código para máquinas de fluxo de dados. Muitas abordagens utilizaram grafos
+geração de código para máquinas de fluxo de dados. Muitas abordagens utilizam grafos
 de fluxo de dados para explorar paralelismo, como Tarefas Movidas à Dados \cite{tasirlar:icpp:2011},
 em que o programador pode manipular cláusulas para determinar os argumentos da tarefa
-antes de sua execução. Paralelismo baseado em função também foi proposto em \cite{gupta:micro:2011}
-para utilizar argumentos de funções como especificadores de dependências entre tarefas.
+antes de sua execução. Paralelismo baseado em função também foi proposto
+para utilizar argumentos de funções como especificadores de dependências entre tarefas \cite{gupta:micro:2011}.
 
@@
 em nenhum desses trabalhos, e \Taskminer{} segue como primeira ferramenta capaz 
-de anotar código como paralelo
-automaticamente de maneira correta.
+de anotar automaticamente código com paralelismo irregular
+de maneira correta.
 
@@
 \Taskminer{} implementa algoritmos de análise de código em representação intermediária do LLVM e contorna problemas clássicos no paralelismo irregular.
-Apesar das dificuldades, \Taskminer{} prova-se eficiente e competitivo, sendo capaz de anotar programas não triviais e encontrar paralelismo escondido sem custo adicional.
+\Taskminer{} prova-se eficiente e competitivo, sendo capaz de anotar programas não triviais e encontrar paralelismo escondido sem custo adicional.
 

### 2018-07-14 docs/ACM/paper.tex
Adding latest changes.
Adding new figures with examples.

@@
 %% For double-blind review submission
-\documentclass[sigplan,10pt,review,anonymous]{acmart}
+\documentclass[sigplan,10pt,review]{acmart}
 \settopmatter{printfolios=true}
@@
 %% Supplied to authors by publisher for camera-ready submission
-\acmConference[PL'17]{IEEE}{2018}{Planet Earh}
+\acmConference[PACT]{ACM}{2018}{Limassol, Cyprus}
 \acmYear{2017}
@@
 
-\title[Automatic Identification and Annotation of Tasks in Structured
-Programs]
-{Automatic Identification and Annotation of Tasks in Structured Programs}
-
-\author{Pedro Henrique Ramos Costa}
-\authornote{with author1 note}          %% \authornote is optional;
+\title[Automatic Annotation of Tasks in Structured
+Code]
+{Automatic Annotation of Tasks in Structured Code}
+
+\author{Pedro Ramos, Gleison Souza}
 \orcid{nnnn-nnnn-nnnn-nnnn}
 \affiliation{
-  \position{Researcher}
-  \department{DCC}
-  \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
+%  \position{Researcher}
+%  \department{DCC}
+  \institution{UFMG, Brazil}
+%  \streetaddress{6627 Antonio Carlos Avenue}
+%  \city{Belo Horizonte}
+%  \state{Minas Gerais}
+%  \postcode{31.270-213}
+%  \country{Brazil}
 }
 \email{pedroramos@dcc.ufmg.br}
-
-\author{Gleison Souza Diniz Mendonc\c{c}a}
-\authornote{with author1 note}          %% \authornote is optional;
-\orcid{nnnn-nnnn-nnnn-nnnn}
+\email{gleison.mendonca@dcc.ufmg.br}
+
+%\author{Gleison Souza Diniz Mendonc\c{c}a}
+%\authornote{with author1 note}          %% \authornote is optional;
+%\orcid{nnnn-nnnn-nnnn-nnnn}
+%\affiliation{
+%  \position{Researcher}
+%  \department{DCC}
+%  \institution{UFMG}
+%  \streetaddress{6627 Antonio Carlos Avenue}
+%  \city{Belo Horizonte}
+%  \state{Minas Gerais}
+%  \postcode{31.270-213}
+%  \country{Brazil}
+%}
+%\email{gleison.mendonca@dcc.ufmg.br}
+
+\author{Divino C\'{e}sar, Guido Ara\'{u}jo}
+%\authornote{with author1 note}
+%\orcid{nnnn-nnnn-nnnn-nnnn}
 \affiliation{
-  \position{Researcher}
-  \department{DCC}
-  \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
-}
-\email{gleison.mendonca@dcc.ufmg.br}
-
-\author{Divino C\'{e}sar}
-\authornote{with author1 note}
-\orcid{nnnn-nnnn-nnnn-nnnn}
-\affiliation{
-  \position{Researcher}
-  \department{IC}
-  \institution{UNICAMP}
-  \streetaddress{Cidade Universit\'{a}ria}
-  \city{Campinas}
-  \state{S\~{a}o Paulo}
-  \postcode{13083-970}
-  \country{Brazil}
+%  \position{Researcher}
+%  \department{IC}
+  \institution{UNICAMP, Brazil}
+%  \streetaddress{Cidade Universit\'{a}ria}
+%  \city{Campinas}
+%  \state{S\~{a}o Paulo}
+%  \postcode{13083-970}
+%  \country{Brazil}
 }
 \email{divcesar@gmail.com}
-
-\author{Guido Ara\'{u}jo}
-\authornote{with author1 note}
-\orcid{nnnn-nnnn-nnnn-nnnn}
+\email{guido@ic.unicamp.br}
+
+%\author{Guido Ara\'{u}jo}
+%\authornote{with author1 note}
+%\orcid{nnnn-nnnn-nnnn-nnnn}
+%\affiliation{
+%  \position{Professor}
+%  \department{IC}
+%  \institution{UNICAMP}
+%  \streetaddress{Cidade Universit\'{a}ria}
+%  \city{Campinas}
+%  \state{S\~{a}o Paulo}
+%  \postcode{13083-970}
+%  \country{Brazil}
+%}
+%\email{guido@ic.unicamp.br}
+
+\author{Fernando Magno Quint\~{a}o Pereira}
+\authornote{This work is sponsored by CNPq, CAPEs, FAPEMIG, FAPESP, LG Electronics and
+the CONTINUUM ANR Project.}          %% \authornote is optional;
+%\orcid{nnnn-nnnn-nnnn-nnnn}
 \affiliation{
-  \position{Professor}
-  \department{IC}
-  \institution{UNICAMP}
-  \streetaddress{Cidade Universit\'{a}ria}
-  \city{Campinas}
-  \state{S\~{a}o Paulo}
-  \postcode{13083-970}
-  \country{Brazil}
-}
-\email{guido@ic.unicamp.br}
-
-\author{Fernando Magno Quint\~{a}o Pereira}
-\authornote{with author1 note}
-\orcid{nnnn-nnnn-nnnn-nnnn}
-\affiliation{
-  \position{Professor}
-  \department{DCC}
-  \institution{UFMG}
-  \streetaddress{6627 Antonio Carlos Avenue}
-  \city{Belo Horizonte}
-  \state{Minas Gerais}
-  \postcode{31.270-213}
-  \country{Brazil}
+%  \position{Professor}
+%  \department{DCC}
+  \institution{UFMG, Brazil}
+%  \streetaddress{6627 Antonio Carlos Avenue}
+%  \city{Belo Horizonte}
+%  \state{Minas Gerais}
+%  \postcode{31.270-213}
+%  \country{Brazil}
 }
@@
 OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
-OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
+OpenSs~\cite{MeenderinckJ11} and
 OmpSs~\cite{bueno:icpp:2011, duran:ppl:2011}.
-Annotations work as a meta-language: they let developers grant parallel
+Annotations let developers grant parallel
 semantics to syntax originally written to execute sequentially.
 %\guido{What do you mean by modern accelerators? Not clear.}
-Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
+Combined with hardware accelerators such as GPUs and FPGAs, they have led
 to substantial performance gains~\cite{Bertolli14,Mendonca17,Poesia17}.
 %\guido{Suppport what?}
-Nevertheless, although convenient, the use of annotations is not straightforward, 
-and still lacks supporting tools that help programmers to check if annotations
+Nevertheless, although convenient, the use of annotations is not straightforward.
+We still lack tools that help programmers to check if annotations
 are correct and/or effective.
@@
 the same computation independently on different data.
-Another form of parallelism, based on tasks, remains still uncharted land in what
+Task parallelism remains still uncharted land in what
 concerns automatic annotation.
@@
 
-The main advantage of using OpenMP annotations to split a program into parallel
-tasks is
-the ability  of leaving the job of  handling dependences to a runtime.
-The OpenMP runtime maintains a task dependence graph which dynamically exposes more parallelism 
+OpenMP task annotations let developers leave to the runtime the job of handling data
+dependences.
+The OpenMP runtime maintains a dependence graph which dynamically exposes more parallelism 
 opportunities than those resulting from a conservative  compile-time  analysis.
@@
 the invocation of recursive functions annotated with task pragmas with a
-counter -- \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:ex_cutoff}.
+counter -- \textsf{cutoff} in Figure~\ref{fig:ex_cutoff}.
 The guard in line 7 ensures that we never exceed \textsf{DEPTH\_CUTOFF}, a
@@
 program.
-This variable is \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:ex_cutoff}.
+This variable is \textsf{cutoff} in Figure~\ref{fig:ex_cutoff}.
 We insert code to increment it at the beginning of recursive functions that
@@
 annotated) versions.
-Baseline and annotated sources are compiled with gcc-6.
+Baseline and annotated sources are compiled with gcc-6 -O3.
 

### 2018-07-14 docs/ACM/paper.tex
Adding references.

@@
 Neither the runtime checks of Alves~\cite{Alves15} or Rus~\cite{Rus02}, nor
-Whaley's context and flow sensitive alias analysis would be able to ensure the
+Whaley's context and flow sensitive alias analysis~\cite{Whaley04} would be able to ensure the
 correctness of the automatic parallelization of this program.}
@@
 $T_1$.
-If a program $P$ is partitioned into a set of $n$ tasks, then this partition is
-said to be {\em correct} if it abides by Definition~\ref{def:correctness}.
-
-\begin{definition}[Correctness]
-\label{def:correctness}
-A set $T$ of $n$ tasks is a correct parallelization of a program $P$ if:
-\begin{compactenum}
-\item $T$ does not contain cyclic dependence relations;
-\item the execution of the tasks in $T$ in any ordering determined by dependence
+If a program $P$ is partitioned into a set $T$ of $n$ tasks, then this partition is
+said to be {\em correct} if:
+(i) $T$ does not contain cyclic dependence relations; and
+(ii) the execution of the tasks in $T$ in any ordering determined by dependence
 relations leads to the same results as the sequential execution of $P$.
-\end{compactenum}
-\end{definition}
 
@@
 \begin{compactitem}
-\item \textsf{default([shared/private])}: indicates that variables are either
-shared or replicated among tasks.
+\item \textsf{default(shared)}: indicates that variables are
+shared by default among tasks.
 \item \textsf{firstprivate($v$)}: indicates that $v$ must be replicated among
@@
 within a task region; thus, effectively setting dependences among tasks.
-\item \textsf{if}({\em condition}): this clause defines the conditions
-under which a task is allowed to create threads.
+\item \textsf{if}({\em condition}): this clause leads to the creation of an {\em undeferred}
+task, which must be executed immediately.
 We use it to enforce the cost model.
+\item \textsf{final}({\em condition}) \textsf{mergeable}: this clause limits the creation of
+tasks, and reuses the data environment of the father task.
+We use it prune tasks considered too small, as discussed in Section~\ref{sub:ir}.
 \end{compactitem}
@@
 15Gb of main memory.
-We use OpenMP 4.5, from November of 2015.
+We use OpenMP 4.0, from November of 2015.
 
@@
 Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, and TEMANEJO
-\cite{brinkmann:parco:2011, brinkmann:journal:2013, temanejo} were  designed to
+\cite{Brinkmann13} were  designed to
 enable performance analysis and visualization of task-based programs.

### 2018-07-25 docs/SBLP/paper.tex
SBLP Cameraready

@@
 %% For double-blind review submission
-\documentclass[sigplan,10pt]{acmart}
+%\documentclass[sigplan,10pt]{acmart}
+\documentclass[sigconf]{acmart}
 \settopmatter{printfolios=true}
@@
 \acmYear{2018}
-\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
+\acmISBN{978-1-4503-6480-5/18/09}
 \acmDOI{10.1145/nnnnnnn.nnnnnnn}
@@
 estáticas espúrias, detecção de condições de corrida, e, principalmente, a avaliação do custo do paralelismo. Para solucioná-los,
-\Taskminer{} implementa uma série de otimizações em representa\-ção intermediária do LLVM, que analisam código C e inserem anotações OpenMP automaticamente.
+\Taskminer{} implementa uma série de otimizações em representa\-ção intermedi-ária do LLVM, que analisam código C e inserem anotações OpenMP automaticamente.
 \Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente.
@@
 
+\Taskminer{} está online e disponível para uso acadêmico em \url{http://cuda.dcc.ufmg.br/taskminer/}.
+
 \section{Visão geral}
@@
 
-A construção de um compilador como o \Taskminer{} envolve a superação de uma série  de desafios.
+A construção de um compilador como o \Taskminer{} envolve a supera-ção de uma série  de desafios.
 \Taskminer{} recebe como entrada um programa escrito em C e retorna o mesmo programa anotado com 
@@
 rastrear dependências entre ponteiros~\cite{LaGrone11}. Entretanto, a inserção
-automática das anotações é apenas a última etapa. Nesta Seção detalha-se os problemas
+automática das anotações é apenas a última etapa. Nesta Seção detalham-se os problemas
 encontrados pelo \Taskminer{} no percalço de mineração de tarefas. A solução para esses problemas é descrita na Seção~\ref{sec:sol}.
@@
 deve-se aproximar esse tamanho
-estaticamente. Assim, define-se a noção de {\em Trabalho Estatico Estimado}:
+estaticamente. Assim, define-se a noção de {\em Trabalho Estático Estimado}:
 
@@
 descrita na Seção \ref{sec:sra} para inserir informações dinâmicas estaticamente
-através da construção de expressões simbólicas que representam o número de iterações
+através da construção de expressões simbó-licas que representam o número de iterações
 de laços. Essas expressões são inseridas em condicionais para a criação da
@@
 (ii) as regiões de memória em \textsf{HÉLICE} podem ser analisadas de acordo com
-a seção \ref{sub:sra};
+a Seção \ref{sec:sra};
 (iii) \textsf{HÉLICE} não depende de uma outra hélice no mesmo moinho $W$.
@@
 
-As análises deste artigo foram implementadas na representação intermediária (R.I.)
+As análises deste artigo foram implementadas na representa\c{c}\~{a}o intermediária (R.I.)
 do LLVM devido à facilidade do uso de análises como evolução escalar~\cite[p.18]{Grosser12} e outras.
@@
 \caption{Comparações de performance. Anotações automáticas comparam-se favoralmente a intervenções
-manuais, e levam à ganhos de desempenho. No eixo y, ganho de desempenho de cada versão anotada
-pelo {\Taskminer} sobre a versão anotada manualmente. Os números nas caixas representam
+manuais, e levam a ganhos de desempenho. No eixo y, o ganho de desempenho de cada versão anotada
+pelo {\Taskminer} e de cada versão anotada manualmente. Os números nas caixas representam
 o crescimento em velocidade obtido.}
@@
 e do \textsf{Swan}~\cite{Moreira17}.
-Ambos vem com versões sequenciais e paralelas (anotadas manualmente). Os códigos foram compilados
+Ambos vêm com versões sequenciais e paralelas (anotadas manualmente). Os códigos foram compilados
 com gcc-6.
@@
 ganhos consideráveis se comparados às versões sequenciais e manualmente anotadas.
+
+Além disso, destaca-se o fato de que as anotações do \Taskminer{} levaram resultados próximos às anotações manuais.
+Dessa forma, \Taskminer{} retira do programador o fardo de inserir as anotações manualmente.
 
@@
 inferiores à 10\%.
+Porém, nota-se uma necessidade de desenvolver-se um modelo de custo mais robusto para evitar a geração de programas paralelos que sejam mais lentos que os originais sequenciais.
+Como trabalho futuro, pretende-se estudar melhores heurísticas para a estimativa do custo de uma tarefa, a fim de diminuir esse tipo de resultado.
+Observa-se que os programas que resultaram em perda de velocidade possuiam tarefas muito pequenas e irrelevantes proporcionalmente em relação ao resto do programa.
+É necessário um modelo de custo que considere também o tamanho do programa em relação às poções sequenciais e seus impactos no mesmo.
 
@@
 %SCALABILITY
-
 \section{Trabalhos Relacionados}
@@
 Compiladores modernos adicionaram suporte ao paralelismo de tarefas 
-do OpenMP apenas recentemente. 
+do OpenMP apenas recentemente. Uma implementação do \textsf{clang} com suporte a Tasks foi lançada em Março, 2014. Tal suporte foi integrado ao \textsf{gcc} em Abril do mesmo ano.
 Uma vez que a infra-estrutura necessária para
-a implementação de tarefas é nova, não existem ferramentas 
+a implementação de tarefas é nova, não existem ferramentas estáticas
 além do {\Taskminer} capazes de anotar programas
-automaticamente com diretivas de tarefas. Exemplos
-de modelos que permitem paralelismo de tarefas são OpenMP 4.X,
-StarSs \cite{planas:hpca:2009} e OmpSs \cite{duran:ppl:2011}.
-Por exemplo, Tareador \cite{Ayguade15} apresenta uma interface gráfica para identificação de potencial paralelismo e anotação de código sequencial.
+automaticamente com diretivas de tarefas. Entretanto, existe muita pesquisa em paralelização automática de código.
 
-A técnica utilizada pelo {\Taskminer} para identificação de tarefas se assemelha às análises usadas durante
-geração de código para máquinas de fluxo de dados. Muitas abordagens utilizam grafos
-de fluxo de dados para explorar paralelismo, como Tarefas Movidas à Dados \cite{tasirlar:icpp:2011},
-em que o programador pode manipular cláusulas para determinar os argumentos da tarefa
-antes de sua execução. Paralelismo baseado em função também foi proposto
-para utilizar argumentos de funções como especificadores de dependências entre tarefas \cite{gupta:micro:2011}.
+Padrões de anotação de código baseados em diretivas provêm, ao programador, um modelo de programação paralela fácil de se utilizar.
+Extensões destes padrões baseadas em tarefas resultaram em  OpenMP 4.X,
+StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
+tejedor:hpdc:2011} e OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}.
+Tais modelos vem com ferramentas que ajudam os programadores a achar as melhores anotações para seus códigos.
+Por exemplo, Tareador \cite{Ayguade15} permite ao programador, através de uma interface gráfica, a anotar código sequencial, permitindo assim a identificação de potenciais oportunidades de tarefas.
+Ao contrário do Tareador, este trabalho propõe uma abordagem que permite a inserção automática de anotações OpenMP em fragmentos relevantes de um programa sequencial.
 
-Muitos sistemas foram desenvolvidos para extrair paralelismo de tarefas a partir de código sequencial.
-Entretanto, a mineração e inserção automática dessas diretivas não consta como objetivo
-em nenhum desses trabalhos, e \Taskminer{} segue como primeira ferramenta capaz 
-de anotar automaticamente código com paralelismo irregular
-de maneira correta.
+As técnicas utilizadas neste trabalho para mapear regiões de programas em tarefas é similar às análises muito utilizadas em geração de código para máquinas de fluxo de dados.
+Programação de fluxo de dados foi originalmente proposto como um paradigma adequado ao paralelismo de tarefas \cite{agrawal:ipdps:2010, chan:spaa:2007,
+gupta:micro:2011}.
+Este paradigma foi extendido com especificações para entrada e saída de tarefas em Cilk++ \cite{agrawal:ipdps:2010}, e mais tarde Cilk++ foi extendido com cláusulas dependência para facilitar a projeção de padrões de paralelização \cite{vandierendonck:hotpar:2011}.
+O modelo até então apresentava um escalonador unificado baseado em paralelismo fork-join que permitia a execução de aplicações baseadas em tarefas.
+Outras abordagens também utilizaram grafos de fluxo de dados para explorar paralelismo, como tarefas de dados, nas quais o programador pode utilizar cláusulas de \textit{put} e \textit{await} para determinar os argumento de uma tarefa antes de sua execução.
+Paralelismo de tarefas baseado em argumentos de funções também foi proposto para determinação de dependências entre tarefas \cite{gupta:micro:2011}.
+Nota-se que os esforços listados focam-se em conceder ao programador as ferramentas para construir programas paralelos.
+A geração automática de programas paralelos simples não estava entre seus objetivos.
+
+Muitos sistemas foram desenvolvidos para extrais paralelismo de tarefas a partir de programas sequenciais de maneira semi-automática.
+Exemplos incluem OSCAR (Optimally SCheduled Advanced multprocessoR), um compilador-paralelizador \cite{ishizaka:journal:2000}, MAPS (MPSoC Application Programming Studio) \cite{castrillon:tii:2013} e DiscoPoP (Discovery of Potential Parallelism) \cite{li:jss:2016}.
+Além de sistemas de paralelização, ferramentas como Paraver  \cite{paraver}, Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, e TEMANEJO
+\cite{temanejo} foram projetadas para permitir análise de performance e visualização de programas em tarefas.
+
+Apesar dessas ferramentas ajudarem o programador a adaptar código para rodar em paralelo, elas não são completamente automáticas.
+Por exemplo, o trabalho que é mais próximo ao descrito neste artigo é o conjunto de análises estáticas propostas por Ravishankar {\em et al.} \cite{Ravishankar14}.
+O tipo de laços irregulares com os quais eles lidam é impressionante; porém, a falta de suporte a OpenMP 4.X ainda requer ao programador modificar código antes da paralelização.
+Nas palavras dos autores, ``{\em para todos os benchmarks e aplicações, todas as funções foram alinhadas, e arranjos de estruturas foram convertidos a estruturas de arranjos para uso em conjunto com o nosso protótipo}", de forma que o sistema modifica o código original para atingir tal paralelismo.
+\Taskminer{}, por outro lado, não modifica a sintaxe sequencial original.
+
+Em outro contexto, ferramentas foram desenvolvidas para inser-ção de anotações automáticas que expõe paralelismo de dados \cite{Wang2009}.
+Essas ferramentas, porém, além de explorarem outro tipo de paralelismo, não são completamente estáticas como o \Taskminer{}.
 
@@
 Como trabalho futuro, pretende-se implementar heurísticas de estimativa de custo que sejam mais precisas, para refinar o algoritmo do \Taskminer{}.
+Embora ainda sob constantes atualizações, uma versão inicial do
+\Taskminer{} está online e disponível para uso acadêmico em \url{http://cuda.dcc.ufmg.br/taskminer/}.
 

### 2018-07-25 docs/ACM/paper.tex

@@
 The OpenMP execution environment ensures the correct scheduling of the tasks
-created at lines 9 and 11, by reassuring that the annotated dependencies
+created at lines 10 and 12, by reassuring that the annotated dependencies
 {\tt line} and {\tt pattern}
@@
 The two previous challenges are related to the performance of annotated
-programs: if left unsolved, we shall have correct, albeit inefficient programs.
+code: if left unsolved, we shall have correct, albeit inefficient programs.
 Challenges~\ref{ch:Regions}, and~\ref{ch:privatize}, in turn, are
@@
 In the absence of such action, that variable will be shared among all the
-tasks created at line 5 of Figure~\ref{fig:ex_privatize}.
+tasks created at line 8 of Figure~\ref{fig:ex_privatize}.
 Because \textsf{j} is written to within these tasks, race conditions would
@@
 ``Summary of OpenMP 4.0 C/C++ Syntax", which is made available by the OpenMP
-group.}; hence, we shall not dive into their details.
+ARB.}; hence, we shall not dive into their details.
 %
@@
 $l$ and $u$ are {\em Symbolic Expressions}.
-A symbolic expression $E$ is defined by the grammar below, where $s$ is a
-{\em program symbol}:
-\renewcommand{\arraystretch}{0.9}
-\[
-\begin{array}{rcl}
-E & ::= & z \ \ | \ \ s \ \ | E + E \ \ | \ \ E \times E \ \ | \ \  \mbox{min}(E, E) \ \ | \\
-&  & \mbox{max}(E, E) \ \ | -\infty \ \ | \ \ +\infty
-\end{array}
-\]
+A symbolic expression $E$ is recursively defined as one of the terms:
+$s, c, E + E, E \times E, \mbox{min}(E, E), \mbox{max}(E, E),$
+$-\infty, +\infty$, where $s$ is a {\em program symbol}, and $c \in \mathbb{Z}$.
 \end{definition}
 
-% How we do it.
-The program symbols mentioned in Definition~\ref{def:sra} are names that cannot 
-be reconstructed as functions of other names.
+The program symbols mentioned in Definition~\ref{def:sra} are names that cannot  be
+reconstructed as functions of other names.
 Examples include global variables, function arguments, and values returned by
@@
 We have adopted the one in the \dawn{} compiler~\cite{Mendonca17}, which, itself,
-reuses work from Blume {\em et al.}~\cite{Blume94}.
+reuses an implementation by Nazar\'{e} {\em et al.}~\cite{Nazare14}.
 The only extensions that we have added into \dawn 's implementation was
@@
 To understand the rest of this paper, it suffices to know that this implementation
-is sufficiently solid to handle the entire C99 language, always terminates, and
-runs in time linear on the size of the program's dependence graph.
+is sufficiently solid to handle the entire C99 language, always terminates and runs in time 
+linear on the size of the program's dependence graph.
+Our implementation of Symbolic Range Analysis is interprocedural, to handle recursive 
+functions, for instance.
 Thus, in the worst case, it is quadratic on the number of program variables.
@@
 
-\begin{definition}[Program Dependence Graph -- \cite{Ferrante87}]
+\begin{definition}[Program Dependence Graph (PDG)~\cite{Ferrante87}]
 \label{def:pdg}
-Given a program $P$, its PDG contains one vertex for each statement $s \in P$.
+The PDG of a program $P$ contains one vertex for each statement $s \in P$.
 There exists an edge from $s_1$ to $s_2$ if the latter depends on the former.
@@
 writes.
-It is {\em control dependent} on $s_1$ if $s_1$ determines the outcome of a
-branch, and depending on this outcome, we might execute $s_2$ or not.
+It is {\em control dependent} on $s_1$ if $s_1$ controls a branch, whose result determines
+if $s_2$ executes.
 \end{definition}
@@
 {\em Windmills} are a family of graphs.
-To the best of our knowledge, the term was coined by Rideau
+The term was adopted by Rideau
 {\em et al.}~\cite{Rideau08} to describe structural relations between register
@@
 Our windmills exist as subgraphs of the program's dependence graph.
-We adopt a slightly more general definition than Rideaus'; however, the
+We use a slightly more general definition than Rideaus'; however, the
 metaphor that gave origin to the name: the shape of the graphs, is still
@@
 these two hypothetical replicas of the same structure.
+Tasks can then be synchronized at the post-dominator of vanes marked to run in parallel
+via the \textsf{taskwait} pragma.
 
@@
 We have an edge from node $s_1$ to node $s_2$ if region $s_2$ is nested
-within region $s_2$.
+within region $s_1$.
 In the absence of control-flow optimizations such as loop unrolling or
@@
 Pragmas for the conditional creation of tasks, such as the one seen in
-lines 7 and 10 of Figure~\ref{fig:ex_cutoff}, lets us obtain much of the benefit
+lines 8 and 11 of Figure~\ref{fig:ex_cutoff}, lets us obtain much of the benefit
 of code versioning, as proposed by Iwasaki and Taura.
@@
 The Y-axis shows the speedup of either manual intervention or the \Taskminer{}
-(this paper) upon the original programs, in number of times.
-Small numbers in boxes show speedup achieved by \Taskminer.}
+(this paper) compared to the original programs, in number of times.
+Small numbers in boxes show speedup achieved by \Taskminer.
+The higher this number, the better.}
 \label{fig:TM_Performance}
@@
 and \textsf{fft}.
-In 6 of them, the automatically annotated programs were close and sometimes even 
-slightly above the manually annotated versions.
+In 6 cases, automatically annotated programs were close or slightly faster than the manually
+annotated versions.
 In three examples where \Taskminer{} fell behind the original samples, e.g.,
@@
 it produced code faster than the manually annotated competitor.
-Visual inspection of \textsf{bellmanford} shows that the version parallelized
-manually is dispatching a large number of small tasks.
-Our cost model can prune some of these small tasks, but not enough to win
-on the sequential version.
+The version of \textsf{bellmanford} produced by \Taskminer{} is slower than its sequential
+baseline.
+The slowdown is not due to the cost model.
+This algorithm traverses a graph implemented as an array of arrays, and data dependences
+cause serialization at runtime.
+%Visual inspection of \textsf{bellmanford} shows that the version parallelized
+%manually is dispatching a large number of small tasks.
+%Our cost model can prune some of these small tasks, but not enough to win
+%on the sequential version.
 We emphasize that the human-annotated versions of our benchmarks have not
@@
 with 128 processors~\cite{Duran09}.
-Thus, this difference in hardware might be accountable for the slowdown in
+Thus, hardware differences might be accountable for the slowdown in
 some of the manually annotated samples.

### 2018-07-26 docs/ACM/paper.tex
Adding URL of page.

@@
 %% For double-blind review submission
-\documentclass[sigplan,10pt,review]{acmart}
+\documentclass[sigplan,10pt,screen]{acmart}
+%\documentclass[sigplan,10pt,review]{acmart}
 \settopmatter{printfolios=true}
@@
 
-\title[Automatic Annotation of Tasks in Structured
-Code]
+\title[Automatic Annotation of Tasks in Structured Code]
 {Automatic Annotation of Tasks in Structured Code}
@@
 
-\author{Divino C\'{e}sar, Guido Ara\'{u}jo}
+\author{Divino Soares, Guido Ara\'{u}jo}
 %\authornote{with author1 note}
@@
 %  \department{DCC}
-  \institution{UFMG, Brazil}
+  \institution{UFMG, Brazil \& LIRMM, France}
 %  \streetaddress{6627 Antonio Carlos Avenue}
@@
 \maketitle
+\renewcommand{\shortauthors}{Ramos, P., Souza, G., Soares, D., Ara\'{u}jo, G., Quint\~{a}o, F.}
 
@@
 The analyses described in Sections~\ref{sub:sra}-\ref{sub:variance} have
-been implemented at the level of the LLVM intermediate representation.
+been implemented at the level of the LLVM intermediate representation, and can be used
+through an online interface\footnote{\Taskminer{} can be
+used at \url{http://cuda.dcc.ufmg.br/taskminer/}}.
 We chose to implement those techniques at that level to benefit from the support
-of several data-flow analyses already in place in the LLVM infra-structure.
-In particular, this decision let us reuse LLVM's scalar
-evolution~\cite[p.18]{Grosser12}, from which we derive our symbolic analysis.
-Additionally, we could reuse LLVM's program dependence graph, and its suite of
-powerful alias analyses.
-This toolbox gave us the necessary means to disambiguate pointers, albeit
-conservatively, and estimate safe limits to memory regions.
-However, our annotations are still inserted in C programs.
-Having them in a high-level programming language has two main advantages:
-they are human-readable, and thus can be debugged, and they are compatible with
-compilers other than \textsf{clang}, such as \textsf{gcc}.
-Thus, a major part of this work was the engineering effort to map
-information from LLVM's intermediate representation back into C.
+of several data-flow analyses already in place in the LLVM infra-structure, such as
+scalar evolution and symbolic execution.
+%In particular, this decision let us reuse LLVM's scalar
+%evolution~\cite[p.18]{Grosser12}, from which we derive our symbolic analysis.
+%Additionally, we could reuse LLVM's program dependence graph, and its suite of
+%powerful alias analyses.
+This toolbox gave us the necessary means to disambiguate pointers
+and estimate safe limits to memory regions.
+Yet, our annotations are still inserted in C programs.
+Having them in a high-level programming language has two advantages:
+readability and portability across compilers.
+However, this modus operandi also brings two challenges.
+First, we cannot annotate partial code: to produce LLVM bitcodes, we need all the type
+definitions used in the target program.
+Second, we need to map information from LLVM's intermediate representation back into C.
+A type inference engine for C let us deal with the first
+challenge~\cite{Melo18}.
+In this section we explain how we deal with the second.
 
@@
 \textbf{Benchmarking:}
-we have used different benchmarks in our experiments.
+%we have used different benchmarks in our experiments.
 In Sections~\ref{sub:performance} and~\ref{sub:optimizations} we use
@@
 Runtimes are averages of five executions.
-No benchmark has been changed manually.
+%No benchmark has been changed manually.
 
@@
 \caption{Runtime of \Taskminer{} vs size of input programs.
-Each dot represents one of the 100 program generated by \textsf{CSmit}.
+%Each dot represents one of the 100 program generated by \textsf{CSmit}.
 We have fit a degree-2 polynomial on this dataset.
@@
 More specifically, a future release of \Taskminer{} is already expected to
-feature Iwasaki's cut-off~\cite{Iwasaki16B}.
+feature Iwasaki's cut-off~\cite{Iwasaki16B}. \\
+\textbf{Software} available at \url{http://cuda.dcc.ufmg.br/taskminer/}
 

### 2018-07-26 docs/SBLP/paper.tex

@@
 \acmArticle{1}
-\acmYear{2017}
+\acmYear{2018}
 \acmMonth{1}
@@
 %% Supplied to authors by publisher for camera-ready submission
-\acmConference[SBLP'18]{IEEE}{2018}{Brasil}
+\acmConference[SBLP'18]{XXII Brazilian Symposium on Programming Languages}{2018}{Brasil}
 \acmYear{2018}
@@
 <concept>
-<concept_id>10010147.10010169.10010175</concept_id>
-<concept_desc>Computing methodologies~Parallel programming languages</concept_desc>
+<concept_id>10010520.10010521.10010528</concept_id>
+<concept_desc>Computer systems organization~Parallel architectures</concept_desc>
 <concept_significance>500</concept_significance>
@@
 <concept>
-<concept_id>10010147.10011777.10011014</concept_id>
-<concept_desc>Computing methodologies~Concurrent programming languages</concept_desc>
-<concept_significance>500</concept_significance>
+<concept_id>10010520.10010521.10010528.10010536</concept_id>
+<concept_desc>Computer systems organization~Multicore architectures</concept_desc>
+<concept_significance>100</concept_significance>
 </concept>
@@
 </concept>
+<concept>
+<concept_id>10011007.10011006.10011041.10011047</concept_id>
+<concept_desc>Software and its engineering~Source code generation</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
 </ccs2012>
 \end{CCSXML}
+
+\ccsdesc[500]{Computer systems organization~Parallel architectures}
+\ccsdesc[500]{Software and its engineering~Compilers}
+\ccsdesc[300]{Software and its engineering~Source code generation}
 
@@
 
-Padrões de anotação de código baseados em diretivas provêm, ao programador, um modelo de programação paralela fácil de se utilizar.
+Padrões de anotação de código baseados em diretivas conferem ao programador um modelo de programação paralela fácil de se utilizar.
 Extensões destes padrões baseadas em tarefas resultaram em  OpenMP 4.X,
-StarSs \cite{bellens:sc:2006, perez:iccc:2008, planas:hpca:2009,
-tejedor:hpdc:2011} e OmpSs \cite{bueno:icpp:2011, duran:ppl:2011}.
+StarSs \cite{planas:hpca:2009,
+tejedor:hpdc:2011} e OmpSs \cite{bueno:icpp:2011}.
 Tais modelos vem com ferramentas que ajudam os programadores a achar as melhores anotações para seus códigos.
@@
 As técnicas utilizadas neste trabalho para mapear regiões de programas em tarefas é similar às análises muito utilizadas em geração de código para máquinas de fluxo de dados.
-Programação de fluxo de dados foi originalmente proposto como um paradigma adequado ao paralelismo de tarefas \cite{agrawal:ipdps:2010, chan:spaa:2007,
+Programação de fluxo de dados foi originalmente proposto como um paradigma adequado ao paralelismo de tarefas \cite{agrawal:ipdps:2010,
 gupta:micro:2011}.
-Este paradigma foi extendido com especificações para entrada e saída de tarefas em Cilk++ \cite{agrawal:ipdps:2010}, e mais tarde Cilk++ foi extendido com cláusulas dependência para facilitar a projeção de padrões de paralelização \cite{vandierendonck:hotpar:2011}.
-O modelo até então apresentava um escalonador unificado baseado em paralelismo fork-join que permitia a execução de aplicações baseadas em tarefas.
-Outras abordagens também utilizaram grafos de fluxo de dados para explorar paralelismo, como tarefas de dados, nas quais o programador pode utilizar cláusulas de \textit{put} e \textit{await} para determinar os argumento de uma tarefa antes de sua execução.
-Paralelismo de tarefas baseado em argumentos de funções também foi proposto para determinação de dependências entre tarefas \cite{gupta:micro:2011}.
+Este paradigma foi extendido com especificações para entrada e saída de tarefas em Cilk++ \cite{agrawal:ipdps:2010}, e mais tarde Cilk++ foi extendido com cláusulas de dependência para facilitar a projeção de padrões de paralelização \cite{vandierendonck:hotpar:2011}.
+O modelo, até então, apresentava um escalonador unificado baseado em paralelismo {\em fork-join} que permitia a execução de aplicações baseadas em tarefas.
+Outras abordagens também utilizaram grafos de fluxo de dados para explorar paralelismo, como tarefas de dados, nas quais o programador pode utilizar cláusulas de \textit{put} e \textit{await} para determinar os argumentos de uma tarefa antes de sua execução.
+Paralelismo de tarefas baseado em argumentos de funções também foi proposto para a determinação de dependências entre tarefas \cite{gupta:micro:2011}.
 Nota-se que os esforços listados focam-se em conceder ao programador as ferramentas para construir programas paralelos.
@@
 
-Muitos sistemas foram desenvolvidos para extrais paralelismo de tarefas a partir de programas sequenciais de maneira semi-automática.
+Muitos sistemas foram desenvolvidos para extrair paralelismo de tarefas a partir de programas sequenciais de maneira semi-automática.
 Exemplos incluem OSCAR (Optimally SCheduled Advanced multprocessoR), um compilador-paralelizador \cite{ishizaka:journal:2000}, MAPS (MPSoC Application Programming Studio) \cite{castrillon:tii:2013} e DiscoPoP (Discovery of Potential Parallelism) \cite{li:jss:2016}.
 Além de sistemas de paralelização, ferramentas como Paraver  \cite{paraver}, Aftermath~\cite{drebes:hipeac:2014}, DAGvis \cite{huynh:wvpa:2015}, e TEMANEJO
-\cite{temanejo} foram projetadas para permitir análise de performance e visualização de programas em tarefas.
+\cite{temanejo} foram projetadas para permitir análises de performance e visualização de programas em tarefas.
 
@@
 Por exemplo, o trabalho que é mais próximo ao descrito neste artigo é o conjunto de análises estáticas propostas por Ravishankar {\em et al.} \cite{Ravishankar14}.
-O tipo de laços irregulares com os quais eles lidam é impressionante; porém, a falta de suporte a OpenMP 4.X ainda requer ao programador modificar código antes da paralelização.
-Nas palavras dos autores, ``{\em para todos os benchmarks e aplicações, todas as funções foram alinhadas, e arranjos de estruturas foram convertidos a estruturas de arranjos para uso em conjunto com o nosso protótipo}", de forma que o sistema modifica o código original para atingir tal paralelismo.
-\Taskminer{}, por outro lado, não modifica a sintaxe sequencial original.
+O tipo de laços irregulares com os quais eles lidam é impressionante; porém, a falta de suporte a \textsf{OpenMP 4.X} ainda requer ao programador modificar código antes da paralelização.
+Nas palavras dos autores, ``{\em para todos os benchmarks e aplicações, todas as funções foram alinhadas, e arranjos de estruturas foram convertidos a estruturas de arranjos para uso em conjunto com o nosso protótipo}", de forma que o sistema modifica o código original para atingir o paralelismo desejado.
+\Taskminer{}, por outro lado, não modifica a sintaxe do programa sequencial original.
 
 Em outro contexto, ferramentas foram desenvolvidas para inser-ção de anotações automáticas que expõe paralelismo de dados \cite{Wang2009}.
-Essas ferramentas, porém, além de explorarem outro tipo de paralelismo, não são completamente estáticas como o \Taskminer{}.
+Essas ferramentas, porém, além de explorarem outro tipo de paralelismo, não são completamente estáticas e automáticas como o \Taskminer{}.
 

### 2018-08-06 docs/SBLP/paper.tex
SBLP published with DOI

@@
 %% Supplied to authors by publisher for camera-ready submission
-\acmConference[SBLP'18]{XXII Brazilian Symposium on Programming Languages}{2018}{Brasil}
+\copyrightyear{2018} 
 \acmYear{2018} 
+\setcopyright{othergov}
+\acmConference[SBLP 2018]{XXII Brazilian Symposium on Programming Languages}{September 20--21, 2018}{SAO CARLOS, Brazil}
+\acmPrice{15.00}
+\acmDOI{10.1145/3264637.3264639}
 \acmISBN{978-1-4503-6480-5/18/09}
-\acmDOI{10.1145/nnnnnnn.nnnnnnn}
+
 \startPage{1}
@@
 
-\title[TaskMiner: Identifica\c{c}\~{a}o Autom\'{a}tica de Tarefas]
-{TaskMiner: Identificação Automática de Tarefas}
+\title[TaskMiner: Automatic Identification of Tasks.]
+{TaskMiner: Automatic Identification of Tasks.}
 
-\author{Pedro Ramos, Gleison Souza, Guilherme Leobas, Fernando Magno Quint\~{a}o Pereira}
+\author{Pedro Ramos, Gleison Souza, Guilherme Leobas, Fernando Magno Q. Pereira}
 %\authornote{with author1 note}          %% \authornote is optional;
@@
 \begin{abstract}
-Este artigo apresenta \Taskminer{}, uma ferramenta que encontra paralelismo de tarefas
-em código C automaticamente. \Taskminer{} lida com problemas clássicos de paralelismo irregular 
-como a delimitação simbólica de regiões de memória, remoção de dependências
-estáticas espúrias, detecção de condições de corrida, e, principalmente, a avaliação do custo do paralelismo. Para solucioná-los,
-\Taskminer{} implementa uma série de otimizações em representa\-ção intermedi-ária do LLVM, que analisam código C e inserem anotações OpenMP automaticamente.
-\Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente.
-\Taskminer{} também é capaz de encontrar paralelismo escondido em programas sequenciais, sem intervenção humana.
+This paper presents \Taskminer{}, a tool that automatically finds task parallelism in C code.
+\Taskminer{} solves classic problems of irregular parallelism, such as finding the memory ranges accessed by tasks, removing spurious static dependencies, detecting data-racing conditions and, most importantly, assessing the cost of parallelism for a given task or program.
+\Taskminer{} implements a suite of optimizations in LLVM's intermediate representation, which in the end insert \textsf{OpenMP} annotations to the code automatically, exposing task parallelism.
+\Taskminer{} finds parallelism that was previously manually appointed in benchmarks such as \textsf{BSC-Bots}, producing programs that are as fast or even faster than their sequential and manually annotated counterparts.
+\Taskminer{} also finds hidden parallelism in sequential programs, without human intervention.
 \end{abstract}
@@
 
-\keywords{paralelismo, tarefas, OpenMP, compiladores}
+\keywords{parallelism, tasks, OpenMP}
 

### 2018-08-06 docs/ACM/paper.tex

@@
 \author{Fernando Magno Quint\~{a}o Pereira}
-\authornote{This work is sponsored by CNPq, CAPEs, FAPEMIG, FAPESP, LG Electronics and
-the CONTINUUM ANR Project.}          %% \authornote is optional;
+\authornote{This work is sponsored by CNPq, CAPEs, FAPEMIG, FAPESP, ANR and LG Electronics.
+While working on this project, Fernando was supported by a grant from the CONTINUUM ANR
+Project (ANR-15-CE25-0007-0).}          %% \authornote is optional;
 %\orcid{nnnn-nnnn-nnnn-nnnn}
@@
 %  \department{DCC}
-  \institution{UFMG, Brazil \& LIRMM, France}
+  \institution{UFMG, Brazil}
 %  \streetaddress{6627 Antonio Carlos Avenue}
@@
 Annotation systems have risen to a place of prominence as a simple and
-effective means to write parallel programs.
+effective way to write parallel programs.
 Examples of such systems include OpenMP~\cite{JaegerCP15},
@@
 or Emani's~\cite{Emani15} have already been shown to be effective in this
-domain, and we want to explore them further.
-More specifically, a future release of \Taskminer{} is already expected to
-feature Iwasaki's cut-off~\cite{Iwasaki16B}. \\
-\textbf{Software} available at \url{http://cuda.dcc.ufmg.br/taskminer/}
+domain, and we want to explore them further. \\
+
+\noindent
+\textbf{Software}:
+\Taskminer{} can be used directly through an online interface available at
+\url{http://cuda.dcc.ufmg.br/taskminer/}
 
